% Created 2024-03-04 Mon 21:26
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}
\author{Shane Mulligan}
\date{\textit{<2024-04-02 Tue>}}
\title{Thoughts on Faith and Judgement}
\hypersetup{
 pdfauthor={Shane Mulligan},
 pdftitle={Thoughts on Faith and Judgement},
 pdfkeywords={faith christianity},
 pdfsubject={},
 pdfcreator={Emacs 29.1.50 (Org mode 9.6.8)}, 
 pdflang={English}}
\begin{document}

\maketitle
This document is a work in progress. I am learning.

I agree whole heartedly with Keith Green here:
\begin{itemize}
\item \href{https://www.youtube.com/watch?v=z7oCa9BvO9g}{Keith Green 1978 : Make My Life A Prayer to You \{live\} - YouTube}
\end{itemize}

Almost all of verses are taken from the ESV
(English Standard Version) bible with the odd NASB
(New American Standard Bible), KJV (King
James Version), and BSB (Berean Study Bible) used here and there.

By default I will use the ESV and where it is
not from the ESV, I have almost certainly marked it with the alternative version used.

\textbf{Isaiah 30:20-21} - And \uline{though the Lord give you the bread of adversity and the water of affliction, yet your Teacher will not hide himself anymore}, but your eyes shall see your Teacher. And your ears shall hear a word behind you, saying, \textbf{This is the way, walk in it}, when you turn to the right or when you turn to the left.

I believe the above prophetically talks about Jesus. We must obey Jesus. God doesn't guarantee that following Jesus will be easy.

\textbf{John 6:44-46} - No one can come to me unless the Father who sent me draws him. And I will raise him up on the last day. It is written in the Prophets, And they will all be taught by God. Everyone who has heard and learned from the Father comes to me— not that anyone has seen the Father except he who is from God; he has seen the Father. (ESV)

\textbf{II John 1:6} - And this is love, that we walk according to his commandments; this is the \textbf{commandment}, just as you have heard from the beginning, so that you should \textbf{walk in it}. (ESV)

\textbf{II Peter 2:20-21} - For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first. For it would have been better for them never to have known \textbf{the way of righteousness} than after knowing it to turn back from the holy commandment delivered to them.

\textbf{Matthew 21:32} - For John came to you in the \uline{way of righteousness}, and you did not believe him, but the tax collectors and the prostitutes believed him. And even when you saw it, you did not afterward change your minds and believe him.

\textbf{John 14:6} - Jesus said to him, \uline{I am the way}, and the truth, and the life. No one comes to the Father except through me.

\section{Great commission}
\label{sec:orgdc92e3a}
\textbf{Luke 24:46-47} - and said to them, Thus it is written, that the Christ should suffer and on the third day rise from the dead, and that \textbf{repentance} (G3341 metanoia) and \textbf{forgiveness} (G859 aphesis) of sins should be proclaimed in his name to all nations, beginning from Jerusalem.

\textbf{Matthew 28:18-20} - And Jesus came up and spoke to them, saying, “All authority has been given to Me in heaven and on earth. Go therefore and make disciples of all the nations, baptizing them in the name of the Father and the Son and the Holy Spirit, teaching them to observe \textbf{all that I commanded you}; and lo, I am with you always, even to the end of the age.”

\textbf{Mark 16:15-18} - And he said to them, Go into all the world and proclaim the gospel to the whole creation. Whoever believes and is baptized will be saved, but whoever does not believe will be condemned. And these signs will accompany those who believe: in my name they will cast out demons; they will speak in new tongues; they will pick up serpents with their hands; and if they drink any deadly poison, it will not hurt them; they will lay their hands on the sick, and they will recover.

\textbf{John 21:15-17} - When they had finished breakfast, Jesus said to Simon Peter, Simon, son of John, do you love me more than these? He said to him, Yes, Lord; you know that I love you. He said to him, Feed my lambs. He said to him a second time, Simon, son of John, do you love me? He said to him, Yes, Lord; you know that I love you. He said to him, Tend my sheep. He said to him the third time, Simon, son of John, do you love me? Peter was grieved because he said to him the third time, Do you love me? and he said to him, Lord, you know everything; you know that I love you. Jesus said to him, Feed my sheep.

\textbf{2 Timothy 3:15} -  and how from childhood you have been acquainted with the sacred writings, which are able to make you wise for salvation through faith in Christ Jesus. (ESV)

\section{My thoughts and bible references regarding theology}
\label{sec:orgd0f36bb}
I've been thinking about belief, faith, works, law and receiving the Holy Spirit!
Please let me know what you think if you have the time.

I'm trying to get clearer on this.
Please feel free to discuss it with me.

\subsection{Jesus}
\label{sec:orgda90fd2}
Jesus is the Word incarnate. The world was made through Jesus:

\textbf{John 1:9-11} - The true light, which enlightens everyone, was coming into the world. He was in the world, and the world was made through him, yet the world did not know him. He came to his own, and his own people did not receive him. (ESV)

Jesus is the divinely appointed servant of God:

\textbf{Isaiah 53:4-6} - Surely he has borne our griefs and carried our sorrows; yet we esteemed him stricken, smitten by God, and afflicted. But he was wounded for our transgressions; he was crushed for our iniquities; upon him was the chastisement that brought us peace, and with his stripes we are healed. All we like sheep have gone astray; we have turned every one to his own way; and the Lord has laid on him the iniquity of us all. (ESV)

He's the image of God:

\textbf{Colossians 1:15} - He is the image of the invisible God, the firstborn of all creation. (ESV)

\subsection{Belief}
\label{sec:org1ba546d}
Jesus has life in Him, and the life is the Light of men - the true Light.

\textbf{John 5:26} - For as the Father has life in himself, so he has granted the Son also to have life in himself.

\textbf{John 5:21} - For as the Father raises the dead and gives them life, so also the Son gives life to whom he will.

\textbf{John 6:33} - For the bread of God is he who comes down from heaven and gives life to the world.

\textbf{John 1:4} - In Him was life, and the life was the Light of men. (ESV)

\textbf{John 1:9} - The true light, which enlightens everyone, was coming into the world. (ESV)

\textbf{1 John 2:8} -  At the same time, it is a new commandment that I am writing to you, which is true in him and in you, because the darkness is passing away and the true light is already shining.  (ESV)

\textbf{John 1:6-7} - There came a man sent from God, whose name was John. He came as a witness, to testify about the Light, so that all might believe through him.

\textbf{John 12:36} - While you have the light, \uline{believe in the light, that you may become sons of light}. When Jesus had said these things, he departed and hid himself from them.

We testify about the Light, so that through our testimony, others might believe.

To anyone who receives Jesus, even those who believe on His name, Jesus has given the right to become children of God, to be born of God.

\textbf{John 1:11-13} - He came to His own, and those who were His own did not receive Him. But \uline{as many as received Him, to them He gave the right to become children of God, even to those who believe (G4100 \textbf{pisteuo}) in His name}, who were born, not of blood nor of the will of the flesh nor of the will of man, but of God.

It's those that believe in him (trust Him, receive Him, have an obedient heart towards Him) that receive forgiveness of sins through his name:

\textbf{Acts 10:41-44} - not to all the people but to us who had been chosen by God as witnesses, who ate and drank with him after he rose from the dead. And he commanded us to preach to the people and to testify that he is the one appointed by God to be judge of the living and the dead. To him all the prophets bear witness that everyone who believes in him receives forgiveness of sins through his name. While Peter was still saying these things, the Holy Spirit fell on all who heard the word. (ESV)

\textbf{John 13:20} - Truly, truly, I say to you, whoever receives the one I send receives me, and whoever receives me receives the one who sent me.

\textbf{Mark 9:37} - Whoever receives one such child in my name receives me, and whoever receives me, receives not me but him who sent me.

A person still needs to ask and seek to receive Jesus:

\textbf{Luke 11:10} - For everyone who asks receives, and the one who seeks finds, and to the one who knocks it will be opened.

\textbf{John 6:63} - It is the Spirit who gives life; the flesh is of no avail. The words that I have spoken to you are spirit and life.

The following statement from \texttt{John 5:24} I believe is true. And it doesn't nullify the rest of what Jesus has commanded of and asked of us. If Jesus is your judge, then I think it's wise to take on board the rest of what Jesus has said:

\textbf{John 5:21-24} - For as the Father raises the dead and gives them life, so also the Son gives life to whom he will. The Father judges no one, but has given all judgment to the Son, that all may honor the Son, just as they honor the Father. \uline{Whoever does not honor the Son does not honor the Father who sent him}. Truly, truly, I say to you, whoever \uline{hears my word and believes (G4100 \textbf{pisteuo}) him who sent me has eternal life}. He does not come into judgment, but has passed from death to life.

We must honour Jesus Christ in our lives - fruitful labour, so that we can be confident with \texttt{John 5-24} above:

\textbf{Philippians 1:15-22} - Some indeed preach Christ from envy and rivalry, but others from good will. The latter do it out of love, knowing that I am put here for the defense of the gospel. The former proclaim Christ out of rivalry, not sincerely but thinking to afflict me in my imprisonment. What then? Only that in every way, whether in pretense or in truth, Christ is proclaimed, and in that I rejoice. Yes, and I will rejoice, for I know that through your prayers and the help of the Spirit of Jesus Christ this will turn out for my deliverance, as \uline{it is my eager expectation and hope that I will not be at all ashamed, but that with full courage now as always Christ will be honored in my body, whether by life or by death}. For to me to live is Christ, and to die is gain. \uline{If I am to live in the flesh, that means fruitful labor for me.} Yet which I shall choose I cannot tell.

Paul and the other faithful Apostles were exhibited as last of all, like men sentenced to death for following Jesus:

\textbf{I Corinthians 4:9} - For I think that God has exhibited us apostles as last of all, like men sentenced to death, because we have become a spectacle to the world, to angels, and to men.

God still makes apostles:

\textbf{Revelation of John 2:2} - I know your works, your toil and your patient endurance, and how you cannot bear with those who are evil, but have tested those who call themselves apostles and are not, and found them to be false.

God is loving and altogether gracious.

Having faith in God involves following Jesus:

\textbf{Hebrews 10:32-39} - But recall the former days when, \uline{after you were enlightened, you endured a hard struggle with sufferings, sometimes being publicly exposed to reproach and affliction}, and sometimes being partners with those so treated. For you had compassion on those in prison, and you joyfully accepted the plundering of your property, since you knew that you yourselves had a better possession and an abiding one. Therefore do not throw away your confidence, which has a great reward. For you have need of endurance, so that \uline{when you have done the will of God you may receive what is promised}. For, Yet a little while, and the coming one will come and will not delay; but my righteous one shall live by faith, and if he shrinks back, my soul has no pleasure in him. But \uline{we are not of those who shrink back and are destroyed, but of those who have faith and preserve their souls}.

\subsection{Obedience - A heart of obedience is the start of faith, and belief is the start of continued obedience}
\label{sec:org4ff4b7b}
\textbf{John 7:17} -  If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority. (ESV)

\subsubsection{Fear of the Lord}
\label{sec:org4192dfe}
\textbf{Isaiah 11:2} - And the Spirit of the Lord shall rest upon him, the Spirit of wisdom and understanding, the Spirit of counsel and might, the \uline{Spirit of knowledge and the fear of the Lord}.

Even after Jesus has come, the fear of the Lord is still important in feting God's attention. We still must obey God by obeying Jesus:

\textbf{Psalms 34:11-22} - Come, O children, listen to me; I will teach you the \uline{fear of the Lord}. What man is there who desires life and loves many days, that he may see good? Keep your tongue from evil and your lips from speaking deceit. Turn away from evil and do good; seek peace and pursue it. \uline{The eyes of the Lord are toward the righteous and his ears toward their cry}. The face of the Lord is against those who do evil, to cut off the memory of them from the earth. When the righteous cry for help, the Lord hears and delivers them out of all their troubles. The Lord is near to the brokenhearted and saves the crushed in spirit. Many are the afflictions of the righteous, but the Lord delivers him out of them all. He keeps all his bones; not one of them is broken. Affliction will slay the wicked, and those who hate the righteous will be condemned. The Lord redeems the life of his servants; none of those who take refuge in him will be condemned.

We make it our aim to please him:

\textbf{II Corinthians 5:9-12} - So whether we are at home or away, we make it our aim to please him. For we must all appear before the judgment seat of Christ, so that each one may receive what is due for what he has done in the body, whether good or evil. Therefore, knowing the \uline{fear of the Lord}, we persuade others. But what we are is known to God, and I hope it is known also to your conscience. We are not commending ourselves to you again but giving you cause to boast about us, so that you may be able to answer those who boast about outward appearance and not about what is in the heart.

\textbf{Proverbs 1:7} -The fear of the Lord is the beginning of knowledge; fools despise wisdom and instruction.

\textbf{Proverbs 2:5} - then you will understand the fear of the Lord and find the knowledge of God.

\textbf{Proverbs 8:13} - The fear of the Lord is hatred of evil. Pride and arrogance and the way of evil and perverted speech I hate.

\textbf{Proverbs 9:10} - The fear of the Lord is the beginning of wisdom, and the knowledge of the Holy One is insight.

\textbf{Proverbs 10:27} - The fear of the Lord prolongs life, but the years of the wicked will be short.

\textbf{Proverbs 14:27} - The fear of the Lord is a fountain of life, that one may turn away from the snares of death.

\textbf{Proverbs 15:33} - The fear of the Lord is instruction in wisdom, and humility comes before honor.

\textbf{Proverbs 19:23} - The fear of the Lord leads to life, and whoever has it rests satisfied; he will not be visited by harm.

\subsection{Repentance does involve turning from sin}
\label{sec:orgb818414}
\textbf{Luke 24:46-47} - and said to them, Thus it is written, that the Christ should suffer and on the third day rise from the dead, and that \textbf{repentance} (G3341 metanoia) and \textbf{forgiveness} (G859 aphesis) of sins should be proclaimed in his name to all nations, beginning from Jerusalem.

\textbf{Malachi 4:4-6} - Remember the law of my servant Moses, the statutes and rules that I commanded him at Horeb for all Israel. Behold, I will send you Elijah the prophet before the great and awesome day of the LORD comes. And he will turn the hearts of fathers to their children and the hearts of children to their fathers, lest I come and strike the land with a decree of utter destruction. (ESV)

\textbf{Matthew 11:12-14} - From the days of John the Baptist until now the kingdom of heaven has suffered violence, and the violent take it by force. For all the Prophets and the Law prophesied until John, and if you are willing to accept it, he is Elijah who is to come.

\textbf{Mark 9:11-13} - And they asked him, Why do the scribes say that first Elijah must come? And he said to them, Elijah does come first to restore all things. And how is it written of the Son of Man that he should suffer many things and be treated with contempt? But I tell you that Elijah has come, and they did to him whatever they pleased, as it is written of him.

\textbf{Matthew 11:21-21} - Woe to you, Chorazin! Woe to you, Bethsaida! For if the mighty works done in you had been done in Tyre and Sidon, they would have repented long ago in sackcloth and ashes. But I tell you, it will be more bearable on the day of judgment for Tyre and Sidon than for you.

\subsection{Faith, Law, Works}
\label{sec:org6d5d554}
I enjoyed this video, but I still am of the opinion that following the full Mosaic law is not necessary, (but not prohibited, so long as it is pursued by faith and submits to God's righteousness):
\begin{itemize}
\item \href{https://www.youtube.com/watch?v=CNHKqhwu6Bo}{Public Debate - Should Christians Keep The Law? - YouTube}
\begin{itemize}
\item \textbf{Galatians 3:10} - For all who rely on works of the law are under a curse; for it is written, Cursed be everyone who does not abide by all things written in the Book of the Law, and do them.
\begin{itemize}
\item Relying on the 'works of the law' for one's righteousness puts a person under a curse.
\end{itemize}
\end{itemize}
\item The whole world is accountable to God over the law of God
\begin{itemize}
\item \textbf{Romans 3:19-20} - Now we know that whatever the law says it speaks to those who are under the law, so that every mouth may be stopped, and the whole world may be held accountable to God. For by works of the law no human being will be justified in his sight, since through the law comes knowledge of sin. (ESV)
\end{itemize}
\item The law is still used in judgement, but the one who has faith in Jesus is not condemned
\item The law is good and just and Jesus both obeyed it flawlessly, but He also fulfilled it like a prophesy.
\begin{itemize}
\item Through faith we are justified, but we should absolutely stop sinning - we are sanctified by the Spirit \textbf{and} faith in the truth.
\begin{itemize}
\item \textbf{II Thessalonians 2:13} - But we should always give thanks (G2168 eucharisteo) to God for you, brethren beloved by the Lord, because God has chosen you from the beginning (G746 arche) for salvation through sanctification by the Spirit \textbf{and} faith (G4102 \textbf{pistis}) in the truth (G225 aletheia). (NASB)
\begin{itemize}
\item And the Spirit is the Truth
\item And God's Word is Truth
\begin{itemize}
\item God's Words are Truth
\item Jesus is the Truth
\end{itemize}
\item We must have faith in the truth (i.e. believe and trust in the truth)
\end{itemize}
\item Those who are in the faith \uline{can't do anything against the truth} - So those who are in the faith find no contradiction
\begin{itemize}
\item \textbf{II Corinthians 13:5-8} - Examine yourselves, to see whether you are in the faith. Test yourselves. Or do you not realize this about yourselves, that Jesus Christ is in you? —unless indeed you fail to meet the test! I hope you will find out that we have not failed the test. But we pray to God that you may not do wrong—not that we may appear to have met the test, but that you may do what is right, though we may seem to have failed. For we cannot do anything against the truth, but only for the truth.
\item Because truth is truth, it is imperishable
\begin{itemize}
\item \textbf{I Peter 1:23-25} - since you have been born again, not of perishable seed but of imperishable, through the living and abiding word of God; for All flesh is like grass and all its glory like the flower of grass. The grass withers, and the flower falls, but the word of the Lord remains forever. And this word is the good news that was preached to you. (ESV)
\item \textbf{I Corinthians 15:51-58} - Behold! I tell you a mystery. We shall not all sleep, but we shall all be changed, in a moment, in the twinkling of an eye, at the last trumpet. For the trumpet will sound, and the dead will be raised imperishable, and we shall be changed. For this perishable body must put on the imperishable, and this mortal body must put on immortality. When the perishable puts on the imperishable, and the mortal puts on immortality, then shall come to pass the saying that is written: Death is swallowed up in victory. O death, where is your victory? O death, where is your sting? The sting of death is sin, and the power of sin is the law. But thanks be to God, who gives us the victory through our Lord Jesus Christ. Therefore, my beloved brothers, be steadfast, immovable, always abounding in the work of the Lord, knowing that in the Lord your labor is not in vain. (ESV)
\end{itemize}
\end{itemize}
\item \textbf{1 Thessalonians 4:3} -  For this is the will of God, your sanctification: that you \uline{abstain} from sexual immorality;  (ESV)
\begin{itemize}
\item Stop sinning by faith in the truth - by faith in Jesus, and trusting obedience in God's words.
\end{itemize}
\end{itemize}
\item \textbf{Mark 10:19} - You know the commandments: Do not murder, Do not commit adultery, Do not steal, Do not bear false witness, Do not defraud, Honor your father and mother. (ESV)
\item \textbf{1 John 3:4-9} - Everyone who makes a practice of sinning also practices lawlessness; sin is lawlessness.  You know that he appeared to take away sins, and in him there is no sin.  No one who abides in him keeps on sinning; no one who keeps on sinning has either seen him or known him.  Little children, let no one deceive you.  Whoever practices righteousness is righteous, as he is righteous.  Whoever makes a practice of sinning is of the devil, for the devil has been sinning from the beginning.  The reason the Son of God appeared was to destroy the works of the devil.  No one born of God makes a practice of sinning, for God's seed abides in him, and he cannot keep on sinning because he has been born of God.  (ESV)
\end{itemize}
\item Jesus' words will not pass away
\begin{itemize}
\item \textbf{Matthew 24:35} - Heaven and earth will pass away, but my words will not pass away.  (ESV)
\item \textbf{John 6:68} -  Simon Peter answered him, Lord, to whom shall we go?  You have the words of eternal life,  (ESV)
\item \textbf{I Peter 1:23} - since you have been born again, not of perishable seed but of imperishable, through the living and abiding word of God;
\item \textbf{I Peter 1:25} - but the word of the Lord remains forever. And this word is the good news that was preached to you.
\item \textbf{Ephesians 1:13,14} -  In him you also, when you heard the word of truth, the gospel of your salvation, and believed in him, were sealed with the promised Holy Spirit, who is the guarantee of our inheritance until we acquire possession of it, to the praise of his glory.  (ESV)
\end{itemize}
\item Adhering strictly to the Mosaic law is not needed to be justified by God if we believe in and follow Jesus
\begin{itemize}
\item \textbf{Galatians 3:15-18} - To give a human example, brothers: even with a man-made covenant, no one annuls it or adds to it once it has been ratified. Now the promises were made to Abraham and to his offspring. It does not say, And to offsprings, referring to many, but referring to one, And to your offspring, who is Christ. This is what I mean: the law, which came 430 years afterward, does not annul a covenant previously ratified by God, so as to make the promise void. For if the inheritance comes by the law, it no longer comes by promise; but God gave it to Abraham by a promise.
\item The Mosaic law is not really in the same category as the 10 commandments, I believe. The 10 commandments if obeyed in truth from the heart would result in a clean heart, I think. So it serves to describe what a pure heart looks like, and the laws we should always try to keep whether Gentile or Jew.
\begin{itemize}
\item \textbf{I Peter 1:22} - Having purified your souls by your obedience to the truth for a sincere brotherly love, love one another earnestly from a pure heart,
\item \textbf{Matthew 5:28} - But I say to you that everyone who looks at a woman with lustful intent has \textbf{already committed adultery with her in his heart}.
\item \textbf{Revelation of John 2:23} - and I will strike her children dead. And all the churches will know that I am \textbf{he who searches mind and heart}, and I will give to each of you as your works deserve.
\item \textbf{II Peter 2:14} - They have eyes full of adultery, insatiable for sin. They entice unsteady souls. They have \textbf{hearts trained in greed}. Accursed children!
\item \textbf{II Corinthians 5:11-12} - Therefore, knowing the fear of the Lord, we persuade others. But what we are is known to God, and I hope it is known also to your conscience. We are not commending ourselves to you again but giving you cause to boast about us, so that you may be able to answer those who boast about outward appearance and not about what is in the heart.
\item The Holy Spirit cleanses our hearts by faith:
\begin{itemize}
\item \textbf{Acts 15:8-9} - And God, who knows the heart, bore witness to them, by giving them the Holy Spirit just as he did to us, and he made no distinction between us and them, having cleansed their hearts by faith.
\end{itemize}
\end{itemize}
\end{itemize}
\item Do what Jesus says and receive eternal life - obey Jesus
\begin{itemize}
\item \textbf{Romans 6:13-23} - Do not present your members to sin as instruments for unrighteousness, but present yourselves to God as those who have been brought from death to life, and your members to God as instruments for righteousness.  For sin will have no dominion over you, since you are not under law but under grace.  What then? Are we to sin because we are not under law but under grace? By no means!  Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of \textbf{obedience, which leads to righteousness}?  But thanks be to God, that you who were once slaves of sin have become \textbf{obedient from the heart to the standard of teaching to which you were committed}, and, having been set free from sin, have become \textbf{slaves of righteousness}.  I am speaking in human terms, because of your natural limitations. For just as you once presented your members as slaves to impurity and to lawlessness leading to more lawlessness, so now present your members as slaves to righteousness leading to sanctification.  When you were slaves of sin, you were free in regard to righteousness.  But what fruit were you getting at that time from the things of which you are now ashamed? The end of those things is death.  But now that you have been \uline{set free from sin and have become slaves of God, the fruit you get leads to sanctification and its end, eternal life.  For the wages of sin is death, but the free gift of God is eternal life in Christ Jesus our Lord}.
\item Being a slave to righteousness is possible without adhering to the Mosaic law, by being led by Jesus' Spirit
\begin{itemize}
\item \textbf{1 Corinthians 1:30-31} -  He is the source of your life in Christ Jesus, whom God made our wisdom and our righteousness and sanctification and redemption.  Therefore, as it is written, Let the one who boasts, boast in the Lord.  (ESV)
\begin{itemize}
\item God through Jesus is the source of our personal righteousness, and He \textbf{is} our righteousness.
\end{itemize}
\item \textbf{Philippians 1:9-11} - And it is my prayer that your love may abound more and more, with knowledge and all discernment, so that you may approve what is excellent, and so be pure and blameless for the day of Christ, filled with the fruit of righteousness that comes through Jesus Christ, to the glory and praise of God.
\begin{itemize}
\item We are set free from sin and become slaves of God (so we obey God!!) and the obedience leads to sanctification, and leads to righteousness.
\begin{itemize}
\item \textbf{Romans 6:16} - Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of obedience, which leads to righteousness? (ESV)
\item If a person is led by the Spirit then the Lord Jesus is in control of their life, which means that person obeys Jesus' commandments
\begin{itemize}
\item Faith receives and continues to receive the supply of the Spirit and we are led by the Spirit.
\item \textbf{Galatians 3:1-5} - O foolish Galatians! Who has bewitched you? It was before your eyes that Jesus Christ was publicly portrayed as crucified. Let me ask you only this: Did you \textbf{receive the Spirit} by works of the law or \textbf{by hearing with faith}? Are you so foolish? Having begun by the Spirit, are you now being perfected by the flesh? Did you suffer so many things in vain—if indeed it was in vain? Does he who \textbf{supplies the Spirit} to you and works miracles among you do so by works of the law, or by hearing with faith— (ESV)
\item \href{https://www.youtube.com/watch?v=34pBf5pZq\_I}{The Law Refutes Justification by Law: Galatians 3:6a??9, Part 1 - YouTube}
\item Faith receives and continues to receive the supply of the Spirit. So a person needs to be having faith in Jesus to be led by the Spirit.
\end{itemize}
\end{itemize}
\item Sanctification is personal righteousness that is fruit that comes from being in Jesus Christ, Him being our righteousness - we're grafted into Jesus like branches on a tree and become healthier. We must and \textbf{should} stop sinning.
\end{itemize}
\end{itemize}
\item We must simultaneously make the tree good (abide in Jesus) and make the fruit good (be sanctified and glorify God and Jesus in our hearts, minds, bodies and actions).
\begin{itemize}
\item \textbf{Matthew 12:33-37} - Either make the tree good and its fruit good, or make the tree bad and its fruit bad, for the tree is known by its fruit. You brood of vipers! How can you speak good, when you are evil? For out of the abundance of the heart the mouth speaks. The good person out of his good treasure brings forth good, and the evil person out of his evil treasure brings forth evil. I tell you, on the day of judgment people will give account for every careless word they speak, for by your words you will be justified, and by your words you will be condemned. (ESV)
\item As we make the tree good, we make the fruit good!
\end{itemize}
\item I still think the 10 commandments are special, and following them in truth is repenting from sin
\begin{itemize}
\item \textbf{Mark 10:19} - You know the commandments: Do not murder, Do not commit adultery, Do not steal, Do not bear false witness, Do not defraud, Honor your father and mother. (ESV)
\item \textbf{Acts 15:28-29} - For it has seemed good to the Holy Spirit and to us to lay on you no greater burden than these requirements: that you abstain from what has been sacrificed to idols, and from blood, and from what has been strangled, and from sexual immorality. If you keep yourselves from these, you will do well. Farewell.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Didache}
\label{sec:org55511aa}
What I like about the didache is that it still upholds righteous living and following God's Great commandments and precepts.

\href{https://www.earlychristianwritings.com/text/didache-roberts.html}{Didache: The Lord's Teaching Through the Twelve Apostles to the Nations}

I think it's important to live righteously out of love for God and one's neighbour, and out of faith.
That being said, I think God does justify through faith, and I believe faith works. And working may indeed be called faith if the work is done in faith.
I also think God likely saves through works because it may be their way of demonstrating faith to Jesus.

\subsubsection{Judgement}
\label{sec:orged5d6bb}
\textbf{Luke 18:8} - I tell you, he will give justice to them speedily. Nevertheless, when the Son of Man comes, \uline{will he find faith on earth}?

The law is still used in judgement, but the one who has faith in Jesus is not condemned because they are believing on Jesus.

\begin{itemize}
\item Whoever is actively believing/trusting in Jesus is not judged.
\item Whoever is disbelieving/distrusting in Jesus is judged even now.
\end{itemize}

\href{https://biblehub.com/interlinear/john/3-18.htm}{John 3:18 Interlinear: he who is believing in him is not judged, but he who is not believing hath been judged already, because he hath not believed in the name of the only begotten Son of God.}

\textbf{John 3:18} - He who believes (G4100 \textbf{pisteuo}) in Him is not judged; he who does not believe (G4100 pisteuo) has been judged (G2919 \textbf{krino}) already (G2235 ede), because he has not believed (G4100 pisteuo) in the name of the only begotten Son of God. (NASB)

\begin{verbatim}
1  :  2919  krino  kree'-no
2  
3   properly, to distinguish, i.e. decide (mentally or judicially); by
4   implication, to try, condemn, punish:--avenge, conclude, condemn,
5   damn, decree, determine, esteem, judge, go to (sue at the) law,
6   ordain, call in question, sentence to, think.
\end{verbatim}

\begin{verbatim}
1  :  2235  ede  ay'-day
2  
3   apparently from 2228 (or possibly 2229) and 1211; even now:--already,
4   (even) now (already), by this time.
5   see GREEK for 2228
6   see GREEK for 2229
7   see GREEK for 1211
\end{verbatim}

\textbf{John 3:19} - This is the judgment, that the Light has come into the world, and men loved the darkness rather than the Light, for their deeds were evil. (ESV)

\textbf{Matthew 12:36-37} - I tell you, on the day of judgment people will give account for every careless word they speak, for by your words you will be justified, and by your words you will be condemned.

When one speaks evil against a brother, they become a judge of the law.

\textbf{James 4:11} - Do not speak evil against one another, brothers. The one who speaks against a brother or judges his brother, speaks evil against the law and judges the law. But if you judge the law, you are not a doer of the law but a judge. (ESV)

\subsubsection{We should not rebel against the law - but we should obey the truth in truth}
\label{sec:org459de60}
\textbf{Matthew 23:2-7} - The scribes and the Pharisees sit on Moses' seat, so practice and observe whatever they tell you—but not what they do. For they preach, but do not practice. They tie up heavy burdens, hard to bear, and lay them on people's shoulders, but they themselves are not willing to move them with their finger. They do all their deeds to be seen by others. For they make their phylacteries broad and their fringes long, and they love the place of honor at feasts and the best seats in the synagogues and greetings in the marketplaces and being called rabbi by others. (ESV)

\begin{itemize}
\item \href{https://www.youtube.com/watch?v=alOI2zxIPgc}{How Preachers Grow Graceless - YouTube}
\end{itemize}

We should not live a double-life.
We should not deny in our private life what we preach in public.

I'm not a perfect person. I'm writing this document as I am learning, and interpreting as I go.
And I am trying to clean myself up in my own private life.

\subsubsection{Eternal judgement}
\label{sec:orgd5048dc}
\textbf{Hebrews 6:2} - and of instruction about washings, the laying on of hands, the resurrection of the dead, and eternal judgment.

\section{Faith requires obedience}
\label{sec:org78ab60b}
Luke writes that Peter says the Holy Spirit goes to those who obey Jesus.
If the book of Acts is finished after Paul went to Galatia, then it is in knowledge of the letter to the Galatians, where Paul says the promised Spirit is received through faith.

\textbf{Acts 5:32} - And we are witnesses to these things, and so is \textbf{the Holy Spirit, whom God has given to those who obey him}. (ESV)

\textbf{Galatians 3:14} - so that in Christ Jesus the blessing of Abraham might come to the Gentiles, so that we might \textbf{receive the promised Spirit through faith}. (ESV)

Or since Paul's journey to Galatia happened after Peter said the Holy Spirit is given to \uline{those who obey Jesus}, and Paul writes that the promised Spirit is received through \uline{faith}, even in these two passages, it's doubly confirmed that faith necessitates obedience.

\textbf{Acts 16:6} - And they went through the region of Phrygia and Galatia, having been forbidden by the Holy Spirit to speak the word in Asia.

Jesus says you must obey God to be part of His family:

\textbf{Luke 8:21} - But He answered and said to them, “My mother and My brothers are these who hear the word of God and do it.”

Jesus implies you must obey Him (Jesus) to be part of His family:

\textbf{John 7:16} - So Jesus answered them, My teaching is not mine, but his who sent me.

\subsection{The obedient children are the ones who are not conformed to the passions of our former ignorance}
\label{sec:org6680ed7}
\textbf{I Peter 1:14-16} - As obedient children, do not be conformed to the passions of your former ignorance, but as he who called you is holy, you also be holy in all your conduct, since it is written, You shall be holy, for I am holy.

\subsection{The sons of disobedience are the ones who are conformed to sexual immorality, impurity, or covetousness, etc.}
\label{sec:org043e275}
\textbf{Ephesians 5:5-7} - For you may be sure of this, that everyone who is sexually immoral or impure, or who is covetous (that is, an idolater), has no inheritance in the kingdom of Christ and God. Let no one deceive you with empty words, for because of these things the wrath of God comes upon the sons of disobedience. Therefore do not associate with them;

\subsection{Get to know Jesus by following His commandments}
\label{sec:org1b3a797}
\textbf{Matthew 7:21-27} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven.  On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name?  And then will I declare to them, I never knew you; depart from me, you workers of lawlessness.  Everyone then who hears these words of mine and does them will be like a wise man who built his house on the rock.  And the rain fell, and the floods came, and the winds blew and beat on that house, but it did not fall, because it had been founded on the rock.  And everyone who hears these words of mine and does not do them will be like a foolish man who built his house on the sand.  And the rain fell, and the floods came, and the winds blew and beat against that house, and it fell, and great was the fall of it. (ESV)

\textbf{I John 2:4} - Whoever says I know him but does not keep his commandments is a liar, and the truth is not in him,

\section{True religion}
\label{sec:org3a94882}
\begin{itemize}
\item Be a disciple and representative of Jesus
\begin{itemize}
\item Obedient to Jesus
\end{itemize}
\item Being a servant to other people
\item Sticking up for truth
\begin{itemize}
\item Be faithful to Jesus
\begin{itemize}
\item Be personally accountable to God and to Jesus
\item Do not deny Jesus
\end{itemize}
\end{itemize}
\item Have a pure heart
\begin{itemize}
\item Obey God, being accountable to God
\end{itemize}
\item Have Jesus' heart
\item Serving Jesus
\item Endeavour to please God
\item Be holy
\item Be godly (behaviour in accordance with the knowledge of God)
\end{itemize}

\textbf{Galatians 1:10} - For am I now seeking the approval of man, or of God? Or am I trying to please man? If I were still trying to please man, I would not be a servant of Christ. (ESV)

\textbf{James 1:27} - Religion that is pure and undefiled before God, the Father, is this: to visit orphans and widows in their affliction, and to keep oneself unstained from the world. (ESV)

\textbf{Matthew 15:8-9} - This people honors me with their lips, but their heart is far from me; in vain do they worship me, teaching as doctrines the commandments of men. (ESV)

\textbf{1 Samuel 16:7} - But the LORD said to Samuel, Do not look on his appearance or on the height of his stature, because I have rejected him.  For the LORD sees not as man sees: man looks on the outward appearance, but the LORD looks on the heart.  (ESV)

I do actually consider theology to be quite important but we should not be whitewashed tombs.

I think the person's lifestyle should be 'pure and undefiled religion' as James defines it.

I should probably actually do my own Bible study though because there's a lot of false religion out there.
Rather than fill my mind with other people's doctrines and religion, we should obey God, knowing God knows.

Also endeavor to also do lots of service as that is what Jesus' Kingdom is all about.

\section{Obtain a faith of equal standing with the Apostles by the righteousness of our God and Savior Jesus Christ}
\label{sec:orgbbabcf6}
\textbf{II Peter 1:1} - Simeon Peter, a servant and apostle of Jesus Christ, To those who have obtained a faith of equal standing with ours by the righteousness of our God and Savior Jesus Christ:

We obtain a strong faith by the righteousness of Jesus Christ.

This requires obedience to Jesus.

\textbf{Romans 6:16} - Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of \textbf{obedience, which leads to righteousness}?

Faith:
\begin{itemize}
\item Belief and Obedience => true knowledge => fruit
\begin{itemize}
\item Belief and obedience leads to true knowledge, and after true knowledge, fruit
\end{itemize}
\end{itemize}

Also, the Old Testament speaks a lot about how to walk in righteousness:

\textbf{II Timothy 3:16} All Scripture is breathed out by God and profitable for teaching, for reproof, for correction, and for \textbf{training in righteousness},

This is why it's a good idea to study the Old Testament including Old Testament law, the nature of faith etc. and God's character, precepts and statues, to love God and one's neighbour.

\subsection{Knowing and being found in Christ Jesus is what it's all about}
\label{sec:org6532ade}
Suffering for righteousness sake (suffering for being Christlike).

\textbf{Philippians 3:8-11} - Indeed, I count everything as loss because of the surpassing worth of knowing Christ Jesus my Lord. For his sake I have suffered the loss of all things and count them as rubbish, in order that I may gain Christ and be found in him, not having a righteousness of my own that comes from the law, but that which comes through faith in Christ, the righteousness from God that depends on faith— that I may know him and the power of his resurrection, and may share his sufferings, becoming like him in his death, that by any means possible I may attain the resurrection from the dead. (ESV)

It involves:
\begin{itemize}
\item believing the truth
\item sanctification while believing the truth
\begin{itemize}
\item putting a stop to sin
\item becoming holy
\end{itemize}
\item loving selflessly as Jesus loved
\end{itemize}

\subsection{We must believe the truth, stop sinning, and live to righteousness}
\label{sec:org5dcfa2e}
Jesus stopped sinning. We need to have the same way of thinking as Jesus had.
We need to cease from sin, and live for the will of God.

\textbf{1 Peter 4:1-2} - Since therefore Christ suffered in the flesh, arm yourselves with the same way of thinking, for whoever has suffered in the flesh has ceased from sin, so as to live for the rest of the time in the flesh no longer for human passions but for the will of God. (ESV)

\textbf{II Thessalonians 2:13} - But we should always give thanks (G2168 eucharisteo) to God for you, brethren beloved by the Lord, because God has chosen you from the beginning (G746 arche) for salvation through sanctification by the Spirit \textbf{and} faith (G4102 \textbf{pistis}) in the truth (G225 aletheia). (NASB)

Jesus has enabled us to die to sin and live to righteousness:

\textbf{1 Peter 2:24} - He himself bore our sins in his body on the tree, that we might die to sin and live to righteousness.  By his wounds you have been healed.  (ESV)

\textbf{Matthew 25:46} - And these will go away into eternal punishment, but the righteous into eternal life. (ESV)

Cleaned up by having faith in the truth.

\textbf{Faith} in the truth - strong faith word! Belief and ongoing faithfulness, trust, reliance.

\begin{verbatim}
1  :  4102  pistis  pis'-tis
2  
3   from 3982; persuasion, i.e. credence; moral conviction (of religious
4   truth, or the truthfulness of God or a religious teacher), especially
5   reliance upon Christ for salvation; abstractly, constancy in such
6   profession; by extension, the system of religious (Gospel) truth
7   itself:--assurance, belief, believe, faith, fidelity.
8   see GREEK for 3982
\end{verbatim}

\textbf{II Thessalonians 2:11-14} - Therefore God sends them a strong delusion, so that they may believe what is false, in order that all may be condemned who did not believe the truth but had pleasure in unrighteousness. But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through \textbf{sanctification by the Spirit} \uline{and} \textbf{belief in the truth}. To this he called you through our gospel, so that you may obtain the glory of our Lord Jesus Christ.

We want to obtain the glory of our Lord Jesus Christ - we do this by being Christlike through obeying Jesus Christ, which brings glory to Jesus and glory to God. We obey when we believe and are being sanctified.

\textbf{Ephesians 6:14} - Stand therefore, having fastened on the belt of truth, and having put on the breastplate of righteousness,

We \textbf{must} have faith in Jesus for the righteousness of God that comes by faith.
We must believe what He's achieved, and we must be born-again of the Spirit.

\textbf{Romans 10:4} - For Christ is the end of the law for righteousness to everyone who believes (G4100 \textbf{pisteuo}).

Saved, and being saved. Being cleaned while believing.

Jesus is our High Priest
\begin{itemize}
\item \textbf{Romans 8:1} - There is therefore now no condemnation for those who are in Christ Jesus.
\item \textbf{Romans 8:3-4} - For God has done what the law, weakened by the flesh, could not do. By sending his own Son in the likeness of sinful flesh and for sin, he condemned sin in the flesh, \textbf{in order that the righteous requirement of the law might be fulfilled in us}, who walk not according to the flesh but according to the Spirit.
\end{itemize}

Jesus condemned sin in the flesh. Now we walk according to the spirit so that the righteous requirement of the law might be fulfilled in us.
It's still really important to put a stop to sin! And we must walk according to Jesus' commandments.

\subsubsection{Holiness}
\label{sec:orga3a958a}
When we repent from sin we allow Jesus' holiness to shine through us increasingly.
Therefore, it's really not our own holiness or power that is responsible for miracles that happen through us or in cooperation with us, but it is Jesus' power and holiness.

Jesus is the True Vine. We are the branches. AMEN!! We can do nothing apart from Him. AMEN!!

\textbf{Acts 3:12} - And when Peter saw it, he answered unto the people, Ye men of Israel, why marvel ye at this? or why look ye so earnestly on us, as though by our own power or holiness we had made this man to walk? (KJV)

Everyone who names the name of the Lord must depart from iniquity:

\textbf{II Timothy 2:19-22} - But God's firm foundation stands, bearing this seal: The Lord knows those who are his, and, Let everyone who names the name of the Lord depart from iniquity. Now in a great house there are not only vessels of gold and silver but also of wood and clay, some for honorable use, some for dishonorable. Therefore, if anyone cleanses himself from what is dishonorable, he will be a vessel for honorable use, set apart as holy, useful to the master of the house, ready for every good work. So flee youthful passions and pursue righteousness, faith, love, and peace, along with those who call on the Lord from a pure heart.

Our bodies are a vessel for Jesus' holiness to shine out of. It's the vessel of the Holy Spirit:

\textbf{1 Thessalonians 4:3-5} - For this is the will of God, your sanctification; that is, that you abstain from sexual immorality; that each of you know how to possess his own (G1438 heautou) vessel (G4632 skeuos) in sanctification and honor, not in lustful passion, like the Gentiles who do not know God; (NASB)

We should not deceive our brothers by lying about the matter of sanctifying our bodies:

\textbf{I Thessalonians 4:6-7} - and that no man transgress and defraud his brother in the matter because the Lord is the avenger in all these things, just as we also told you before and solemnly warned you.
For God has not called us for the purpose of impurity, but in sanctification. (NASB)

Jesus is the light in us, and we must let our light shine:

\textbf{Luke 8:14-16} - And as for what fell among the thorns, they are those who hear, but as they go on their way they are choked by the cares and riches and pleasures of life, and their fruit does not mature.
As for that in the good soil, they are those who, hearing the word, hold it fast in an honest and good heart, and bear fruit with patience. No one after lighting a lamp covers it with a jar or puts it under a bed, but puts it on a stand, so that those who enter may see the light.

Jesus' family actually do the will of God: those who, hearing the word, hold it fast in an honest and good heart, and bear fruit with patience:

\textbf{Luke 8:21} - But he answered them, My mother and my brothers are those who hear the word of God and do it.

The power comes from Jesus:

\textbf{Luke 8:46} - But Jesus said, Someone touched me, for I perceive that power has gone out from me.

When we repent and clean ourselves up, we allow Jesus' light to shine through us. The sanctification process is like cleaning a muddy window.

\textbf{Luke 6:40} - A disciple is not above his teacher, but everyone when he is fully trained will be like his teacher.

\textbf{Luke 6:41-42} - Why do you see the speck that is in your brother's eye, but do not notice the log that is in your own eye? How can you say to your brother, Brother, let me take out the speck that is in your eye, when you yourself do not see the log that is in your own eye? You hypocrite, first take the log out of your own eye, and then you will see clearly to take out the speck that is in your brother's eye.

\textbf{John 15:5} - I am the vine; you are the branches. Whoever abides in me and I in him, he it is that bears much fruit, for apart from me you can do nothing.

\textbf{Luke 6:43} - For no good tree bears bad fruit, nor again does a bad tree bear good fruit,

\subsubsection{We approach Christ's very image}
\label{sec:org494cd1b}
\textbf{Romans 8:29} - For those whom he foreknew he also predestined to be conformed to the image of his Son, in order that he might be the firstborn among many brothers.

\textbf{Hebrews 2:11-12} -  For he who sanctifies and those who are sanctified all have one origin.  That is why he is not ashamed to call them brothers, saying, I will tell of your name to my brothers; in the midst of the congregation I will sing your praise.  (ESV)

\subsubsection{Repentance: Put off the old self}
\label{sec:orgbdd9187}
\textbf{Colossians 3:4-9} - When Christ who is your life appears, then you also will appear with him in glory. Put to death therefore what is earthly in you: sexual immorality, impurity, passion, evil desire, and covetousness, which is idolatry. On account of these the wrath of God is coming. In these you too once walked, when you were living in them. But now you must put them all away: anger, wrath, malice, slander, and obscene talk from your mouth. Do not lie to one another, seeing that you have put off the old self with its practices

\begin{itemize}
\item Stop sexual immorality.
\item Stop idolatry.
\end{itemize}

\textbf{I Corinthians 10:7-14} - Do not be idolaters as some of them were; as it is written, The people sat down to eat and drink and rose up to play. We must not indulge in sexual immorality as some of them did, and twenty-three thousand fell in a single day. We must not put Christ to the test, as some of them did and were destroyed by serpents, nor grumble, as some of them did and were destroyed by the Destroyer. Now these things happened to them as an example, but they were written down for our instruction, on whom the end of the ages has come. Therefore let anyone who thinks that he stands take heed lest he fall. No temptation has overtaken you that is not common to man. God is faithful, and he will not let you be tempted beyond your ability, but with the temptation he will also provide the way of escape, that you may be able to endure it. Therefore, my beloved, flee from idolatry.

\subsubsection{Put on the new self: Christ-likeness}
\label{sec:orgce3a6b6}
\textbf{Colossians 3:10-17} - and have put on the new self, which is being renewed in knowledge after the image of its creator. Here there is not Greek and Jew, circumcised and uncircumcised, barbarian, Scythian, slave, free; but Christ is all, and in all. Put on then, as God's chosen ones, holy and beloved, compassion, kindness, humility, meekness, and patience, bearing with one another and, if one has a complaint against another, forgiving each other; as the Lord has forgiven you, so you also must forgive. And above all these put on love, which binds everything together in perfect harmony. And let the peace of Christ rule in your hearts, to which indeed you were called in one body. And be thankful. Let the word of Christ dwell in you richly, teaching and admonishing one another in all wisdom, singing psalms and hymns and spiritual songs, with thankfulness in your hearts to God. And whatever you do, in word or deed, do everything in the name of the Lord Jesus, giving thanks to God the Father through him.

\subsubsection{What must be believe, and what we must do: Walk in \textbf{truth} and \textbf{love} the way Jesus has commanded us}
\label{sec:orgff16f56}

We must receive Jesus' words through faith, walk in them through faith and come to \textbf{know in truth} (we must truly know) that Jesus came from God, and continue in faith, continuing to be sanctified.

We must practice the truth.

\textbf{John 3:21} - But he who \textbf{practices the truth} comes to the Light, so that his deeds may be manifested as having been wrought in God.”

\textbf{Hebrews 10:14} - For by a single offering he has perfected for all time those who are \textbf{being sanctified}.

This is what we must come to know in truth - that Jesus came from Father God, and that Father God sent Him - it is Father God's will:

\textbf{John 17:8} - For I have given them the words that you gave me, and they have received them and have \textbf{come to know in truth that I came from you}; \uline{and} they have believed that you sent me.

\subsubsection{Come to the \underline{knowledge} of the truth}
\label{sec:orga9263b5}

\textbf{I Timothy 2:3-6} - This is good, and it is pleasing in the sight of God our Savior, who desires all people to be saved and to \textbf{come to the knowledge of the truth}. For \uline{there is one God, and there is one mediator between God and men, the man Christ Jesus}, \uline{who gave himself as a ransom for all}, which is the testimony given at the proper time.

Therefore, we should receive Jesus' words and \uline{obey} Jesus and \uline{arrive} at the truth. Obedience is an essential part of faith. Like Abraham obeying God, or like Israel crossing through the Red Sea, it's obedience which \uline{leads} to sure belief, and obedience that leads a person into sure knowledge of the truth, and obedience which cooperates with sanctification by the Spirit.

\textbf{Exodus 14:31} - When Israel saw the great power which the Lord had used against the Egyptians, the people feared the Lord, and they believed (H539 \textbf{'aman}) in the Lord and in His servant Moses.

\textbf{John 8:31-32} - So Jesus was saying to those Jews who had believed Him, “If you \textbf{continue in My word}, then you are truly disciples of Mine; and \textbf{you will know the truth}, and the truth will make you free.” (NASB)

The true knowledge of Jesus grants us everything pertaining to life and godliness, allowing us to partake in the divine nature:

\textbf{II Peter 1:3-4} - seeing that His divine power has granted to us everything pertaining to life and godliness, \textbf{through the true knowledge} of Him who called us by His own glory and excellence. For by these He has granted to us His precious and magnificent promises, so that by them you may become partakers of the divine nature, having escaped the corruption that is in the world by lust. (NASB)

Being set free through the knowledge of our Lord and Savior Jesus Christ is at least in part being set free from the defilements of the world.

\textbf{II Peter 2:20-21} - For if, after they have escaped the \uline{defilements of the world through the knowledge of our Lord and Savior Jesus Christ}, they are again entangled in them and overcome, the last state has become worse for them than the first. For it would have been better for them never to have known \textbf{the way of righteousness} than after knowing it to turn back from the holy commandment delivered to them.

Then we continue to add Work/Love/Virtue to be fruitful:

\textbf{II Peter 1:8} - For \textbf{if these qualities are yours and are increasing}, they render you \uline{neither useless nor unfruitful} in the \uline{true knowledge} (G1922 \textbf{epignosis}) of our Lord Jesus Christ.

But we must practice Jesus' commandments even before we have arrived at the knowledge of the truth, in order to arrive at the knowledge of the truth:

\textbf{I John 2:3} - And by this we know that we have come to know him, if we \uline{keep} his commandments.

We come to know Him through obeying Him. He is the Truth. God sent Him.
The point at which we have come to know Him is if we are managing to actually \textbf{keep} His commandments.

\textbf{John 14:6} - Jesus said to him, I am the way, and the truth, and the life. No one comes to the Father except through me. (ESV)

Jesus is the living Word. He obeyed God perfectly, and fulfilled the Law, Prophets and Psalms.

\textbf{Psalms 119:160} - The sum of Your word is truth, And every one of Your righteous ordinances is everlasting. (ESV)

\textbf{John 17:17-19} - Sanctify them in the truth; Your word is truth. As you sent me into the world, so I have sent them into the world. And for their sake I consecrate myself, that they also may be sanctified in truth.  (ESV)

Jesus is eternally our Great High Priest. I believe this says Father God has sworn and will not change His mind.

\textbf{Psalms 110:4} - The Lord has sworn and will not change his mind, You are a priest forever after the order of Melchizedek.

\textbf{Hebrews 4:14} - Since then we have a great high priest who has passed through the heavens, Jesus, the Son of God, let us hold fast our confession.

\textbf{Hebrews 5:9} - And being made perfect, he became the source of eternal salvation to all who obey him,

\textbf{I John 2:4} - Whoever says I know him but does not keep his commandments is a liar, and the truth is not in him,

And the obedience doesn't end. We continue to be sanctified through faith. We are saved from darkness, and saved from sinning, and even start doing good works pleasing to God.

\textbf{II Peter 1:1-11} - Simeon Peter, a servant and apostle of Jesus Christ, To those who have obtained a faith of equal standing with ours by the righteousness of our God and Savior Jesus Christ: May grace and peace be multiplied to you in the knowledge of God and of Jesus our Lord.  His divine power has granted to us all things that pertain to life and godliness, through the knowledge of him who called us to his own glory and excellence, by which he has granted to us his precious and very great promises, so that through them you may become partakers of the divine nature, having escaped from the corruption that is in the world because of sinful desire.  For this very reason, make every effort to supplement your faith with virtue, and virtue with knowledge, and knowledge with self-control, and self-control with steadfastness, and steadfastness with godliness, and godliness with brotherly affection, and brotherly affection with love.  For if these qualities are yours and are increasing, they keep you from being ineffective or unfruitful in the knowledge of our Lord Jesus Christ.  For whoever lacks these qualities is so nearsighted that he is blind, having forgotten that he was cleansed from his former sins.  Therefore, brothers, be all the more diligent to make your calling and election sure, for if you practice these qualities you will never fall.  For in this way \uline{there will be richly provided for you an entrance into the eternal kingdom of our Lord and Savior Jesus Christ}.

\textbf{II Thessalonians 2:11-14} - Therefore God sends them a strong delusion, so that they may believe what is false, in order that all may be condemned who did not believe the truth but had pleasure in unrighteousness. But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through \textbf{sanctification by the Spirit} \uline{and} \textbf{belief in the truth}. To this he called you through our gospel, so that you may \uline{obtain the glory of our Lord Jesus Christ}.

Continuing to be sanctified by faith is a process where a person continues in Jesus' words because they are sanctified by faith in Jesus and that means ongoing trust and faithful obedience.

\textbf{Acts 26:18} - to open their eyes, so that they may turn from darkness to light and from the power of Satan to God, that they may receive forgiveness of sins and a place among those who are \textbf{sanctified by faith in me}. (ESV)

\uline{II John 1:1-11 highlights}:
\begin{itemize}
\item knowing the truth
\item the truth abiding in us
\item walking in the truth
\begin{itemize}
\item we are commanded to do so
\end{itemize}
\item love one another and loving one another is walking according to Jesus' commandments commandments
\begin{itemize}
\item we are commanded to do so
\end{itemize}
\item lose not what we have worked for, but may win a full reward
\item to not abide in this teaching is to work wickedness
\end{itemize}

\textbf{II John 1:1-11} - The elder to the elect lady and her children, whom I love in truth, and not only I, but also all who \textbf{know the truth}, because of the \textbf{truth that abides in us and will be with us forever}: Grace, mercy, and peace will be with us, from God the Father and from Jesus Christ the Father's Son, in \textbf{truth and love}.  I rejoiced greatly to find some of your children \textbf{walking in the truth}, just as we were \textbf{commanded by the Father}.  And now I ask you, dear lady—not as though I were writing you a new commandment, but the one we have had from the beginning—that we \textbf{love one another}.  And this is love, that we walk according to his commandments; this is the commandment, just as you have heard from the beginning, so that you should walk in it.  For many deceivers have gone out into the world, those who do not confess the coming of Jesus Christ in the flesh. Such a one is the deceiver and the antichrist.  \uline{Watch yourselves, so that you may not lose what we have worked for, but may win a full reward}.  Everyone who goes on ahead and does not abide in the teaching of Christ, does not have God. Whoever abides in the teaching has both the Father and the Son.  If anyone comes to you and does not bring this teaching, do not receive him into your house or give him any greeting, for whoever greets him takes part in his \textbf{wicked works}. (ESV)

Definitely stop sinning after receiving the knowledge of the truth:

\textbf{Hebrews 10:26-29} - For if we go on sinning deliberately \textbf{after receiving the knowledge of the truth}, there no longer remains a sacrifice for sins, but a fearful expectation of judgment, and a fury of fire that will consume the adversaries. Anyone who has set aside the law of Moses dies without mercy on the evidence of two or three witnesses. How much worse punishment, do you think, will be deserved by the one who has spurned the Son of God, and has profaned the blood of the covenant by which he was sanctified, and has outraged the Spirit of grace? (ESV)

\textbf{Hebrews 10:16-18} - This is the covenant that I will make with them after those days, declares the Lord: I will put my laws on their hearts, and write them on their minds, then he adds, I will remember their sins and their lawless deeds no more. Where there is forgiveness of these, there is no longer any offering for sin.

To \textbf{know} if Jesus' teaching comes from God, one must desire to do God's will.

\textbf{John 7:17} -  If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.  (ESV)

Therefore, to arrive at the knowledge of the truth, you've got to have an obedient heart.

\section{Put a stop to sin and practice personal righteousness}
\label{sec:org6006755}
\textbf{I John 3:7} - Little children, let no one deceive you. Whoever practices righteousness is righteous, as he is righteous.

\textbf{I John 3:10} - By this it is evident who are the children of God, and who are the children of the devil: whoever does not practice righteousness is not of God, nor is the one who does not love his brother.

\textbf{I Peter 2:24} - He himself bore our sins in his body on the tree, that we might die to sin and live to righteousness. By his wounds you have been healed.

We must die to sin and practice righteousness.

Then while practicing righteousness after dying to sin, we may suffer for practicing righteousness.
Therefore this righteousness is a personal righteousness, which we practice after dying to sin.

\textbf{I Peter 3:14} But even if you should suffer for righteousness' sake, you will be blessed. Have no fear of them, nor be troubled,

Faith working through love is obeying Jesus.

\textbf{Galatians 5:5-6} - For through the Spirit, by faith, we ourselves eagerly wait for the hope of righteousness. For in Christ Jesus neither circumcision nor uncircumcision counts for anything, but only faith working through love.

Paul awaits Christ to be formed in the person:

\textbf{Galatians 4:18-19} - It is always good to be made much of for a good purpose, and not only when I am present with you, my little children, for whom I am again in the anguish of childbirth until Christ is formed in you!

\section{Justifying faith vs justifying works is misunderstood and is a false dichotomy}
\label{sec:org765f88d}
There's a false dichotomy between faith and works - because obedience is intrinsic to faith.

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.} (ESV)

True faith is always obedient; faith is always prepared to obey more:

\textbf{John 7:17}- If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.

You can't even have faith in God without obeying Jesus because the one who has faith in God has already obeyed Jesus whether they know about \texttt{Mark 11:22 or not}. So it's not a dead work.

And justifying faith is having obedient faith in God with regards to the promise given to Abraham.

Obeying God \textbf{is} having faith in God. Obeying God \textbf{is} loving God. AMEN!!

\textbf{Mark 11:22} - And Jesus answered them, Have (G2192 echo) faith (G4102 \textbf{pistis}) in God (G2316 theos). (ESV)

\textbf{pistis} is the faith noun.

\textbf{John 14:1} - “Do not let your heart be troubled; believe (G4100 \textbf{pisteuo}) in God, believe (G4100 \textbf{pisteuo}) also in Me. (NASB)

\textbf{pisteuo} is the faith verb.

\textbf{echo} means 'to hold' - so in \textbf{Mark 11:22} Jesus says 'hold faith' in God.
And in \textbf{John 14:1} Jesus tells us to 'do faith' in God and to 'do faith' in Him.

If you are believing in Jesus, then you are obediently working.

To be justified, a person must \uline{walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

Having faith in God \textbf{is} obeying God. Loving God \textbf{is} obeying God. AMEN!!

So what Jesus is saying is quite similar - we must have the faith that Abraham had when he put Isaac on the Altar, but in regards to following Jesus:

\textbf{Luke 9:23-24} - And he said to all, If anyone would come after me, let him deny himself and take up his cross daily and follow me. For whoever would save his life will lose it, but whoever loses his life for my sake will save it. (ESV)

Now about the following:

\textbf{Romans 4:4} - Now to the one who works, his wages are not counted as a gift but as his due.

I believe that what \emph{Romans 4:4} is saying is that before accepting God's forgiveness yourself, submitting to the righteousness of God, believing that you were in need of God's forgiveness,
anything you try to give God is simply giving God what is due to Him, and that you will never be able to return enough stolen goods to God to ever be justified. Nor would you ever be able to forgive enough other people to attain that justification.
\uline{You ultimately need God's forgiveness}. However, forgiving others is still required if someone wants God to forgive them.

\textbf{Mark 11:25} - And whenever you stand praying, forgive, if you have anything against anyone, so that your Father also who is in heaven may forgive you your trespasses.

\textbf{Matthew 6:12-15} -  and forgive us our debts, as we also have forgiven our debtors.  And lead us not into temptation, but deliver us from evil.  For if you forgive others their trespasses, your heavenly Father will also forgive you, but if you do not forgive others their trespasses, neither will your Father forgive your trespasses.  (ESV)

\subsection{Obedient action including seeking God in faith (trusting God's words and seeking)}
\label{sec:org23e6c0c}
I believe that obedient action which includes seeking God is an important part of faith.

I believe obedience is intrinsic to faith, actually.

True faith is always obedient; faith is always prepared to obey more:

\textbf{John 7:17}- If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.

Obedient action is not dead works, and I believe that obedient action is just working faith.

Being disobedient to Jesus means disbelieving in Jesus:

\textbf{John 3:36} - Whoever believes (G4100 pisteuo) in the Son has eternal life; whoever does not obey the Son shall not see life, but the wrath of God remains on him. (ESV)

\textbf{Romans 4:2} - For if Abraham was justified by works, he has something to boast about, but not before God.

Paul doesn't deny that Abraham could have been
justified by works, but he claims that Abraham
doesn't have anything to boast about before
God. AMEN!!

Because he offered nothing to God through his work other than what was asked of him.

Jesus was perfectly faithful to God by being obedient:

\textbf{Philippians 2:8} - And being found in human form, he humbled himself by becoming obedient to the point of death, even death on a cross.

\textbf{Romans 9:15-16} - For he says to Moses, I will have mercy on whom I have mercy, and I will have compassion on whom I have compassion. So then it depends not on human will or exertion, but on God, who has mercy. (ESV)

AMEN!! But that doesn't mean human will or exertion cannot be utilised by God.

God rewards faith and may choose to reveal Himself after a while serving God in faith instead of immediately.

\textbf{Matthew 25:19} - Now after a long time the master of those servants came and settled accounts with them.

\textbf{Acts 20:35} - In all things I have shown you that by working hard in this way we must help the weak and remember the words of the Lord Jesus, how he himself said, It is more \textbf{blessed to give} than to receive.

\subsection{Obedience belongs in faith}
\label{sec:orgc4094f8}
In God's mercy He has shown us the Way to be reconciled with Him. He has given us Jesus. He has told us what to do, and we can choose to be obedient or to not be obedient.

Jesus is the author of our faith, so having faith is grace from God, and even if works are working with our faith, it's all by grace and we still can't boast before God because our faith and our works are all gifted to us from God.

For example, Noah's works of building the ark was given to Him by God. God even outlined every detail.

\textbf{Hebrews 12:1-2} - Therefore, since we are surrounded by so great a cloud of witnesses, let us also lay aside every weight, and sin which clings so closely, and let us run with endurance the race that is set before us, looking to Jesus, the \textbf{founder} and \textbf{perfecter} of our faith, who for the joy that was set before him endured the cross, despising the shame, and is seated at the right hand of the throne of God.

\begin{itemize}
\item Obedience belongs inside faith because
\begin{itemize}
\item God commanded it and complying is not really bringing anything
to God which He hasn't told you to bring to Him.
\begin{itemize}
\item So it's just acting in faith
\item If God commands you to build an ark, and you build it exactly as specified, is that considered dead works? No, it's just doing exactly what God said. It's faith.
\item If God commands you to wait 5 days before going into battle but you think 8 days would be better, thinking God needs the extra time so you can be more prepared so you wait 8 days then that is no longer faith because it's disobedience.
\item Abraham was commanded to offer Isaac as a sacrifice, and Abraham did offer Isaac out of faithful obedience.
\begin{itemize}
\item \textbf{Genesis 22:2} - He said, Take your son, your only son Isaac, whom you love, and go to the land of Moriah, and offer him there as a burnt offering on one of the mountains of which I shall tell you.
\item \textbf{James 2:22} - You see that faith was active along with his works, and faith was completed by his works;
\end{itemize}
\item But if Abraham thought he could get even more rewards from God by trying the same thing again and putting Isaac on the altar again without God even commanding it, then that is like trying to justify yourself by doing dead works (i.e. deeds without faith).
\end{itemize}

\item Choosing to obey God's commandments even when no-one is watching (aside from God) is having faith in God.
\begin{itemize}
\item For example, not stealing from your employer.
\item Therefore, there is a way of abiding by God's commandments which is faith and not works.
\item To not steal is to love God and have faith in God.
\end{itemize}
\end{itemize}
\item Seeking God in action belongs in faith because:
\begin{itemize}
\item When someone wills to do God's will, they come to know the truth
\begin{itemize}
\item \textbf{John 7:17} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority. (ESV)
\end{itemize}
\item When someone has faith, they believe that God exists and that in seeking God, God rewards them:
\begin{itemize}
\item \textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God must believe that he exists and that he rewards those who seek him.
\end{itemize}
\end{itemize}
\end{itemize}

Salvation is the gift, and faith implies an obedient heart. Works can be dead works when they're not done in faith. Faith is what justifies. But faith works. Faith requires obedience to God. Faithless works do not justify:

\textbf{Ephesians 2:8-9} - For by grace you have been saved through faith. And this is not your own doing; it is the gift of God, not a result of works, so that no one may boast. (ESV)

With an obedient heart, a person will receive revelation as they hear the teaching of Jesus.

A person must be at least willing to do His will - obedience is the essence of faith:

\textbf{John 7:17} - If anyone is willing to do His will, he will know of the teaching, whether it is of God or whether I speak from Myself.

Therefore, faith quickly progresses into good work, serving the living God.

\textbf{Hebrews 9:14} - how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God.

'Believing in rewards from God for seeking Him' belongs in faith, or it's not faith anymore, even in regards to justifying faith.

\textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God must believe that he exists and that he rewards those who seek him.

\textbf{Hebrews 11:24-26} - By faith Moses, when he was grown up, refused to be called the son of Pharaoh's daughter, choosing rather to be mistreated with the people of God than to enjoy the fleeting pleasures of sin. \textbf{He considered the reproach of Christ greater wealth than the treasures of Egypt, for he was looking to the reward}.

We should pursue Jesus Christ similarly. God commanded it.

\textbf{Mark 9:7} - And a cloud overshadowed them, and a voice came out of the cloud, This is my beloved Son; listen to him.

\textbf{Luke 9:35} - And a voice came out of the cloud, saying, This is my Son, my Chosen One; listen to him!

\textbf{1 Timothy 1:15-17} - The saying is trustworthy and deserving of full acceptance, that \textbf{Christ Jesus came into the world to save sinners}, of whom I am the foremost. But I received mercy for this reason, that in me, as the foremost, Jesus Christ might display his perfect patience \textbf{as an example} to those who were to believe (G4100 \textbf{pisteuo}) in him for eternal life. To the King of ages, immortal, invisible, the only God, be honor and glory forever and ever. Amen. (ESV)

\subsection{The type of work that is good - works done in faith}
\label{sec:org9ada8d9}
\textbf{John 15:5} - I am the vine; you are the branches. Whoever abides in me and I in him, he it is that bears much fruit, for apart from me you can do nothing. (ESV)

Obedience is good.

\textbf{Psalms 40:6-8} - Sacrifice and offering you have not desired, but you have given me an open ear. Burnt offering and sin offering you have not required. Then I said, Behold, I have come; in the scroll of the book it is written of me: I desire to do your will, O my God; your law is within my heart. (ESV)

'Working' for God is OK when it's done in faith.
Obedience is intrinsic to faith.

\textbf{Hebrews 11:31} - By faith Rahab the prostitute did not perish with those who were disobedient, because she had given a friendly welcome to the spies.

And after a time, the LORD visits and judges on deeds:

\textbf{Revelation of John 3:2-3} - Wake up, and strengthen what remains and is about to die, for I have not found your works complete in the sight of my God. So remember what you have received and heard; and keep it, and repent. Therefore if you do not wake up, I will come like a thief, and you will not know at what hour I will come to you.

\textbf{Matthew 25:19} - Now after a long time the master of those servants came and settled accounts with them.

\textbf{Matthew 25:21} - His master said to him, Well done, good and faithful servant. You have been faithful over a little; I will set you over much. Enter into the joy of your master.

\textbf{I Peter 1:17} - And if you call on him as Father who judges impartially according to each one's deeds, conduct yourselves with fear throughout the time of your exile,

\subsubsection{Since Jesus has made the way, we serve God with good works. We have received mercy. We should then be merciful:}
\label{sec:org3ffa908}
\textbf{I Peter 2:10} - Once you were not a people, but now you are God's people; once you had not received mercy, but now you have received mercy.

\textbf{Luke 6:36} - Be merciful, even as your Father is merciful.

\subsubsection{Works must serve God, submitted to the righteousness that comes from God}
\label{sec:orgb784fc2}

We have to submit to God's righteousness, accepting that we are sinners, and accept God's forgiveness through the atonement that comes through Jesus, and be obedient to God through being obedient to Jesus.

\textbf{Mark 2:17} - And when Jesus heard it, he said to them, Those who are well have no need of a physician, but those who are sick. I came not to call the righteous, but sinners.

\textbf{Luke 5:32} - I have not come to call the righteous but sinners to repentance.

\textbf{Romans 10:3-4} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness. For Christ is the end of the law for righteousness to everyone who believes (G4100 \textbf{pisteuo}). (ESV)

\textbf{Philippians 3:8-11} - Indeed, I count everything as loss because of the surpassing worth of knowing Christ Jesus my Lord. For his sake I have suffered the loss of all things and count them as rubbish, in order that I may gain Christ and be found in him, not having a righteousness of my own that comes from the law, but that which comes through faith in Christ, the righteousness from God that depends on faith— that I may know him and the power of his resurrection, and may share his sufferings, becoming like him in his death, that by any means possible I may attain the resurrection from the dead. (ESV)

\subsection{Dead works: The type of work that's bad}
\label{sec:org7f333fa}
What is wrong is trying to establish a righteousness of one's own apart from submitting to the righteousness of God - it's saying, "God, I think you should have this, or, God I think I'm righteous because I did this for you." rather than, "here is what you asked of me, LORD."

Work not done in faith:

\textbf{Leviticus 10:1-2} - Now Nadab and Abihu, the sons of Aaron, each took his censer and put fire in it and laid incense on it and offered unauthorized fire before the Lord, which he had not commanded them. And fire came out from before the Lord and consumed them, and they died before the Lord.

God didn't ask for the offering which Nadab and Abihu offered.

Ananias gave to God unfaithfully, in a manner similar to Cain.

\textbf{Acts 4:32} - Now the full number of those who believed were of one heart and soul, and no one said that any of the things that belonged to him was his own, but they had everything in common.

\textbf{Acts 5:1-5} -  But a man named Ananias, with his wife Sapphira, sold a piece of property, and with his wife's knowledge he kept back for himself some of the proceeds and brought only a part of it and laid it at the apostles' feet.  But Peter said, Ananias, why has Satan filled your heart to lie to the Holy Spirit and to keep back for yourself part of the proceeds of the land?  While it remained unsold, did it not remain your own?  And after it was sold, was it not at your disposal?  Why is it that you have contrived this deed in your heart?  You have not lied to men but to God.  When Ananias heard these words, he fell down and breathed his last.  And great fear came upon all who heard of it.  (ESV)

Cain was half-hearted with his offering to the LORD, as Ananias was:

\textbf{Genesis 4:3-5} - In the course of time Cain brought to the Lord an offering of the fruit of the ground, and Abel also brought of the firstborn of his flock and of their fat portions. And the Lord had regard for Abel and his offering, but for Cain and his offering he had no regard. So Cain was very angry, and his face fell. (ESV)

\textbf{1 John 3:12} - We should not be like Cain, who was of the evil one and murdered his brother. And why did he murder him? Because his own deeds were evil and his brother's righteous. (ESV)

\textbf{Hebrews 6:1} - Therefore let us leave the elementary doctrine of Christ and go on to maturity, not laying again a foundation of repentance from dead works and of faith toward God,

Dead works are works not done in service to God, but works done in service to God, He may accept.

\subsubsection{Works of the law are dead works. God always desired us to serve Him with mercy}
\label{sec:org14097d2}
\textbf{Hebrews 10:8} - When he said above, You have neither desired nor taken pleasure in sacrifices and offerings and burnt offerings and sin offerings (these are \uline{offered according to the law}),

Hebrews addressed the same passage which Jesus addressed:

\textbf{Matthew 12:3-8} - He said to them, Have you not read what David did when he was hungry, and those who were with him: how he entered the house of God and ate the bread of the Presence, which it was not lawful for him to eat nor for those who were with him, but only for the priests? Or have you not read in the Law how on the Sabbath the priests in the temple profane the Sabbath and are guiltless? I tell you, something greater than the temple is here. And if you had known what this means, I desire mercy, and not sacrifice, you would not have condemned the guiltless. For the Son of Man is lord of the Sabbath.

\subsubsection{Working faith}
\label{sec:org9040a73}
Works and faith can't exist apart from one another because even to believe in Jesus is a work, and if the belief is true then the obedience continues.

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.}

To be justified, a person must \uline{walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

So what Jesus is saying is quite similar - we must have the faith that Abraham had when he put Isaac on the Altar, but in regards to following Jesus:

\textbf{Luke 9:23-24} - And he said to all, If anyone would come after me, let him deny himself and take up his cross daily and follow me. For whoever would save his life will lose it, but whoever loses his life for my sake will save it. (ESV)

Even the demons believe God is one and they shudder. The faithful believe God and love God (a totally different response). Love is obedience to God, and includes accepting and having faith in the one who God sent, Jesus.

\textbf{James 2:19} - You believe that God is one; you do well. Even the demons believe—and shudder!

\textbf{John 8:42} - Jesus said to them, If God were your Father, you would love me, for I came from God and I am here. I came not of my own accord, but he sent me.

\textbf{I John 5:2-3} - By this we know that we love the children of God, when we love God and obey his commandments. For this is the love of God, that we keep his commandments. And his commandments are not burdensome.

Faith doesn't exist without obedience. Obedience doesn't exist without faith. The obedient will love Jesus, obeying Jesus, having faith in Jesus.

\textbf{James 2:18} - But someone will say, You have faith and I have works. Show me your faith apart from your works, and I will show you my faith by my works.

\textbf{Romans 1:5} - through whom we have received grace and apostleship to bring about the \textbf{obedience of faith} for the sake of his name among all the nations, (ESV)

\textbf{Romans 16:26} - but has now been disclosed and through the prophetic writings has been made known to all nations, according to the command of the eternal God, to bring about the \textbf{obedience of faith} — (ESV)

We go from performing 'dead works' to 'faithful works'.

\textbf{Hebrews 9:14} - how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God.

\textbf{Matthew 25:21} - His master said to him, Well done, good and faithful servant. You have been faithful over a little; I will set you over much. Enter into the joy of your master.

We stop doing dead works to serve the living God, which I believe is obedience,
which is really similar to work but it's obeying. Obedience gives glory to God.

\textbf{John 13:34-35} - A new commandment I give to you, that you love one another: just as I have loved you, you also are to love one another. By this all people will know that you are my disciples, if you have love for one another. (ESV)

Obeying Jesus' commandments are not 'dead works'.

\textbf{Exodus 20:12-17} - Honor your father and your mother, that your days may be long in the land that the Lord your God is giving you. You shall not murder. You shall not commit adultery. You shall not steal. You shall not bear false witness against your neighbor. You shall not covet your neighbor's house; you shall not covet your neighbor's wife, or his male servant, or his female servant, or his ox, or his donkey, or anything that is your neighbor's.

Jesus said:

\textbf{Mark 10:19} - You know the commandments: Do not murder, Do not commit adultery, Do not steal, Do not bear false witness, Do not defraud, Honor your father and mother. (ESV)

Obeying God by following the 10 commandments properly, in truth, is not performing 'dead works'.

The Holy Spirit cleanses our hearts by faith:

\textbf{Acts 15:8-9} - And God, who knows the heart, bore witness to them, by giving them the Holy Spirit just as he did to us, and he made no distinction between us and them, having cleansed their hearts by faith.

\textbf{Hebrews 9:14} - how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God.

Service to God is obeying God through Christ's commandments. It's being a bond-servant of Christ.

Also, the following means that having faith in Jesus is tightly coupled to doing the works that Jesus did - to acting like Jesus - to obeying His commandments.

\textbf{John 14:12} - Truly, truly, I say to you, whoever believes in me will also do the works that I do; and \textbf{greater works than these will he do}, because I am going to the Father.

Whoever has faith in Jesus, the works that Jesus does, that person will do.
Pisteuo (pisteuōn) = faith.

\textbf{John 14:12} - Truly (G281 amen), truly (G281 amen), I say (G3004 lego) to you, he who believes (G4100 pisteuo) in Me, the works (G2041 ergon) that I do (G4160 poieo), he will do (G4160 poieo) also (G2548 kakeinos); and greater (G3173 megas) works than these (G3778 houtos) he will do (G4160 poieo); because (G3754 hoti) I go (G4198 poreuomai) to the Father (G3962 pater). (NASB)

\begin{verbatim}
1  :  4100  pisteuo  pist-yoo'-o
2  
3   from 4102; to have faith (in, upon, or with respect to, a person or
4   thing), i.e. credit; by implication, to entrust (especially one's
5   spiritual well-being to Christ):--believe(-r), commit (to trust), put
6   in trust with.
7   see GREEK for 4102
\end{verbatim}

If someone trusts their Lord then they do what their Lord does and has commanded.

\subsubsection{Faith is faithful, humble, and enduring - it's active and enduring faithfulness to God in humility}
\label{sec:org847d0d7}
\textbf{Psalms 31:23} - Love the LORD, all you his saints! The LORD preserves the faithful but abundantly repays the one who acts in pride. (ESV)

\subsubsection{Faith has an amount}
\label{sec:org8e1b7ca}
I think even saving faith requires an amount.
Fear of God or love for Him in obedience or thankfulness is work which comes out of belief.
But faith works, even saving faith works. Saving faith \textbf{especially} requires obedience, I think.
Faith without work doesn't exist I think because the work of God is to believe on who He has sent - Jesus.

\textbf{Exodus 14:14-16} - The Lord will fight for you, and you have only to be silent.  The Lord said to Moses, Why do you cry to me? Tell the people of Israel to go forward.  Lift up your staff, and stretch out your hand over the sea and divide it, that the people of Israel may go through the sea on dry ground.

With Lazarus - Jesus performed the miracle so the people watching could believe and have faith.
Jesus wept before he raise Lazarus from the dead, and many other people believed in Jesus and were saved, I assume.

\textbf{John 11:41-42} - So they took away the stone. And Jesus lifted up his eyes and said, Father, I thank you that you have heard me. I knew that you always hear me, but I said this on account of the people standing around, that they may believe that you sent me.

\textbf{I Corinthians 13:13} - So now faith, hope, and love abide, these three; but the greatest of these is love.

\textbf{John 11:35} - Jesus wept.

\textbf{John 11:41-42} - So they took away the stone. And Jesus lifted up his eyes and said, Father, I thank you that you have heard me. I knew that you always hear me, but I said this on account of the people standing around, that they may believe that you sent me.

And Jesus is able to save a person out of Jesus' own will, as he resurrected Lazarus.

\href{https://www.youtube.com/watch?v=49JgVR30bLA}{www.youtube.com/watch?v=49JgVR30bLA}

\textbf{John 11:43} - When He had said these things, He cried out with a loud voice, “Lazarus, come forth.”

But faith is like Peter stepping out on the water. Faith works. But I think sometimes to create faith someone just has to actually believe Jesus because Jesus performs the miracle / the work. The account of Jesus itself when it's read, and Jesus' words, are enough to inspire faith. Jesus calls persistent endurance a work. Therefore, faith comes by hearing the word of Christ.

The LORD did something similar for the Israelites when He parted the Red Sea.
The Israelites obeyed God, and their obedience led them to sure belief.
Obedience, belief and trust are all important in faith.

Revelation comes as we do what God commands us:

\textbf{John 7:17} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority. (ESV)

And I feel like we just need to start obeying God and obeying Jesus in order to be saved. Obedience is steps of faith.

\textbf{Exodus 14:14-16} - The Lord will fight for you, and you have only to be silent.  The Lord said to Moses, Why do you cry to me? Tell the people of Israel to go forward.  Lift up your staff, and stretch out your hand over the sea and divide it, that the people of Israel may go through the sea on dry ground.

\textbf{Exodus 14:21-30} - Then Moses stretched out his hand over the sea, and the Lord drove the sea back by a strong east wind all night and made the sea dry land, and the waters were divided. And the people of Israel went into the midst of the sea on dry ground, the waters being a wall to them on their right hand and on their left. The Egyptians pursued and went in after them into the midst of the sea, all Pharaoh's horses, his chariots, and his horsemen. And in the morning watch the Lord in the pillar of fire and of cloud looked down on the Egyptian forces and threw the Egyptian forces into a panic, clogging their chariot wheels so that they drove heavily. And the Egyptians said, Let us flee from before Israel, for the Lord fights for them against the Egyptians. Then the Lord said to Moses, Stretch out your hand over the sea, that the water may come back upon the Egyptians, upon their chariots, and upon their horsemen. So Moses stretched out his hand over the sea, and the sea returned to its normal course when the morning appeared. And as the Egyptians fled into it, the Lord threw the Egyptians into the midst of the sea. The waters returned and covered the chariots and the horsemen; of all the host of Pharaoh that had followed them into the sea, not one of them remained. But the people of Israel walked on dry ground through the sea, the waters being a wall to them on their right hand and on their left. Thus the Lord saved Israel that day from the hand of the Egyptians, and Israel saw the Egyptians dead on the seashore.

\textbf{Exodus 14:31} - When Israel saw the great power which the Lord had used against the Egyptians, the people feared the Lord, and they believed (H539 \textbf{'aman}) in the Lord and in His servant Moses.

\begin{verbatim}
 1  :  539  'aman
 2  
 3   a primitive root; properly, to build up or support; to foster
 4   as a parent or nurse; figuratively to render (or be) firm or
 5   faithful, to trust or believe, to be permanent or quiet;
 6   morally to be true or certain; once (Isa. 30:21;
 7   interchangeable with 541) to go to the right hand:--hence,
 8   assurance, believe, bring up, establish, + fail, be faithful
 9   (of long continuance, stedfast, sure, surely, trusty,
10   verified), nurse, (-ing father), (put), trust, turn to the
11   right.
12   see HEBREW for 0541
\end{verbatim}

\textbf{Exodus 15:2} - The Lord is my strength and my song, and he has become my salvation; this is my God, and I will praise him, my father's God, and I will exalt him.

Salvation is the gift, and faith implies an obedient heart. Works can be dead works when they're not done in faith. Faith is what justifies. But faith works. Faith requires obedience to God. Faithless works do not justify:

\textbf{Ephesians 2:8-9} - For by grace you have been saved through faith. And this is not your own doing; it is the gift of God, not a result of works, so that no one may boast. (ESV)

\subsubsection{The obedience of faith}
\label{sec:orgeac3c57}

A person must be at least willing to do His will - obedience is the essence of faith:

\textbf{John 7:17} - If anyone is willing to do His will, he will know of the teaching, whether it is of God or whether I speak from Myself.

I think \textbf{Ephesians 2:8-9} when it says 'through faith' doesn't actually exclude obedience (obeying Jesus), because I think obedience is intrinsic to faith.

\textbf{Exodus 14:14-16} - The Lord will fight for you, and you have only to be silent.  The Lord said to Moses, Why do you cry to me? Tell the people of Israel to go forward.  Lift up your staff, and stretch out your hand over the sea and divide it, that the people of Israel may go through the sea on dry ground.

When it says "not a result of works", I believe that something more like, even if works were tied into the faith, it's by grace. If a person's saving faith included works then that is fine.

Faith-in-God is hearing God's word and believing it, and even acting on it, or at least the readiness to act on it.
A person may act on faith in their heart by arriving at a conviction to the point where a person makes it truth for them.
Then, like Peter stepping out on the water, or like the woman at the well going in to town to tell people about Jesus, or turning from sinful things, it produces more obedience.

\textbf{Matthew 14:27-32} - But immediately Jesus spoke to them, saying, Take heart; it is I. Do not be afraid. And Peter answered him, Lord, if it is you, \textbf{command} me to come to you on the water. He said, Come. So Peter \textbf{got out of the boat and walked on the water and came to Jesus}. But when he saw the wind, he was afraid, and beginning to sink he cried out, Lord, save me. Jesus immediately reached out his hand and took hold of him, saying to him, O you of little faith, why did you doubt? And when they got into the boat, the wind ceased.

And there is an amount of faith, and true belief is all that's required to be saved, but Faith is so tightly linked to Obedience like Faith is linked to Hope. True belief is enough because it accepts what Jesus says, as a child believes. But I don't think this discounts that the same faith continues and increases through obedience.

Some people never seem to arrive:

\textbf{II Timothy 3:6-9} - For among them are those who creep into households and capture weak women, burdened with sins and led astray by various passions, always learning and \uline{never able to arrive at a knowledge of the truth}. Just as Jannes and Jambres opposed Moses, so these \uline{men also oppose the truth, men corrupted in mind and disqualified regarding the faith}. But they will not get very far, for their folly will be plain to all, as was that of those two men.

But the ones who do arrive actually \uline{follow the teaching}:

\textbf{II Timothy 3:10-13} - You, however, have \uline{followed my teaching, my conduct, my aim in life, my faith, my patience, my love, my steadfastness, my persecutions and sufferings that happened to me} at Antioch, at Iconium, and at Lystra—which persecutions I endured; yet from them all the Lord rescued me. Indeed, all who desire to live a godly life in Christ Jesus will be persecuted, while evil people and impostors will go on from bad to worse, deceiving and being deceived.

Peter demonstrated obedience. A changed heart is essential to be saved, I think, because it must produce more obedience.

\textbf{II Corinthians 10:5-6} - We destroy arguments and every lofty opinion raised against the knowledge of God, and take every thought captive to obey Christ, being ready to punish every disobedience, when your obedience is complete.

Hebrews describes faith as the hope and conviction we need to draw near to God because we need to believe that He exists and that He rewards those who seek him.

\textbf{Hebrews 11:1} - Now faith is the assurance of things hoped for, the conviction of things not seen.

\textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God must believe that he exists and that he rewards those who seek him.

The whole chapter of Hebrews 11 also describes many 'acts' of faith.

\textbf{I Corinthians 13:13} - So now faith, hope, and love abide, these three; but the greatest of these is love.

\textbf{1 Timothy 1:5} -  The aim of our charge is love that issues from a pure heart and a good conscience and a sincere faith.  (ESV)

\subsubsection{Faith requires obedience}
\label{sec:org9f88fdd}
\textbf{Luke 8:21} - But He answered and said to them, “My mother and My brothers are these who hear the word of God and do it.”

\begin{itemize}
\item The Holy Spirit is given to those who obey Jesus.
\item The Holy Spirit is given to those who have faith in Jesus.
\end{itemize}

You can't have faith without obedience.

\textbf{Acts 5:32} - And we are witnesses to these things, and so is \textbf{the Holy Spirit, whom God has given to those who obey him}. (ESV)

\textbf{Galatians 3:14} - so that in Christ Jesus the blessing of Abraham might come to the Gentiles, so that we might \textbf{receive the promised Spirit through faith}. (ESV)

\begin{verbatim}
 1  Faith-in-God = Hope-from/in-God * Work/Love
 2  
 3  Hope-from/in-God = Belief(believing God) * Truth(God's word is truth)
 4  
 5  Work/Love = Obedience * Faithfulness * Fear-of-God * Response-of-love-to-Jesus * Patient-Endurance(time)
 6  
 7  Obedience = Submitting to the Righteousness of God * Turning from sin, loving, showing mercy, etc.
 8  
 9  Fear-of-God = e.g. The poor in spirit recognise their need of God's mercy and tremble at His Word: "beat his breast, saying, God, be merciful to me, a sinner!"
10  
11  Response-of-love-to-Jesus = e.g. praise, thankfulness, obeying His commandments
12  
13  L ∝ f
14  Love is proportional-to the baggage which has been forgiven
15  Love ∝ forgiven-baggage
16  
17  Obedience ∝ Love
18  
19  F = H * L
20  Faith = Hope * Love
21  
22  Faith-in-God when tested by God is found to be true Faith in God.
23  Faith-in-God must submit to the Righteousness of God through faith in Jesus Christ,
24  Jesus Christ having paid the price of sin, enabling a relationship with God.
\end{verbatim}

Even after arriving at the true knowledge through obedience, faith is further supplemented/nourished/aided by virtue, knowledge, self-control, steadfastness, godliness, brotherly affection and love:

\textbf{II Peter 1:3-7} - His divine power has granted to us all things that pertain to life and godliness, through the knowledge of him who called us to his own glory and excellence, by which he has granted to us his precious and very great promises, so that through them you may become partakers of the divine nature, having escaped from the corruption that is in the world because of sinful desire. For this very reason, make every effort to \uline{supplement your faith with virtue}, and virtue with knowledge, and knowledge with self-control, and self-control with steadfastness, and steadfastness with godliness, and godliness with brotherly affection, and brotherly affection with love. (ESV)

The true knowledge of Jesus grants us everything pertaining to life and godliness, allowing us to partake in the divine nature. We should then reinforce the divine nature with such things:

\textbf{II Peter 1:3-4} - seeing that His divine power has granted to us everything pertaining to life and godliness, \textbf{through the true knowledge} of Him who called us by His own glory and excellence. For by these He has granted to us His precious and magnificent promises, so that by them you may become partakers of the divine nature, having escaped the corruption that is in the world by lust. (NASB)

Because, having \textbf{arrived} at the true knowledge of Jesus, we are partakers of the divine nature, in order to be fruitful we should supply to our faith those qualities:

\textbf{II Peter 1:8} - For \textbf{if these qualities are yours and are increasing}, they render you \uline{neither useless nor unfruitful} in the \uline{true knowledge} (G1922 \textbf{epignosis}) of our Lord Jesus Christ.

\begin{verbatim}
1  :  1922  epignosis  ep-ig'-no-sis
2  
3   from 1921; recognition, i.e. (by implication) full discernment,
4   acknowledgement:--(ac-)knowledge(-ing, - ment).
5   see GREEK for 1921
\end{verbatim}

Work/Love:
\begin{itemize}
\item \textbf{II John 1:6} - And this is love, that we walk according to his commandments; this is the commandment, just as you have heard from the beginning, so that you should walk in it. (ESV)
\item \textbf{John 15:12} - This is my commandment, that you love one another as I have loved you.
\begin{itemize}
\item We must love in the same \textbf{way} Jesus has loved us - sacrificially, obedient to God - showing God's truthfulness, serving others.
\end{itemize}
\item \textbf{Matthew 19:17} And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments.
\item \textbf{Matthew 22:37-40} - And he said to him, You shall love the Lord your God with all your heart and with all your soul and with all your mind. This is the great and first commandment. And a second is like it: You shall love your neighbor as yourself. On these two commandments depend all the Law and the Prophets.
\item \textbf{Mark 10:19} You know the commandments: Do not murder, Do not commit adultery, Do not steal, Do not bear false witness, Do not defraud, Honor your father and mother.
\item \textbf{Mark 12:28} And one of the scribes came up and heard them disputing with one another, and seeing that he answered them well, asked him, Which commandment is the most important of all?
\item \textbf{Mark 12:31} The second is this: You shall love your neighbor as yourself. There is no other commandment greater than these.
\item \textbf{Luke 1:6} And they were both righteous before God, walking blamelessly in all the commandments and statutes of the Lord.
\item \textbf{John 12:49-50} For I have not spoken on my own authority, but the Father who sent me has himself given me a commandment—what to say and what to speak. And I know that his commandment is eternal life. What I say, therefore, I say as the Father has told me.
\begin{itemize}
\item Jesus' commandments are consistent with the rest of God's commandments.
\end{itemize}
\item \textbf{John 13:34} A new commandment I give to you, that you love one another: just as I have loved you, you also are to love one another.
\item \textbf{John 14:15} If you love me, you will keep my commandments.
\item \textbf{John 14:21} Whoever has my commandments and keeps them, he it is who loves me. And he who loves me will be loved by my Father, and I will love him and manifest myself to him.
\item \textbf{John 15:10} If you keep my commandments, you will abide in my love, just as I have kept my Father's commandments and abide in his love.
\item \textbf{John 15:12} This is my commandment, that you love one another as I have loved you.
\end{itemize}

Fear-of-God:
\begin{itemize}
\item \textbf{Romans 4:5} - And to the one who does not work but trusts him who justifies the ungodly, his faith is counted as righteousness,
\end{itemize}

AMEN!! But this doesn't mean the other elements of working faith can't play a part.

Without love, faith is dead:

\textbf{I Corinthians 13:1} - If I speak in the tongues of men and of angels, but have not love, I am a noisy gong or a clanging cymbal.

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.} (ESV)

\texttt{pisteuo} is obedient faith as it is the verb for faith (pistis).

\textbf{James 2:22-26} - You see that faith was active along with his works, and faith was completed by his works; and the Scripture was fulfilled that says, Abraham believed God, and it was counted to him as righteousness-and he was called a friend of God. You see that a person is justified by works and not by faith alone. And in the same way was not also Rahab the prostitute justified by works when she received the messengers and sent them out by another way? For as the body apart from the spirit is dead, so also faith apart from works is dead. (ESV)

Without faith, work is dead. Whatever actions we make outside of faith is sin:

\textbf{Romans 14:23} - But whoever has doubts is condemned if he eats, because the eating is not from faith. For whatever does not proceed from faith is sin.

But the work of God is to believe in whom He has sent. So even believing in Jesus is work that is done in faith:

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.} (ESV)

Deeds, love, faith, service and perseverance are not mutually exclusive. They're all important to God and overlap:

\textbf{Revelation of John 2:19} - ‘I know your deeds, and your love and faith and service and perseverance, and that your deeds of late are greater than at first.

There is a relation here:

\textbf{I Corinthians 13:7} - Love bears all things, believes all things, hopes all things, endures all things.

\textbf{1 Timothy 1:5} -  The aim of our charge is love that issues from a pure heart and a good conscience and a sincere faith.  (ESV)

\textbf{I Corinthians 13:13} - So now faith, hope, and love abide, these three; but the greatest of these is love.

Belief and action are like a vector.

\begin{verbatim}
 1  
 2         Faith plane                 __
 3         Serving God plane            /|
 4                                     /                       From past
 5                                    /                          baggage          o     _
 6  Minimum        __              __/                         persecuting       /       /|
 7  Initial         /| 1x Love      /|    2x Love               Jesus           /       /
 8  Belief         /               /                           to receiving    /   →   /
 9    _           /               /                             forgiveness   /       /
10    /|         /               /                             and loving   |/_      /
11   o          o               o                                Jesus              o
12  
13  --------------------------------------------+-------------+----------------------------
14                                              |  Dead faith |    Impossible to be
15        Faithless plane                       |             |     simultaneously
16        Serving yourself plane                |      o      |
17        Justifying yourself plane             |             |   yoked to God  _
18             __                               | disobedient |  (led by)       /|
19              /| Dead works                   +-------------+                /
20             /                                              |    while      o
21            /                                               |              /
22           /            These are entirely worthless        |            |/_
23          x                                                 |  (led by)
24                                                            |   yoked to money
\end{verbatim}

Faith has 'substance/magnitude' and may be described as a vector:
\begin{itemize}
\item The origin of hope/belief is represented by the point.
\begin{itemize}
\item On the Faith plane, positive magnitude comes from trust in God
\end{itemize}
\item Hope-from/in-God is the direction.
\item Work/Love/Obedience is the magnitude.
\end{itemize}

I want to be clear, having faith in Jesus Christ is not dead faith.
Dead faith is precisely not having faith in Jesus Christ.

An obedient heart is required for it to not be 'dead faith'.

\textbf{John 7:17} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.

Faith in the wrong thing:
\begin{itemize}
\item On the Faithless plane, positive magnitude comes from trust in something else, i.e. money or self
\end{itemize}

But it's God that tests the faith, and God that justifies. That's why I don't like making an assertion on the exact way that God justifies, because God is the justifier.

\textbf{Galatians 5:5} - For through the Spirit, by faith, we ourselves eagerly \textbf{wait for the hope of righteousness}.

\textbf{Galatians 5:18} - But if you are led by the Spirit, you are not under the law.

\textbf{John 6:63} - It is the Spirit who gives life; the flesh is of no avail. The words that I have spoken to you are spirit and life.

\textbf{John 8:12} - Again Jesus spoke to them, saying, I am the light of the world. Whoever follows me will not walk in darkness, but \textbf{will have the light of life}.

Righteousness is the free gift to be received through obedience:

\textbf{Romans 5:17} - If, because of one man's trespass, death reigned through that one man, much more will those who receive the abundance of grace and the \textbf{free gift of righteousness} reign in life through the one man Jesus Christ.

Jesus made the Way - He \textbf{is} the Way:

\textbf{Romans 5:18-19} - Therefore, as one trespass led to condemnation for all men, so one act of righteousness \uline{leads to} \textbf{justification and life} for all men. For as by the one man's disobedience the many were made sinners, so by the one man's obedience \textbf{the many} will be made righteous.

The Way is \uline{available} to walk for everyone who is \uline{obedient}.

Doing the will of Father God:
\begin{itemize}
\item obedience to Jesus leads to righteousness - obedience/faith to receive the gift, even of the Spirit
\begin{itemize}
\item led by the Spirit, obeying Jesus' words
\begin{itemize}
\item being led by the Spirit and obeying Jesus' words are in alignment and do not contradict
\end{itemize}
\end{itemize}
\item slaves to righteousness leading to sanctification
\begin{itemize}
\item at its end, eternal life
\end{itemize}
\item sanctification leading to eternal life
\begin{itemize}
\item sanctification by the Spirit and belief in the truth
\item knowledge of the truth
\item justification
\end{itemize}

\item \textbf{Romans 6:13-23} - Do not present your members to sin as instruments for unrighteousness, but present yourselves to God as those who have been brought from death to life, and your members to God as instruments for righteousness.  For sin will have no dominion over you, since you are not under law but under grace.  What then? Are we to sin because we are not under law but under grace? By no means!  Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of \textbf{obedience, which leads to righteousness}?  But thanks be to God, that you who were once slaves of sin have become \textbf{obedient from the heart to the standard of teaching to which you were committed}, and, having been set free from sin, have become \textbf{slaves of righteousness}.  I am speaking in human terms, because of your natural limitations. For just as you once presented your members as slaves to impurity and to lawlessness leading to more lawlessness, so now present your members as slaves to righteousness leading to sanctification.  When you were slaves of sin, you were free in regard to righteousness.  But what fruit were you getting at that time from the things of which you are now ashamed? The end of those things is death.  But now that you have been \uline{set free from sin and have become slaves of God, the fruit you get leads to sanctification and its end, eternal life.  For the wages of sin is death, but the free gift of God is eternal life in Christ Jesus our Lord}.
\end{itemize}

The love of the truth must be received and accepted to be saved:

\textbf{II Thessalonians 2:10} - and with all the deception of wickedness for those who perish, because they did not receive the love of the truth so as to be saved. (NASB)

People will trust in what is false:

\textbf{II Thessalonians 2:11} - For this reason God will send upon them a deluding influence so that they will believe (G4100 \textbf{pisteuo}) what is false (G5579 pseudos), (NASB)

Those people who took pleasure in unrighteousness may be condemned:

\textbf{II Thessalonians 2:12} - in order that all may be condemned who did not believe (G4100 \textbf{pisteuo}) the truth but had pleasure in unrighteousness.

But God chose some to be saved through sanctification by the Spirit and belief in the truth:

\textbf{II Thessalonians 2:13} - But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through \textbf{sanctification by the Spirit} and \textbf{belief in the truth}.

So that they may be obtain the glory of our Lord Jesus Christ:

\textbf{II Thessalonians 2:14} - To this he called you through our gospel, so that you may \textbf{obtain the glory of our Lord Jesus Christ}.

We live by the Spirit:

\textbf{Ephesians 2:18} - For through him we both have access in one Spirit to the Father.

We are made alive by the Spirit so we should walk by the Spirit:

\textbf{Galatians 5:25} - If we live by the Spirit, let us also walk by the Spirit.

If we walk by the Spirit, we will not gratify the desires of the flesh:

\textbf{Galatians 5:16} - But I say, walk by the Spirit, and you will not gratify the desires of the flesh.

There are sinning people that alienate themselves from the life of God because of the ignorance that is in them, due to their hardness of heart:

\textbf{Ephesians 4:18-29} - They are darkened in their understanding, alienated from the life of God because of the ignorance that is in them, due to their hardness of heart. They have become callous and have given themselves up to sensuality, greedy to practice every kind of impurity.

But having been taught in Jesus, the truth which is in Jesus, to put off the old self and to be renewed in the spirit our our mind, and put on the new self, created after the likeness of God in true righteousness:

\textbf{Ephesians 4:21-24} - assuming that you have heard about him and were taught in him, as the truth is in Jesus, to put off your old self, which belongs to your former manner of life and is corrupt through deceitful desires, and to be renewed in the spirit of your minds, and to put on the new self, created after the likeness of God in true righteousness and holiness.

Speak the truth and do not sin:

\textbf{Ephesians 4:25-27} - Therefore, having put away falsehood, let each one of you speak the truth with his neighbor, for we are members one of another. Be angry and do not sin; do not let the sun go down on your anger, and give no opportunity to the devil.

\textbf{Ephesians 1:17} - that the God of our Lord Jesus Christ, the Father of glory, may give you a spirit of wisdom and of revelation in the knowledge of him,

The outcome of being set free from sin and becoming a slave to God is receiving the gift of eternal life:

\textbf{Romans 8:33} -  Who shall bring any charge against God's elect?  It is God who justifies.  (ESV)

\textbf{Romans 6:22-23} - But now that you have been set free from sin and have become slaves to God, the fruit you reap leads to holiness, and the outcome is eternal life. For the wages of sin is death, but the gift of God is eternal life in Christ Jesus our Lord. (BSB)

A person must \textbf{do} the will \textbf{of Father God} (not their own will); They must be obedient.
Faith and obedience are inseparable.

To be fruitful, a person must be further obedient after arriving at the knowledge of the truth and supplement their faith with Christian virtues:

\textbf{II Peter 1:8} - For \textbf{if these qualities are yours and are increasing}, they render you \uline{neither useless nor unfruitful} in the \uline{true knowledge} (G1922 \textbf{epignosis}) of our Lord Jesus Christ.

\section{Jesus has immortality and gives eternal life}
\label{sec:orgfa4c632}
We must take hold of the eternal life to which we are called.
We made the confession to eternal life, and we must now fight the good fight of the faith.

\textbf{I Timothy 6:11-16} - But as for you, O man of God, flee these things. Pursue righteousness, godliness, faith, love, steadfastness, gentleness.  Fight the good fight of the faith. Take hold of the eternal life to which you were called and about which you made the good confession in the presence of many witnesses.  I charge you in the presence of God, who gives life to all things, and of Christ Jesus, who in his testimony before Pontius Pilate made the good confession, to \uline{keep the commandment unstained and free from reproach until the appearing of our Lord Jesus Christ}, which he will display at the proper time—he who is the blessed and only Sovereign, the King of kings and Lord of lords, who alone has immortality, who dwells in unapproachable light, whom no one has ever seen or can see. To him be honor and eternal dominion. Amen.

\textbf{Matthew 7:21-23} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven. On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name? And then will I declare to them, I never knew you; depart from me, you workers of lawlessness. (ESV)

So those people doing works in Jesus' name were still disobedient, similar to the following example:

\textbf{Leviticus 10:1-2} - Now Nadab and Abihu, the sons of Aaron, each took his censer and put fire in it and laid incense on it and offered unauthorized fire before the Lord, which he had not commanded them. And fire came out from before the Lord and consumed them, and they died before the Lord.


\textbf{John 11:41-42} - So they took away the stone. And Jesus lifted up his eyes and said, Father, I thank you that you have heard me. I knew that you always hear me, but I said this on account of the people standing around, that they may believe that you sent me.

The works have to be the will of Father God. Initially, and ongoing, this is believing in Him whom He has sent. It's believing in Jesus, and continuing to believe in Jesus, putting your trust in Jesus, having faith in Jesus, obeying Jesus and submitting to the righteousness of God.

\textbf{John 6:29} - Jesus answered them, This is the work of God, that you \textbf{believe in him whom he has sent}. (ESV)

Being a servant of Christ from the heart is doing the will of God.

\textbf{Ephesians 6:6} - not by the way of eye-service, as people-pleasers, but as \textbf{servants of Christ}, doing the will of God from the heart,

Repenting from sin is doing the will of God.

\textbf{I Thessalonians 4:3} - For this is the will of God, your sanctification: that you abstain from sexual immorality;

Doing good is doing the will of God.

\textbf{I Peter 2:15} - For this is the will of God, that by doing good you should put to silence the ignorance of foolish people.

Doing the will of God, a person will have eternal life.

\textbf{I John 2:17} - And the world is passing away along with its desires, but whoever does the will of God abides forever. (ESV)

\subsection{Do not doubt, and believe that you have received it, even acting in a way in which it is already received}
\label{sec:org11d8ecd}
\textbf{James 1:1-5} - James, a bond-servant of God and of the Lord Jesus Christ, To the twelve tribes who are dispersed abroad: Greetings.  Consider it all joy, my brethren, when you encounter various trials, knowing that the testing of your faith produces endurance.  And let endurance have its perfect result, so that you may be perfect and complete, lacking in nothing.  But if any of you lacks wisdom, let him ask of God, who gives to all generously and without reproach, and it will be given to him.

The one who does not doubt is unwavering and is not tossed around by the sea.
Therefore, it's an ongoing thing.

\textbf{James 1:6} - But he must ask in faith (G4102 \textbf{pistis}) without any doubting (G1252 \textbf{diakrino}), for the one who doubts (G1252 diakrino) is like the surf of the sea, driven and tossed by the wind. (NASB)

Faith begins and continues:
\begin{itemize}
\item no doubting
\item no wavering
\item no withdrawing
\item no hesitating
\end{itemize}

\textbf{Mark 11:22-23} - And Jesus answered them, Have faith in God. Truly, I say to you, whoever says to this mountain, Be taken up and thrown into the sea, and does not doubt in his heart, but believes that what he says \uline{will come to pass}, it will be done for him.

Walk in what you have asked for in prayer:

\textbf{Mark 11:24} - Therefore I tell you, whatever you ask in prayer, believe that you have received it, and it \uline{will be} yours.

It's important to forgive others in order to move forward, because unforgiveness I think may inhibit moving into what you have asked for in prayer:

\textbf{Mark 11:25} - And whenever you stand praying, forgive, if you have anything against anyone, so that your Father also who is in heaven may forgive you your trespasses.

We must receive Jesus' words, walk in them and come to \textbf{know in truth} (we must truly know) that Jesus came from God.

\textbf{John 17:8} - For I have given them the words that you gave me, and they have received them and have \textbf{come to know in truth that I came from you}; and they have believed that you sent me.

Therefore, we should obey Jesus and arrive at the truth. Obedience is a part of faith. Like Abraham obeying God, or like Israel crossing through the Red Sea, it's obedience which leads to sure belief.
And the obedience doesn't end.

\textbf{John 8:31-32} - So Jesus was saying to those Jews who had believed Him, “If you \textbf{continue in My word}, then you are truly disciples of Mine; and \textbf{you will know the truth}, and the truth will make you free.” (NASB)

\subsection{We work as servants of God, and the foundation of our work must be Jesus Christ}
\label{sec:org9eaba65}
\textbf{I Corinthians 3:9-15} - For we are God's fellow workers. You are God's field, God's building.  According to the grace of God given to me, like a skilled master builder I laid a foundation, and someone else is building upon it. Let each one take care how he builds upon it.  For no one can lay a foundation other than that which is laid, which is Jesus Christ.  Now if anyone builds on the foundation with gold, silver, precious stones, wood, hay, straw— each one's work will become manifest, for the Day will disclose it, because it will be revealed by fire, and the fire will test what sort of work each one has done.  If the work that anyone has built on the foundation survives, he will receive a reward.  If anyone's work is burned up, he will suffer loss, though he himself will be saved, but only as through fire.

\subsubsection{For Christ}
\label{sec:org0cf703a}
\textbf{I Corinthians 4:9-10} - For I think that God has exhibited us apostles as last of all, like men sentenced to death, because we have become a spectacle to the world, to angels, and to men. We are fools for Christ's sake, but you are wise in Christ. We are weak, but you are strong. You are held in honor, but we in disrepute.

\subsection{Love}
\label{sec:orgd2ebe0b}
\begin{itemize}
\item \href{https://www.youtube.com/watch?v=d2FKSxaa76w\&ab\_channel=FatherSpyridon}{Love without God's grace is not God's love}
\begin{itemize}
\item It's sacrificial
\begin{itemize}
\item Not what we give, but how we give
\item The condition of the heart is what God will judge
\end{itemize}
\item It's cheerful obedience to God, cheerful obedience to Jesus
\end{itemize}
\end{itemize}

\subsubsection{Love is doing what Jesus has said for us to do. Love is following the commandments}
\label{sec:org343320f}
\textbf{II John 1:6} - And this is love, that we walk according to his commandments; this is the commandment, just as you have heard from the beginning, so that you should walk in it. (ESV)

\textbf{2 Corinthians 9:6-7} - The point is this: whoever sows sparingly will also reap sparingly, and whoever sows bountifully will also reap bountifully.  Each one must give as he has made up his mind, not reluctantly or under compulsion, for God loves a \textbf{cheerful} giver.  (ESV)

\subsubsection{Almsgiving}
\label{sec:orgc329ae2}
\textbf{Acts 10:2} - a devout man and one who feared God with all his household, and gave many alms to the Jewish people and prayed to God continually.  About the ninth hour of the day he clearly saw in a vision an angel of God who had just come in and said to him, “Cornelius!” And fixing his gaze on him and being much alarmed, he said, “What is it, Lord?” And he said to him, “Your prayers and alms have ascended as a memorial before God.

\subsubsection{The person who loves their brother abides in light}
\label{sec:org0982748}
\textbf{1 John 2:10} - Whoever loves his brother abides in the light, and in him there is no cause for stumbling.  (ESV)

\subsection{Justifying faith should result in going from it being impossible to obey God to possible}
\label{sec:orga1d9ba7}
All things are possible for God.
Without God we can't have eternal life, because we need a relationship with Jesus.

We need to be able to fulfill the requirement
of the law, to love God and one's neighbour and at the same time
submit to the righteousness of God through faith in Jesus
Christ and to do the will of Father God in
order to have eternal life. It's impossible without God's help.

\subsubsection{Faith submits to God's will}
\label{sec:org0d87824}
\textbf{Mark 14:36} - And he said, Abba, Father, all things are possible for you. Remove this cup from me. Yet not what I will, but what you will.

Learning God's will through submission to God's Word.

\textbf{Ephesians 5:24} - Now as the church submits to Christ, so also wives should submit in everything to their husbands.

\textbf{James 4:7} - Submit yourselves therefore to God. Resist the devil, and he will flee from you.

All things are possible for those who have faith.

\textbf{Mark 9:22-27} - It has often thrown him both into the fire and into the water to destroy him. But if You can do anything, take pity on us and help us!” And Jesus said to him, “‘If You can?’ All things are possible to him who believes (G4100 \textbf{pisteuo}).” Immediately the boy’s father cried out and said, “I do believe; help my unbelief.” When Jesus saw that a crowd was rapidly gathering, He rebuked the unclean spirit, saying to it, “You deaf and mute spirit, I command you, come out of him and do not enter him again.” After crying out and throwing him into terrible convulsions, it came out; and the boy became so much like a corpse that most of them said, “He is dead!” But Jesus took him by the hand and raised him; and he got up.

\textbf{Matthew 17:20} - He said to them, Because of your little faith. For truly, I say to you, if you have faith like a grain of mustard seed, you will say to this mountain, Move from here to there, and it will move, and nothing will be impossible for you.

\textbf{Matthew 19:26} - But Jesus looked at them and said, With man this is impossible, but with God all things are possible.

\textbf{Mark 10:27} - Jesus looked at them and said, With man it is impossible, but not with God. For all things are possible with God.

\textbf{Luke 1:37} - For nothing will be impossible with God.

\textbf{Luke 18:27} - But he said, What is impossible with men is possible with God.

It's impossible to please God without faith, but with faith all things are possible.

\textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God must believe that he exists and that he rewards those who seek him.

\subsubsection{The Mosaic law doesn't help people to keep the law. It doesn't save - it only condemns or justifies. Only Jesus saves, clean us up and helps us to fulfill the requirement of the law}
\label{sec:orgfacef63}

\textbf{Acts 13:38-39} - Therefore let it be known to you, brethren, that through (G1223 \textbf{dia}) Him forgiveness (G859 aphesis) of sins is proclaimed to you, and through (G1722 en) Him everyone who believes (G4100 \textbf{pisteuo}) is freed (G1344 dikaioo) from all things, from which you could not be freed through the Law of Moses. (NASB)

Due to Jesus, forgiveness is proclaimed:

\begin{verbatim}
1  :  1223  dia  dee-ah'
2  
3   a primary preposition denoting the channel of an act; through (in very
4   wide applications, local, causal, or occasional):--after, always,
5   among, at, to avoid, because of (that), briefly, by, for (cause) ...
6   fore, from, in, by occasion of, of, by reason of, for sake, that,
7   thereby, therefore, X though, through(-out), to, wherefore, with
8   (-in). In composition it retains the same general importance.
\end{verbatim}

Forgiveness: Pardon, freedom.

\begin{verbatim}
1  :  859  aphesis  af'-es-is
2  
3   from 863; freedom; (figuratively) pardon:--deliverance, forgiveness,
4   liberty, remission.
5   see GREEK for 863
\end{verbatim}

Together with him, everyone who has faith (continues in faith) in him is freed from all things from which you could not be freed through the Law of Moses:

\begin{verbatim}
 1  :  1722  en  en
 2  
 3   a primary preposition denoting (fixed) position (in place, time or
 4   state), and (by implication) instrumentality (medially or
 5   constructively), i.e. a relation of rest (intermediate between 1519
 6   and 1537); "in," at, (up-)on, by, etc.:--about, after, against, +
 7   almost, X altogether, among, X as, at, before, between, (here-)by (+
 8   all means), for (... sake of), + give self wholly to, (here-)in(-to,
 9   -wardly), X mightily, (because) of, (up-)on, (open-)ly, X outwardly,
10   one, X quickly,
11   X shortly, (speedi-)ly, X that, X there(-in, -on),
12   through(-out), (un-)to(-ward), under, when, where(-with), while,
13   with(-in). Often used in compounds, with substantially the same
14   import; rarely with verbs of motion, and then not to indicate
15   direction, except (elliptically) by a separate (and different)
16   preposition.
\end{verbatim}

Faith is how we receive the propitiation by His blood. God justifies the one who \textbf{has} (continues having) faith in Jesus. The law of faith is what we keep:

\textbf{Romans 3:20-27} - For by works of the law no human being will be justified in his sight, since through the law comes knowledge of sin. But now the righteousness of God has been manifested apart from the law, although the Law and the Prophets bear witness to it— the righteousness of God through faith in Jesus Christ for all who believe. For there is no distinction: for all have sinned and fall short of the glory of God, and are justified by his grace as a gift, through the redemption that is in Christ Jesus, whom God put forward as a propitiation by his blood, \textbf{to be received by faith}. This was to show God's righteousness, because in his divine forbearance he had passed over former sins. It was to show his righteousness at the present time, so that he might be just and the justifier of the one who has faith in Jesus. Then what becomes of our boasting? It is excluded. By what kind of law? By a law of works? No, but by the law of faith.

Yes, the requirement of the \textbf{law} might be fulfilled in us, who do something i.e. walk according to the spirit.

\textbf{Romans 8:4} - in order that the righteous requirement of the law might be fulfilled in us, who walk not according to the flesh but according to the Spirit.

The mind set on the spirit submits to the law.

\textbf{Romans 8:5-7} - For those who live according to the flesh set their minds on the things of the flesh, but those who live according to the Spirit set their minds on the things of the Spirit.  To set the mind on the flesh is death, but to set the mind on the Spirit is life and peace.  For the mind that is set on the flesh is hostile to God, for it does not submit to God's law; indeed, it cannot.

But the Spirit helps us to put to death the deeds of the flesh.

\textbf{Galatians 5:19} - Now the works of the flesh are evident: sexual immorality, impurity, sensuality,

\textbf{Romans 8:10-13} - But if Christ is in you, although the body is dead because of sin, the Spirit is life because of righteousness. If the Spirit of him who raised Jesus from the dead dwells in you, he who raised Christ Jesus from the dead will also give life to your mortal bodies through his Spirit who dwells in you. So then, brothers, we are debtors, not to the flesh, to live according to the flesh. For if you live according to the flesh you will die, but if by the Spirit you put to death the deeds of the body, you will live.

So we still must/should stop sinning after getting born-again, but the Holy Spirit helps us to do that.
God saves us from sin by giving us immediate justification through faith to be in relationship with Him, plus the strength to stop sinning.

\textbf{II Peter 2:2-4} - And many will follow their sensuality, and because of them \uline{the way of truth} will be blasphemed. And in their greed they will exploit you with false words. Their condemnation from long ago is not idle, and their destruction is not asleep. For if God did not spare angels when they sinned, but cast them into hell and committed them to chains of gloomy darkness to be kept until the judgment;

\textbf{II Peter 2:19-20} - They promise them freedom, but they themselves are slaves of corruption. For \uline{whatever overcomes a person, to that he is enslaved}. For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first.

Therefore, the way of truth involves following Jesus and putting a stop to sin.

\subsubsection{With God, following the 10 commandments and to love God and our neighbour is possible}
\label{sec:orgf955be2}

\textbf{Matthew 19:16-26} - And behold, a man came up to him, saying, Teacher, what good deed must I do to have eternal life? And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me. When the young man heard this he went away sorrowful, for he had great possessions. And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. When the disciples heard this, they were greatly astonished, saying, Who then can be saved? But Jesus looked at them and said, With man this is impossible, but with God all things are possible.

The guy was still coveting his possessions. To find life, one needs to let go of covetousness.

\begin{itemize}
\item \textbf{Luke 12:15} - And he said to them, Take care, and be on your guard against all covetousness, for one's life does not consist in the abundance of his possessions. (ESV)
\end{itemize}

\subsection{Justifying faith should result in going from disobedient to obedient}
\label{sec:orgabc0bc2}
\textbf{Colossians 1:21} - And you, who once were alienated and hostile in mind, doing evil deeds,

\textbf{II Corinthians 10:5-6} - We destroy arguments and every lofty opinion raised against the knowledge of God, and take every thought captive to obey Christ, being ready to punish every disobedience, when your obedience is complete.

\textbf{Ephesians 2:2} - in which you once walked, following the course of this world, following the prince of the power of the air, the spirit that is now at work in the sons of disobedience—

\textbf{Ephesians 5:6} - Let no one deceive you with empty words, for because of these things the wrath of God comes upon the sons of disobedience.

Now obeying God is more than just believing, it's obeying (which is proportional to the magnitude of the faith).

Understand that the ones who remained in the boat and did not step out onto the water did not have enough faith to walk on water.

\textbf{Matthew 14:27-32} - But immediately Jesus spoke to them, saying, Take heart; it is I. Do not be afraid. And Peter answered him, Lord, if it is you, \textbf{command} me to come to you on the water. He said, Come. So Peter \textbf{got out of the boat and walked on the water and came to Jesus}. But when he saw the wind, he was afraid, and beginning to sink he cried out, Lord, save me. Jesus immediately reached out his hand and took hold of him, saying to him, O you of little faith, why did you doubt? And when they got into the boat, the wind ceased.

Fear made them disobedient. They had only a small amount of faith.

\textbf{Hebrews 2:2} - For since the message declared by angels proved to be reliable and every transgression or disobedience received a just retribution,

\textbf{Hebrews 9:14} - how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God.

\subsection{Obedience is essential to justifying faith}
\label{sec:orgcecd22d}
Abraham's \uline{obedience} which he had as part of his faith led him to \uline{obey}:

\textbf{Hebrews 11:8} - By faith Abraham obeyed when he was called to go out to a place that he was to receive as an inheritance.  And he went out, not knowing where he was going. (ESV)

\textbf{Hebrews 4:6} - Since therefore it remains for some to enter it, and those who formerly received the good news failed to enter because of disobedience,

\textbf{Hebrews 4:11} - Let us therefore strive to enter that rest, so that no one may fall by the same sort of disobedience.

And \uline{willing} to do the will of God must become '\textsubscript{doing}\_'.

\textbf{I John 2:17} - And the world is passing away along with its desires, but \textbf{whoever does the will of God abides forever}.

\textbf{John 7:17} - If anyone is willing to do His will, he will know of the teaching, whether it is of God or whether I speak from Myself.

\texttt{pisteuo = to have faith upon}

\textbf{John 3:36} - Whoever believes (G4100 \textbf{pisteuo}) in the Son has eternal life; whoever does not \textbf{obey} the Son shall not see life, but the wrath of God remains on him. (ESV)

\textbf{John 3:16} - "For God so loved (G25 agapao) the world (G2889 kosmos), that He gave His only (G3439 monogenes) begotten (G3439 monogenes) Son (G5207 huios), that whoever believes (G4100 pisteuo) in Him shall not perish, but have eternal (G166 aionios) life (G2222 zoe).

\begin{verbatim}
1  :  4100  pisteuo  pist-yoo'-o
2  
3   from 4102; to have faith (in, upon, or with respect to, a person or
4   thing), i.e. credit; by implication, to entrust (especially one's
5   spiritual well-being to Christ):--believe(-r), commit (to trust), put
6   in trust with.
7   see GREEK for 4102
\end{verbatim}

We must trust Him and Obey.

\subsection{Jesus' odedience resulted in turning others to obedience}
\label{sec:org3db2789}
\textbf{Romans 5:19} - For as by the one man's disobedience the many were made sinners, so by the one man's obedience the many \textbf{will be made} righteous.

A process:
\begin{itemize}
\item 'Will be made' => Turning people to obedience.
\end{itemize}


Adam disobeyed, and his descendants become disobedient.

Jesus obeyed, and his disciples become obedient.

\subsubsection{Likewise, we are commanded to do the same}
\label{sec:orgcb5cf3c}
\textbf{Matthew 28:18-20} - And Jesus came and said to them, All authority in heaven and on earth has been given to me. Go therefore and make disciples of all nations, baptizing them in the name of the Father and of the Son and of the Holy Spirit, teaching them to observe all that I have commanded you. And behold, I am with you always, to the end of the age.

\subsection{It is the mercy of God that we are turned from disobedience to obedience}
\label{sec:orga5c41c5}
\textbf{II Corinthians 10:6} - being ready to punish every disobedience, when your obedience is complete.

I think that is the correct way to see the following Scripture:

\textbf{Romans 11:29-33}: For the gifts and the calling of God are irrevocable. Just as you were at one time disobedient to God but now have received mercy because of their disobedience, so they too have now been disobedient in order that by the mercy shown to you they also may now receive mercy. For God has consigned all to disobedience, that he may have mercy on all. Oh, the depth of the riches and wisdom and knowledge of God! How unsearchable are his judgments and how inscrutable his ways!

\subsubsection{As obedient children, we are to be conformed to holiness}
\label{sec:org6235ecd}
\textbf{I Peter 1:14-16} - As obedient children, do not be conformed to the passions of your former ignorance, but as he who called you is holy, you also be holy in all your conduct, since it is written, You shall be holy, for I am holy.

\textbf{Ephesians 5:5-10} - For you may be sure of this, that everyone who is sexually immoral or impure, or who is covetous (that is, an idolater), has no inheritance in the kingdom of Christ and God. Let no one deceive you with empty words, for because of these things the wrath of God comes upon the sons of disobedience. Therefore do not associate with them; for at one time you were darkness, but now you are light in the Lord. Walk as children of light (for the fruit of light is found in all that is good and right and true), and try to discern what is pleasing to the Lord.

\subsubsection{Legitimate children are left without discipline}
\label{sec:org050a615}
\textbf{Hebrews 12:6-8} - For the Lord disciplines the one he loves, and chastises every son whom he receives. It is for discipline that you have to endure. God is treating you as sons. For what son is there whom his father does not discipline? If you are left without discipline, in which all have participated, then you are illegitimate children and not sons.

\subsection{What we hear and how we hear}
\label{sec:org0f9ce2d}
\textbf{Mark 4:24} - And he said to them, Pay attention to what you hear: with the measure you use, it will be measured to you, and still more will be added to you.

\textbf{Luke 8:18} - So take care how you listen; for whoever has, to him more shall be given; and whoever does not have, even what he thinks he has shall be taken away from him.”

If you do not take care of \texttt{how} you hear and \texttt{what} you hear, then \ldots{}

\textbf{Isaiah 6:10} - “Render the hearts of this people insensitive, Their ears dull, And their eyes dim, Otherwise they might see with their eyes, Hear with their ears, Understand with their hearts, And return and be healed.”

I think it's important to take in all the words which Jesus spoke which are available to us, and to come to a faith which is able to reconcile faith with works, and law and obedience, and the gospel Jesus taught before and after the resurrection, and reconcile the teachings of the epistles from Peter, Paul and John, and Epistle to the Hebrews.

\textbf{Matthew 13:15} - For the heart of this people has become dull, With their ears they scarcely hear, And they have closed their eyes, Otherwise they would see with their eyes, Hear with their ears, And understand with their heart and \textbf{return}, And I would heal them.’

The word return specifies 'action'.

\textbf{John 12:40} - “He has blinded their eyes and He hardened their heart, so that they would not see with their eyes and perceive with their heart, and be converted and I heal them.”

\textbf{Acts 28:27} - For the heart of this people has become dull, And with their ears they scarcely hear, And they have closed their eyes; Otherwise they might see with their eyes, And hear with their ears, And understand with their heart and \textbf{return}, And I would heal them.”’

\section{Spirit of Truth vs Spirit of Error}
\label{sec:orgf6a7b40}
\subsection{Don't believe falsehood}
\label{sec:orga397078}
If you listen to someone with a deceptive, beguiling spirit, then the same measure of that would come into you.

And that would would probably affect the truthfulness of your dreams if you have a prophetic gift, but there are other reasons a person may get dreams of falsehood including spiritual attack.

\subsubsection{No lie is of the truth}
\label{sec:org986024b}
\textbf{1 John 2:21} -  I write to you, not because you do not know the truth, but because you know it, and because no \textbf{lie is of the truth}.  (ESV)

\subsubsection{Garden of Eden}
\label{sec:org6e4eb77}
\begin{itemize}
\item Eve listened to another voice
\end{itemize}

\textbf{Genesis 3:4} - The serpent said to the woman, “You surely will not die! (ESV)

\textbf{I Timothy 2:14} - And it was not Adam who was deceived, but the woman being deceived, fell into transgression. (ESV)

\subsection{Not all 'spirit' is true}
\label{sec:org28fb40e}
It's false to say that 'all spirit is true' and body and soul are false.

\textbf{John 14:6} - Jesus said to him, I am the way, and the truth, and the life. No one comes to the Father except through me. (ESV)

\textbf{Psalms 119:160} - The sum of Your word is truth, And every one of Your righteous ordinances is everlasting. (ESV)

\textbf{John 17:17} - Sanctify them in the truth; Your word is truth. (ESV)

\subsection{Spirit of Truth}
\label{sec:orgf069c4c}
These do not contradict:
\begin{itemize}
\item Jesus is the Truth
\item Jesus' words are Truth and Life
\item God's word is truth
\begin{itemize}
\item The Scripture does not contradict
\end{itemize}
\item Jesus Christ is the Word of God in the Flesh
\begin{itemize}
\item Emmanuel
\end{itemize}
\item The Spirit of Truth is the Truth
\end{itemize}

\subsubsection{We should listen to and obey Jesus' words and compare everything with the scripture}
\label{sec:org590d74b}

\textbf{Psalms 119:105} - Your word is a lamp to my feet and a light to my path. (ESV)

\textbf{Acts 17:11} - Now these Jews were more noble than those in Thessalonica; they received the word with all eagerness, examining the Scriptures daily to see if these things were so. (ESV)

\textbf{II Corinthians 10:5} - We destroy arguments and every lofty opinion raised against the knowledge of God, and take every thought captive to obey Christ, (ESV)

\subsubsection{\texttt{sola scriptura} as the source of truth against false dreams}
\label{sec:orgd337378}
I've definitely had some issues, but I've noticed that repenting from sinful habits and obeying Jesus helps a lot to deal with that.

On 2 Jan 2023 I had a dream of defending a house with Bible verses written
on the doorposts.

I didn't know this was Biblical until very recently:

\textbf{Deuteronomy 6:9} -  You shall write them on the doorposts of your house and on your gates.  (ESV)

But now I know.

\texttt{sola scriptura} (by Scripture alone) AMEN!!

\subsubsection{Do God's will - follow Jesus in truth, and be obedient to God to combat falsehood}
\label{sec:orgc03b89f}
\textbf{John 7:17-19} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority. The one who speaks on his own authority seeks his own glory, but the one who seeks the glory of him who sent him is true, and in him there is no falsehood. Has not Moses given you the law? Yet none of you keeps the law. Why do you seek to kill me? (ESV)

\subsection{Spirit of Error}
\label{sec:org9e53689}
\begin{itemize}
\item Contradicts Jesus
\item Contradicts Scripture
\item Contradicts God's Word
\end{itemize}

\subsubsection{Don't believe lies nor even listen to false dreams from false prophets and diviners}
\label{sec:org131bb82}
\textbf{Zechariah 10:2} - For the household gods utter nonsense, and the diviners see lies; they tell false dreams and give empty consolation. Therefore the people wander like sheep; they are afflicted for lack of a shepherd. (ESV)

\textbf{Jeremiah 23:25-28} -  I have heard what the prophets have said who prophesy lies in my name, saying, I have dreamed, I have dreamed! How long shall there be lies in the heart of the prophets who prophesy lies, and who prophesy the deceit of their own heart, who think to make my people forget my name by their dreams that they tell one another, even as their fathers forgot my name for Baal?  Let the prophet who has a dream tell the dream, but let him who has my word speak my word faithfully.  What has straw in common with wheat?  declares the LORD.  (ESV)

\textbf{Jeremiah 23:32} - Behold, I am against those who prophesy lying dreams, declares the Lord, and who tell them and lead my people astray by their lies and their recklessness, when I did not send them or charge them. So they do not profit this people at all, declares the Lord. (ESV)

\textbf{Jeremiah 27:9} - So do not listen to your prophets, your diviners, your dreamers, your fortune-tellers, or your sorcerers, who are saying to you, You shall not serve the king of Babylon. (ESV)

\textbf{Jeremiah 29:8} - For thus says the Lord of hosts, the God of Israel: Do not let your prophets and your diviners who are among you deceive you, and do not listen to the dreams that they dream, (ESV)

\subsection{Renovating vs Innovating}
\label{sec:orgf4cb992}
I think God wants us to be born-again and move on from the old life,
not asking us to renovate our old life.

\textbf{I Corinthians 5:7} - Cleanse out the old leaven that you may be a new lump, as you really are unleavened. For Christ, our Passover lamb, has been sacrificed. (ESV)

Renovating is seeking to establish ones own righteousness while not submitting to God's righteousness.
Following God's commandments is great - a person can renovate for a while but when presented with the Gospel of Jesus they \textbf{must} submit to God's righteousness and have faith in Jesus.

\textbf{Romans 10:3-4} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness. For Christ is the end of the law for righteousness to everyone who believes (G4100 \textbf{pisteuo}).

\begin{itemize}
\item Seek God's kingdom and His righteousness first of all
\begin{itemize}
\item \textbf{Matthew 6:33} - But seek first the kingdom of God and his righteousness, and all these things will be added to you. (ESV)
\end{itemize}
\end{itemize}

Renovating (bad):
\begin{itemize}
\item Disobedient to the gospel
\begin{itemize}
\item Pursues the fruit of righteousness but trying to establish a righteousness of their own without submitting to the righteousness of God.
\item Working for justification outside of faith / obedience
\item Tries to have the 'holiness' without Jesus.
\item Has not obeyed the gospel.
\item Never died with Jesus.
\item From God's perspective even when they forgive others, it's out of self-righteousness.
\item Forgiving is still good but they still need to submit to the righteousness of God, by believing and obeying the gospel of Jesus.
\end{itemize}
\end{itemize}

\textbf{Romans 4:4} - Now to the one who works, his wages are not counted as a gift but as his due.

The devil does not submit to Jesus. So anyone who doesn't submit to the righteousness of God, instead sides with the devil.

\textbf{II Corinthians 11:14-15} - And no wonder, for even Satan disguises himself as an angel of light. So it is no surprise if his servants, also, disguise themselves as servants of righteousness. Their end will correspond to their deeds.

Innovating (good):
\begin{itemize}
\item The fruit of the Spirit is fruit (it comes after receiving the Holy Spirit).
\item Obey the gospel for justification.
\begin{itemize}
\item Christ is the head.
\item Died and rose with Jesus.
\begin{itemize}
\item \textbf{II Timothy 2:11-13} - The saying is trustworthy, for: If we have died with him, we will also live with him; if we endure, we will also reign with him; if we deny him, he also will deny us; if we are faithless, he remains faithful— for he cannot deny himself.
\item \textbf{Ephesians 2:6} - and \uline{raised us up with him} and seated us with him in the heavenly places in Christ Jesus,
\item \textbf{Colossians 2:12} - having been \uline{buried with him} in baptism, in which you were \uline{also raised with him through faith in the powerful working of God}, who raised him from the dead.
\begin{itemize}
\item Raised with Christ through faith in the powerful working of God.
\end{itemize}
\item \textbf{Colossians 3:3} - For you have died, and your life is hidden with Christ in God.
\end{itemize}
\item Now live to serve Christ.
\begin{itemize}
\item \textbf{II Corinthians 5:15} - and he died for all, that those who live might no longer live for themselves but for him who for their sake died and was raised.
\item \textbf{Colossians 3:1} - If then you have been raised with Christ, seek the things that are above, where Christ is, seated at the right hand of God.
\end{itemize}
\item Approaches Christ-likeness following Jesus.
\item Having accepted their own need of forgiveness, and having been forgiven \textbf{then} forgives others who don't even see their need of forgiveness.
\item \textbf{freely} forgives:
\begin{itemize}
\item \textbf{Matthew 18:21-22} -  Then Peter came up and said to him, Lord, how often will my brother sin against me, and I forgive him?  As many as seven times?  Jesus said to him, I do not say to you seven times, but seventy times seven. (ESV)
\end{itemize}
\item forgives even those who do not see their need of forgiveness:
\begin{itemize}
\item \textbf{Luke 23:33-35} - And when they came to the place that is called The Skull, there they crucified him, and the criminals, one on his right and one on his left.  And Jesus said, Father, forgive them, for they know not what they do. And they cast lots to divide his garments.  And the people stood by, watching, but the rulers scoffed at him, saying, He saved others; let him save himself, if he is the Christ of God, his Chosen One! (ESV)
\end{itemize}
\end{itemize}
\end{itemize}

\textbf{Ephesians 4:32} - Be kind to one another, tenderhearted, forgiving one another, as God in Christ forgave you. (ESV)

We must forgive others the same way that God in Christ forgave us.

\textbf{Colossians 2:14} - by canceling the record of debt that stood against us with its legal demands. This he set aside, nailing it to the cross.

\textbf{Luke 11:4} - and forgive us our sins, for we ourselves forgive everyone who is indebted to us. And lead us not into temptation.

It's necessary to submit to the righteousness of God:
\begin{itemize}
\item You have accepted that you needed forgiveness from God.
\item You have accepted that it's through the shedding of the blood of Jesus Christ that God has forgiven you, forgiving a debt which was impossible for you to pay.
\item Forgive others freely, knowing you've been forgiven of your sin. Give freely. Forgive the debt of others towards you. That looks like being a scapegoat and letting oneself be fleeced. Imagine you've just been born-again but noone else knows. You know you must forgive others. You know God can see your heart. Now all of a sudden people make these claims that you owe them X, Y and Z. You know you've been forgiven of a debt you were not able to pay. Now instead of contesting others on whether or not you owe them, you give freely. Seventy-times-seven.
\end{itemize}

Self-righteous forgiveness:
\begin{itemize}
\item Conditional forgiveness (not freely)
\item Self-righteously forgive others as if you're perfectly innocent and of course they sinned against innocence by sinning against you
\item Without accepting that you needed the forgiveness which Jesus has paid through His blood, you then forgive others
\begin{itemize}
\item This tries to establish one's own righteousness without submitting to the righteousness of God
\end{itemize}
\item Believing that you're already good with God and never needed Jesus
\begin{itemize}
\item not prepared to forgive freely
\item but not having yet submitted to the fact that you need forgiveness from God.
\item Forgiving others is good to do, but without having truly accepted that you needed forgiveness yourself, you'd still be forgiving others out of debt to God.
\item I think it's impossible to have Christ's heart without having first accepted being forgiven by Jesus
\end{itemize}
\item Do not accept that one needs or ever needed forgiveness from God.
\begin{itemize}
\item That actually means that person's forgiveness is at least a bit self-righteous (at least from God's perspective)
\begin{itemize}
\item They do not give out of credit, but while indebted to God, they still give God what is due by forgiving others their offenses towards them
\begin{itemize}
\item nevertheless, a person can never achieve perfect right standing with God without submitting to the righteousness of God through faith in Christ and accepting the atonement which Jesus has purchased through His blood
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

\section{laws}
\label{sec:orgd9e031b}
\begin{itemize}
\item Great commandments
\begin{itemize}
\item to love the Lord your God with all your heart, soul, mind and strength and your neighbour as yourself
\end{itemize}
\item 10 Commandments
\item the 613 Mosaic laws
\item the law of Christ
\end{itemize}

\textbf{John 7:19} - Has not Moses given you the law? Yet none of you keeps the law. Why do you seek to kill me?

\subsection{Follow the law in faith, not works, making yourself accountable to God, not men}
\label{sec:orgf63975f}
Keeping to the precepts of the law is great, and making yourself accountable to God with it, is great.

\textbf{Romans 2:25-29} - For circumcision indeed is of value if you obey the law, but if you break the law, your circumcision becomes uncircumcision. So, if a man who is uncircumcised keeps the precepts of the law, will not his uncircumcision be regarded as circumcision? Then he who is physically uncircumcised but keeps the law will condemn you who have the written code and circumcision but break the law. For no one is a Jew who is merely one outwardly, nor is circumcision outward and physical. But a Jew is one inwardly, and circumcision is a matter of the heart, by the Spirit, not by the letter. His praise is not from man but from God.

\textbf{Luke 16:15-17} - And he said to them, You are those who justify yourselves before men, but God knows your hearts. For what is exalted among men is an abomination in the sight of God.  The Law and the Prophets were until John; since then the good news of the kingdom of God is preached, and everyone forces his way into it.  But it is easier for heaven and earth to pass away than for one dot of the Law to become void.

\textbf{I Kings 11:38} - And if you will listen to all that I command you, and will walk in my ways, and do what is right in my eyes by keeping my statutes and my commandments, as David my servant did, I will be with you and will build you a sure house, as I built for David, and I will give Israel to you.

\section{Whoever puts their faith in Jesus, puts their faith in God}
\label{sec:orgac3a3c4}
We must follow Jesus, similarly to how the Israelites followed Moses through the Red Sea - it requires action.

\textbf{John 12:44-50} - And Jesus cried out and said, Whoever believes (G4100 pisteuo) in me, believes (G4100 pisteuo) not in me but in him who sent me.  And whoever sees me sees him who sent me.  I have come into the world as light, so that whoever believes in me may not remain in darkness.  If anyone hears my words and does not keep them, I do not judge him; for I did not come to judge the world but to save the world.  The one who rejects me and does not receive my words has a judge; the word that I have spoken will judge him on the last day.  For I have not spoken on my own authority, but the Father who sent me has himself given me a commandment—what to say and what to speak.  And I know that his commandment is eternal life.  What I say, therefore, I say as the Father has told me. (ESV)

This is similar to how the Israelites trusted in Moses, and they actually were trusting in God.

\textbf{Exodus 14:14-16} - The Lord will fight for you, and you have only to be silent.  The Lord said to Moses, Why do you cry to me? Tell the people of Israel to go forward.  Lift up your staff, and stretch out your hand over the sea and divide it, that the people of Israel may go through the sea on dry ground. (ESV)

\textbf{Exodus 14:21-22} - Then Moses stretched out his hand over the sea, and the LORD drove the sea back by a strong east wind all night and made the sea dry land, and the waters were divided. And the people of Israel went into the midst of the sea on dry ground, the waters being a wall to them on their right hand and on their left. (ESV)

\textbf{Exodus 14:31} - When Israel saw the great power which the Lord had used against the Egyptians, the people feared the Lord, and they believed (H539 \textbf{'aman}) in the Lord and in His servant Moses. (ESV)

\section{We should observe the law - but be a doer, and avoid judging others with the law}
\label{sec:org98d60d5}
\textbf{Matthew 23:2-7} - The scribes and the Pharisees sit on Moses' seat, so practice and observe whatever they tell you—but not what they do. For they preach, but do not practice. They tie up heavy burdens, hard to bear, and lay them on people's shoulders, but they themselves are not willing to move them with their finger. They do all their deeds to be seen by others. For they make their phylacteries broad and their fringes long, and they love the place of honor at feasts and the best seats in the synagogues and greetings in the marketplaces and being called rabbi by others. (ESV)

\begin{itemize}
\item \href{https://www.youtube.com/watch?v=alOI2zxIPgc}{How Preachers Grow Graceless - YouTube}
\end{itemize}

\section{Be a doer of good, not merely a hearer}
\label{sec:org74cdc66}
\textbf{James 1:22-23} -  But be doers of the word, and not hearers only, deceiving yourselves. For if anyone is a hearer of the word and not a doer, he is like a man who looks intently at his natural face in a mirror. (ESV)

\textbf{Romans 2:13-16} - For it is not the hearers of the law who are righteous before God, but the doers of the law who will be justified.  For when Gentiles, who do not have the law, by nature do what the law requires, they are a law to themselves, even though they do not have the law.  They show that the work of the law is written on their hearts, while their conscience also bears witness, and their conflicting thoughts accuse or even excuse them on that day when, according to my gospel, God judges the secrets of men by Christ Jesus. (ESV)

\section{Mosaic Law, and progressing from having hope in Moses to having hope in Jesus}
\label{sec:org1e116ed}
I enjoyed this video, but I still am of the opinion that keeping the law is not necessary, (but not prohibited, so long as it is pursued by faith and submitting to God's righteousness):
\begin{itemize}
\item \href{https://www.youtube.com/watch?v=CNHKqhwu6Bo}{Public Debate - Should Christians Keep The Law? - YouTube}
\item The law is good and just and Jesus both obeyed it flawlessly, but He also fulfilled it like a prophesy.
\end{itemize}

I read the following as, as we have faith in Jesus, following Him, where we have fallen short, Jesus has covered us, but we still try to live righteously. We still live with faith in God.

And when we continue to sin, Jesus is our High Priest and Advocate, and covers us, as we continue to have faith in Him.

The 10 Commandments and the 2 Great commandments are special because when followed from the heart they show people how to love God and one's neighbour.

And we are \uline{commanded} (even as Christians not \uline{under the law}) to love our neighbours:

\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that \uline{whatever you ask the Father in my name, he may give it to you}.􀀂(ESV)

\textbf{I John 3:21-24} - Beloved, if our heart does not condemn us, we have confidence before God; and \uline{whatever we ask we receive from him}, because we keep his commandments and do what pleases him. And this is his commandment, that we believe in the name of his Son Jesus Christ and love one another, just as he has commanded us. Whoever keeps his commandments abides in him, and he in them. And by this we know that he abides in us, by the Spirit whom he has given us. (ESV)

The rest of the Mosaic law is still useful for training in righteousness. It shows people how to live in obedience to God and in love for God and one's neighbour. But we are not under the Mosaic law, but we are under the law of Christ. We have faith in Christ.

We can pursue the righteousness that is through faith (G4100 \textbf{pisteuo}) in Jesus Christ.

We must set our hope on Jesus, not on Moses.

\textbf{John 5:45} -  Do not think that I will accuse you to the Father.  There is one who accuses you: Moses, on whom you have set your hope.  (ESV)

\textbf{Acts 7:35} - “This Moses whom they disowned, saying, ‘Who made you a ruler and a judge?’ is the one whom God sent to be both a ruler and a deliverer with the help of the angel who appeared to him in the thorn bush.

Moses wrote about Jesus:

\textbf{Acts 7:37} - This is the Moses who said to the sons of Israel, ‘God will raise up for you a prophet like me from your brethren.’

Moses said we must listen to Jesus:

\textbf{Deuteronomy 18:15-19} - The LORD your God will raise up for you a prophet like me from among you, from your brothers—it is to him \uline{you shall listen} — just as you desired of the LORD your God at Horeb on the day of the assembly, when you said, Let me not hear again the voice of the LORD my God or see this great fire any more, lest I die. And the LORD said to me, They are right in what they have spoken. I will raise up for them a prophet like you from among their brothers. And I will put my words in his mouth, and he shall speak to them all that I command him. And whoever will not listen to my words that he shall speak in my name, I myself will require it of him. (ESV)

\textbf{Acts 7:52-55} - Which one of the prophets did your fathers not persecute? They killed those who had previously announced the coming of the Righteous One, whose betrayers and murderers you have now become; you who received the law as ordained by angels, and yet did not keep it.” Now when they heard this, they were cut to the quick, and they began gnashing their teeth at him.  But being full of the Holy Spirit, he gazed intently into heaven and saw the glory of God, and Jesus standing at the right hand of God;

We must obey Jesus:

\begin{itemize}
\item \textbf{Romans 10:4} - For Christ is the end of the law for righteousness to everyone who believes (G4100 \textbf{pisteuo}).
\end{itemize}

(G4100 \textbf{pisteuo}) is \uline{practicing} faith.

This means, yes that by practicing faith in Jesus, we can pursue righteousness - Jesus' righteousness given to us.

\textbf{II Peter 1:1} - Simeon Peter, a servant and apostle of Jesus Christ, To those who have obtained a faith of equal standing with ours by the righteousness of our God and Savior Jesus Christ:

We obtain a strong faith by the righteousness of Jesus Christ.

This requires obedience to Jesus:

\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that \uline{whatever you ask the Father in my name, he may give it to you}.􀀂(ESV)

\textbf{I John 3:21-24} - Beloved, if our heart does not condemn us, we have confidence before God; and \uline{whatever we ask we receive from him}, because we keep his commandments and do what pleases him. And this is his commandment, that we believe in the name of his Son Jesus Christ and love one another, just as he has commanded us. Whoever keeps his commandments abides in him, and he in them. And by this we know that he abides in us, by the Spirit whom he has given us. (ESV)

\textbf{John 15:10} - If you keep my commandments, you will abide in my love, just as I have kept my Father's commandments and abide in his love.

By having an obedient, trusting faith (which fundamentally includes belief) in Jesus, following, we have Jesus' righteousness.

I read this as we are under grace and not
under the Mosaic law, but we must bear fruit
of repentance from disbelief and sin, and
becoming good instead of evil, bearing fruit
in our life which glorifies God in our bodies,
hearts and deeds:
\begin{itemize}
\item obedience leads to righteousness
\item slaves to righteousness leading to sanctification
\begin{itemize}
\item at its end, eternal life
\end{itemize}

\item \textbf{Romans 6:13-23} - Do not present your members to sin as instruments for unrighteousness, but present yourselves to God as those who have been brought from death to life, and your members to God as instruments for righteousness.  For sin will have no dominion over you, since you are not under law but under grace.  What then? Are we to sin because we are not under law but under grace? By no means!  Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of \textbf{obedience, which leads to righteousness}?  But thanks be to God, that you who were once slaves of sin have become obedient from the heart to the standard of teaching to which you were committed, and, having been set free from sin, have become \textbf{slaves of righteousness}.  I am speaking in human terms, because of your natural limitations. For just as you once presented your members as slaves to impurity and to lawlessness leading to more lawlessness, so now present your members as \textbf{slaves to righteousness leading to sanctification}.  When you were slaves of sin, you were free in regard to righteousness.  But what fruit were you getting at that time from the things of which you are now ashamed? The end of those things is death.  But now that you have been \textbf{set free from sin and have become slaves of God, the fruit you get leads to sanctification and its end, eternal life}.  For the wages of sin is death, but the free gift of God is eternal life in Christ Jesus our Lord.
\end{itemize}

\section{Commandments and faith}
\label{sec:org23c738f}
\textbf{Revelation of John 14:12} - Here is a call for the endurance of the saints, those who keep the commandments of God and their faith in Jesus.

I read this as 'A saint is someone who has faith in Jesus AND keeps the commandments (pursuing by faith, not works)'.
I read this as the Great commandments, 10 Commandments and faith in Jesus Christ, and potentially various other commandments from the Mosaic law if you know about them, or whatever subset a person practices by faith making themself accountable to God.
But the law, if it's pursued at all, should be pursued by faith and not by works.

\textbf{John 15:10} - If you keep my commandments, you will abide in my love, just as I have kept my Father's commandments and abide in his love.

\textbf{Romans 9:30-32} - What shall we say, then? That Gentiles who did not pursue righteousness have attained it, that is, a righteousness that is by faith; but that Israel who pursued a law that would lead to righteousness did not succeed in reaching that law. Why? Because they did not pursue it by faith, but as if it were based on works. They have stumbled over the stumbling stone, (ESV)

\subsubsection{Christians do not Judaize (Christians do not instruct Gentiles to conform to Judaism)}
\label{sec:orge974f75}
\textbf{Ignatius to the Magnesians 10} - Let us not, therefore, be insensible to His kindness. For were He to reward us according to our works, we should cease to be. Therefore, \textbf{having become His disciples, let us learn to live according to the principles of Christianity}. For whosoever is called by any other name besides this, is not of God. Lay aside, therefore, the evil, the old, the sour leaven, and be ye changed into the new leaven, which is Jesus Christ. Be ye salted in Him, lest any one among you should be corrupted, since by your savour ye shall be convicted. It is absurd to profess Christ Jesus, and to Judaize. For \uline{Christianity did not embrace Judaism, but Judaism Christianity, that so every tongue which believeth might be gathered together to God}.

\subsubsection{Jesus' commandments don't contradict the rest of the commandments}
\label{sec:orgd6ea214}
Also God's commandments (especially the 10 Commandments; loving God and your neighbour) are still binding on us - written on our heart when we get born-again and after being born-again we follow them in Spirit, but they don't bind on us in a way that condemns us if we  break them, but we \textbf{want} to follow them.

Jesus fulfilled the law => We have the Spirit of Christ => We are led by the Spirit and naturally want to follow the law in faith but the world opposes us because when a person actually follows the commandments, they do not lie, do not commit adultery, do not commit idolatry, etc. and that means a person can be 'taken advantage of' by unfaithful people who do not obey God's commandments but exploit others who follow God.

But we neither pursue the law by works, nor seek it to be justified.
We are freed from being under the law, and free from the curse of the law to serve and obey God in actuality, being under God's grace.

\textbf{Romans 7:6} - But now we are released from the law, having died to that which held us captive, so that we serve not under the old written code but in the new life of the Spirit. (ESV)

I think that being led by the Spirit is still acting in a way that without observing the law is technically compliant with the law, and that is because we are led by the Spirit.

By being led by the Spirit, we are not \textbf{under} the law. And we have Jesus Christ as our Advocate and High Priest.

\textbf{I John 2:1} - My little children, I am writing these things to you so that you may not sin. But if anyone does sin, we have an advocate with the Father, Jesus Christ the righteous.

Nevertheless, when we judge others by the law, we're judged by the same standard.

\textbf{Matthew 7:1} - Judge not, that you be not judged. (ESV)

But if someone judges by the law, it seems right to submit to the law, unless it is that you are actually being obedient to Jesus (being led by the Spirit / following Jesus' commandments), in which you should carry on being obedient to Jesus. The law is meant for sinners.

\textbf{Matthew 23:2-3} - The scribes and the Pharisees sit on Moses' seat, so practice and observe whatever they tell you—but not what they do. For they preach, but do not practice. (ESV)

We then may observe the law and keep it in faith (not adhering strictly thought), and do not teach others to annul even the smallest commandment, and as we are led by the Spirit (obeying and following Jesus) we are not under the law, nor under its curse, and we are not seeking to be justified by the law, and if we are being obedient servants of Jesus then we naturally submit to God's law.

\textbf{Romans 8:7} - For the mind that is set on the flesh is hostile to God, for it does not submit to God's law; indeed, it cannot. (ESV)

When someone uses the law to judge, comply if they are right, but do not act like the hypocrites.

\textbf{John 7:24} - Do not judge by appearances, but judge with right judgment.

\textbf{Matthew 23:2-7} - The scribes and the Pharisees sit on Moses' seat, \uline{so practice and observe whatever they tell you} —but not what they do. For they preach, but do not practice. They tie up heavy burdens, hard to bear, and lay them on people's shoulders, but they themselves are not willing to move them with their finger. They do all their deeds to be seen by others. For they make their phylacteries broad and their fringes long, and they love the place of honor at feasts and the best seats in the synagogues and greetings in the marketplaces and being called rabbi by others. (ESV)

But the mind set on the Spirit does submit to God's law meaning that they may walk in God's statues, and therefore the mind set on the Spirit is not hostile to God.

\textbf{Ezekiel 11:19-20} - And I will give them one heart, and a new spirit I will put within them. I will remove the heart of stone from their flesh and give them a heart of flesh, that they may walk in my statutes and keep my rules and obey them. And they shall be my people, and I will be their God. (ESV)

\textbf{Deuteronomy 4:13} - And he declared to you his covenant, which he commanded you to perform, that is, the Ten Commandments, and he wrote them on two tablets of stone.

\textbf{Romans 10:5} - For Moses writes about the righteousness that is based on the law, that the person who does the commandments shall live by them.

\textbf{Romans 13:9} - The commandments, You shall not commit adultery, You shall not murder, You shall not steal, You shall not covet, and any other commandment, are summed up in this word: You shall love your neighbor as yourself.

There's no contradiction between what the 10 commandments say and loving one's neighbour, i.e. for the way in which we must live entering into life.

\subsubsection{However, we must submit to God's righteousness through faith in Jesus Christ - this is what saves}
\label{sec:org4538748}
\textbf{Romans 10:6-13} - But the righteousness based on faith says, Do not say in your heart, Who will ascend into heaven? (that is, to bring Christ down) or Who will descend into the abyss? (that is, to bring Christ up from the dead).  But what does it say? The word is near you, in your mouth and in your heart (that is, the word of faith that we proclaim); because, if you confess with your mouth that Jesus is Lord and believe in your heart that God raised him from the dead, you will be saved.  For \textbf{with the heart one believes (G4100 pisteuo) and is justified}, and with the mouth one confesses and is saved.  For the Scripture says, Everyone who believes in him will not be put to shame.  For there is no distinction between Jew and Greek; the same Lord is Lord of all, bestowing his riches on all who call on him.  For everyone who calls on the name of the Lord will be saved.

But what does it take for the heart to truly believe? Because that's the condition.

More obedience may still need to take place for that individual to arrive at justifying faith, and God may be allowing you to come to your faith.

To be justified, a person must \uline{walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

It does say '\textbf{you will be saved}', not '\textbf{you are saved}'.

And the word \textbf{confess} I think means to admit with repentance - an admission of guilt to God and change of mind resulting in confessing that Jesus is Lord and that God indeed raised Him from the dead, and that you needed Him to do so, because His name means Jesus (The LORD Saves), Christ (Annointed Messiah, Saviour), Son of God.

If a person confesses this truthfully, they professes that they submit to the righteousness of God.

That's a little bit loaded. It results in a heart growing in obedience towards God.
And I believe it's the resulting obedience to God that ends up saving that person, even if that obedience hasn't produced any work yet other than belief. God is the one that saves and justifies.

Then Jesus hits us with this:

\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that whatever you ask the Father in my name, he may give it to you.

\textbf{Ephesians 1:4} - even as he chose us in him before the foundation of the world, that we should be holy and blameless before him. In love

So while we might think we have done something, God had planned it in advance, and the entire thing is grace - but that doesn't mean from our perspective it does not look like we need to obey God - because we still need to have faith and do something. And if we don't do anything then we are asking God to do it for us.

Since the Bible does not teach that all people will be saved because they remain disobedient, I think we should teach people that they should do something; That they should repent from sin and they should repent from unbelief if they want to be saved from sin and leading to death, and if they want to enter into the light of the truth, and enter into a relationship with God.

The root of disobedience/rebellion is unbelief/denial.

\textbf{John 20:27-28} - Then he said to Thomas, Put your finger here, and see my hands; and put out your hand, and place it in my side. Do not disbelieve, but believe. Thomas answered him, My Lord and my God!

Jesus helped Thomas believe by giving him a commandment to do. It's implied that Thomas obeyed and arrived at belief.

\textbf{John 20:29-31} - Jesus said to him, Have you believed because you have seen me? Blessed are those who have not seen and yet have believed.  Now Jesus did many other signs in the presence of the disciples, which are not written in this book; but these are written so that you may believe that Jesus is the Christ, the Son of God, and that by believing you may have life in his name.

\textbf{Mark 6:11} - And if any place will not receive you and they will not listen to you, when you leave, shake off the dust that is on your feet as a testimony against them.

\subsubsection{Love never ends. Jesus' words never end.}
\label{sec:orgc9d1399}
\textbf{1 Corinthians 13:8} -  Love never ends.  As for prophecies, they will pass away; as for tongues, they will cease; as for knowledge, it will pass away. (ESV)

\textbf{Matthew 24:35} - Heaven and earth will pass away, but my words will not pass away. (ESV)

\textbf{Luke 16:16-17} -  The Law and the Prophets were until John; since then the good news of the kingdom of God is preached, and everyone forces his way into it.  But it is \textbf{easier} for heaven and earth to pass away than for one dot of the Law to become void. (ESV)

\subsubsection{The new heavens and new earth}
\label{sec:org8b4c6c7}
\textbf{Isaiah 65:17} - For behold, I create new heavens and a new earth, and the former things shall not be remembered or come into mind.

\textbf{Isaiah 66:22} - For as the new heavens and the new earth that I makeshall remain before me, says the Lord, so shall your offspring and your name remain.

\textbf{II Peter 3:13} - But according to his promise we are waiting for new heavens and a new earth in which righteousness dwells.

\textbf{Revelation of John 21:1-7} - Then I saw a new heaven and a new earth, for the first heaven and the first earth had passed away, and the sea was no more. And I saw the holy city, new Jerusalem, coming down out of heaven from God, prepared as a bride adorned for her husband. And I heard a loud voice from the throne saying, Behold, the dwelling place of God is with man. He will dwell with them, and they will be his people, and God himself will be with them as their God. He will wipe away every tear from their eyes, and death shall be no more, neither shall there be mourning nor crying nor pain anymore, for the former things have passed away. And he who was seated on the throne said, Behold, I am making all things new. Also he said, Write this down, for these words are trustworthy and true. And he said to me, It is done! I am the Alpha and the Omega, the beginning and the end. To the thirsty I will give from the spring of the water of life without payment. The one who conquers will have this heritage, and I will be his God and he will be my son.

\subsubsection{The Mosaic law is not abolished but Jesus fulfilled it like a prophesy}
\label{sec:org0b94090}
\textbf{Luke 16:17} - But it is easier for heaven and earth to pass away than for one dot of the Law to become void.

The righteousness we have through faith in Jesus Christ is needed whether someone keeps the Mosaic law or not.

Not that I keep the Mosaic law in its entirety, nor are circumcised. But I try to keep the Great commandments
and the 10 Commandments out of faith (and a relationship with God) and follow parts of the Mosaic law,
but I have faith in Jesus Christ for the righteousness that comes through faith because I need that because my own
righteousness will never be enough without faith in Jesus for God's righteousness imputed to me.

Thank You God.

And I follow pursue the commandments by faith and not works.

\textbf{Ephesians 2:8-9} - For by grace you have been saved through faith. And this is not your own doing; it is the gift of God, not a result of works, so that no one may boast. (ESV)

A person must be at least willing to do His will - obedience is the essence of faith:

\textbf{John 7:17} - If anyone is willing to do His will, he will know of the teaching, whether it is of God or whether I speak from Myself.

There is still obedience required. Obedience is intrinsic to faith.

\textbf{Exodus 14:14-16} - The Lord will fight for you, and you have only to be silent.  The Lord said to Moses, Why do you cry to me? Tell the people of Israel to go forward.  Lift up your staff, and stretch out your hand over the sea and divide it, that the people of Israel may go through the sea on dry ground.

AMEN!!

\textbf{Galatians 2:17} -- But if, in our endeavor to be justified in Christ, we too were found to be sinners, is Christ then a servant of sin? Certainly not! (ESV)

AMEN!!

\textbf{Romans 10:3-4} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness. For Christ is the end of the law for righteousness to everyone who believes.

This is why we are not \textbf{under} the law because we have the righteousness that comes through faith in Christ.

But we are under the law of faith in Christ.

And we are supposed to keep the commandments by pursuing them in faith.

If we teach others to annul even the least of the commandments and annul them ourselves, this I don't think condemn us but is prideful and result in being called the least in the Kingdom.

\textbf{Matthew 5:19} - Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven.

\subsubsection{A person must begin repenting of sin and have a faithful heart towards God to receive the Holy Spirit}
\label{sec:orgb5f8e3c}
\textbf{Acts 8:9}: But there was a man named Simon, who had previously practiced magic in the city and amazed the people of Samaria, saying that he himself was somebody great.

\textbf{Acts 8:18-21} - Now when Simon saw that the Spirit was given through the laying on of the apostles' hands, he offered them money, saying, Give me this power also, so that anyone on whom I lay my hands may receive the Holy Spirit.  But Peter said to him, May your silver perish with you, because you thought you could obtain the gift of God with money!  You have neither part nor lot in this matter, for your heart is not right before God.

\textbf{Acts 5:32} - And we are witnesses to these things, and so is \textbf{the Holy Spirit, whom God has given to those who obey him}. (ESV)

\textbf{Galatians 3:14} - so that in Christ Jesus the blessing of Abraham might come to the Gentiles, so that we might receive the promised Spirit through faith.

\subsubsection{I believe the 10 commandments are special, and Jesus calls us to follow them from the heart}
\label{sec:org42614cd}
Otherwise why would God make a distinction in Exodus 16 between commandments (mitsvah) and instructions/law (towrah)?

\textbf{Genesis 26:5} - because Abraham obeyed my voice and kept my charge, my commandments, my statutes, and my laws. (ESV)

\textbf{Exodus 15:26} - saying, If you will diligently listen to the voice of the Lord your God, and do that which is right in his eyes, and give ear to his commandments and keep all his statutes, I will put none of the diseases on you that I put on the Egyptians, for I am the Lord, your healer. (ESV)

\textbf{Exodus 16:28} - And the Lord said to Moses, How long will you refuse to keep my commandments and my laws? (ESV)

\textbf{Exodus 16:28} - Then the Lord (H3068 Yhovah) said (H559 'amar) to Moses (H4872 Mosheh), “How (H575 'an) long (H5704 `ad) do you refuse (H3985 ma'en) to keep (H8104 shamar) My commandments (H4687 mitsvah) and My instructions (H8451 towrah)? (NASB)

\textbf{Exodus 20:5} - You shall not bow down to them or serve them, for I the Lord your God am a jealous God, visiting the iniquity of the fathers on the children to the third and the fourth generation of those who hate me, (ESV)

\textbf{Exodus 20:6} - but showing steadfast love to thousands of those who love me and keep my commandments. (ESV)

\textbf{Exodus 34:28} - So he was there with the Lord forty days and forty nights. He neither ate bread nor drank water. And he wrote on the tablets the words of the covenant, the Ten Commandments. (ESV)

\subsubsection{The Apostles also placed requirements on the Gentiles similar to the 10 commandments}
\label{sec:org7c472c1}
\textbf{Acts 15:28-29} - For it has seemed good to the Holy Spirit and to us to lay on you no greater burden than these requirements: that you abstain from what has been sacrificed to idols, and from blood, and from what has been strangled, and from sexual immorality. If you keep yourselves from these, you will do well. Farewell.

\subsubsection{Faith in Jesus justifies but Jesus helps us to follow the commandments}
\label{sec:org3140f6b}
\textbf{Mark 10:27} - Jesus looked at them and said, With man it is impossible, but not with God. For all things are possible with God.

\subsubsection{Grace from Jesus is essential. Faith in Jesus is essential, even for the one who pursues the law}
\label{sec:orgcabcd02}
\textbf{Galatians 5:4} - You are severed from Christ, you who would be justified by the law; you have fallen away from grace.

\textbf{I John 2:1} - My little children, I am writing these things to you so that you may not sin. But if anyone does sin, we have an advocate with the Father, Jesus Christ the righteous.

\subsubsection{The doers of the law are justified. Jesus judges. No-one can be justified without faith}
\label{sec:org1c9b652}
Complying with the law (not breaking it) is good.

\textbf{Romans 2:13-16} - For it is not the hearers of the law who are righteous before God, but the doers of the law who will be justified.  For when Gentiles, who do not have the law, by nature do what the law requires, they are a law to themselves, even though they do not have the law.  They show that the work of the law is written on their hearts, while their conscience also bears witness, and their conflicting thoughts accuse or even excuse them on that day when, according to my gospel, God judges the secrets of men by Christ Jesus.

\subsubsection{I still think there is hope for people who do what the law requires, and have not yet heard the gospel}
\label{sec:orgeefdfa6}
\textbf{I Timothy 4:10-11} - For to this end we toil and strive, because we have our hope set on the living God, who is the Savior of all people, especially of those who believe. Command and teach these things.

\textbf{Romans 10:3-4} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness. For Christ is the end of the law for righteousness to everyone who believes.

\textbf{I Peter 3:18-21} - For Christ also suffered once for sins, the righteous for the unrighteous, that he might bring us to God, being put to \textbf{death in the flesh but made alive in the spirit}, in which he went and proclaimed to the spirits in prison, because \textbf{they formerly did not obey}, when God's patience waited in the days of Noah, while the ark was being prepared, in which a few, that is, eight persons, were brought safely through water. Baptism, which corresponds to this, now saves you, not as a removal of dirt from the body but as an appeal to God for a good conscience, through the resurrection of Jesus Christ,

\textbf{I Thessalonians 4:14} - For since we believe that Jesus died and rose again, even so, through Jesus, God will bring with him those who have fallen asleep.

\textbf{Romans 10:12-21} - For there is no distinction between Jew and Greek; the same Lord is Lord of all, bestowing his riches on all who call on him.  For everyone who calls on the name of the Lord will be saved.  But how are they to call on him in whom they have not believed? And how are they to believe in him of whom they have never heard? And how are they to hear without someone preaching?  And how are they to preach unless they are sent? As it is written, How beautiful are the feet of those who preach the good news!  But they have not all obeyed the gospel. For Isaiah says, Lord, who has believed what he has heard from us?  So faith comes from hearing, and hearing through the word of Christ.  But I ask, have they not heard? Indeed they have, for Their voice has gone out to all the earth, and their words to the ends of the world.  But I ask, did Israel not understand? First Moses says, I will make you jealous of those who are not a nation; with a foolish nation I will make you angry.  Then Isaiah is so bold as to say, \textbf{I have been found by those who did not seek me; I have shown myself to those who did not ask for me.} But of Israel he says, All day long I have held out my hands to a disobedient and contrary people.

\subsubsection{Faith in Jesus essential to even those who pursue the law, but the law is still pursued}
\label{sec:org0aa88fb}
\textbf{Romans 3:28-31} For we hold that one is justified by faith apart from works of the law.  Or is God the God of Jews only? Is he not the God of Gentiles also? Yes, of Gentiles also, since God is one. He will justify the circumcised by faith and the uncircumcised through faith.  Do we then overthrow the law by this faith? By no means! On the contrary, we uphold the law.

That's not a contradiction.

Jesus helps us to follow the law and where we fall short it's still faith in Jesus that justifies because Jesus is our advocate and High Priest.

Also, I think there's a difference between the commandments (10 and 2) and the full Mosaic law (613 laws).

\textbf{Exodus 16:28} - Then the Lord (H3068 Yhovah) said (H559 'amar) to Moses (H4872 Mosheh), “How (H575 'an) long (H5704 `ad) do you refuse (H3985 ma'en) to keep (H8104 shamar) My commandments (H4687 mitsvah) and My instructions (H8451 towrah)? (NASB)

\section{Old Testament theology is profitable for training in righteousness}
\label{sec:org51b922e}
Old Testament theology is supposed to be profitable for:
\begin{itemize}
\item doctrine
\item reproof
\item correction
\item \textbf{training in righteousness}
\end{itemize}

\textbf{2 Timothy 3:15-16} -  and how from childhood you have been acquainted with the sacred writings, which are able to make you wise for salvation through faith in Christ Jesus.  All Scripture is breathed out by God and profitable for teaching, for reproof, for correction, and for training in righteousness,  (ESV)

Torah means instruction for righteousness.

\section{Jesus allowed himself to be baptised by John for the fulfillment of all righteousness}
\label{sec:org1eb0988}
\textbf{Matthew 3:11-17} - I baptize you with water for repentance, but he who is coming after me is mightier than I, whose sandals I am not worthy to carry. He will baptize you with the Holy Spirit and with fire.  His winnowing fork is in his hand, and he will clear his threshing floor and gather his wheat into the barn, but the chaff he will burn with unquenchable fire.  Then Jesus came from Galilee to the Jordan to John, to be baptized by him.  John would have prevented him, saying, I need to be baptized by you, and do you come to me?  But Jesus answered him, \textbf{Let it be so now, for thus it is fitting for us to fulfill all righteousness}. Then he consented.  And when Jesus was baptized, immediately he went up from the water, and behold, the heavens were opened to him, and he saw the Spirit of God descending like a dove and coming to rest on him; and behold, a voice from heaven said, This is my beloved Son, with whom I am well pleased. (ESV)

\section{Jesus fulfilled the law}
\label{sec:orgbb8c64a}
\begin{itemize}
\item Who gave Moses the law and the instructions to build the tabernacle? God did.
\begin{itemize}
\item The blueprints came from God.
\end{itemize}
\item The Law, the Psalms and the Prophets all point to Jesus.
\item Moses wrote about Jesus.
\item Jesus fulfilled the Law and the prophecies.
\end{itemize}

We still follow the law but by faith and not by works.

We keep accountability with God, and in truth over following the law - God knows when we lie, cheat, commit adultery, idolise etc.
We follow the law in truth.
Jesus fulfilled the law. Jesus' blood is the atonement for sin.
So we go to Jesus for forgiveness instead of perform the ceremonial law to try to make atonement for sin.

This looks like an interesting resource about that - \url{http://www.abideinchrist.com/messages/tabernacletype.html}

\subsection{Don't be deceived: Keeping commandments isn't the same thing as placing oneself under the Mosaic law for justification. We're commanded to obey Jesus, and that matters}
\label{sec:orgf73f36f}
\textbf{I Corinthians 7:17-19} - Only let each person lead the life that the Lord has assigned to him, and to which God has called him. This is my rule in all the churches. Was anyone at the time of his call already circumcised? Let him not seek to remove the marks of circumcision. Was anyone at the time of his call uncircumcised? Let him not seek circumcision. For neither circumcision counts for anything nor uncircumcision, but keeping the commandments of God.

\subsection{Justified by faith alone}
\label{sec:org789c3dd}
\textbf{Romans 4:12} -  and to make him the father of the circumcised who are not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised.  (ESV)

Faith eclipses the law:

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

I think someone who trusts in God to save them through saving faith in Jesus Christ, is saved, or is in the process of being saved.
But keep in mind that someone who truly trusts Jesus will do as Jesus has commanded.

Abraham's faith was both obedient and believing.

God is the judge of what saving faith looks like, and how long the process of 'being saved' takes.

We must receive Jesus' words, walk in them and come to \textbf{know in truth} (we must truly know) that Jesus came from God.

\textbf{John 17:8} - For I have given them the words that you gave me, and they have received them and have \textbf{come to know in truth that I came from you}; and they have believed that you sent me.

\textbf{John 1:11-13} - He came to His own, and those who were His own did not receive Him. But \uline{as many as received Him, to them He gave the right to become children of God, even to those who believe (G4100 \textbf{pisteuo}) in His name}, who were born, not of blood nor of the will of the flesh nor of the will of man, but of God.

Therefore, we should obey Jesus and arrive at the truth. Obedience is a part of faith. Like Abraham obeying God, or like Israel crossing through the Red Sea, it's obedience which leads to sure belief.
And the obedience doesn't end.

\textbf{John 8:31-32} - So Jesus was saying to those Jews who had believed Him, “If you \textbf{continue in My word}, then you are truly disciples of Mine; and \textbf{you will know the truth}, and the truth will make you free.” (NASB)

Through faithful endurance we endeavor to be justified in Christ.

\textbf{Galatians 2:17} -- But if, in our endeavor to be justified in Christ, we too were found to be sinners, is Christ then a servant of sin? Certainly not! (ESV)

The Revelation of John shows that Jesus looks at people's works.

Faith without working through love doesn't count for anything.

\subsection{Friends of God obey God}
\label{sec:orgde32986}
\textbf{James 2:22-24} - You see that faith was working with his works, and as a result of the works, faith was perfected; and the Scripture was fulfilled which says, “And \uline{Abraham believed God}, and it was reckoned to him as righteousness,” and he was called the \uline{friend} of God. You see that a man is justified by works and not by faith alone.

\textbf{John 15:14} - You are my friends if you do what I command you.

\textbf{James 4:4} - You adulterous people! Do you not know that friendship with the world is enmity with God? Therefore whoever wishes to be a friend of the world makes himself an enemy of God.

\textbf{2 Thessalonians 2:11} -  Therefore God sends them a strong delusion, so that they may believe what is false, (ESV)

\subsubsection{The love of the truth involves sanctification}
\label{sec:orgd4ef5e5}
\textbf{II Thessalonians 2:10-13} - and with all the deception of wickedness for those who perish, because they did not receive the love of the truth so as to be saved. For this reason God will send upon them a deluding influence so that they will believe what is false, in order that they all may be judged who did not believe the truth, but took pleasure in wickedness. But we should always give thanks to God for you, brethren beloved by the Lord, because God has chosen you from the beginning for \uline{salvation through sanctification by the Spirit and faith in the truth}.

\subsection{Dead faith is disobedient}
\label{sec:org2691e10}
I want to be clear, having faith in Jesus Christ is \uline{not} dead faith.
Dead faith is precisely \uline{not having faith} in Jesus Christ.

Adam's disobedience caused our disobedience:

\textbf{Romans 5:19} - For as by the one man's disobedience the many were made sinners, so by the one man's obedience the many will be made righteous.

\subsubsection{We were disobedient}
\label{sec:org371c9de}
\textbf{Romans 11:30} - Just as you were at one time disobedient to God but now have received mercy because of their disobedience,

\textbf{Romans 11:32} - For God has consigned all to disobedience, that he may have mercy on all.

\textbf{Ephesians 2:2} - in which you once walked, following the course of this world, following the prince of the power of the air, the spirit that is now at work in the sons of disobedience—

\subsubsection{We are brought to obedience}
\label{sec:org2f27603}
An obedient heart is required for it to not be 'dead faith'.

\textbf{John 7:17} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.

\textbf{II Corinthians 10:6} - being ready to punish every disobedience, when your obedience is complete.

\subsubsection{The disobedient will receive the wrath of God}
\label{sec:org0027900}

\textbf{Ephesians 5:6} - Let no one deceive you with empty words, for because of these things the wrath of God comes upon the sons of disobedience.

\textbf{John 3:36} - Whoever believes (G4100 pisteuo) in the Son has eternal life; whoever does not obey the Son shall not see life, but the wrath of God remains on him. (ESV)

\textbf{Hebrews 2:2} - For since the message declared by angels proved to be reliable and every transgression or disobedience received a just retribution,

\textbf{Hebrews 4:6} - Since therefore it remains for some to enter it, and those who formerly received the good news failed to enter because of disobedience,

\textbf{Hebrews 4:11} - Let us therefore strive to enter that rest, so that no one may fall by the same sort of disobedience.

\subsection{Saving faith}
\label{sec:org4fd9f3e}
\subsubsection{believing on Jesus}
\label{sec:orgb37c6c6}
I think baseline saving faith is believing on Jesus' name. He is the resurrection and the life.

Whoever believes in Him, though he die, yet shall he live, and everyone who lives and believes in Him shall never die.

Faith may come from simply observing Jesus work, reading Jesus' words and believing, or through work from disciples of Jesus, etc.

\textbf{John 11:14-15} Then Jesus told them plainly, Lazarus has died, and for your sake I am glad that I was not there, so that you may believe. But let us go to him.

It's for their sake, so that they would be able to believe (have faith).

\textbf{John 11:15} - and I am (G5463 chairo) glad (G5463 chairo) for your sakes (G1223 dia) that I was not there (G1563 ekei), so (G2443 hina) that you may believe (G4100 pisteuo); but let us go (G71 ago) to him.”

\begin{verbatim}
1  :  4100  pisteuo  pist-yoo'-o
2  
3   from 4102; to have faith (in, upon, or with respect to, a person or
4   thing), i.e. credit; by implication, to entrust (especially one's
5   spiritual well-being to Christ):--believe(-r), commit (to trust), put
6   in trust with.
7   see GREEK for 4102
\end{verbatim}

\textbf{John 11:23-27} - Jesus said to her, Your brother will rise again.  Martha said to him, I know that he will rise again in the resurrection on the last day.  Jesus said to her, I am the resurrection and the life. Whoever believes in me, though he die, yet shall he live, and everyone who lives and believes in me shall never die. Do you believe this?  She said to him, Yes, Lord; I believe that you are the Christ, the Son of God, who is coming into the world.

The person has to \textbf{really} believe - to have actual faith - the faith that continues to produce obedient work, the faith that continues to produce love.

Even Martha's faith here was put on display when she confessed,
"Yes, Lord; I believe that you are the Christ, the Son of God, who is coming into the world."
It shows she has faith.

\subsubsection{by the grace of God alone - no works}
\label{sec:orgfb1c4b5}
This guy was \uline{expecting} to receive - he had solid faith:

\textbf{Acts 3:5-7} - And he began to give them his attention, expecting to receive something from them. But Peter said, “I do not possess silver and gold, but what I do have I give to you: In the name of Jesus Christ the Nazarene-- walk!” And seizing him by the right hand, he raised him up; and immediately his feet and his ankles were strengthened.

\textbf{Acts 3:16} - And on the basis of faith in His name, it is \uline{the name of Jesus which has strengthened this man whom you see and know}; and \uline{the faith which comes through Him has given him this perfect health} in the presence of you all.

I think it's possible but you have to expect to receive it:

\textbf{John 11:25-26} - Jesus said to her, I am the resurrection and the life. Whoever believes in me, though he die, yet shall he live, and everyone who lives and believes in me shall never die. Do you believe this?

AMEN!!

\textbf{True} belief (does a person actually believe) is enough to be spared from death.

However, I still think that inheriting the Kingdom and inheriting eternal life involves being obedient to Jesus which leads to true knowledge.

\subsubsection{fear of God}
\label{sec:org752f151}
\textbf{Matthew 5:3} - Blessed are the poor in spirit, for theirs is the kingdom of heaven.

\textbf{Acts 10:34-35}: So Peter opened his mouth and said: Truly I understand that God shows no partiality, but in every nation anyone who fears him and does what is right is acceptable to him.

\textbf{Isaiah 66:2} - All these things my hand has made, and so all these things came to be, declares the LORD. But this is the one to whom I will look: he who is humble and contrite in spirit and trembles at my word. (ESV)

\begin{itemize}
\item Fear of God
\begin{itemize}
\item Fear-of-God = e.g. The poor in spirit recognise their need of God's mercy and tremble at His Word
\item \textbf{Luke 18:13} - But the tax collector, standing far off, would not even lift up his eyes to heaven, but beat his breast, saying, God, be merciful to me, a sinner! (ESV)
\begin{itemize}
\item And a sinner (with that attitude, I believe) who trusts God to justify him, that person's faith is counted as righteousness:
\begin{itemize}
\item \textbf{Romans 4:5} - And to the one who does not work but trusts him who justifies the ungodly, his faith is counted as righteousness,
\end{itemize}
\end{itemize}
\end{itemize}
\item Do what is right and acceptable to him
\begin{itemize}
\item \textbf{Romans 13:10} - Love does no wrong to a neighbor; therefore love is the fulfilling of the law. (ESV)
\end{itemize}
\end{itemize}

\subsubsection{a life of faith}
\label{sec:orgd45f8e9}
I think there's probably some nuance between between being spared from death, from condemnation and receiving eternal life.

\textbf{Romans 6:22} - But now that you have been set free from sin and have become slaves of God, the fruit you get leads to sanctification and its end, eternal life.

While Jesus can save someone from dying, I think eternal life the way it's presented is more than that - it's becoming a part of the Truth - it's union with Christ and with God.
I think it's \uline{perpetually having faith in Jesus}, having arrived at true knowledge of Him, and being in relationship with Him and with God.

\textbf{Matthew 19:29} - And everyone who has left houses or brothers or sisters or father or mother or children or lands, for my name's sake, will receive a hundredfold and will inherit eternal life. (ESV)

\subsubsection{Saving faith / Works of faith / Faith with works}
\label{sec:org47717cf}
Jesus said that patient endurance is a work.

\textbf{Revelation of John 2:2} - I know your works, your toil and your patient endurance, and how you cannot bear with those who are evil, but have tested those who call themselves apostles and are not, and found them to be false.

\textbf{Revelation of John 2:19} - I know your works, your love and faith and service and patient endurance, and that your latter works exceed the first.

Likewise, love for Jesus by obeying His commandments, love for Jesus by loving one's neighbour also qualifies as a work, love for Jesus by .

\textbf{Mark 11:23} - Truly, I say to you, whoever \textbf{says to this mountain, Be taken up and thrown into the sea}, and \textbf{does not doubt in his heart}, but believes that what he says \textbf{will come to pass}, it will be done for him.

Saving faith with work (yes, obedience is intrinsic to faith, like belief):

\textbf{Matthew 14:28-31} - And Peter answered him, Lord, if it is you, command me to come to you on the water. He said, Come. So Peter got out of the boat and walked on the water and came to Jesus. But when he saw the wind, he was afraid, and beginning to sink he cried out, Lord, save me. Jesus immediately reached out his hand and took hold of him, saying to him, O you of little faith, why did you doubt?

Obeying Jesus' commandments - believing Jesus and acting on Jesus' commandments \textbf{is} faith.

Keeping \uline{Jesus' deeds} is saving faith:

\textbf{Revelation of John 2:25-29} - Nevertheless what you have, \textbf{hold fast until I come. He who overcomes, and he who keeps My deeds until the end}, to him I will give authority over the nations; and he shall rule them with a rod of iron, as the vessels of the potter are broken to pieces, as I also have received authority from My Father; and I will give him the morning star. He who has an ear, let him hear what the Spirit says to the churches.’

James isn't talking about work of the law, he's talking about the works of faith.

God desires us to have mercy.

There are a lot of 'do nots' in the law but the most important thing is the 2 'do' commandments.
The 'do nots' are to stop people from doing bad things, but the 2 Greatest commandments command us to love God and our neighbour.

\textbf{Matthew 22:37-40} - And he said to him, You shall love the Lord your God with all your heart and with all your soul and with all your mind. This is the great and first commandment. And a second is like it: You shall love your neighbor as yourself. On these two commandments depend all the Law and the Prophets.

\textbf{James 2:13-17} - For judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment. What good is it, my brothers, if someone says he has faith but does not have works? Can that faith save him? If a brother or sister is poorly clothed and lacking in daily food, and one of you says to them, Go in peace, be warmed and filled, without giving them the things needed for the body, what good is that? So also faith by itself, if it does not have works, is dead.

MERCY.

\textbf{Matthew 12:3-8} - He said to them, Have you not read what David did when he was hungry, and those who were with him: how he entered the house of God and ate the bread of the Presence, which it was not lawful for him to eat nor for those who were with him, but only for the priests? Or have you not read in the Law how on the Sabbath the priests in the temple profane the Sabbath and are guiltless? I tell you, something greater than the temple is here. And if you had known what this means, I desire mercy, and not sacrifice, you would not have condemned the guiltless. For the Son of Man is lord of the Sabbath.

MERCY.

Faith without work is dead; it's useless.

That person is completely at the mercy of Jesus and of the saints, I think.

\textbf{1 Corinthians 3:15} - If anyone's work is burned up, he will suffer loss, though he himself will be saved, but only as through fire. (ESV)

But having true faith in Jesus is work.

Sometimes a person's work is all burned up but they are \textbf{still saved}.

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.} (ESV)

\subsubsection{Salvation is through grace alone, but through sanctification by the Spirit and faith in the truth, which is cooperative}
\label{sec:org3e0d5a5}

\textbf{II Thessalonians 2:10-13} - and with all the deception of wickedness for those who perish, because they did not receive the love of the truth so as to be saved. For this reason God will send upon them a deluding influence so that they will believe what is false, in order that they all may be judged who did not believe the truth, but took pleasure in wickedness. But we should always give thanks to God for you, brethren beloved by the Lord, because God has chosen you from the beginning for \uline{salvation through sanctification by the Spirit and faith in the truth}.

The Spirit sanctifies as we have faith in the truth.
The faith in the truth is the cooperative part, where we obey the truth.

\subsection{Working faith / faith with substance}
\label{sec:org340bf67}

Faith is a relationship with God. God has promised inheriting the Kingdom, inheriting eternal life to those who obey Him. But God is sovereign to save.

I made these equations to describe my understanding that faith is actually closely related to belief, obedience, hope and love, and they actually are not completely separate things.

\begin{verbatim}
 1  Faith-in-God = Hope-from/in-God * Work/Love
 2  
 3  Hope-from/in-God = Belief(believing God) * Truth(God's word is truth)
 4  
 5  Work/Love = Obedience * Faithfulness * Fear-of-God * Response-of-love-to-Jesus * Patient-Endurance(time)
 6  
 7  Obedience = Submitting to the Righteousness of God * Turning from sin, loving, showing mercy, etc.
 8  
 9  Fear-of-God = e.g. The poor in spirit recognise their need of God's mercy and tremble at His Word: "beat his breast, saying, God, be merciful to me, a sinner!"
10  
11  Response-of-love-to-Jesus = e.g. praise, thankfulness, obeying His commandments
12  
13  Love is proportional-to the baggage which has been forgiven
14  Love ∝ forgiven-baggage
15  
16  Obedience ∝ Love
17  
18  F = H * L
19  
20  Faith-in-God when tested by God is found to be true Faith in God.
21  Faith-in-God must submit to the Righteousness of God through faith in Jesus Christ,
22  Jesus Christ having paid the price of sin, enabling a relationship with God.
\end{verbatim}

But salvation is a gift and God is sovereign to save.
That's why it's grace.
Saved by grace through faith.

I think a person needs \textbf{some} faith to be saved, and faith works. Salvation has to be accepted.

\textbf{Ephesians 2:8-9} - For by grace you have been saved through faith. And this is not your own doing; it is the gift of God, not a result of works, so that no one may boast. (ESV)

A person must be at least willing to do His will - obedience is the essence of faith:

\textbf{John 7:17} - If anyone is willing to do His will, he will know of the teaching, whether it is of God or whether I speak from Myself.

There is still obedience required. Obedience is intrinsic to faith. Obedience leads to knowledge of Jesus.

\textbf{John 8:31-32} - So Jesus was saying to those Jews who had believed Him, “If you \textbf{continue in My word}, then you are truly disciples of Mine; and \textbf{you will know the truth}, and the truth will make you free.” (NASB)

\textbf{John 17:8} - For I have given them the words that you gave me, and they have received them and have \textbf{come to know in truth that I came from you}; \uline{and} they have believed that you sent me.

\textbf{I Timothy 2:3-6} - This is good, and it is pleasing in the sight of God our Savior, who desires all people to be saved and to \textbf{come to the knowledge of the truth}. For \uline{there is one God, and there is one mediator between God and men, the man Christ Jesus}, \uline{who gave himself as a ransom for all}, which is the testimony given at the proper time.

Everyone \textbf{believing} that Jesus is the Christ has been born of God, and everyone who loves the Father loves whoever has been born of him.

\begin{itemize}
\item \href{https://biblehub.com/interlinear/1\_john/5-1.htm}{1 John 5:1 Interlinear: Every one who is believing that Jesus is the Christ, of God he hath been begotten, and every one who is loving Him who did beget, doth love also him who is begotten of Him:}
\end{itemize}

\textbf{I John 5:1} - Everyone who believes that Jesus is the Christ has been born of God, and everyone who loves the Father loves whoever has been born of him. (ESV)

Therefore, we should receive Jesus' words and \uline{obey} Jesus and \uline{arrive} at the truth. Obedience is an essential part of faith. Like Abraham obeying God, or like Israel crossing through the Red Sea, it's obedience which \uline{leads} to sure belief, and obedience that leads a person into sure knowledge of the truth, and obedience which cooperates with sanctification.

\textbf{Exodus 14:14-16} - The Lord will fight for you, and you have only to be silent.  The Lord said to Moses, Why do you cry to me? Tell the people of Israel to go forward.  Lift up your staff, and stretch out your hand over the sea and divide it, that the people of Israel may go through the sea on dry ground.

Mercy is available:

\textbf{Luke 18:13} - But the tax collector, standing far off, would not even lift up his eyes to heaven, but beat his breast, saying, God, be merciful to me, a sinner! (ESV)

Those who fear God inherit the Kingdom.

\textbf{Matthew 5:3} - Blessed are the poor in spirit, for theirs is the kingdom of heaven.

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Some will be inherit the kingdom of Heaven & Those who are poor in spirit\\[0pt]
\end{tabular}
\end{center}

\textbf{Isaiah 66:2} - All these things my hand has made, and so all these things came to be, declares the LORD. But this is the one to whom I will look: he who is humble and contrite in spirit and trembles at my word. (ESV)

We need faithfulness and not faithlessness and disbelief to inherit the promises:

\textbf{Hebrews 12:16-17} - that no one is sexually immoral or unholy like Esau, who sold his birthright for a single meal. For you know that afterward, when he desired to inherit the blessing, he was rejected, for he found no chance to repent, though he sought it with tears.

\textbf{Revelation of John 2:2} - I know your works, your toil and your patient endurance, and how you cannot bear with those who are evil, but have tested those who call themselves apostles and are not, and found them to be false.

Here it says that unless the church \textbf{does the work} which it had started out doing, their lampstand will be removed from its place.

\textbf{Revelation of John 2:5} - Remember therefore from where you have fallen; repent, and do the works you did at first. If not, I will come to you and remove your lampstand from its place, unless you repent.

A response of love for Jesus \textbf{is} justifying work.

\textbf{Luke 7:47-50} - Therefore I tell you, her sins, which are many, are forgiven-for she loved much. But he who is forgiven little, loves little. And he said to her, Your sins are forgiven. Then those who were at table with him began to say among themselves, Who is this, who even forgives sins? And he said to the woman, Your faith has saved you; go in peace. (ESV)

\textbf{James 2:22-25} - You see that faith was active along with his works, and faith was completed by his works; and the Scripture was fulfilled that says, Abraham believed God, and it was counted to him as righteousness-and he was called a friend of God. You see that a person is justified by works and not by faith alone. And in the same way was not also Rahab the prostitute justified by works when she received the messengers and sent them out by another way?

ONLY \textbf{working faith} counts for anything. Even Paul agrees. However, it says 'in Christ Jesus', and I believe that those who trust in Jesus without work still abide, but by the skin of their teeth.

\textbf{Galatians 5:6} - For in Christ Jesus neither circumcision nor uncircumcision counts for anything, but \textbf{only faith working through love}. (ESV)

Loving God is obeying His commandments.

\textbf{I John 5:2-3} - By this we know that we love the children of God, when we love God and obey his commandments. For this is the love of God, that we keep his commandments. And his commandments are not burdensome.

\section{Kingdom of Servants}
\label{sec:orged86382}
\begin{itemize}
\item Jesus Christ is God's servant
\item We are Jesus' servants
\end{itemize}

\textbf{Psalms 34:22} - The LORD redeems the life of his servants; none of those who take refuge in him will be condemned. (ESV)

Jesus is God's servant:

\textbf{Acts 3:13} - The God of Abraham, the God of Isaac, and the God of Jacob, the God of our fathers, glorified \textbf{his servant Jesus}, whom you delivered over and denied in the presence of Pilate, when he had decided to release him.

\textbf{Acts 4:24-30} - And when they heard it, they lifted their voices together to God and said, Sovereign Lord, who made the heaven and the earth and the sea and everything in them, who through the mouth of our father David, your servant, said by the Holy Spirit, Why did the Gentiles rage, and the peoples plot in vain?  The kings of the earth set themselves, and the rulers were gathered together, against the Lord and against his Anointed— for truly in this city there were gathered together against your \textbf{holy servant Jesus}, whom you anointed, both Herod and Pontius Pilate, along with the Gentiles and the peoples of Israel, to do whatever your hand and your plan had predestined to take place.  And now, Lord, look upon their threats and grant to your servants to continue to speak your word with all boldness, while you stretch out your hand to heal, and signs and wonders are performed through the name of your holy servant Jesus.

\textbf{Romans 15:8} - For I tell you that Christ became a servant to the circumcised to show God's truthfulness, in order to confirm the promises given to the patriarchs,

Jesus, as God's servant, came to serve others, and to save:

\textbf{Mark 10:45} - For even the Son of Man came not to be served \textbf{but to serve}, and to give his life as a ransom for many.

Because God loves people, and wants them to be saved:

\textbf{John 3:16} - For God so loved the world, that he gave his only Son, that whoever believes in him should not perish but have eternal life.

God loves and sees as a son those who love (by obedience) Jesus and believe that He came from God:

\textbf{John 16:26-27} - In that day you will ask in my name, and I do not say to you that I will ask the Father on your behalf; for the Father himself loves you, because you have loved me and have believed that I came from God.

We are Jesus' servants:

\textbf{John 18:36} - Jesus answered, My kingdom is not of this world. If my kingdom were of this world, \textbf{my servants} would have been fighting, that I might not be delivered over to the Jews. But my kingdom is not from the world.

\textbf{Philippians 1:1} - Paul and Timothy, \textbf{servants of Christ Jesus}, To all the saints in Christ Jesus who are at Philippi, with the overseers and deacons:

\textbf{Colossians 4:12} - Epaphras, who is one of you, a \textbf{servant of Christ Jesus}, greets you, always struggling on your behalf in his prayers, that you may stand mature and fully assured in all the will of God.

For Jesus' sake we serve others:

\textbf{II Corinthians 4:5} - For what we proclaim is not ourselves, but Jesus Christ as Lord, with ourselves as your servants for Jesus' sake.

A good servant of Jesus is trained in the words of the faith and of the good doctrine.

\textbf{I Timothy 4:6} - If you put these things before the brothers, you will be a good \textbf{servant of Christ Jesus}, being trained in the words of the faith and of the good doctrine that you have followed.

God saved us through Jesus:

\textbf{Titus 1:1-3} - Paul, a servant of God and an apostle of Jesus Christ, for the sake of the faith of God's elect and their knowledge of the truth, which accords with godliness, in hope of eternal life, which God, who never lies, promised before the ages began and at the proper time manifested in his word through the preaching with which I have been entrusted by the command of God our Savior;

Servants of Jesus Christ are servants of God. Servants of God are servants of Jesus Christ:

\textbf{James 1:1} - James, a servant of God and of the Lord Jesus Christ, To the twelve tribes in the Dispersion: Greetings.

\textbf{I Corinthians 4:1} - This is how one should regard us, as servants of Christ and stewards of the mysteries of God.

The apostles of Jesus are servants:

\textbf{II Peter 1:1} - Simeon Peter, a servant and apostle of Jesus Christ, To those who have obtained a faith of equal standing with ours by the righteousness of our God and Savior Jesus Christ:

\textbf{Romans 1:1} - Paul, a \textbf{servant of Christ Jesus}, called to be an apostle, set apart for the gospel of God,

Jude is Jesus' servant:

\textbf{Jude 1:1} - Jude, a servant of Jesus Christ and brother of James, To those who are called, beloved in God the Father and kept for Jesus Christ:

The Revelation of John is for God's servants:

\textbf{Revelation of John 1:1} - The revelation of Jesus Christ, which God gave him to show to his servants the things that must soon take place. He made it known by sending his angel to his servant John,

If anyone's will is to be a servant of God, they will receive revelation which confirms the scriptures:

\textbf{John 7:17} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.

God's angels are servants:

\textbf{Revelation of John 19:10} - Then I fell down at his feet to worship him, but he said to me, You must not do that! I am a fellow servant with you and your brothers who hold to the testimony of Jesus. Worship God. For the testimony of Jesus is the spirit of prophecy.

The world cannot hate people who are disobedient to God:

\textbf{John 7:5-7} - For not even his brothers believed in him. Jesus said to them, My time has not yet come, but your time is always here. The world cannot hate you, but it hates me because I testify about it that its works are evil.

Servants of Jesus who are servants of God encounter resistance from the world:

\textbf{I John 2:15} - Do not love the world or the things in the world. If anyone loves the world, the love of the Father is not in him.

\textbf{John 12:25} -  Whoever loves his life loses it, and whoever hates his life in this world will keep it for eternal life.  (ESV)

\textbf{Matthew 6:30-32} - But if God so clothes the grass of the field, which today is alive and tomorrow is thrown into the oven, will he not much more clothe you, O you of little faith? Therefore do not be anxious, saying, What shall we eat? or What shall we drink? or What shall we wear? For the Gentiles seek after all these things, and your heavenly Father knows that you need them all.

\textbf{John 15:18-19} - If the world hates you, know that it has hated me before it hated you. If you were of the world, the world would love you as its own; but because you are not of the world, but I chose you out of the world, therefore the world hates you.

\textbf{John 15:23} - Whoever hates me hates my Father also.

\textbf{II Corinthians 11:23} - Are they servants of Christ? I am a better one—I am talking like a madman—with far greater labors, far more imprisonments, with countless beatings, and often near death.

Pleasing man is loving the world:

\textbf{Galatians 1:10} - For am I now seeking the approval of man, or of God? Or am I trying to please man? If I were still trying to please man, I would not be a servant of Christ.

\textbf{Ephesians 6:6} - not by the way of eye-service, as people-pleasers, but as servants of Christ, doing the will of God from the heart,

As servants of Jesus, we should encourage other servants of Jesus to maturity:

\textbf{Colossians 4:12} - Epaphras, who is one of you, a servant of Christ Jesus, greets you, always struggling on your behalf in his prayers, that you may stand mature and fully assured in all the will of God.

\textbf{Colossians 1:7} - just as you learned it from Epaphras our beloved fellow servant. He is a faithful minister of Christ on your behalf

\subsection{Entering into life / the Kingdom of Heaven}
\label{sec:org54ec91a}
Repentance is important:

\textbf{Matthew 3:3-9} - For this is he who was spoken of by the prophet Isaiah when he said, The voice of one crying in the wilderness: Prepare the way of the Lord; make his paths straight. Now John wore a garment of camel's hair and a leather belt around his waist, and his food was locusts and wild honey. Then Jerusalem and all Judea and all the region about the Jordan were going out to him, and they were baptized by him in the river Jordan, confessing their sins. But when he saw many of the Pharisees and Sadducees coming for baptism, he said to them, You brood of vipers! Who warned you to flee from the wrath to come? Bear fruit in keeping with repentance. And do not presume to say to yourselves, We have Abraham as our father, for I tell you, God is able from these stones to raise up children for Abraham.

Jesus will gather His \uline{wheat} into the barn:

\textbf{Matthew 3:10-12} - Even now the axe is laid to the root of the trees. Every tree therefore that does not bear good fruit is cut down and thrown into the fire. I baptize you with water for repentance, but he who is coming after me is mightier than I, whose sandals I am not worthy to carry. He will baptize you with the Holy Spirit and with fire. His winnowing fork is in his hand, and he will clear his threshing floor and gather his wheat into the barn, but the chaff he will burn with unquenchable fire.

We should become followers of Jesus.

Justice, mercy and faithfulness are \textbf{essential} for entering the Kingdom of God.

Repentance and holiness are \uline{very important} for entering the Kingdom of God too.

\textbf{Matthew 23:23-25} - Woe to you, scribes and Pharisees, hypocrites! For you tithe mint and dill and cumin, and have neglected the weightier matters of the law: \uline{justice and mercy and faithfulness. These you ought to have done, without neglecting the others}. You blind guides, straining out a gnat and swallowing a camel! Woe to you, scribes and Pharisees, hypocrites! For you clean the outside of the cup and the plate, but inside they are full of greed and self-indulgence.

We must turn from sin and lead godly lives with faith in Jesus:

\textbf{Matthew 5:14-20} - You are the light of the world. A city set on a hill cannot be hidden. Nor do people light a lamp and put it under a basket, but on a stand, and it gives light to all in the house. In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. Do not think that I have come to abolish the Law or the Prophets; I have not come to abolish them but to fulfill them. For truly, I say to you, until heaven and earth pass away, not an iota, not a dot, will pass from the Law until all is accomplished. Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. For I tell you, \uline{unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven}.

Believing John the Baptist is in accordance with believing Jesus:

\textbf{Matthew 21:28-32} - What do you think? A man had two sons. And he went to the first and said, Son, go and work in the vineyard today. And he answered, I will not, but afterward he changed his mind and went. And he went to the other son and said the same. And he answered, I go, sir, but did not go. Which of the two did the will of his father? They said, The first. Jesus said to them, Truly, I say to you, the tax collectors and the prostitutes go into the kingdom of God before you. For John came to you in the way of righteousness, and you did not believe him, but the tax collectors and the prostitutes believed him. And even when you saw it, you did not afterward change your minds and believe him.

The works of the law are not essential for being justified by God, but faith in Jesus is, and I believe that following Jesus is in accordance with having faith in Jesus:

\textbf{Galatians 2:16} - yet we know that a person is not justified by works of the law but through faith in Jesus Christ, so we also have believed in Christ Jesus, in order to be justified by faith in Christ and not by works of the law, because by works of the law no one will be justified.

Nevertheless, following the commandments and repenting from sin are of great value, I think.

But through faith in Christ Jesus we are justified and have peace with God.

\textbf{Galatians 3:24-26} - So then, the law was our guardian until Christ came, in order that we might be justified by faith. But now that faith has come, we are no longer under a guardian, for in Christ Jesus you are all sons of God, through faith.

Guideline:
\begin{itemize}
\item According to \texttt{Matthew 19}, keeping the commandments (10 commandments, from the heart, and in reality, accountable to God / the 2 Great commandments) is important for entering into the Kingdom of Heaven [well], entering into life [well].
\begin{itemize}
\item \textbf{Matthew 19:16-26} - And behold, a man came up to him, saying, Teacher, what good deed must I do to have eternal life? And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me. When the young man heard this he went away sorrowful, for he had great possessions. And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. When the disciples heard this, they were greatly astonished, saying, Who then can be saved? But Jesus looked at them and said, With man this is impossible, but with God all things are possible.
\item \textbf{II Corinthians 11:31} - The God and Father of the Lord Jesus, he who is blessed forever, knows that I am not lying.
\begin{itemize}
\item Apply them in truth - keep accountability to God, not merely to other people. God can see.
\end{itemize}
\end{itemize}
\item Also, lay up treasure in Heaven.
\begin{itemize}
\item \textbf{Matthew 19:21} - Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me.
\end{itemize}
\item Also, follow Jesus
\begin{itemize}
\item Obey Jesus' commandments
\item Become a servant of Jesus
\item \textbf{Matthew 10:24} - A disciple is not above his teacher, nor a servant above his master.
\item \textbf{Matthew 18:33} - And should not you have had mercy on your fellow servant, as I had mercy on you?
\item We must forgive others
\end{itemize}
\end{itemize}

Follow the law in faith, not works, making yourself accountable to God, not men:

We need to be justified before God, and that is through faith in Jesus Christ.

\textbf{Luke 16:15-17} - And he said to them, You are those who justify yourselves before men, but God knows your hearts. For what is exalted among men is an abomination in the sight of God.  The Law and the Prophets were until John; since then the good news of the kingdom of God is preached, and everyone forces his way into it. But it is easier for heaven and earth to pass away than for one dot of the Law to become void.

Do the will of Father God.

To do the will of Father God, one must do it in truth - God knows and can see the heart.

\textbf{II Corinthians 11:31} - The God and Father of the Lord Jesus, he who is blessed forever, knows that I am not lying.

Don't be a ravenous wolf on the inside (repent from sin)!

\textbf{Matthew 7:14-23} - For the gate is narrow and the way is hard that leads to life, and those who find it are few.  Beware of false prophets, who come to you in sheep's clothing but inwardly are ravenous wolves.  You will recognize them by their fruits. Are grapes gathered from thornbushes, or figs from thistles?  So, every healthy tree bears good fruit, but the diseased tree bears bad fruit.  A healthy tree cannot bear bad fruit, nor can a diseased tree bear good fruit.  Every tree that does not bear good fruit is cut down and thrown into the fire.  Thus you will recognize them by their fruits.  Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven.  On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name?  And then will I declare to them, I never knew you; depart from me, you workers of lawlessness.

We \textbf{must} obey God's commandments to love Him and love our neighbour, and have faith in Jesus Christ.
We must submit to the righteousness of God.

\textbf{II Peter 1:10-11} - Therefore, brothers, be all the more diligent to make your calling and election sure, for if you practice these qualities you will never fall. For in this way there will be richly provided for you an \uline{entrance into the eternal kingdom} of our Lord and Savior Jesus Christ.

\subsubsection{We practice personal righteousness AND we have obtained a faith of equal standing with the Apostles \underline{by the righteousness of our God and Savior Jesus Christ}}
\label{sec:orgc640a76}
An entrance into the eternal kingdom of our Lord and Saviour Jesus Christ will
be provided, so long as you do this.

\textbf{II Peter 1:1-11} - Simeon Peter, a servant and apostle of Jesus Christ, To those who have obtained a faith of equal standing with ours by the righteousness of our God and Savior Jesus Christ: May grace and peace be multiplied to you in the knowledge of God and of Jesus our Lord.  His divine power has granted to us all things that pertain to life and godliness, through the knowledge of him who called us to his own glory and excellence, by which he has granted to us his precious and very great promises, so that through them you may become partakers of the divine nature, having escaped from the corruption that is in the world because of sinful desire.  For this very reason, make every effort to supplement your faith with virtue, and virtue with knowledge, and knowledge with self-control, and self-control with steadfastness, and steadfastness with godliness, and godliness with brotherly affection, and brotherly affection with love.  For if these qualities are yours and are increasing, they keep you from being ineffective or unfruitful in the knowledge of our Lord Jesus Christ.  For whoever lacks these qualities is so nearsighted that he is blind, having forgotten that he was cleansed from his former sins.  Therefore, brothers, be all the more diligent to make your calling and election sure, for if you practice these qualities you will never fall.  For in this way \uline{there will be richly provided for you an entrance into the eternal kingdom of our Lord and Savior Jesus Christ}.

\subsubsection{Follow the commandments (get out of falsehood; stop sinning) and put your heart in Heaven}
\label{sec:org60bfcb5}
\textbf{Matthew 6:19-21} - Do not lay up for yourselves treasures on earth, where moth and rust destroy and where thieves break in and steal, but lay up for yourselves treasures in heaven, where neither moth nor rust destroys and where thieves do not break in and steal. For where your treasure is, there your heart will be also.

\emph{\textbf{Loving God is obedience to God.}}

\textbf{I John 5:2-3} - By this we know that we love the children of God, when we love God and obey his commandments. For this is the love of God, that we keep his commandments. And his commandments are not burdensome.

AMEN!!

\textbf{Deuteronomy 11:13-14} - And if you will indeed obey my commandments that I command you today, to love the Lord your God, and to serve him with all your heart and with all your soul, he will give the rain for your land in its season, the early rain and the later rain, that you may gather in your grain and your wine and your oil.

\textbf{I Kings 3:14} - And if you will walk in my ways, keeping my statutes and my commandments, as your father David walked, then I will lengthen your days.

AMEN!!

Obey God, put your heart in Heaven, follow Jesus.

\textbf{Matthew 19:16-26} - And behold, a man came up to him, saying, Teacher, what good deed must I do to have eternal life? And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me. When the young man heard this he went away sorrowful, for he had great possessions. And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. When the disciples heard this, they were greatly astonished, saying, Who then can be saved? But Jesus looked at them and said, With man this is impossible, but with God all things are possible.

AMEN!!

The guy thought he was obeying the commandments, but he still coveted his possessions, probably making an idol out of his money.
I don't think he was really following the commandments from the heart.
Also he wasn't prepared to give up his old life to follow Jesus.
Following Jesus is obeying his commandments.

\subsubsection{Then arriving at eternal life - follow Jesus}
\label{sec:orgc65dee5}
\textbf{Matthew 19:17-21} - And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me.

\textbf{Romans 2:7-8} - to those who by patience in well-doing seek for glory and honor and immortality, he will give eternal life; but for those who are self-seeking and do not obey the truth, but obey unrighteousness, there will be wrath and fury.

\subsection{We are certainly supposed to keep the commandments - we're supposed to love God and our neighbour in truth}
\label{sec:org8f88ec7}
\subsubsection{Keeping the commandments is how to love.}
\label{sec:org0087205}

\textbf{Romans 13:9} - The commandments, You shall not commit adultery, You shall not murder, You shall not steal, You shall not covet, and any other commandment, are summed up in this word: You shall love your neighbor as yourself.

AMEN!!

\textbf{Galatians 5:14} - For the whole law is fulfilled in one word: You shall love your neighbor as yourself.

AMEN!!

\textbf{James 2:8-13} - If you really fulfill the royal law according to the Scripture, You shall love your neighbor as yourself, you are doing well. But if you show partiality, you are committing sin and are convicted by the law as transgressors. For whoever keeps the whole law but fails in one point has become accountable for all of it. For he who said, Do not commit adultery, also said, Do not murder. If you do not commit adultery but do murder, you have become a transgressor of the law. So speak and so act as those who are to be judged under the law of liberty. For judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment.

AMEN!!

\textbf{Romans 2:13} - For it is not the hearers of the law who are righteous before God, but the doers of the law who will be justified. (ESV)

Yup - and in truth. I think the commandments often need to be looked at to see what loving looks like.

\textbf{Romans 3:31} - Do we then overthrow the law by this faith? By no means! On the contrary, we uphold the law. (ESV)

AMEN!!

\subsubsection{It matters that we are loving, going into eternity}
\label{sec:orga4555bb}
\textbf{Matthew 5:30} - And if your right hand causes you to sin, cut it off and throw it away. For it is better that you lose one of your members than that your whole body go into hell. (ESV)

\textbf{Matthew 18:3} - and said, Truly, I say to you, unless you turn and become like children, you will never enter the kingdom of heaven.

\textbf{Matthew 18:9} - And if your eye causes you to sin, tear it out and throw it away. It is better for you to enter life with one eye than with two eyes to be thrown into the hell of fire.

\subsubsection{We must submit to the righteousness from God through faith in Jesus}
\label{sec:orge5ee830}
\textbf{Romans 10:3-5} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness. For Christ is the end of the law for righteousness to everyone who believes. For Moses writes about the righteousness that is based on the law, that the person who does the commandments shall live by them.

Following the law is how to love. It's always important.

Following Jesus is having faith in Him.

Submitting to the righteousness that comes through having faith in Jesus is believing and obeying the Gospel.

\subsubsection{All things \textbf{are} put under Jesus' feet whether we are compliant or understand it or not}
\label{sec:org0c79565}
The victory has already been won.

Jesus Christ has overcome the world and He is the head of all rule and authority.

Everything is in subjection to Jesus, God has left nothing outside Jesus' control.

From our perspective it may look like things are still being brought into subjection to Him:

\textbf{John 16:33} - I have said these things to you, that in me you may have peace.  In the world you will have tribulation.  But take heart; I have overcome the world.  (ESV)

\textbf{Colossians 2:9-15} - For in him the whole fullness of deity dwells bodily, and you have been filled in him, who is the head of all rule and authority. In him also you were circumcised with a circumcision made without hands, by putting off the body of the flesh, by the circumcision of Christ, having been buried with him in baptism, in which you were also raised with him through faith in the powerful working of God, who raised him from the dead. And you, who were dead in your trespasses and the uncircumcision of your flesh, God made alive together with him, having forgiven us all our trespasses, by canceling the record of debt that stood against us with its legal demands. This he set aside, nailing it to the cross. He disarmed the rulers and authorities and put them to open shame, by triumphing over them in him.

\textbf{Colossians 2:20} - If with Christ you died to the elemental spirits of the world, why, as if you were still alive in the world, do you submit to regulations—

Even from the believer's perspective, we have already won:

\textbf{1 John 4:4} -  Little children, you are from God and have overcome them, for he who is in you is greater than he who is in the world.  (ESV)

\textbf{Romans 8:37} - No, in all these things we are more than conquerors through him who loved us.

Father God is LORD of Heaven and Earth:

\textbf{Matthew 11:25} - At that time Jesus declared, I thank you, Father, Lord of heaven and earth, that you have hidden these things from the wise and understanding and revealed them to little children;

\textbf{Luke 10:21} - In that same hour he rejoiced in the Holy Spirit and said, I thank you, Father, Lord of heaven and earth, that you have hidden these things from the wise and understanding and revealed them to little children; yes, Father, for such was your gracious will.

\textbf{Acts 17:24} - The God who made the world and everything in it, being Lord of heaven and earth, does not live in temples made by man,

All things are placed under Jesus' feet:

\textbf{Psalms 8:6} - You have given him dominion over the works of your hands; you have put all things under his feet,

\textbf{Colossians 2:15} - He disarmed the rulers and authorities and put them to open shame, by triumphing over them in him.  (ESV)

Jesus has already conquered:

\textbf{Revelation of John 3:21} - The one who conquers, I will grant him to sit with me on my throne, as I also conquered and sat down with my Father on his throne.

In our own lives we conquer the enemy by the blood of the Lamb (the blood of Jesus Christ) and the word of our testimony:

\textbf{Revelation of John 12:11} - And they have conquered him by the blood of the Lamb and by the word of their testimony, for they loved not their lives even unto death.

All things are under God's feet. \uline{In the LORD}, all of the offspring of Israel shall be justified:

\textbf{Isaiah 45:22-25} - Turn to me and be saved, all the ends of the earth! For I am God, and there is no other. By myself I have sworn; from my mouth has gone out in righteousness a word that shall not return: To me every knee shall bow, every tongue shall swear allegiance. Only in the LORD, it shall be said of me, are righteousness and strength; to him shall come and be ashamed all who were incensed against him. In the LORD all the offspring of Israel shall be justified and shall glory. (ESV)

Everything is in subjection to Jesus, God has left nothing outside Jesus' control.

From our perspective it may look like things are still being brought into subjection to Him:

\textbf{Ephesians 1:22} - And he put all things under his feet and gave him as head over all things to the church,

\textbf{Hebrews 2:5-8} - Now it was not to angels that God subjected the world to come, of which we are speaking. It has been testified somewhere, What is man, that you are mindful of him, or the son of man, that you care for him? You made him for a little while lower than the angels; you have crowned him with glory and honor, putting everything in subjection under his feet. Now in putting \textbf{everything in subjection to him}, \uline{he left nothing outside his control}. At present, we do not yet see everything in subjection to him.

Everything is put in subjection under Jesus and in subjection under Father God:

\textbf{I Corinthians 15:24-28} - Then comes the end, when he delivers the kingdom to God the Father after destroying every rule and every authority and power. For he must reign until he has put all his enemies under his feet. The last enemy to be destroyed is death. For God has put all things in subjection under his feet. But when it says, all things are put in subjection, it is plain that he is excepted who put all things in subjection under him. When all things are subjected to him, then the Son himself will also be subjected to him who put all things in subjection under him, that God may be all in all.

\subsubsection{The Kingdom of Heaven - is a kingdom of servants}
\label{sec:org0ea0c32}
\subsubsection{you must be holy!}
\label{sec:org8c57e25}
The parable of the 10 virgins:

\textbf{Matthew 25:1-13} - Then the kingdom of heaven will be like ten virgins who took their lamps and went to meet the bridegroom. Five of them were foolish, and five were wise. For when the foolish took their lamps, they took no oil with them, but the wise took flasks of oil with their lamps. As the bridegroom was delayed, they all became drowsy and slept. But at midnight there was a cry, Here is the bridegroom! Come out to meet him. Then all those virgins rose and trimmed their lamps. And the foolish said to the wise, Give us some of your oil, for our lamps are going out. But the wise answered, saying, Since there will not be enough for us and for you, go rather to the dealers and buy for yourselves. And while they were going to buy, the bridegroom came, and those who were ready went in with him to the marriage feast, and the door was shut. Afterward the other virgins came also, saying, Lord, lord, open to us. But he answered, Truly, I say to you, I do not know you. Watch therefore, for you know neither the day nor the hour.

When we repent from sin we allow Jesus' holiness to shine through us increasingly.
Therefore, it's really not our own holiness or power that is responsible for miracles that happen through us or in cooperation with us, but it is Jesus' power and holiness.
Jesus is the True Vine. We are the branches. AMEN!! We can do nothing apart from Him. AMEN!!
Everyone who names the name of the Lord must depart from iniquity.
Our bodies are a vessel for Jesus' holiness to shine out of. It's the vessel of the Holy Spirit:
Jesus is the light in us, and we must let our light shine.

\subsubsection{you must be a servant!}
\label{sec:org48b9510}
The parable of the bags of gold:

\textbf{Matthew 25:14-30} - For it will be like a man going on a journey, who called \uline{his servants and entrusted to them his property}. To one he gave five talents, to another two, to another one, to each according to his ability. Then he went away. He who had received the five talents went at once and traded with them, and he made five talents more. So also he who had the two talents made two talents more. But he who had received the one talent went and dug in the ground and hid his master's money. Now after a long time the master of those servants came and settled accounts with them. And he who had received the five talents came forward, bringing five talents more, saying, Master, you delivered to me five talents; here I have made five talents more. His master said to him, \textbf{Well done, good and faithful servant. You have been faithful over a little; I will set you over much}. Enter into the joy of your master. And he also who had the two talents came forward, saying, Master, you delivered to me two talents; here I have made two talents more. His master said to him, Well done, good and faithful servant. You have been faithful over a little; I will set you over much. Enter into the joy of your master. He also who had received the one talent came forward, saying, Master, I knew you to be a hard man, reaping where you did not sow, and gathering where you scattered no seed, so I was afraid, and I went and hid your talent in the ground. Here you have what is yours. But his master answered him, You wicked and slothful servant! You knew that I reap where I have not sowed and gather where I scattered no seed? Then you ought to have invested my money with the bankers, and at my coming I should have received what was my own with interest. So take the talent from him and give it to him who has the ten talents. \textbf{For to everyone who has will more be given, and he will have an abundance. But from the one who has not, even what he has will be taken away. And cast the worthless servant into the outer darkness}. In that place there will be weeping and gnashing of teeth. (ESV)

Eternal punishment vs eternal life:

\textbf{Matthew 25:31-46} - When the Son of Man comes in his glory, and all the angels with him, then he will sit on his glorious throne. Before him will be gathered all the nations, and he will separate people one from another as a shepherd separates the sheep from the goats. And he will place the sheep on his right, but the goats on the left. Then the King will say to those on his right, Come, you who are blessed by my Father, inherit the kingdom prepared for you from the foundation of the world. For \textbf{I was hungry and you gave me food, I was thirsty and you gave me drink, I was a stranger and you welcomed me, I was naked and you clothed me, I was sick and you visited me, I was in prison and you came to me. Then the righteous will answer him, saying, Lord, when did we see you hungry and feed you, or thirsty and give you drink? And when did we see you a stranger and welcome you, or naked and clothe you? And when did we see you sick or in prison and visit you? And the King will answer them, Truly, I say to you, as you did it to one of the least of these my brothers, you did it to me.} Then he will say to those on his left, Depart from me, you cursed, into the eternal fire prepared for the devil and his angels. For I was hungry and you gave me no food, I was thirsty and you gave me no drink, I was a stranger and you did not welcome me, naked and you did not clothe me, sick and in prison and you did not visit me. Then they also will answer, saying, Lord, when did we see you hungry or thirsty or a stranger or naked or sick or in prison, and did not minister to you? Then he will answer them, saying, Truly, I say to you, as you did not do it to one of the least of these, you did not do it to me. And these will go away into eternal punishment, but the righteous into eternal life. (ESV)

\section{Coming into the Body of Christ / into abiding in Jesus}
\label{sec:org82e0446}
\textbf{Psalms 127:1} - Unless the Lord builds the house, those who build it labor in vain. Unless the Lord watches over the city, the watchman stays awake in vain.

\textbf{Luke 6:47-49} - Everyone who comes to me and hears my words and does them, I will show you what he is like: he is like a man building a house, who dug deep and laid the foundation on the rock. And when a flood arose, the stream broke against that house and could not shake it, because it had been well built. But the one who hears and does not do them is like a man who built a house on the ground without a foundation. When the stream broke against it, immediately it fell, and the ruin of that house was great. (ESV)

We must throw out the old and allow God to build the new house/life for us.
We must cooperate with God by doing what Jesus has instructed, and not fighting against Jesus' commandments.

We must obey Jesus.

\section{Faith}
\label{sec:org67fec85}
One must have faith to receive the gift of salvation.

\textbf{Mark 11:22} - And Jesus answered them, Have faith in God.

The basic Faith equation is Believing-God * Obedience/Action/Work.

\textbf{Mark 11:23} - Truly, I say to you, whoever \textbf{says to this mountain, Be taken up and thrown into the sea}, and \textbf{does not doubt in his heart}, but believes that what he says \textbf{will come to pass}, it will be done for him.

\textbf{Mark 11:24} - Therefore I tell you, whatever you ask in prayer, believe that you have received it, and it will be yours.

Here, asking God in prayer is the work.

\section{Receiving the Holy Spirit}
\label{sec:orgebbd075}
\subsection{The Holy Spirit cleanses the heart by faith}
\label{sec:org2638e9e}
\textbf{Acts 15:7} - And after there had been much debate, Peter stood up and said to them, Brothers, you know that in the early days God made a choice among you, that by my mouth the Gentiles should hear the word of the gospel and believe.

\textbf{Acts 15:8-9} - And God, who knows the heart, bore witness to them, by giving them the Holy Spirit just as he did to us, and he made no distinction between us and them, having cleansed their hearts by faith.

For example, out of faith in trying to follow the 10 Commandments / 2 Great Commandments, the heart is cleaned by the Holy Spirit.

Faith involves obedience. It's repentance from sin to the aligning of the heart to God's commandments.

\subsection{The faith itself may be a gift, but certainly is cooperative}
\label{sec:org9f1e07a}
God and Abram (Abraham) had a real relationship first.

God spoke to Abram first, and then Abram \textbf{obeyed}.
Abraham was faithful.
God noticed Abram's faithfulness, and told Abram he would be rewarded.
God gave Abram a promise.
Abram believed God.

But God made the first move.
The first move from Abraham's perspective was obedience, followed by belief.

The Lord God spoke first - this itself is a gift. We have the Bible and the testimony of others as a gift from God.
We must then believe what is said in the Holy Scriptures and trust it and obey it (put into practice).

The Holy Spirit goes to those who obey God, and causes the person to walk in God's precepts - stopping lying, stealing, coveting, idolizing, cheating, etc.

\textbf{Acts 5:32} - And we are witnesses to these things, and so is \textbf{the Holy Spirit, whom God has given to those who obey him}. (ESV)

Faith involves:
\begin{itemize}
\item Obedience
\item Loyalty (faithfulness to God)
\item God rewarded Abram with a promise
\item Abram believed God
\item God counted Abram's belief as righteousness
\end{itemize}

\textbf{Genesis 12:1} - Now the Lord said to Abram, Go from your country and your kindred and your father's house to the land that I will show you.

Abraham \textbf{obeyed} God.

\textbf{Genesis 12:4} - So Abram went, as the Lord had told him, and Lot went with him. Abram was seventy-five years old when he departed from Haran.

God promised him something, and gave Abram an instruction.

\textbf{Genesis 13:14} - The Lord said to Abram, after Lot had separated from him, Lift up your eyes and look from the place where you are, northward and southward and eastward and westward, for all the land that you see I will give to you and to your offspring forever. I will make your offspring as the dust of the earth, so that if one can count the dust of the earth, your offspring also can be counted. Arise, walk through the length and the breadth of the land, for I will give it to you.

Abram obeyed.

\textbf{Genesis 13:18} - So Abram moved his tent and came and settled by the oaks of Mamre, which are at Hebron, and there he built an altar to the Lord.

OBEDIENCE!

\textbf{Hebrews 5:9-10} - And being made perfect, he became the source of eternal salvation to all who \textbf{obey} him, being designated by God a high priest after the order of Melchizedek.

Abram interacted with Melchizedek, priest of God Most High, blessed by God Most High. Abram was faithful to God even when God wasn't speaking directly to Him. God can see everything though.

\textbf{Genesis 14:18-20} - And Melchizedek king of Salem brought out bread and wine. (He was priest of God Most High. ) And he blessed him and said, Blessed be Abram by God Most High, Possessor of heaven and earth; and blessed be God Most High, who has delivered your enemies into your hand! And Abram gave him a tenth of everything.

Abram, in an act of faith with faithfulness, displayed loyalty to God. Abram wanted to prove it will be God who has empowered future blessing which Abram has faith about.

\textbf{Genesis 14:21-24} - And the king of Sodom said to Abram, Give me the persons, but take the goods for yourself. But Abram said to the king of Sodom, I have lifted my hand to the Lord, God Most High, Possessor of heaven and earth, that I would not take a thread or a sandal strap or anything that is yours, lest you should say, I have made Abram rich. I will take nothing but what the young men have eaten, and the share of the men who went with me. Let Aner, Eshcol, and Mamre take their share.

God noticed and gave Abram a vision and made a promise to Abram, and Abram believed God and God counted it to Abram as righteousness.

\textbf{Genesis 15:1} - After these things the word of the Lord came to Abram in a vision: Fear not, Abram, I am your shield; your reward shall be very great. But Abram said, O Lord God, what will you give me, for I continue childless, and the heir of my house is Eliezer of Damascus? And Abram said, Behold, you have given me no offspring, and a member of my household will be my heir. And behold, the word of the Lord came to him: This man shall not be your heir; your very own son shall be your heir. And he brought him outside and said, Look toward heaven, and number the stars, if you are able to number them. Then he said to him, So shall your offspring be. And he believed the Lord, and he counted it to him as righteousness.

\subsubsection{Faith and works - they overlap and are \textbf{not} mutually exclusive!}
\label{sec:org22d2d72}
\textbf{James 2:22-25} - You see that faith was active along with his works, and faith was completed by his works; and the Scripture was fulfilled that says, Abraham believed God, and it was counted to him as righteousness-and he was called a friend of God. You see that a person is justified by works and not by faith alone. And in the same way was not also Rahab the prostitute justified by works when she received the messengers and sent them out by another way?

A person, I think, can be justified by faith that includes obedient action.

Even continued belief in the form of patient endurance is a work, I think!

I believe justification is God's prerogative, and He justifies because of our faith in Jesus, not because of any dead work we offer Him. I just believe that faith in Jesus may include obedient action.
Actually, I believe that even believing in Jesus is obedience, because Jesus commanded it.

\textbf{Romans 5:1} - Therefore, since we have been justified by faith, we have peace with God through our Lord Jesus Christ.

\textbf{Galatians 2:16} - yet we know that a person is not justified by works of the law but through faith in Jesus Christ, so we also have believed in Christ Jesus, in order to be justified by faith in Christ and not by works of the law, because by works of the law no one will be justified.

\textbf{Galatians 3:24-26} - So then, the law was our guardian until Christ came, in order that we might be justified by faith. But now that faith has come, we are no longer under a guardian, for in Christ Jesus you are all sons of God, through faith.

But I think God can save a person who has belief without work because God is sovereign to save in this way.

Anyway, see Revelation and you will see Jesus points out different works for different churches.

\textbf{Revelation of John 2:2} - I know your works, your toil and your patient endurance, and how you cannot bear with those who are evil, but have tested those who call themselves apostles and are not, and found them to be false.

\textbf{Revelation of John 2:5} - Remember therefore from where you have fallen; repent, and do the works you did at first. If not, I will come to you and remove your lampstand from its place, unless you repent.

\textbf{Revelation of John 2:6} - Yet this you have: you hate the works of the Nicolaitans, which I also hate.

\textbf{Revelation of John 2:19} - I know your works, your love and faith and service and patient endurance, and that your latter works exceed the first.

\textbf{Revelation of John 2:22-23} - Behold, I will throw her onto a sickbed, and those who commit adultery with her I will throw into great tribulation, unless they repent of her works, and I will strike her children dead. And all the churches will know that I am he who searches mind and heart, and \textbf{I will give to each of you as your works deserve}.

\textbf{Revelation of John 3:1-2} - And to the angel of the church in Sardis write: The words of him who has the seven spirits of God and the seven stars. I know your works. You have the reputation of being alive, but you are dead. Wake up, and strengthen what remains and is about to die, for I have not found your works complete in the sight of my God.

\textbf{Revelation of John 3:8} - I know your works. Behold, I have set before you an open door, which no one is able to shut. I know that you have but little power, and yet you have kept my word and have not denied my name.

\textbf{Revelation of John 3:15} - I know your works: you are neither cold nor hot. Would that you were either cold or hot!

\subsubsection{The faith of Abraham looks like this. This is what salvation-accepting faith looks like}
\label{sec:orgac84b62}
To be justified, a person must \uline{walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

Salvation is received by faith - which necessitates an obedient heart:

\textbf{Romans 3:25} - whom God put forward as a propitiation by his blood, to be received by faith. This was to show God's righteousness, because in his divine forbearance he had passed over former sins.

Faith receives - believing in Him is \uline{having faith} in Him - trusting Him:

\textbf{Acts 10:41-44} - not to all the people but to us who had been chosen by God as witnesses, who ate and drank with him after he rose from the dead. And he commanded us to preach to the people and to testify that he is the one appointed by God to be judge of the living and the dead. To him all the prophets bear witness that everyone who believes in him receives forgiveness of sins through his name. While Peter was still saying these things, the Holy Spirit fell on all who heard the word. (ESV)

Although a gift, salvation must be asked for and sought after:

\textbf{Luke 11:9-13} - And I tell you, \textbf{ask, and it will be given} to you; \textbf{seek, and you will find}; \textbf{knock, and it will be opened} to you.  For \textbf{everyone who asks receives}, and \textbf{the one who seeks finds}, and to \textbf{the one who knocks it will be opened}.  What father among you, if his son asks for a fish, will instead of a fish give him a serpent; or if he asks for an egg, will give him a scorpion?  If you then, who are evil, know how to give \textbf{good gifts} to your children, how much more will the heavenly Father give the Holy Spirit to those who ask him!

\emph{\textbf{Obeying God.}}

\textbf{Hebrews 11:8} - By faith Abraham obeyed when he was called to go out to a place that he was to receive as an inheritance. And he went out, not knowing where he was going.

\textbf{Genesis 12:1-3} - Now the LORD said to Abram, Go from your country and your kindred and your father's house to the land that I will show you. And I will make of you a great nation, and I will bless you and make your name great, so that you will be a blessing. I will bless those who bless you, and him who dishonors you I will curse, and in you all the families of the earth shall be blessed. (ESV)

\emph{\textbf{Believing God.}}

\textbf{Genesis 15:1} - After these things the word of the Lord came to Abram in a vision: Fear not, Abram, I am your shield; your reward shall be very great. But Abram said, O Lord God, what will you give me, for I continue childless, and the heir of my house is Eliezer of Damascus? And Abram said, Behold, you have given me no offspring, and a member of my household will be my heir. And behold, the word of the Lord came to him: This man shall not be your heir; your very own son shall be your heir. And he brought him outside and said, Look toward heaven, and number the stars, if you are able to number them. Then he said to him, So shall your offspring be. And he believed the Lord, and he counted it to him as righteousness.

\emph{\textbf{Conviction.}}

\textbf{Hebrews 11:17-19} - By faith Abraham, when he was tested, offered up Isaac, and he who had received the promises was in the act of offering up his only son, of whom it was said, Through Isaac shall your offspring be named. He considered that God was able even to raise him from the dead, from which, figuratively speaking, he did receive him back.

Like Abraham, a believer's faith may be tested.

\emph{\textbf{Trust in God.}},

\emph{\textbf{Fear of God.}},

\emph{\textbf{Testable faith.}}

\textbf{Genesis 22:9-14} - When they came to the place of which God had told him, Abraham built the altar there and laid the wood in order and bound Isaac his son and laid him on the altar, on top of the wood. Then Abraham reached out his hand and took the knife to slaughter his son. But the angel of the Lord called to him from heaven and said, Abraham, Abraham! And he said, Here am I. He said, Do not lay your hand on the boy or do anything to him, for now I know that you fear God, seeing you have not withheld your son, your only son, from me. And Abraham lifted up his eyes and looked, and behold, behind him was a ram, caught in a thicket by his horns. And Abraham went and took the ram and offered it up as a burnt offering instead of his son. So Abraham called the name of that place, The Lord will provide; as it is said to this day, On the mount of the Lord it shall be provided.

\emph{\textbf{Holding onto the promise, even to death if required.}}

\textbf{Hebrews 11:13} - These all died in faith, not having received the things promised, but having seen them and greeted them from afar, and having acknowledged that they were strangers and exiles on the earth.

Like Abraham, a believer keeps the faith right to the end of their life or until Jesus takes them home.

\emph{\textbf{Patient endurance / waiting on God (belief * time).}}

We should have \textbf{busy} (non-sluggish) faith,
and imitate the faith of people such as
Abraham, so that we inherit the promises.
We can believe those promises which we inherit.

\textbf{Hebrews 6:12-15} - so that you may not be sluggish, but imitators of those who through faith and patience inherit the promises. For when God made a promise to Abraham, since he had no one greater by whom to swear, he swore by himself, saying, Surely I will bless you and multiply you. And thus Abraham, having patiently waited, obtained the promise.

\textbf{Revelation of John 3:8} - I know your \textbf{works}. Behold, I have set before you an open door, which no one is able to shut. I know that you have but little power, and yet you have \textbf{kept my word and have not denied my name}. Behold, I will make those of the synagogue of Satan who say that they are Jews and are not, but lie-behold, I will make them come and bow down before your feet and they will learn that I have loved you. Because you have kept my word about \textbf{patient endurance}, I will keep you from the hour of trial that is coming on the whole world, to try those who dwell on the earth.

\href{https://www.youtube.com/watch?v=GamlYvhJyiM}{Rich Mullins - Sometimes By Step - YouTube}

\subsubsection{The repentance of turning away from sin is an act of faith / a work of faith and also essential for eternal life, I think}
\label{sec:org9ce256c}
\textbf{Matthew 21:32} - For John came to you in the way of righteousness, and you did not believe him, but the tax collectors and the prostitutes believed him. And even when you saw it, you did not afterward change your minds and believe him. (ESV)

To follow the law by faith, I think, is to not lie, commit adultery, idolize, etc. in truth and reality, keeping yourself accountable to God.

This is the key, I think, to following the law by faith: \textbf{praise from God and not men}.

\textbf{Romans 2:29} - But he is a Jew who is one inwardly; and circumcision is that which is of the heart, by the Spirit, not by the letter; and his praise is not from men, but from God.

\textbf{Luke 16:15-17} - And he said to them, You are those who justify yourselves before men, but God knows your hearts. For what is exalted among men is an abomination in the sight of God.  The Law and the Prophets were until John; since then the good news of the kingdom of God is preached, and everyone forces his way into it.  But it is easier for heaven and earth to pass away than for one dot of the Law to become void.

\begin{itemize}
\item John the baptist taught 'turn from sin and believe in the One to come'.
\item Jesus taught to 'come to and believe in Him (Jesus) for forgiveness and stop sinning'.
\end{itemize}

\textbf{Acts 3:25-26} - You are the sons of the prophets and of the covenant that God made with your fathers, saying to Abraham, And in your offspring shall all the families of the earth be blessed. God, having raised up his servant, \textbf{sent him to you first, to bless you by turning every one of you from your wickedness}.

Stopping sinning is important from either angle.

\begin{itemize}
\item The apostles also taught people to turn from sin, believe and stop sinning.
\end{itemize}

\textbf{John 5:14} - Afterward Jesus found him in the temple and said to him, See, you are well! Sin no more, that nothing worse may happen to you.

\textbf{Ezekiel 18:20} - The soul who sins shall die. The son shall not suffer for the iniquity of the father, nor the father suffer for the iniquity of the son. The righteousness of the righteous shall be upon himself, and the wickedness of the wicked shall be upon himself. (ESV)

\textbf{Romans 8:13} - For if you live according to the flesh you will die, but if by the Spirit you put to death the deeds of the body, you will live.

Examples of receiving forgiveness from Jesus.

\textbf{Matthew 9:2} - And behold, some people brought to him a paralytic, lying on a bed. And when Jesus saw their faith, he said to the paralytic, Take heart, my son; your sins are forgiven.

Forgiven after Jesus saw their faith.

\textbf{Mark 2:5} - And when Jesus saw their faith, he said to the paralytic, My son, your sins are forgiven.

Acts of faith.

\textbf{Matthew 9:5} - For which is easier, to say, Your sins are forgiven, or to say, \textbf{Rise and walk?}

\textbf{Mark 2:9} - Which is easier, to say to the paralytic, Your sins are forgiven, or to say, \textbf{Rise, take up your bed and walk?}

Turning.

\textbf{Mark 4:11-12} - And he said to them, To you has been given the secret of the kingdom of God, but for those outside everything is in parables, so that they may indeed see but not perceive, and may indeed hear but not understand, lest they should \textbf{turn} and be forgiven.

\textbf{John 8:11} - She said, No one, Lord. And Jesus said, Neither do I condemn you; go, and from now on sin no more.

\subsection{Loving God is obedience to God}
\label{sec:org05162d3}
\textbf{I John 5:2-3} - By this we know that we love the children of God, when we love God and obey his commandments. For this is the love of God, that we keep his commandments. And his commandments are not burdensome.

\subsection{The law}
\label{sec:org4a74c4d}

\textbf{Matthew 19:4-9} - He answered, Have you not read that he who created them from the beginning made them male and female, and said, Therefore a man shall leave his father and his mother and hold fast to his wife, and they shall become one flesh? So they are no longer two but one flesh. What therefore God has joined together, let not man separate. They said to him, Why then did Moses command one to give a certificate of divorce and to send her away? He said to them, Because of your hardness of heart Moses allowed you to divorce your wives, but from the beginning it was not so. And I say to you: whoever divorces his wife, except for sexual immorality, and marries another, commits adultery. (ESV)

\textbf{Matthew 5:14-20} - You are the light of the world. A city set on a hill cannot be hidden. Nor do people light a lamp and put it under a basket, but on a stand, and it gives light to all in the house. In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. Do not think that I have come to abolish the Law or the Prophets; I have not come to abolish them but to fulfill them. For truly, I say to you, until heaven and earth pass away, not an iota, not a dot, will pass from the Law until all is accomplished. Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. For I tell you, unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven. (ESV)

\textbf{Leviticus 18:22} - You shall not lie with a male as with a woman; it is an abomination. (ESV)

\textbf{Romans 7:22} - For I delight in the law of God, in my inner being, (ESV)

\subsubsection{The law may be pursued by faith. Justification through faith}
\label{sec:org90b95f4}

Faith eclipses the law:

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

The ones under the law who also walk in the footsteps of the faith that Abraham had before he was circumcised, come under the umbrella of the faith of Abraham, which the Gentiles who also share the faith of Abraham are included within.

\begin{verbatim}
1           Faith (Galatians 3:6-9)
2         /       \
3    Those who     Gentiles who share
4  pursue the law      the faith
5    by faith          of Abraham
\end{verbatim}

\textbf{Galatians 3:6-9} -  just as Abraham believed God, and it was counted to him as righteousness?  Know then that it is those of faith who are the sons of Abraham.  And the Scripture, foreseeing that God would justify the Gentiles by faith, preached the gospel beforehand to Abraham, saying, In you shall all the nations be blessed.  So then, those who are of faith are blessed along with Abraham, the man of faith.  (ESV)

\textbf{Romans 9:31-32} - but that Israel who pursued a law that would lead to righteousness did not succeed in reaching that law. Why? Because they \uline{did not pursue it by faith}, but as if it were based on works. They have stumbled over the stumbling stone, (ESV)

The most important thing though is faith because it applies to both the adherent of the law and also the Gentile who has faith.

\textbf{Romans 4:16} - That is why it depends on faith, in order that the promise may rest on grace and be guaranteed to all his offspring-not only to the adherent of the law but also to the one who shares the \textbf{faith of Abraham}, who is the father of us all, (ESV)

\textbf{I Corinthians 10:1-5} - I want you to know, brothers, that our fathers were all under the cloud, and all passed through the sea, and all were baptized into Moses in the cloud and in the sea, and all ate the same spiritual food, and all drank the same spiritual drink. \textbf{For they drank from the spiritual Rock that followed them, and the Rock was Christ}. Nevertheless, with most of them God was not pleased, for they were overthrown in the wilderness.

\subsubsection{One in Christ Jesus - not excluding the adherent of the law}
\label{sec:orgdec8fe7}

\textbf{Romans 10:12} - For there is no distinction between Jew and Greek; the same Lord is Lord of all, bestowing his riches on all who call on him.

\textbf{I Corinthians 12:13} - For in one Spirit we were all baptized into one body-Jews or Greeks, slaves or free-and all were made to drink of one Spirit.

\textbf{Galatians 3:28} - There is neither Jew nor Greek, there is neither slave nor free, there is neither male nor female, for you are all one in Christ Jesus.

\subsubsection{But we are not justified by the law. We are justified by faith}
\label{sec:org6d5ae6a}

\textbf{Galatians 5:4} - You are severed from Christ, you who would be justified by the law; you have fallen away from grace.

We receive the Holy Spirit through faith:

\textbf{Galatians 3:2} - Let me ask you only this: Did you receive the Spirit by works of the law or by hearing with faith?􄌹

But faith is obedient.

\subsection{The law is good, if used properly - and its usage is part of the gospel}
\label{sec:orgd467477}
\textbf{1 Timothy 1:8-11} - Now we know that the law is good, if one uses it lawfully, understanding this, that the law is not laid down for the just but for the lawless and disobedient, for the ungodly and sinners, for the unholy and profane, for those who strike their fathers and mothers, for murderers, the sexually immoral, men who practice homosexuality, enslavers, liars, perjurers, and whatever else is contrary to sound doctrine, in accordance with the glorious gospel of the blessed God with which I have been entrusted. (ESV)

\subsection{Both Father God and Jesus Christ God's Son have life in Himself and the power to resurrect}
\label{sec:org72836a3}
\textbf{John 5:21} - For as the Father raises the dead and gives them life, so also the Son gives life to whom he will. (ESV)

\textbf{John 5:24-26} - Truly, truly, I say to you, whoever hears my word and believes him who sent me has eternal life. He does not come into judgment, but has passed from death to life. Truly, truly, I say to you, an hour is coming, and is now here, when the dead will hear the voice of the Son of God, and those who hear will live. For as the Father has life in himself, so he has granted the Son also to have life in himself.

\subsection{Salvation in no-one else other than Jesus Christ - But we must obey the gospel, and walk in the Way}
\label{sec:orgb14129b}
\textbf{Acts 4:12} - And there is salvation in no one else, for there is no other name under heaven given among men by which we must be saved. (ESV)

\textbf{John 14:6} - Jesus said to him, I am the way, and the truth, and the life. No one comes to the Father except through me.

Jesus has shown us the Way we have to \textbf{walk} in. The Way is Himself. To walk in it we make Him our Teacher and believe Him and obey Him, and arrive at the Truth, and the Truth is Himself.

\textbf{Hebrews 10:19} - Therefore, brothers, since we have confidence to enter the holy places by the blood of Jesus, by the new and living way that he opened for us through the curtain, that is, through his flesh,

\textbf{Isaiah 30:20-21} - And \uline{though the Lord give you the bread of adversity and the water of affliction, yet your Teacher will not hide himself anymore}, but your eyes shall see your Teacher. And your ears shall hear a word behind you, saying, \textbf{This is the way, walk in it}, when you turn to the right or when you turn to the left.

\textbf{Deuteronomy 18:15-19} - The LORD your God will raise up for you a prophet like me from among you, from your brothers—it is \textbf{to him you shall listen} — just as you desired of the LORD your God at Horeb on the day of the assembly, when you said, Let me not hear again the voice of the LORD my God or see this great fire any more, lest I die. And the LORD said to me, They are right in what they have spoken. I will raise up for them a prophet like you from among their brothers. And \textbf{I will put my words in his mouth, and he shall speak to them all that I command him}. And whoever will not listen to my words that he shall speak in my name, I myself will require it of him. (ESV)

\textbf{John 12:49-50} - For I have not spoken on my own authority, but the Father who sent me has himself given me a commandment—what to say and what to speak. And I know that his commandment is eternal life. What I say, therefore, I say as the Father has told me.

\textbf{John 14:6-7} - Jesus said to him, I am the way, and the truth, and the life. No one comes to the Father except through me. If you had known me, you would have known my Father also. From now on you do know him and have seen him.

\textbf{John 14:16-24} - And I will ask the Father, and he will give you another Helper, to be with you forever, In that day you will know that I am in my Father, and you in me, and I in you. Whoever has my commandments and keeps them, he it is who loves me. And he who loves me will be loved by my Father, and I will love him and manifest myself to him.

Jesus manifests to those who keep His word and obey Him.

\textbf{John 14:22-23} - Judas (not Iscariot) said to him, Lord, how is it that you will manifest yourself to us, and not to the world? Jesus answered him, If anyone loves me, he will keep my word, and my Father will love him, and we will come to him and make our home with him.

\textbf{I John 2:4-6} - Whoever says I know him but does not keep his commandments is a liar, and the truth is not in him, but whoever keeps his word, in him truly the love of God is perfected. By this we may be sure that we are in him: whoever says he abides in him ought to walk in the same way in which he walked.

\textbf{John 14:24} - Whoever does not love me does not keep my words. And the word that you hear is not mine but the Father's who sent me.

\subsection{Anyone who believes in Him receives forgiveness of sins}
\label{sec:org759b840}
\textbf{Acts 10:43:} Of Him all \textbf{the prophets bear witness} that \textbf{through His name} everyone who believes in Him receives forgiveness of sins."

But before and/or after believing and being forgiven a person needs to also turn away from sin.
To be '\textbf{saved}' I think means:
\begin{itemize}
\item for God to forgive one's sins through Jesus Christ, and
\item for that person to be progressing towards holiness and not away from holiness - towards sanctification and ultimately, eternal life
\begin{itemize}
\item the Holy Spirit helps a person to do that
\end{itemize}
\item to be eagerly waiting for Jesus to save them
\end{itemize}

\textbf{Hebrews 9:27-28} - And just as it is appointed for man to die once, and after that comes judgment, so Christ, having been offered once to bear the sins of many, will appear a second time, not to deal with sin but \textbf{to save those who are eagerly waiting for him}.

Becoming a slave of God, rather than sin, the fruit you get leads to sanctification and at the end, eternal life - it leads to knowing the only true God, and Jesus Christ who He sent.

\textbf{Romans 6:16-22} - Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of obedience, which leads to righteousness? But thanks be to God, that you who were once slaves of sin have become obedient from the heart to the standard of teaching to which you were committed, and, having been set free from sin, have become slaves of righteousness. I am speaking in human terms, because of your natural limitations. For just as you once presented your members as slaves to impurity and to lawlessness leading to more lawlessness, so now present your members as slaves to righteousness leading to sanctification. When you were slaves of sin, you were free in regard to righteousness. But what fruit were you getting at that time from the things of which you are now ashamed? The end of those things is death. But now that you have been set free from sin and have become slaves of God, the fruit you get leads to sanctification and its end, \textbf{eternal life}. (ESV)

So obedience leads to sanctification which leads to eternal life which is knowing God and Jesus Christ.

Repentance from sin is required step for those who are in sin, along with forgiveness, and is followed up with sanctification and eternal life.

\textbf{Luke 15:7} - Just so, I tell you, there will be more joy in heaven over one sinner who repents than over ninety-nine righteous persons who need no repentance. (ESV)

\textbf{John 17:3} - And this is eternal life, that they know you the only true God, and Jesus Christ whom you have sent.

\subsubsection{Eternal life \textbf{available} for all who believe in Jesus, but obedience and sanctification is necessary}
\label{sec:org3334a18}
\textbf{John 3:14-18} - And as Moses lifted up the serpent in the wilderness, so must the Son of Man be lifted up, that whoever believes in him may have eternal life. For God so loved the world, that he gave his only Son, that whoever believes in him should not perish but have eternal life. For God did not send his Son into the world to condemn the world, but in order that the world might be saved through him. Whoever believes in him is not condemned, but whoever does not believe is condemned already, because he has not believed in the name of the only Son of God.

I believe there is a strong emphasis on continued belief, and becoming a bondservant of God.
\begin{itemize}
\item 'may have'
\item 'should' not perish
\end{itemize}

\section{Spiritual gifts}
\label{sec:org0028f5c}
\subsection{Excel in building up the church to see manifestations of the Spirit}
\label{sec:org3537bea}
\textbf{I Corinthians 14:12} - So with yourselves, since you are eager for manifestations of the Spirit, strive to excel in building up the church.

\subsection{Using one's mind to speak to others intelligible words in the church is not subordinate to speaking in tongues}
\label{sec:org68e9339}
\textbf{I Corinthians 14:19} - Nevertheless, in church I would rather speak five words with my mind in order to instruct others, than ten thousand words in a tongue.

\subsection{Speaking in tongues speaks to God}
\label{sec:org6f35474}
\textbf{I Corinthians 14:2} - For one who speaks in a tongue speaks not to men but to God; for no one understands him, but he utters mysteries in the Spirit.

\subsection{The spirit prays when a person prays in tongues}
\label{sec:orgd64c181}
\textbf{I Corinthians 14:2} - For one who speaks in a tongue speaks not to men but to God; for no one understands him, but he utters mysteries in the Spirit.

\textbf{I Corinthians 14:14-15} - For if I pray in a tongue, my spirit prays but my mind is unfruitful. What am I to do? I will pray with my spirit, but I will pray with my mind also; I will sing praise with my spirit, but I will sing with my mind also.

\section{The prophets}
\label{sec:org099cd4e}
\textbf{Psalms 51:9-11} - Hide your face from my sins, and blot out all my iniquities. Create in me a clean heart, O God, and renew a right spirit within me. Cast me not away from your presence, and take not your Holy Spirit from me. (ESV)

\textbf{Zechariah 13:1} - "In that day a fountain will be opened for the house of David and for the inhabitants of Jerusalem, for sin and for impurity. (ESV)

\textbf{Isaiah 53:11} - As a result of the anguish of His soul, He will see it and be satisfied; By His knowledge the Righteous One, My Servant, will justify the many, As He will bear their iniquities. (ESV)

\textbf{Jeremiah 31:34} - They will not teach again, each man his neighbor and each man his brother, saying, 'Know the LORD,' for they will all know Me, from the least of them to the greatest of them," declares the LORD, "for I will forgive their iniquity, and their sin I will remember no more." (ESV)

\textbf{Malachi 4:2} - "But \textbf{for you who fear My name}, the sun of righteousness will rise with healing in its wings; and you will go forth and skip about like calves from the stall. (ESV)

\textbf{Daniel 9:24} - "Seventy weeks have been decreed for your people and your holy city, to finish the transgression, to make an end of sin, to make atonement for iniquity, to bring in everlasting righteousness, to seal up vision and prophecy and to anoint the most holy place. (ESV)

\textbf{Micah 7:18} - Who is a God like You, who pardons iniquity And passes over the rebellious act of the remnant of His possession? He does not retain His anger forever, Because He delights in unchanging love. (ESV)

\textbf{2 Chronicles 7:14} - if my people who are \textbf{called by my name} humble themselves, and pray and seek my face and turn from their wicked ways, then I will hear from heaven and will forgive their sin and heal their land. (ESV)

\subsection{44 Prophecies Jesus Christ Fulfilled}
\label{sec:orga833d39}
\begin{center}
\begin{tabular}{lll}
Prophecies About Jesus & Old Testament Scripture & New Testament Fulfillment\\[0pt]
\hline
Messiah would be born of a woman. & Ge 3:15 & Mt 1:20 Ga 4:4\\[0pt]
Messiah would be born in Bethlehem. & Mc 5:2 & Mt 2:1 Lk 2:4-6\\[0pt]
Messiah would be born of a virgin. & Is 7:14 & Mt 1:22-23 Lk 1:26-31\\[0pt]
Messiah would come from the line of Abraham. & Ge 12:3 Ge 22:18 & Mt 1:1 Rm 9:5\\[0pt]
Messiah would be a descendant of Isaac. & Ge 17:19 Ge 21:12 & Lk 3:34\\[0pt]
Messiah would be a descendant of Jacob. & Nb 24:17 & Mt 1:2\\[0pt]
Messiah would come from the tribe of Judah. & Ge 49:10 & Lk 3:33 Heb 7:14\\[0pt]
Messiah would be heir to King David's throne. & 2Sa 7:12-13 Is 9:7 & Lk 1:32-33 Rm 1:3\\[0pt]
Messiah's throne will be anointed and eternal. & Ps 45:6-7 Da 2:44 & Lk 1:33 Heb 1:8-12\\[0pt]
Messiah would be called Immanuel. & Is 7:14 & Mt 1:23\\[0pt]
Messiah would spend a season in Egypt. & Ho 11:1 & Mt 2:14-15\\[0pt]
A massacre of children would happen at Messiah's birthplace. & Je 31:15 & Mt 2:16-18\\[0pt]
A messenger would prepare the way for Messiah & Is 40:3-5 & Lk 3:3-6\\[0pt]
Messiah would be rejected by his own people. & Ps 69:8 Is 53:3 & Jn 1:11 John 7:5\\[0pt]
Messiah would be a prophet. & De 18:15 & Ac 3:20-22\\[0pt]
Messiah would be preceded by Elijah. & Ml 4:5-6 & Mt 11:13-14\\[0pt]
Messiah would be declared the Son of God. & Ps 2:7 & Mt 3:16-17\\[0pt]
Messiah would be called a Nazarene. & Is 11:1 & Mt 2:23\\[0pt]
Messiah would bring light to Galilee. & Is 9:1-2 & Mt 4:13-16\\[0pt]
Messiah would speak in parables. & Ps 78:2-4 Is 6:9-10 & Mt 13:10-15, 34-35\\[0pt]
Messiah would be sent to heal the brokenhearted. & Is 61:1-2 & Lk 4:18-19\\[0pt]
Messiah would be a priest after the order of Melchizedek. & Ps 110:4 & Heb 5:5-6\\[0pt]
Messiah would be called King. & Ps 2:6 Zc 9:9 & Mt 27:37 Mk 11:7-11\\[0pt]
Messiah would be praised by little children. & Ps 8:2 & Mt 21:16\\[0pt]
Messiah would be betrayed. & Ps 41:9 Zc 11:12-13 & Lk 22:47-48 Mt 26:14-16\\[0pt]
Messiah's price money would be used to buy a potter's field. & Zc 11:12-13 & Mt 27:9-10\\[0pt]
Messiah would be falsely accused. & Ps 35:11 & Mk 14:57-58\\[0pt]
Messiah would be silent before his accusers. & Is 53:7 & Mk 15:4-5\\[0pt]
Messiah would be spat upon and struck. & Is 50:6 & Mt 26:67\\[0pt]
Messiah would be hated without cause. & Ps 35:19 Psalm 69:4 & Jn 15:24-25\\[0pt]
Messiah would be crucified with criminals. & Is 53:12 & Mt 27:38 Mk 15:27-28\\[0pt]
Messiah would be given vinegar to drink. & Ps 69:21 & Mt 27:34 Jn 19:28-30\\[0pt]
Messiah's hands and feet would be pierced. & Ps 22:16 Zc 12:10 & Jn 20:25-27\\[0pt]
Messiah would be mocked and ridiculed. & Ps 22:7-8 & Lk 23:35\\[0pt]
Soldiers would gamble for Messiah's garments. & Ps 22:18 & Lk 23:34 Mt 27:35-36\\[0pt]
Messiah's bones would not be broken. & Ex 12:46 Ps 34:20 & Jn 19:33-36\\[0pt]
Messiah would be forsaken by God. & Ps 22:1 & Mt 27:46\\[0pt]
Messiah would pray for his enemies. & Ps 109:4 & Lk 23:34\\[0pt]
Soldiers would pierce Messiah's side. & Zc 12:10 & Jn 19:34\\[0pt]
Messiah would be buried with the rich. & Is 53:9 & Mt 27:57-60\\[0pt]
Messiah would resurrect from the dead. & Ps 16:10 Psalm 49:15 & Mt 28:2-7 Ac 2:22-32\\[0pt]
Messiah would ascend to heaven. & Ps 24:7-10 & Mk 16:19 Lk 24:51\\[0pt]
Messiah would be seated at God's right hand. & Ps 68:18 Psalm 110:1 & Mk 16:19 Mt 22:44\\[0pt]
Messiah would be a sacrifice for sin. & Is 53:5-12 & Rm 5:6-8\\[0pt]
\end{tabular}
\end{center}

\subsubsection{Psalm 31 and Jesus' last words and Jesus saving me}
\label{sec:orga9b3f82}

\textbf{Psalms 31:5}  Into Your hand I commit my spirit; You have ransomed me, O LORD, God of truth.  (NASB)

\textbf{Luke 23:46} - Then Jesus, calling out with a loud voice, said, Father, into your hands I commit my spirit! And having said this he breathed his last.  (ESV)

Jesus saving me:

\href{https://web.archive.org/web/20220402091720/https://mullikine.github.io/posts/astral-projection-pt-2/}{Astral Projection Pt. 2 // Bodacious Blog}

\textbf{I Timothy 2:6} - who gave himself as a ransom for all, which is the testimony given at the proper time. (ESV)

God never lies:

\textbf{Titus 1:1-3} - Paul, a servant of God and an apostle of Jesus Christ, for the sake of the faith of God's elect and their knowledge of the truth, which accords with godliness, in hope of eternal life, which God, who \textbf{never lies}, promised before the ages began and at the proper time manifested in his word through the preaching with which I have been entrusted by the command of God our Savior;

\textbf{1 John 2:21} -  I write to you, not because you do not know the truth, but because you know it, and because no lie is of the truth.  (ESV)

\subsection{Faith has a quantity, and faith receives from God / walks into what He has promised}
\label{sec:org28ab122}
\textbf{Luke 17:5} - The apostles said to the Lord, \textbf{Increase our faith}!

\textbf{II Corinthians 10:15} - We do not boast beyond limit in the labors of others. But our hope is that as your \textbf{faith increases}, our area of influence among you may be greatly enlarged,

\textbf{Luke 7:8-9} - For I too am a man set under authority, with soldiers under me: and I say to one, Go, and he goes; and to another, Come, and he comes; and to my servant, Do this, and he does it. When Jesus heard these things, he marveled at him, and turning to the crowd that followed him, said, I tell you, not even in Israel have I found such faith. (ESV)

Since Faith is proportional to Love for God, which is proportional to obeying God, the following can be understood.

\textbf{James 1:12} - Blessed is the man who remains steadfast under trial, for when he has stood the test he will receive the crown of life, which God has promised to those who love him.

\textbf{James 2:5} - Listen, my beloved brothers, has not God chosen those who are poor in the world to be rich in faith and heirs of the kingdom, which he has promised to those who love him?

A person with true faith in God walks into the truth because true faith has eyes fixed on Jesus and goes to Jesus as it obeys the will of God.

\subsubsection{Faith has substance, and a quantity, usually drawn out over time}
\label{sec:orged219d1}
\textbf{Hebrews 11:1} - Now faith is the substance of things hoped for, the evidence of things not seen. (KJV)

\textbf{Hebrews 11:1} - Now faith is the assurance of things hoped for, the conviction of things not seen. (ESV)

\textbf{Matthew 17:20} - He said to them, Because of your little faith. For truly, I say to you, if you have faith like a grain of mustard seed, you will say to this mountain, Move from here to there, and it will move, and nothing will be impossible for you. (ESV)

\textbf{Revelation of John 3:8} - I know your \textbf{works}. Behold, I have set before you an open door, which no one is able to shut. I know that you have but little power, and yet you have \textbf{kept my word and have not denied my name}. Behold, I will make those of the synagogue of Satan who say that they are Jews and are not, but lie-behold, I will make them come and bow down before your feet and they will learn that I have loved you. Because you have kept my word about \textbf{patient endurance}, I will keep you from the hour of trial that is coming on the whole world, to try those who dwell on the earth.

I think faith is like casting a net to receive something.

If you want to catch something big then you need a lot of faith.

Faith receives salvation, and salvation is the gift which is received through faith.
Faith is something which a person must have to receive the free gift.
The onus is on us to receive the free gift.

We must approach Jesus.
We must repent (change our minds, turning from our wicked ways, and turn to God) and obey God.
God has said many things, about his statutes and about how we should listen to Jesus.
I think repentance (from the heart turning from sin) is still approaching Jesus because Jesus fulfilled the law.

Humble yourself and obey God's commandments (not out of pride, but out of authentic faith with God, being accountable to God, in secret).

For example, abstaining from partaking in stealing, or adultery and being faithful to God, even if you lose friends over it.
This type of obeying God's commandments is nothing to do with pride or self-exultation or self-righteousness and everything to do with being faithful to God and humbling oneself to God.

Trying to turn from sin in truth and reality.

\textbf{2 Chronicles 7:14} - if my people who are called by my name humble themselves, and pray and seek my face and turn from their wicked ways, then I will hear from heaven and will forgive their sin and heal their land. (ESV)

\textbf{Matthew 18:3} - and said, Truly, I say to you, unless you turn and become like children, you will never enter the kingdom of heaven. (ESV)

It says unless \textbf{you} turn - The onus is on you.

\textbf{Matthew 5:20} - For I tell you, unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven. (ESV)

It says unless \textbf{your} righteousness.

Faith in Jesus probably qualifies a person to 'enter' the Kingdom of Heaven.
Also, following the law by faith in truth I think qualifies a person to enter the Kingdom of Heaven.
Also the Kingdom of Heaven, I think is from Heaven to Earth.

\textbf{II Corinthians 5:21} - For our sake he made him to be sin who knew no sin, so that in him we might become the righteousness of God.

\textbf{Titus 3:7} - so that being justified by his grace we might become heirs according to the hope of eternal life.

\emph{\textbf{Through faith a person is saved (the onus is on us to receive)}}

Salvation is the gift. Works can be dead works when they're not done in faith. Therefore works don't save.

\textbf{Ephesians 2:8-9} - For by grace you have been saved through faith. And this is not your own doing; it is the gift of God, not a result of works, so that no one may boast. (ESV)

A person must be at least willing to do His will - obedience is the essence of faith:

\textbf{John 7:17} - If anyone is willing to do His will, he will know of the teaching, whether it is of God or whether I speak from Myself.

\subsubsection{The work of faith}
\label{sec:org79e50c3}
\begin{itemize}
\item love, faith, service and patient endurance are all considered works
\end{itemize}

\textbf{Revelation of John 2:19} - I know your works, your love and faith and service and patient endurance, and that your latter works exceed the first.

Abraham's obedience is a work of faith.

\textbf{Hebrews 11:8} - By faith Abraham obeyed when he was called to go out to a place that he was to receive as an inheritance. And he went out, not knowing where he was going. (ESV)

\textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God \textbf{must believe that he exists and that he rewards those who seek him.} (ESV)

Work substantiates faith because it is the act of receiving from God.

A work of faith could indeed be following the law in faith (as opposed to following the law by works).

For example, keeping your integrity, remaining faithful to God and not lying to God.

Patient endurance is a 'work of faith'.

\textbf{Revelation of John 3:8} - I know your \textbf{works}. Behold, I have set before you an open door, which no one is able to shut. I know that you have but little power, and yet you have \textbf{kept my word and have not denied my name}. Behold, I will make those of the synagogue of Satan who say that they are Jews and are not, but lie-behold, I will make them come and bow down before your feet and they will learn that I have loved you. Because you have kept my word about \textbf{patient endurance}, I will keep you from the hour of trial that is coming on the whole world, to try those who dwell on the earth.

\subsubsection{Justified by Faith + Works of faith (works not necessarily works of the law)}
\label{sec:orgfe3e1a3}
\textbf{James 2:22-26} - You see that faith was active along with his works, and faith was completed by his works; and the Scripture was fulfilled that says, Abraham believed God, and it was counted to him as righteousness-and he was called a friend of God. You see that a person is justified by works and not by faith alone. And in the same way was not also Rahab the prostitute justified by works when she received the messengers and sent them out by another way? For as the body apart from the spirit is dead, so also faith apart from works is dead. (ESV)

This is not a work of the law, but it is a work of faith: "\emph{when she received the messengers and sent them out by another way}"

\textbf{James 2:26} - For as the body apart from the spirit is dead, so also faith apart from works is dead.

\textbf{Romans 3:28-31} - For we hold that one is justified by faith apart from works of the law. Or is God the God of Jews only? Is he not the God of Gentiles also? Yes, of Gentiles also, since God is one. He will justify the circumcised by faith and the uncircumcised through faith. Do we then overthrow the law by this faith? By no means! On the contrary, we uphold the law. (ESV)

The law is not overthrown but it is upheld.

\subsubsection{Faith receives}
\label{sec:org3baf40e}
\textbf{Hebrews 11:13} - These all died in faith, not having received the things promised, but having seen them and greeted them from afar, and having acknowledged that they were strangers and exiles on the earth.

\subsubsection{Her faith saved her / is forgiven because she loved much - her love gave substance to her faith}
\label{sec:orgfc2675b}
Her love is a work of faith.

\textbf{Luke 7:47-50} - Therefore I tell you, her sins, which are many, are forgiven-for she loved much. But he who is forgiven little, loves little. And he said to her, Your sins are forgiven. Then those who were at table with him began to say among themselves, Who is this, who even forgives sins? And he said to the woman, Your faith has saved you; go in peace. (ESV)

I also currently believe that one's response to forgiveness must be like the woman Jesus mentions in Luke 7:47 - with a PROPROTIONAL love for Jesus.

\section{Worldly precepts completely contradict the Truth and don't help to stop sin}
\label{sec:org9111e81}
\textbf{Colossians 2:20-23} - If with Christ you died to the elemental spirits of the world, why, as if you were still alive in the world, do you submit to regulations— Do not handle, Do not taste, Do not touch (referring to things that all perish as they are used)—according to human precepts and teachings? These have indeed an appearance of wisdom in promoting self-made religion and asceticism and severity to the body, but they are of no value in stopping the indulgence of the flesh. (ESV)

I think that choosing a relationship Biblically is contrary to worldly precepts.

\begin{itemize}
\item \textbf{Mark 7:7-9} in vain do they worship me, teaching as doctrines the commandments of men.  You leave the commandment of God and hold to the tradition of men.  And he said to them, You have a fine way of rejecting the commandment of God in order to establish your tradition!
\end{itemize}

\section{Who will enter Heaven? Only the ones who do the will of Father God}
\label{sec:orgbf1cc2a}
\textbf{Matthew 7:21-23} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven. On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name? And then will I declare to them, I never knew you; depart from me, you workers of lawlessness. (ESV)

OBEDIENCE!

\section{Sermon on the mount}
\label{sec:org3c21ee2}
Those who mourn will be comforted.

\textbf{Matthew 5:4} - Blessed are those who mourn, for they shall be comforted.

The earth may be inherited.

\textbf{Matthew 5:5} - Blessed are the meek, for they shall inherit the earth.

Those who hunger and thirst for righteousness will be satisfied.

\textbf{Matthew 5:6} - Blessed are those who hunger and thirst for righteousness, for they shall be satisfied.

The merciful shall receive mercy.

\textbf{Matthew 5:7} - Blessed are the merciful, for they shall receive mercy.

Without holiness, no-one will see the Lord.

\textbf{Matthew 5:8} - Blessed are the pure in heart, for they shall see God.

Th peacemakers shall be called sons of God.

\textbf{Matthew 5:9} - Blessed are the peacemakers, for they shall be called sons of God.

The kingdom of heaven may be inherited.

\textbf{Matthew 5:10} - Blessed are those who are persecuted for righteousness' sake, for theirs is the kingdom of heaven.

\textbf{Matthew 5:3-9} - Blessed are the poor in spirit, for theirs is the kingdom of heaven.

\textbf{Matthew 5:11-13}  Blessed are you when others revile you and persecute you and utter all kinds of evil against you falsely on my account. Rejoice and be glad, for your reward is great in heaven, for so they persecuted the prophets who were before you. You are the salt of the earth, but if salt has lost its taste, how shall its saltiness be restored? It is no longer good for anything except to be thrown out and trampled under people's feet.

\section{Entering and inheriting the kingdom}
\label{sec:org5643b89}
There's so much stuff to do to enter the kingdom\ldots{} I feel entirely unworthy.

Those who hunger and thirst for righteousness will be satisfied.

Please God, give me the righteousness required to enter the kingdom.

\subsection{Entering the kingdom}
\label{sec:orgeef75ae}
\subsubsection{This is the good news. I do think 'believes' really means has active faith in}
\label{sec:org21f8a37}
\textbf{John 3:16} - For God so loved the world, that he gave his only Son, that whoever believes in him should not perish but have eternal life. (ESV)

\textbf{John 3:36} - Whoever believes in the Son has eternal life; whoever does not obey the Son shall not see life, but the wrath of God remains on him. (ESV)

\textbf{John 5:34} - Not that the testimony that I receive is from man, but I say these things so that you may be saved. (ESV)

\textbf{John 6:47} - Truly, truly, I say to you, whoever believes has eternal life. (ESV)

\textbf{John 11:26} - and everyone who lives and believes in me shall never die. Do you believe this? (ESV)

\subsubsection{We must be born-again}
\label{sec:orga241b08}
\textbf{John 3:3-5} - Jesus answered him, Truly, truly, I say to you, unless one is born again he cannot see the kingdom of God.  Nicodemus said to him, How can a man be born when he is old?  Can he enter a second time into his mother's womb and be born?  Jesus answered, Truly, truly, I say to you, unless one is born of water and the Spirit, he cannot enter the kingdom of God. (ESV)

\textbf{John 1:12} - But to all who did receive him, who believed in his name, he gave the right to become children of God, (ESV)

It is the sovereign work of God to make someone born-again of the Spirit, but the Apostles say the Holy Spirit is given to those who believe in / obey him:

\textbf{Acts 5:32} - And we are witnesses to these things, and so is \textbf{the Holy Spirit, whom God has given to those who obey him}. (ESV)

\textbf{Galatians 3:14} - so that in Christ Jesus the blessing of Abraham might come to the Gentiles, so that we might \textbf{receive the promised Spirit through faith}. (ESV)

\textbf{John 1:11-13} - He came to His own, and those who were His own did not receive Him. But \uline{as many as received Him, to them He gave the right to become children of God, even to those who believe (G4100 \textbf{pisteuo}) in His name}, who were born, not of blood nor of the will of the flesh nor of the will of man, but of God.

\subsubsection{We must do the will of God}
\label{sec:org3bd537f}
\textbf{Matthew 7:21} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven. (ESV)

\subsubsection{We must have faith in Jesus}
\label{sec:orgb376b4a}
\textbf{Matthew 5:20} - For I tell you, unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven. (ESV)

\subsubsection{We must accept it as a child}
\label{sec:org329d8fd}
\textbf{Matthew 18:3} - and said, Truly, I say to you, unless you turn and become like children, you will never enter the kingdom of heaven.

\subsubsection{We must serve people. We must give up our wealth for others' sake}
\label{sec:orgefba3bb}
\textbf{Matthew 19:23-24} - And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. (ESV)

\textbf{Mark 10:23-25} - And Jesus looked around and said to his disciples, How difficult it will be for those who have wealth to enter the kingdom of God! And the disciples were amazed at his words. But Jesus said to them again, Children, how difficult it is to enter the kingdom of God! It is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. (ESV)

\textbf{Luke 18:24-25} - Jesus, looking at him with sadness, said, How difficult it is for those who have wealth to enter the kingdom of God! For it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. (ESV)

\subsubsection{We must turn from sin}
\label{sec:org2433f6b}
\textbf{Mark 9:47} - And if your eye causes you to sin, tear it out. It is better for you to enter the kingdom of God with one eye than with two eyes to be thrown into hell,

\subsubsection{We must endure to enter the kingdom of God}
\label{sec:org02d2651}
\textbf{Acts 14:22} - strengthening the souls of the disciples, encouraging them to continue in the faith, and saying that through many tribulations we must enter the kingdom of God.

\subsection{Inheriting the kingdom}
\label{sec:orgadbae5d}
\subsubsection{We must be born-again}
\label{sec:orga2b3d5e}
\textbf{I Corinthians 15:50} - I tell you this, brothers: flesh and blood cannot inherit the kingdom of God, nor does the perishable inherit the imperishable. (ESV)

\subsubsection{We must repent and be sanctified}
\label{sec:org013844c}
\textbf{Galatians 5:19-21} -  Now the works of the flesh are evident: sexual immorality, impurity, sensuality, idolatry, sorcery, enmity, strife, jealousy, fits of anger, rivalries, dissensions, divisions, envy, drunkenness, orgies, and things like these.  I warn you, as I warned you before, that those who do such things will not inherit the kingdom of God. (ESV)

\textbf{I Corinthians 6:9-10} - Do you not know that the unrighteous will not inherit the kingdom of God? Do not be deceived: neither the sexually immoral, nor idolaters, nor adulterers, nor men who practice homosexuality, nor thieves, nor the greedy, nor drunkards, nor revilers, nor swindlers will inherit the kingdom of God. (ESV)

\textbf{Galatians 5:21} - envy, drunkenness, orgies, and things like these. I warn you, as I warned you before, that those who do such things will not inherit the kingdom of God.

\subsubsection{We must be a good and faithful servant}
\label{sec:org0d7f260}
\textbf{Matthew 25:31-34} - When the Son of Man comes in his glory, and all the angels with him, then he will sit on his glorious throne. Before him will be gathered all the nations, and he will separate people one from another as a shepherd separates the sheep from the goats. And he will place the sheep on his right, but the goats on the left. Then the King will say to those on his right, Come, you who are blessed by my Father, inherit the kingdom prepared for you from the foundation of the world.

\subsubsection{We must be servants}
\label{sec:org856f1f8}
\textbf{Colossians 3:23-24} -  Whatever you do, work heartily, as for the Lord and not for men, knowing that from the Lord you will receive the inheritance as your reward. You are serving the Lord Christ.  (ESV)

\textbf{Matthew 25:35-46} - For I was hungry and you gave me food, I was thirsty and you gave me drink, I was a stranger and you welcomed me, I was naked and you clothed me, I was sick and you visited me, I was in prison and you came to me. Then the righteous will answer him, saying, Lord, when did we see you hungry and feed you, or thirsty and give you drink? And when did we see you a stranger and welcome you, or naked and clothe you? And when did we see you sick or in prison and visit you? And the King will answer them, Truly, I say to you, as you did it to one of the least of these my brothers, you did it to me. Then he will say to those on his left, Depart from me, you cursed, into the eternal fire prepared for the devil and his angels. For I was hungry and you gave me no food, I was thirsty and you gave me no drink, I was a stranger and you did not welcome me, naked and you did not clothe me, sick and in prison and you did not visit me. Then they also will answer, saying, Lord, when did we see you hungry or thirsty or a stranger or naked or sick or in prison, and did not minister to you? Then he will answer them, saying, Truly, I say to you, as you did not do it to one of the least of these, you did not do it to me. And these will go away into eternal punishment, but the righteous into eternal life.

\section{Who will enter the holy city of Jerusalem which is in Heaven? Not sinners. Only servants. Only those who follow Jesus' commandments}
\label{sec:orgd8137ed}
I think it's really the hope of inheritance for people who have strived to enter the kingdom while on earth.

\textbf{Luke 13:22-27} - He went on his way through towns and villages, teaching and journeying toward Jerusalem. And someone said to him, Lord, will those who are saved be few? And he said to them, Strive to enter through the narrow door. For many, I tell you, will seek to enter and will not be able. When once the master of the house has risen and shut the door, and you begin to stand outside and to knock at the door, saying, Lord, open to us, then he will answer you, I do not know where you come from. Then you will begin to say, We ate and drank in your presence, and you taught in our streets. But he will say, I tell you, I do not know where you come from. Depart from me, all you workers of evil!

\textbf{Hebrews 12:22} - But you have come to Mount Zion and to the city of the living God, the heavenly Jerusalem, and to innumerable angels in festal gathering,

\textbf{Revelation of John 21:10} - And he carried me away in the Spirit to a great, high mountain, and showed me the holy city Jerusalem coming down out of heaven from God,

\textbf{Revelation of John 21:27} -  But nothing unclean will ever enter it, nor anyone who does what is detestable or false, but only those who are written in the Lamb's book of life. (ESV)

\subsection{Those who have stopped sinning (potentially through the power of the Holy Spirit) and who believe in Jesus Christ}
\label{sec:org19b8894}
\textbf{Acts 5:31} - God exalted him at his right hand as Leader and Savior, to give repentance to Israel and forgiveness of sins.

\textbf{Acts 11:18} - When they heard these things they fell silent. And they glorified God, saying, Then to the Gentiles also God has granted repentance that leads to life.

\subsection{Sinners will not inherit the kingdom of God}
\label{sec:org016d9cc}
\textbf{Galatians 5:19-21} -  Now the works of the flesh are evident: sexual immorality, impurity, sensuality, idolatry, sorcery, enmity, strife, jealousy, fits of anger, rivalries, dissensions, divisions, envy, drunkenness, orgies, and things like these.  I warn you, as I warned you before, that those who do such things will not inherit the kingdom of God. (ESV)

\subsection{Following the law properly is not a matter of self-righteousness, it's a matter of who has stopped sinning}
\label{sec:orgc46e378}
\textbf{Revelation 22:15} -  Outside are the dogs and sorcerers and the sexually immoral and murderers and idolaters, and everyone who loves and practices falsehood.  (ESV)

\textbf{Ephesians 5:5} -  For you may be sure of this, that everyone who is sexually immoral or impure, or who is covetous (that is, an idolater), has no inheritance in the kingdom of Christ and God.  (ESV)

\textbf{1 John 3:4-9} -  Everyone who makes a practice of sinning also practices lawlessness; sin is lawlessness.  You know that he appeared to take away sins, and in him there is no sin.  No one who abides in him keeps on sinning; no one who keeps on sinning has either seen him or known him.  Little children, let no one deceive you.  Whoever practices righteousness is righteous, as he is righteous.  Whoever makes a practice of sinning is of the devil, for the devil has been sinning from the beginning.  The reason the Son of God appeared was to destroy the works of the devil.  No one born of God makes a practice of sinning, for God's seed abides in him, and he cannot keep on sinning because he has been born of God.  (ESV)

\subsubsection{The law is good, if used properly - and its usage is part of the gospel}
\label{sec:org5cd472e}
\textbf{1 Timothy 1:8-11} - Now we know that the law is good, if one uses it lawfully, understanding this, that the law is not laid down for the just but for the lawless and disobedient, for the ungodly and sinners, for the unholy and profane, for those who strike their fathers and mothers, for murderers, the sexually immoral, men who practice homosexuality, enslavers, liars, perjurers, and whatever else is contrary to sound doctrine, in accordance with the glorious gospel of the blessed God with which I have been entrusted. (ESV)

But Christians are not under the law:
\subsection{\href{http://persweb.wabash.edu/facstaff/royaltyr/AncientCities/web/bradleyj/Project\%201/The\%20Epistle\%20of\%20Ignatius\%20to\%20the\%20Magnesians.htm}{The Epistle of Ignatius to the Magnesians}}
\label{sec:org78faeb8}

\textbf{Ignatius to the Magnesians 8} - Be not deceived with strange doctrines, nor with old fables, which are unprofitable. For if we still live according to the Jewish law, we acknowledge that we have not received grace. For the divinest prophets lived according to Christ Jesus. On this account also they were persecuted, being inspired by His grace to fully convince the unbelieving that there is \textbf{one God, who has manifested Himself by Jesus Christ His Son, who is His eternal Word}, not proceeding forth from silence, and who in all things pleased Him that sent Him.

\subsection{This makes sense - the law certainly still exists}
\label{sec:org2e72fe2}
\textbf{1 Timothy 1:8-11} -  Now we know that the law is good, if one uses it lawfully, understanding this, that the law is not laid down for the just but for the lawless and disobedient, for the ungodly and sinners, for the unholy and profane, for those who strike their fathers and mothers, for murderers, the sexually immoral, men who practice homosexuality, enslavers, liars, perjurers, and whatever else is contrary to sound doctrine, in accordance with the glorious gospel of the blessed God with which I have been entrusted.  (ESV)

\subsection{Gospel}
\label{sec:org5dd86d1}
\textbf{John 3:16-21} - For God so loved the world, that he gave his only Son, that whoever believes in him should not perish but have eternal life. For God did not send his Son into the world to condemn the world, but in order that the world might be saved through him. Whoever believes in him is not condemned, but whoever does not believe is condemned already, because he has not believed in the name of the only Son of God. And this is the judgment: the light has come into the world, and people loved the darkness rather than the light because their deeds were evil. For everyone who does wicked things hates the light and does not come to the light, lest his deeds should be exposed. But whoever does what is true comes to the light, so that it may be clearly seen that his deeds have been carried out in God. (ESV)

\uline{Whoever has faith in and puts their trust in in Jesus Christ is not condemned and should not perish.}

\textbf{Galatians 2:15-16} - “We are Jews by nature and not sinners from among the Gentiles; nevertheless knowing that a man is not justified by the works of the Law but through faith in Christ Jesus, even we have believed in Christ Jesus, so that we may be \textbf{justified by faith in Christ} and not by the works of the Law; since by the works of the Law no flesh will be justified.

It's by faith in Christ that we are justified, and faith involves obedience.

\textbf{John 3:36} - Whoever believes (G4100 pisteuo) in the Son has eternal life; whoever does not \textbf{obey} the Son shall not see life, but the wrath of God remains on him. (ESV)

\textbf{John 3:16} - "For God (G2316 theos) so (G3779 houto) loved (G25 agapao) the world (G2889 kosmos), that He gave (G1325 didomi) His only (G3439 monogenes) begotten (G3439 monogenes) Son (G5207 huios), that whoever (G3956 pas) believes (G4100 pisteuo) in Him shall not perish (G622 apollumi), but have (G2192 echo) eternal (G166 aionios) life (G2222 zoe).

\begin{verbatim}
1  :  4100  pisteuo  pist-yoo'-o
2  
3   from 4102; to have faith (in, upon, or with respect to, a person or
4   thing), i.e. credit; by implication, to entrust (especially one's
5   spiritual well-being to Christ):--believe(-r), commit (to trust), put
6   in trust with.
7   see GREEK for 4102
\end{verbatim}

\begin{verbatim}
1  :  166  aionios  ahee-o'-nee-os
2  
3   from 165; perpetual (also used of past time, or past and future as
4   well):--eternal, for ever, everlasting, world (began).
5   see GREEK for 165
\end{verbatim}

\begin{verbatim}
1  :  2222  zoe  dzo-ay'
2  
3   from 2198; life (literally or figuratively):--life(-time). Compare
4   5590.
5   see GREEK for 2198
6   see GREEK for 5590
\end{verbatim}

\textbf{1 John 3:23} - And this is his commandment, that we believe in the name of his Son Jesus Christ and love one another, just as he has commanded us. (ESV)

\textbf{Matthew 22:37-39} - And he said to him, You shall love the Lord your God with all your heart and with all your soul and with all your mind. This is the great and first commandment. And a second is like it: You shall love your neighbor as yourself. (ESV)

Jesus Christ is the Son of the Living God. Believing on His name is God's will for us, and loving one another is God's will for us as He has commanded. There is more that Jesus has commanded us, too.

Repentance and coming to the light are absolutely part of the gospel!

\textbf{1 Corinthians 15:1-4} -  Now I would remind you, brothers, of the gospel I preached to you, which you received, in which you stand, and by which you are being saved, if you hold fast to the word I preached to you-unless you believed in vain.  For I delivered to you as of first importance what I also received: that Christ died for our sins in accordance with the Scriptures, that he was buried, that he was raised on the third day in accordance with the Scriptures,  (ESV)

\textbf{Acts 2:47} - Praising God, and having favour with all the people. And the Lord added to the church daily such as should be saved. (ESV)

\subsubsection{A life of faith (living in accordance with the truth, and in relationship with God) is required - faith continues}
\label{sec:org5a0bba2}
What I mean by relationship is:
\begin{itemize}
\item being obedient to God,
\begin{itemize}
\item abiding in Jesus
\end{itemize}
\item being accountable to God,
\item waiting on God,
\item trusting on God,
\item being led by the Spirit of God,
\item etc.
\end{itemize}

\subsubsection{We must continue abiding in Jesus}
\label{sec:orgcd13601}

\textbf{Romans 6:23} - For the wages of sin is death, but the free gift of God is eternal life \uline{in} Christ Jesus our Lord. (ESV)

\subsubsection{We must live sowing to the Spirit}
\label{sec:org10a10cb}

\textbf{Galatians 6:7-8} - Do not be deceived: God is not mocked, for whatever one sows, that will he also reap. For the one who sows to his own flesh will from the flesh reap corruption, but the one who sows to the Spirit will from the Spirit reap eternal life. (ESV)

\subsubsection{We must remain faithful to Jesus Christ}
\label{sec:orga401d0e}

\textbf{Jude 1:4} - For certain persons have crept in unnoticed, those who were long beforehand marked out for this condemnation, ungodly persons who turn the grace of our God into licentiousness and deny our only Master and Lord, Jesus Christ. (NASB)

\textbf{Colossians 2:18-19} - Let no one disqualify you, insisting on asceticism and worship of angels, going on in detail about visions, puffed up without reason by his sensuous mind, and not holding fast to the Head, from whom the whole body, nourished and knit together through its joints and ligaments, grows with a growth that is from God.

\subsubsection{We \textbf{should} clean ourselves up}
\label{sec:orgcc65a33}
\textbf{II Timothy 2:21} - Therefore, if anyone cleanses himself from what is dishonorable, he will be a vessel for honorable use, set apart as holy, useful to the master of the house, ready for every good work.

By faith:

\textbf{Acts 15:8-9} - And God, who knows the heart, bore witness to them, by giving them the Holy Spirit just as he did to us, and he made no distinction between us and them, having cleansed their hearts by faith.

\subsubsection{We \textbf{must} clean ourselves up}
\label{sec:orga66bad4}
\textbf{Daniel 12:9-10} - He said, Go your way, Daniel, for the words are shut up and sealed until the time of the end.  Many shall purify themselves and make themselves white and be refined, but the wicked shall act wickedly. And none of the wicked shall understand, but those who are wise shall understand.

\textbf{Revelation of John 21:27} - But nothing unclean will ever enter it, nor anyone who does what is detestable or false, but only those who are written in the Lamb's book of life.

\textbf{Revelation of John 22:14} - Blessed are those who wash their robes, so that they may have the right to the tree of life and that they may enter the city by the gates. (ESV)

\subsubsection{We must stop sinning}
\label{sec:orga3546db}

\textbf{II Peter 2:2-4} - And many will follow their sensuality, and because of them \uline{the way of truth} will be blasphemed. And in their greed they will exploit you with false words. Their condemnation from long ago is not idle, and their destruction is not asleep. For if God did not spare angels when they sinned, but cast them into hell and committed them to chains of gloomy darkness to be kept until the judgment;

\textbf{II Peter 2:19-20} - They promise them freedom, but they themselves are slaves of corruption. For \uline{whatever overcomes a person, to that he is enslaved}. For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first.

Therefore, the way of truth involves following Jesus and putting a stop to sin.

I agree with Billy Graham:
\begin{itemize}
\item \url{https://www.youtube.com/watch?v=jCrhHjQgVhA}
\end{itemize}

\textbf{Revelation of John 21:8} - But as for the cowardly, the faithless, the detestable, as for murderers, the sexually immoral, sorcerers, idolaters, and all liars, their portion will be in the lake that burns with fire and sulfur, which is the second death." (ESV)

\section{The LORD our God and my Lord Jesus Christ}
\label{sec:org3401943}
\textbf{Acts 2:34} - For David is not ascended into the heavens: but he saith himself, The Lord said unto my Lord, Sit thou on my right hand,

\section{Jesus, the Bread of Life}
\label{sec:orgaa5e173}
\subsection{Have faith in Jesus. Continue in faith in Jesus and it will well up to eternal life}
\label{sec:orgc8c2ccf}
\textbf{John 6:35} - Jesus said to them, I am the bread of life; whoever comes to me shall not hunger, and whoever believes in me shall never thirst.

\textbf{John 6:38-40} - For I have come down from heaven, not to do my own will but the will of him who sent me. And this is the will of him who sent me, that I should lose nothing of all that he has given me, but raise it up on the last day. For this is the will of my Father, that everyone who looks on the Son and believes in him should have eternal life, and I will raise him up on the last day.

\subsubsection{Drink}
\label{sec:orga0c2c7d}
\textbf{John 7:37-38} - On the last day of the feast, the great day, Jesus stood up and cried out, If anyone thirsts, let him come to me and drink. Whoever \uline{believes in me}, as the Scripture has said, Out of his heart will flow rivers of living water.

\textbf{John 4:14} - but whoever drinks of the water that I will give him will never be thirsty forever. The water that I will give him will become in him a spring of water \uline{welling up to eternal life}.

Whoever believes in Jesus.

\subsubsection{Food}
\label{sec:orgab5c55d}
\textbf{John 4:34} - Jesus said to them, My food is to do the will of him who sent me and to accomplish his work.

\textbf{John 6:27} - Do not labor for the food that perishes, but for the food that endures to eternal life, which the Son of Man will give to you. For on him God the Father has set his seal.

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.} (ESV)

Whoever believes in him who God has sent.

\subsubsection{Look upon, consider and have faith (which is a relationship with God)}
\label{sec:org5cef905}
\textbf{John 6:40} - For this (G3778 houtos) is the will (G2307 thelema) of My Father (G3962 pater), that everyone (G3956 pas) who beholds (G2334 theoreo) the Son (G5207 huios) and believes (G4100 pisteuo) in Him will have (G2192 echo) eternal (G166 aionios) life (G2222 zoe), and I Myself (G1473 ego) will raise (G450 anistemi) him up on the last (G2078 eschatos) day (G2250 hemera).”

\begin{verbatim}
1  :  2334  theoreo  theh-o-reh'-o
2  
3   from a derivative of 2300 (perhaps by addition of 3708); to be a
4   spectator of, i.e. discern, (literally, figuratively (experience) or
5   intensively (acknowledge)):--behold, consider, look on, perceive, see.
6   Compare 3700.
7   see GREEK for 2300
8   see GREEK for 3708
9   see GREEK for 3700
\end{verbatim}

\textbf{John 6:47-58} - Truly, truly, I say to you, whoever believes has eternal life. I am the bread of life. Your fathers ate the manna in the wilderness, and they died. This is the bread that comes down from heaven, so that one may eat of it and not die. I am the living bread that came down from heaven. If anyone eats of this bread, he will live forever. And the bread that I will give for the life of the world is my flesh. The Jews then disputed among themselves, saying, How can this man give us his flesh to eat? So Jesus said to them, Truly, truly, I say to you, unless you eat the flesh of the Son of Man and drink his blood, you have no life in you. Whoever feeds on my flesh and drinks my blood has eternal life, and I will raise him up on the last day. For my flesh is true food, and my blood is true drink. Whoever feeds on my flesh and drinks my blood abides in me, and I in him. As the living Father sent me, and I live because of the Father, so whoever feeds on me, he also will live because of me. This is the bread that came down from heaven, not as the fathers ate and died. Whoever feeds on this bread will live forever.

\subsection{Jesus, the Bread of Life}
\label{sec:org10b6b36}
Doing words (verbs):, eats, feeds, drinks.

Action is required on the part of the believer - walking in the light, as he is in the light.

Obeying Jesus:
\begin{itemize}
\item Believing in him
\item Continuing to believe in him
\item Trusting him
\item Obeying him
\end{itemize}

\textbf{John 6:48-58} - I am the bread of life. Your fathers ate the manna in the wilderness, and they died. This is the bread that comes down from heaven, so that one may eat of it and not die. I am the living bread that came down from heaven. If anyone eats of this bread, he will live forever. And the bread that I will give for the life of the world is my flesh. The Jews then disputed among themselves, saying, How can this man give us his flesh to eat? So Jesus said to them, Truly, truly, I say to you, unless you eat the flesh of the Son of Man and drink his blood, you have no life in you. Whoever \textbf{feeds} on my flesh and \textbf{drinks} my blood has eternal life, and I will raise him up on the last day. For my flesh is true food, and my blood is true drink. Whoever feeds on my flesh and drinks my blood abides in me, and I in him. As the living Father sent me, and I live because of the Father, so whoever feeds on me, he also will live because of me. This is the bread that came down from heaven, not as the fathers ate and died. Whoever feeds on this bread will live forever.

\textbf{Hebrews 10:16-22} - This is the covenant that I will make with them after those days, declares the Lord: I will put my laws on their hearts, and write them on their minds, then he adds, I will remember their sins and their lawless deeds no more.  Where there is forgiveness of these, there is no longer any offering for sin.  Therefore, brothers, since we have confidence to enter the holy places by the blood of Jesus, by the new and living way that he opened for us through the curtain, that is, through his flesh, and since we have a great priest over the house of God, let us draw near with a true heart in full assurance of faith, with our hearts sprinkled clean from an evil conscience and our bodies washed with pure water.

\subsubsection{They will be taught by God, through Jesus}
\label{sec:org1c8574d}
\textbf{Isaiah 54:5-17} - For your Maker is your husband, the Lord of hosts is his name; and the Holy One of Israel is your Redeemer, the God of the whole earth he is called. For the Lord has called you like a wife deserted and grieved in spirit, like a wife of youth when she is cast off, says your God. For a brief moment I deserted you, but with great compassion I will gather you. In overflowing anger for a moment I hid my face from you, but with everlasting love I will have compassion on you, says the Lord, your Redeemer. This is like the days of Noah to me: as I swore that the waters of Noah should no more go over the earth, so I have sworn that I will not be angry with you, and will not rebuke you. For the mountains may depart and the hills be removed, but my steadfast love shall not depart from you, and my covenant of peace shall not be removed, says the Lord, who has compassion on you. O afflicted one, storm-tossed and not comforted, behold, I will set your stones in antimony, and lay your foundations with sapphires. I will make your pinnacles of agate, your gates of carbuncles, and all your wall of precious stones. \textbf{All your children shall be taught by the Lord}, and great shall be the peace of your children. \textbf{In righteousness you shall be established}; you shall be far from oppression, for you shall not fear; and from terror, for it shall not come near you. If anyone stirs up strife, it is not from me; whoever stirs up strife with you shall fall because of you. Behold, I have created the smith who blows the fire of coals and produces a weapon for its purpose. I have also created the ravager to destroy; no weapon that is fashioned against you shall succeed, and you shall confute every tongue that rises against you in judgment. This is the heritage of the servants of the Lord and their vindication from me, declares the Lord.

\textbf{Isaiah 30:20-21} - And \uline{though the Lord give you the bread of adversity and the water of affliction, yet your Teacher will not hide himself anymore}, but your eyes shall see your Teacher. And your ears shall hear a word behind you, saying, \textbf{This is the way, walk in it}, when you turn to the right or when you turn to the left.

\textbf{John 6:44-47} - No one can come to me unless the Father who sent me draws him. And I will raise him up on the last day. It is written in the Prophets, And they will all be taught by God. Everyone who has heard and learned from the Father comes to me— not that anyone has seen the Father except he who is from God; he has seen the Father. Truly, truly, I say to you, whoever believes has eternal life.

\textbf{Jeremiah 31:33-34} - But this is the covenant that I will make with the house of Israel after those days, declares the LORD: I will put my law within them, and I will write it on their hearts.  And I will be their God, and they shall be my people.  And no longer shall each one teach his neighbor and each his brother, saying, Know the LORD, for they shall all know me, from the least of them to the greatest, declares the LORD.  For I will forgive their iniquity, and I will remember their sin no more.  (ESV)

\subsubsection{Abiding in the Truth}
\label{sec:org7e8bb69}
\textbf{John 6:33} - For the bread of God is he who comes down from heaven and gives life to the world.
\textbf{John 6:35} - Jesus said to them, I am the bread of life; whoever comes to me shall not hunger, and whoever believes in me shall never thirst.

Believing in Jesus is good work.
Believing in Jesus keeps us alive.
Obeying Jesus keeps us alive.
Following Jesus keeps us alive.

He is the Way, the Truth and the Life.

\textbf{John 6:28-29} - Then they said to him, \uline{What must we do, to be doing the works of God?} Jesus answered them, This is the work of God, that \textbf{you believe (G4100 pisteuo) in him whom he has sent.} (ESV)

\textbf{John 6:56} - He who eats My flesh and drinks My blood abides in Me, and I in him.

Get intimate with Jesus - \textbf{really} intimate.

I believe this means to become a disciple of Jesus and become one in spirit with Jesus; to think like Jesus, to walk as Jesus walked, to love God and obey God as Jesus did, even if one is persecuted for being righteous as happened to Jesus, to do as Jesus commanded, to become one in spirit with Jesus. Also, taking communion is about that.

It's really important to come to communion with the type of heart that would yearn to be a good disciple of Jesus - repentant and obedient, and thankful for what He has done.

\textbf{I John 1:7} - But \uline{if we walk in the light, as he is in the light}, we have fellowship with one another, \textbf{and the blood of Jesus his Son cleanses us from all sin}.

\textbf{I Corinthians 2:11} - For who knows a person's thoughts except the spirit of that person, which is in him? So also no one comprehends the thoughts of God except the Spirit of God. Now we have received not the spirit of the world, but the Spirit who is from God, that we might understand the things freely given us by God. And we impart this in words not taught by human wisdom but taught by the Spirit, interpreting spiritual truths to those who are spiritual. The natural person does not accept the things of the Spirit of God, for they are folly to him, and he is not able to understand them because they are spiritually discerned. The spiritual person judges all things, but is himself to be judged by no one. For who has understood the mind of the Lord so as to instruct him? But we have the mind of Christ.

\textbf{John 5:39} - You search the Scriptures because you think that in them you have eternal life; and it is they that bear witness about me,

\textbf{Leviticus 17:11} - For the life of the flesh is in the blood, and I have given it for you on the altar to make atonement for your souls, for it is the blood that makes atonement by the life.

Communion is spiritual:

\textbf{John 6:53-58} - So Jesus said to them, Truly, truly, I say to you, unless you eat the flesh of the Son of Man and drink his blood, you have no life in you.  Whoever feeds on my flesh and drinks my blood has eternal life, and I will raise him up on the last day.  For my flesh is true food, and my blood is true drink.  Whoever feeds on my flesh and drinks my blood abides in me, and I in him.  As the living Father sent me, and I live because of the Father, so whoever feeds on me, he also will live because of me.  This is the bread that came down from heaven, not as the fathers ate and died. Whoever feeds on this bread will live forever.

\textbf{I Corinthians 10:16-18} - The cup of blessing that we bless, is it not a participation in the blood of Christ? The bread that we break, is it not a participation in the body of Christ? Because there is one bread, we who are many are one body, for we all partake of the one bread. Consider the people of Israel: are not those who eat the sacrifices participants in the altar?

\textbf{Hebrews 10:19} - Therefore, brothers, since we have confidence to enter the holy places by the blood of Jesus, by the new and living way that he opened for us through the curtain, that is, through his flesh,

\textbf{Didache 10:6} - Let grace come, and let this world pass away. Hosanna to the Son of David. If any one is holy let him come (to the Eucharist); if any one is not, let him repent. Maranatha. Amen.

Proclaim the Lord's death until He comes:

\textbf{I Corinthians 11:25-26} - In the same way also he took the cup, after supper, saying, This cup is the new covenant in my blood. Do this, as often as you drink it, in remembrance of me. For as often as you eat this bread and drink the cup, you proclaim the Lord's death until he comes.

If a person believes Jesus' words their faith will grow.

Father God authorizes people to come to Jesus, but that person must come to Jesus (of their own volition, I think).

\textbf{John 6:61-65} - But Jesus, knowing in himself that his disciples were grumbling about this, said to them, Do you take offense at this?  Then what if you were to see the Son of Man ascending to where he was before?  It is the Spirit who gives life; the flesh is of no avail. The words that I have spoken to you are spirit and life.  But there are some of you who do not believe. (For Jesus knew from the beginning who those were who did not believe, and who it was who would betray him. ) And he said, This is why I told you that no one can come to me unless it is granted him by the Father.

\section{The day}
\label{sec:org71e4882}
If someone has the light in him, he walks in the day.

\textbf{John 9:3-5} - Jesus answered, It was not that this man sinned, or his parents, but that the works of God might be displayed in him. We must work the works of him who sent me while it is day; night is coming, when no one can work. As long as I am in the world, I am the light of the world. (ESV)

\textbf{John 12:35} - So Jesus said to them, The light is among you for a little while longer.  Walk while you have the light, lest darkness overtake you.  The one who walks in the darkness does not know where he is going.  (ESV)

If someone walks in the day with the light in them, they will not stumble.
With the light in them, they should not be concerned about such worries.
They should put confidence in the light.

\textbf{John 11:6-10} - So, when he heard that Lazarus was ill, he stayed two days longer in the place where he was. Then after this he said to the disciples, Let us go to Judea again. The disciples said to him, Rabbi, the Jews were just now seeking to stone you, and are you going there again? Jesus answered, Are there not twelve hours in the day? If anyone walks in the day, he does not stumble, because he sees the light of this world. But if anyone walks in the night, he stumbles, because the light is not in him. (ESV)

Interestingly, Jesus goes confidently back to Judea where the disciples were worried he would be stoned, but instead of someone killing Jesus, Jesus resurrects Lazarus. I guess it pays to walk while you have the light.

\textbf{John 11:11-15} - After saying these things, he said to them, Our friend Lazarus has fallen asleep, but I go to awaken him. The disciples said to him, Lord, if he has fallen asleep, he will recover. Now Jesus had spoken of his death, but they thought that he meant taking rest in sleep. Then Jesus told them plainly, Lazarus has died, and for your sake I am glad that I was not there, so that you may believe. But let us go to him. (ESV)

We should be more confident with the light!

\textbf{Matthew 5:16} - In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven.

\href{https://www.youtube.com/watch?v=T9Eqm8uIuck}{This Is The Day \{Garratt\} - YouTube}

\subsection{No more night}
\label{sec:org2d5b841}

\textbf{Revelation 22:3-5} -  No longer will there be anything accursed, but the throne of God and of the Lamb will be in it, and his servants will worship him.  They will see his face, and his name will be on their foreheads.  And night will be no more.  They will need no light of lamp or sun, for the Lord God will be their light, and they will reign forever and ever. (ESV)

\textbf{Matthew 17:1-3} -  And after six days Jesus took with him Peter and James, and John his brother, and led them up a high mountain by themselves.  And he was transfigured before them, and his face shone like the sun, and his clothes became white as light.  And behold, there appeared to them Moses and Elijah, talking with him.  (ESV)

\section{Christian perfection through suffering with Christ is a thing}
\label{sec:org8e9c2c4}
\subsection{Living a godly life in Christ Jesus is to be wise for salvation}
\label{sec:org23a4b80}
\textbf{II Timothy 3:12-15} - Indeed, \uline{all who desire to live a godly life in Christ Jesus will be persecuted}, while evil people and impostors will go on from bad to worse, deceiving and being deceived. But as for you, continue in what you have learned and have firmly believed, knowing from whom you learned it and how from childhood you have been acquainted with the sacred writings, which are able to \uline{make you wise for salvation through faith in Christ Jesus}. (ESV)

\subsection{Unity in love}
\label{sec:org92d6e41}
\textbf{Colossians 3:14} - Beyond all (G3956 pas) these things put on love (G26 agape), which (G3739 hos) is the perfect bond of unity.

\textbf{John 17:23} - I in them and You in Me, that they may be perfected (G5048 teleioo) in unity, so that the world (G2889 kosmos) may know (G1097 ginosko) that You sent Me, and loved (G25 agapao) them, even as You have loved (G25 agapao) Me.

\subsection{It's wholeness and fullness, knowledge of Jesus}
\label{sec:org38ac6de}
\textbf{I Corinthians 13:10} - but when the perfect (G5046 teleios) comes, the partial (G3313 meros) will be done away.

\textbf{Ephesians 4:13} - until we all attain to the unity of the faith and of the knowledge of the Son of God, to mature manhood, to the measure of the stature of the fullness of Christ, (ESV)

\subsection{It's cleaning ourselves up from all defilement of flesh and spirit}
\label{sec:orgd6be043}
\textbf{II Corinthians 7:1} - Therefore, having these promises, beloved, let us cleanse ourselves (G1438 heautou) from all (G3956 pas) defilement of flesh (G4561 sarx) and spirit (G4151 pneuma), perfecting holiness in the fear of God (G2316 theos).

\subsection{It's a process leading to the day of Christ Jesus}
\label{sec:orgb1c5bac}
\textbf{Philippians 3:12} - Not that I have already obtained (G2983 lambano) it or have already become perfect (G5048 teleioo), but I press on so that I may lay hold of that for which (G3739 hos) also I was laid hold of by Christ (G5547 Christos) Jesus (G2424 Iesous).

\textbf{Philippians 1:6} - For I am confident of this very thing, that He who began a good work (G2041 ergon) in you will perfect it until the day (G2250 hemera) of Christ (G5547 Christos) Jesus (G2424 Iesous).

\subsection{Having suffered for righteousness-sake}
\label{sec:org93eab91}
\textbf{I Peter 5:10} - After you have suffered (G3958 pascho) for a little (G3641 oligos) while (G3641 oligos), the God (G2316 theos) of all (G3956 pas) grace (G5485 charis), who called (G2564 kaleo) you to His eternal (G166 aionios) glory (G1391 doxa) in Christ (G5547 Christos), will Himself (G846 autos) perfect (G2675 katartizo), confirm (G4741 sterizo), strengthen (G4599 sthenoo) and establish (G2311 themelioo) you.

\subsection{Without lack}
\label{sec:org970898a}
\textbf{James 1:4} - And let endurance have its perfect (G5046 teleios) result (G2041 ergon), so that you may be perfect (G5046 teleios) and complete, lacking in nothing.

\textbf{James 2:22} - You see that faith (G4102 pistis) was working with his works (G2041 ergon), and as a result of the works (G2041 ergon), faith (G4102 pistis) was perfected (G5048 teleioo);

\textbf{I John 2:5} - but whoever keeps His word (G3056 logos), in him the love (G26 agape) of God (G2316 theos) has truly been perfected (G5048 teleioo). By this we know (G1097 ginosko) that we are in Him:

\textbf{I John 4:12} - No one has seen God (G2316 theos) at any time; if we love (G25 agapao) one another, God (G2316 theos) abides in us, and His love (G26 agape) is perfected (G5048 teleioo) in us.

\subsection{Perfection is the result of sanctification}
\label{sec:orgef8a1e5}

\textbf{Hebrews 5:8-10} - Although he was a son, he learned obedience through what he suffered. And being made perfect, he became the source of eternal salvation to all who obey him, being designated by God a high priest after the order of Melchizedek.

\textbf{Hebrews 7:11} - Now if perfection had been attainable through the Levitical priesthood (for under it the people received the law), what further need would there have been for another priest to arise after the order of Melchizedek, rather than one named after the order of Aaron?

\textbf{Hebrews 10:14:} - For by one offering He has perfected (G5048 teleioo) for all (G1336 dienekes) time (G1336 dienekes) those who are sanctified.

\textbf{Hebrews 12:23:} - to the general assembly and church of the firstborn who are enrolled in heaven (G3772 ouranos), and to God (G2316 theos), the Judge of all (G3956 pas), and to the spirits (G4151 pneuma) of the righteous (G1342 dikaios) made (G5048 teleioo) perfect (G5048 teleioo),

\textbf{Hebrews 2:11-12} -  For he who sanctifies and those who are sanctified all have one origin.  That is why he is not ashamed to call them brothers, saying, I will tell of your name to my brothers; in the midst of the congregation I will sing your praise.  (ESV)

\section{Eldership}
\label{sec:orgb96a3d5}
\subsection{Don't dominate the flock, but be an example}
\label{sec:org6e83123}
Dominating others in your flock and forcing them to believe what you believe is like witchcraft, and will forfeit glorification. - See glorification.
We're supposed to lead by example.

To be domineering is to behave like a lord.

\textbf{1 Peter 5:1-4} - So I exhort the elders among you, as a fellow elder and a witness of the sufferings of Christ, as well as a partaker in the \textbf{glory} that is going to be revealed: shepherd the flock of God that is among you, exercising oversight, not under compulsion, but willingly, as God would have you; not for shameful gain, but eagerly; \textbf{not domineering} over those in your charge, but being examples to the flock. And when the chief Shepherd appears, you will receive the unfading crown of glory. (ESV)

\textbf{I Corinthians 8:6} - yet for us there is one God, the Father, from whom are all things and for whom we exist, and one Lord, Jesus Christ, through whom are all things and through whom we exist.

\textbf{Ephesians 4:5} - one Lord, one faith, one baptism,

\textbf{I Corinthians 11:3} - But I want you to understand that the head of every man is Christ, the head of a wife is her husband, and the head of Christ is God. (ESV)

\subsubsection{Jesus is our only Teacher and Lord}
\label{sec:org652d03a}
\textbf{John 13:13} - You call me Teacher and Lord, and you are right, for so I am. (ESV)

\textbf{Matthew 23:8} - But you are not to be called rabbi, for you have one teacher, and you are all brothers. (ESV)

\subsubsection{Jesus has said we must stop sinning and follow Jesus to enter the kingdom}
\label{sec:org57d8c55}
Anyone who says otherwise is a false teacher.

\textbf{Luke 18:18-27} - And a ruler asked him, Good Teacher, what must I do to inherit eternal life? And Jesus said to him, Why do you call me good? No one is good except God alone. You know the commandments: Do not commit adultery, Do not murder, Do not steal, Do not bear false witness, Honor your father and mother. And he said, All these I have kept from my youth. When Jesus heard this, he said to him, One thing you still lack. Sell all that you have and distribute to the poor, and you will have treasure in heaven; and come, follow me. But when he heard these things, he became very sad, for he was extremely rich. Jesus, looking at him with sadness, said, How difficult it is for those who have wealth to enter the kingdom of God! For it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. Those who heard it said, Then who can be saved? But he said, What is impossible with men is possible with God.

\textbf{II Peter 2:1} - But false prophets also arose among the people, just as there will be false teachers among you, who will secretly bring in destructive heresies, \textbf{even denying the Master who bought them}, bringing upon themselves swift destruction.

\subsection{Those that are younger, be subject to the elders}
\label{sec:org15288e2}
\textbf{I Peter 5:5} - Likewise, you who are younger, be subject to the elders. Clothe yourselves, all of you, with humility toward one another, for God opposes the proud but gives grace to the humble.

God's grace goes to the humble.

\subsection{It's more important to obey God if an elder is teaching falsehood}
\label{sec:orgf53e7d2}
\textbf{Acts 5:29} - But Peter and the apostles answered, We must obey God rather than men.

\textbf{I Corinthians 11:3} - But I want you to understand that the head of every man is Christ, the head of a wife is her husband, and the head of Christ is God. (ESV)

\textbf{Ephesians 5:23} - For the husband is the head of the wife even as Christ is the head of the church, his body, and is himself its Savior.

\subsubsection{Obedience to Christ is also necessary for salvation}
\label{sec:org40926f9}
\textbf{Hebrews 5:8-10} - Although he was a son, he learned obedience through what he suffered. And being made perfect, he became the source of eternal salvation to all who obey him, being designated by God a high priest after the order of Melchizedek.

So sometimes a person needs to choose Jesus over false teachers and blind guides.

\section{Can Other religions exist anywhere in the Kingdom of God. They have to put their faith in and follow Jesus}
\label{sec:orgd1ff980}
It's not really the religion but who puts their faith in Jesus and \textbf{obeys} the gospel who will be saved.

Jesus Christ is God's servant. We are Jesus' servants. It is a kingdom of servants, obedient to God.

Not all religions are equal. There is only one true God, the Father of Jesus Christ who has revealed Himself in Jesus Christ.

\textbf{John 14:6} - Jesus said to him, I am the way, and the truth, and the life. No one comes to the Father except through me. (ESV)

\textbf{1 Corinthians 8:5-6} - For although there may be so-called gods in heaven or on earth-as indeed there are many gods and many lords- yet for us there is one God, the Father, from whom are all things and for whom we exist, and one Lord, Jesus Christ, through whom are all things and through whom we exist. (ESV)

\textbf{John 13:34-35} - A new commandment I give to you, that you love one another: just as I have loved you, you also are to love one another. By this all people will know that you are my disciples, if you have love for one another. (ESV)

\textbf{Galatians 1:6-10} - I am astonished that you are so quickly deserting him who called you in the grace of Christ and are turning to a different gospel- not that there is another one, but there are some who trouble you and want to distort the gospel of Christ. But even if we or an angel from heaven should preach to you a gospel contrary to the one we preached to you, let him be accursed. As we have said before, so now I say again: If anyone is preaching to you a gospel contrary to the one you received, let him be accursed. For am I now seeking the approval of man, or of God? Or am I trying to please man? If I were still trying to please man, I would not be a servant of Christ. (ESV)

\textbf{Micah 4:1-13} - It shall come to pass in the latter days that the mountain of the house of the LORD shall be established as the highest of the mountains, and it shall be lifted up above the hills; and peoples shall flow to it, and many nations shall come, and say: Come, let us go up to the mountain of the LORD, to the house of the God of Jacob, that he may teach us his ways and that we may walk in his paths. For out of Zion shall go forth the law, and the word of the LORD from Jerusalem. He shall judge between many peoples, and shall decide for strong nations afar off; and they shall beat their swords into plowshares, and their spears into pruning hooks; nation shall not lift up sword against nation, neither shall they learn war anymore; but they shall sit every man under his vine and under his fig tree, and no one shall make them afraid, for the mouth of the LORD of hosts has spoken. For all the peoples walk each in the name of its god, but we will walk in the name of the LORD our God forever and ever. In that day, declares the LORD, I will assemble the lame and gather those who have been driven away and those whom I have afflicted; and the lame I will make the remnant, and those who were cast off, a strong nation; and the LORD will reign over them in Mount Zion from this time forth and forevermore. And you, O tower of the flock, hill of the daughter of Zion, to you shall it come, the former dominion shall come, kingship for the daughter of Jerusalem. Now why do you cry aloud? Is there no king in you? Has your counselor perished, that pain seized you like a woman in labor? Writhe and groan, O daughter of Zion, like a woman in labor, for now you shall go out from the city and dwell in the open country; you shall go to Babylon. There you shall be rescued; there the LORD will redeem you from the hand of your enemies. Now many nations are assembled against you, saying, Let her be defiled, and let our eyes gaze upon Zion. But they do not know the thoughts of the LORD; they do not understand his plan, that he has gathered them as sheaves to the threshing floor. Arise and thresh, O daughter of Zion, for I will make your horn iron, and I will make your hoofs bronze; you shall beat in pieces many peoples; and shall devote their gain to the LORD, their wealth to the Lord of the whole earth. (ESV)

\textbf{James 1:26} - If anyone thinks he is religious and does not bridle his tongue but deceives his heart, this person's religion is worthless. Religion that is pure and undefiled before God, the Father, is this: to visit orphans and widows in their affliction, and to keep oneself unstained from the world.

\subsection{They also have to repent from idolatry}
\label{sec:org918961e}
\textbf{I Corinthians 10:14-31} - Therefore, my beloved, flee from idolatry. I speak as to sensible people; judge for yourselves what I say. The cup of blessing that we bless, is it not a participation in the blood of Christ? The bread that we break, is it not a participation in the body of Christ? Because there is one bread, we who are many are one body, for we all partake of the one bread. Consider the people of Israel: are not those who eat the sacrifices participants in the altar? What do I imply then? That food offered to idols is anything, or that an idol is anything? No, I imply that what pagans sacrifice they offer to demons and not to God. I do not want you to be participants with demons. \textbf{You cannot drink the cup of the Lord and the cup of demons. You cannot partake of the table of the Lord and the table of demons}. Shall we provoke the Lord to jealousy? Are we stronger than he? All things are lawful, but not all things are helpful. All things are lawful, but not all things build up. Let no one seek his own good, but the good of his neighbor. Eat whatever is sold in the meat market without raising any question on the ground of conscience. For the earth is the Lord's, and the fullness thereof. If one of the unbelievers invites you to dinner and you are disposed to go, eat whatever is set before you without raising any question on the ground of conscience. But if someone says to you, This has been offered in sacrifice, then do not eat it, for the sake of the one who informed you, and for the sake of conscience— I do not mean your conscience, but his. For why should my liberty be determined by someone else's conscience? If I partake with thankfulness, why am I denounced because of that for which I give thanks? So, whether you eat or drink, or whatever you do, do all to the glory of God.

\subsubsection{Idolatry}
\label{sec:org8d9202f}

\textbf{Acts 17:29} - Being then God's offspring, we ought not to think that the divine being is like gold or silver or stone, an image formed by the art and imagination of man.

\textbf{Romans 1:23} - and exchanged the glory of the immortal God for images resembling mortal man and birds and animals and reptiles.􄐺

\textbf{Psalms 106:20} - They exchanged the glory of God for the image of an ox that eats grass.􂉢

\section{Man is made in the image of God}
\label{sec:orgfebdad5}
\textbf{Job 33:4} - The Spirit of God has made me, and the breath of the Almighty gives me life.

\subsection{Male and female}
\label{sec:org5de80e5}
\textbf{Genesis 1:27} So God created man in his own image, in the image of God he created him; male and female he created them.

\textbf{Matthew 19:4} - He answered, Have you not read that he who created them from the beginning made them male and female, (ESV)

\subsection{In God's own likeness}
\label{sec:org91776f3}
\textbf{Genesis 5:1-2} -  This is the book of the generations of Adam.  When God created man, he made him in the likeness of God.  Male and female he created them, and he blessed them and named them Man when they were created.  (ESV)

\subsubsection{Righteousness and holiness}
\label{sec:org2032d58}
\textbf{Ephesians 4:24} - and to put on the new self, created after the likeness of God in true righteousness and holiness. (ESV)

\subsection{Created for God's glory}
\label{sec:org4b23b4e}
\textbf{Isaiah 43:6-7} - I will say to the north, Give up, and to the south, Do not withhold; bring my sons from afar and my daughters from the end of the earth, everyone who is called by my name, whom I created for my glory, whom I formed and made.

\subsubsection{Man wasn't designed to kill and curse each other}
\label{sec:orgb150d1a}
\textbf{Genesis 9:6} - Whoever sheds the blood of man, by man shall his blood be shed, for God made man in his own image. (ESV)

\textbf{Luke 6:31} - And as you wish that others would do to you, do so to them. (ESV)

\textbf{James 3:9} - With it we bless our Lord and Father, and with it we curse people who are made in the likeness of God. (ESV)

\textbf{Matthew 26:52} - Then Jesus said to him, Put your sword back into its place.  For all who take the sword will perish by the sword. (ESV)

\textbf{I John 3:15} - Everyone who hates his brother is a murderer, and you know that no murderer has eternal life abiding in him. (ESV)

\subsection{Jesus Christ, Son of God}
\label{sec:orgb0675f4}
\textbf{II Corinthians 4:4} - In their case the god of this world has blinded the minds of the unbelievers, to keep them from seeing the light of the gospel of the glory of Christ, who is the image of God.

\textbf{John 5:26} - For as the Father has life in himself, so he has granted the Son also to have life in himself.

\textbf{John 5:21} - For as the Father raises the dead and gives them life, so also the Son gives life to whom he will.

\textbf{John 1:4} - In Him was life, and the life was the Light of men. (ESV)

\textbf{John 1:9} - The true light, which enlightens everyone, was coming into the world. (ESV)

\textbf{Ephesians 3:9-11} - and to bring to light for everyone what is the plan of the mystery hidden for ages in God who created all things, so that through the church the manifold wisdom of God might now be made known to the rulers and authorities in the heavenly places. This was according to \uline{the eternal purpose that he has realized in Christ Jesus} our Lord,

\textbf{By} him all things were created. Firstborn here does not mean 'created first'.

\textbf{Colossians 1:15-20} - He is the image of the invisible God, the firstborn of all creation. For by him all things were created, in heaven and on earth, visible and invisible, whether thrones or dominions or rulers or authorities—all things were created through him and for him. And he is before all things, and in him all things hold together. And he is the head of the body, the church. He is the beginning, the firstborn from the dead, that in everything he might be preeminent. For in him all the fullness of God was pleased to dwell, and through him to reconcile to himself all things, whether on earth or in heaven, making peace by the blood of his cross.

\textbf{John 1:2}: He was in the beginning with God.

\textbf{Psalms 2:7} - I will tell of the decree: The Lord said to me, You are my Son; today I have begotten you.

\textbf{Acts 13:33} - this he has fulfilled to us their children by raising Jesus, as also it is written in the second Psalm, You are my Son, today I have begotten you.

\textbf{Hebrews 1:5}- For to which of the angels did God ever say, You are my Son, today I have begotten you? Or again, I will be to him a father, and he shall be to me a son?

\textbf{Hebrews 5:5} - So also Christ did not exalt himself to be made a high priest, but was appointed by him who said to him, You are my Son, today I have begotten you;

\textbf{I John 5:20} - And we know that the Son of God has come and has given us understanding, so that we may know him who is true; and we are in him who is true, in his Son Jesus Christ. He is the true God and eternal life.

\textbf{John 17:3} - And this is eternal life, that they know you the only true God, and Jesus Christ whom you have sent.

\section{Marriage}
\label{sec:orge740692}
\subsection{Marriage is between man and woman}
\label{sec:org7c269de}
This is the design:

\textbf{Genesis 2:22-24} - And the rib that the Lord God had taken from the man he made into a woman and brought her to the man. Then the man said, This at last is bone of my bones and flesh of my flesh; she shall be called Woman, because she was taken out of Man. Therefore a man shall leave his father and his mother and hold fast to his wife, and they shall become one flesh. (ESV)

Jesus is in agreement with God's design:

\textbf{Matthew 19:3-9} - And Pharisees came up to him and tested him by asking, Is it lawful to divorce one's wife for any cause? He answered, Have you not read that he who created them from the beginning made them male and female, and said, Therefore a man shall leave his father and his mother and hold fast to his wife, and they shall become one flesh? So they are no longer two but one flesh. What therefore God has joined together, let not man separate. They said to him, Why then did Moses command one to give a certificate of divorce and to send her away? He said to them, Because of your hardness of heart Moses allowed you to divorce your wives, but from the beginning it was not so. And I say to you: whoever divorces his wife, except for sexual immorality, and marries another, commits adultery. (ESV)

\subsubsection{Pursue marriage with those who share our faith and walk in holiness}
\label{sec:org393dc90}
\textbf{I Corinthians 7:39} - A wife is bound to her husband as long as he lives. But if her husband dies, she is free to be married to whom she wishes, only in the Lord. (ESV)

\subsubsection{Gay 'marriage' is not blessed at all by God}
\label{sec:org65cb06f}
So-called 'marriage' between man and man, or woman and woman, is not blessed at all by God.

We've got to be clear on that, but like all other corruption/falsehood, if agreed with and pursued it leads to the abyss.

\subsubsection{The law may have come later, but the law still doesn't annul God's former decrees}
\label{sec:org63ea85a}
\textbf{Galatians 3:17} - This is what I mean: the law, which came 430 years afterward, does not annul a covenant previously ratified by God, so as to make the promise void. (ESV)

\subsubsection{Let's be clear: God's law does not endorse gay marriage}
\label{sec:org346749d}
\textbf{Leviticus 18:22} - You shall not lie with a male as with a woman; it is an abomination. (ESV)

\textbf{Deuteronomy 18:12} - for whoever does these things is an abomination to the Lord. And because of these abominations the Lord your God is driving them out before you. (ESV)

\textbf{Leviticus 18:26-29} - But you shall keep my statutes and my rules and do none of these abominations, either the native or the stranger who sojourns among you (for the people of the land, who were before you, did all of these abominations, so that the land became unclean), For everyone who does any of these abominations, the persons who do them shall be cut off from among their people. (ESV)

\textbf{Leviticus 20:13} - If a man lies with a male as with a woman, both of them have committed an abomination; they shall surely be put to death; their blood is upon them. (ESV)

\textbf{Deuteronomy 22:5} - A woman shall not wear a man's garment, nor shall a man put on a woman's cloak, for whoever does these things is an abomination to the Lord your God. (ESV)

\textbf{Deuteronomy 7:26} - And you shall not bring an abominable thing into your house and become devoted to destruction like it. You shall utterly detest and abhor it, for \uline{it is devoted to destruction}. (ESV)

\textbf{Jeremiah 44:22} - The Lord could no longer bear your evil deeds and the abominations that you committed. Therefore your land has become a desolation and a waste and a curse, without inhabitant, as it is this day. (ESV)

\subsubsection{However, we are justified by faith in Jesus Christ - but that means obeying Jesus}
\label{sec:orgd40b5ef}
\textbf{Galatians 3:22-26} - But the Scripture imprisoned everything under sin, so that the promise by faith in Jesus Christ might be given to those who believe. Now before faith came, we were held captive under the law, imprisoned until the coming faith would be revealed. So then, the law was our guardian until Christ came, in order that we might be justified by faith. But now that faith has come, we are no longer under a guardian, for in Christ Jesus you are all sons of God, through faith.

Grace and truth have come through Jesus Christ.

\textbf{John 1:17} - For the law was given through Moses; grace and truth came through Jesus Christ.

\textbf{James 2:13} - For judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment.

Jesus' servants are given mercy by Jesus and they also show mercy to others.

\subsection{Marriage should not be forbidden}
\label{sec:org2f9cf5f}
\textbf{1 Timothy 4:1-8} - Now the Spirit expressly says that in later times some will depart from the faith by devoting themselves to deceitful spirits and teachings of demons, \textbf{through the insincerity of liars whose consciences are seared, who forbid marriage and require abstinence from foods that God created to be received with thanksgiving by those who believe and know the truth.} For everything created by God is good, and nothing is to be rejected if it is received with thanksgiving, for it is made holy by the word of God and prayer. If you put these things before the brothers, you will be a good servant of Christ Jesus, being trained in the words of the faith and of the good doctrine that you have followed. Have nothing to do with irreverent, silly myths. Rather train yourself for godliness; for while bodily training is of some value, godliness is of value in every way, as it holds promise for the present life and also for the life to come. (ESV)

\subsection{Workers of the kingdom may take a believing wife}
\label{sec:org3d9d0a5}
\textbf{I Corinthians 9:5-9} - Do we not have the right to take along a believing wife, as do the other apostles and the brothers of the Lord and Cephas? Or is it only Barnabas and I who have no right to refrain from working for a living? Who serves as a soldier at his own expense? Who plants a vineyard without eating any of its fruit? Or who tends a flock without getting some of the milk? Do I say these things on human authority? Does not the Law say the same? For it is written in the Law of Moses, You shall not muzzle an ox when it treads out the grain. Is it for oxen that God is concerned?

\subsubsection{But for the sake of the Kingdom, they may choose to be single}
\label{sec:orgd4bf282}

\textbf{Matthew 19:12} - For there are eunuchs who have been so from birth, and there are eunuchs who have been made eunuchs by men, and there are eunuchs who have made themselves eunuchs for the sake of the kingdom of heaven. Let the one who is able to receive this receive it.

\textbf{I Corinthians 7:8-9} - To the unmarried and the widows I say that it is good for them to remain single as I am. But if they cannot exercise self-control, they should marry. For it is better to marry than to be aflame with passion.

\textbf{Revelation of John 14:4} - It is these who have not defiled themselves with women, for they are virgins. It is these who follow the Lamb wherever he goes. These have been redeemed from mankind as firstfruits for God and the Lamb,

\subsubsection{Being ready for Jesus comes first}
\label{sec:org1f59b1c}
\textbf{Luke 14:20-24} - And another said, I have married a wife, and therefore I cannot come. So the servant came and reported these things to his master. Then the master of the house became angry and said to his servant, Go out quickly to the streets and lanes of the city, and bring in the poor and crippled and blind and lame. And the servant said, Sir, what you commanded has been done, and still there is room. And the master said to the servant, Go out to the highways and hedges and compel people to come in, that my house may be filled. For I tell you, none of those men who were invited shall taste my banquet.

\textbf{Matthew 25:1-13} - Then the kingdom of heaven will be like ten virgins who took their lamps and went to meet the bridegroom. Five of them were foolish, and five were wise. For when the foolish took their lamps, they took no oil with them, but the wise took flasks of oil with their lamps. As the bridegroom was delayed, they all became drowsy and slept. But at midnight there was a cry, Here is the bridegroom! Come out to meet him. Then all those virgins rose and trimmed their lamps. And the foolish said to the wise, Give us some of your oil, for our lamps are going out. But the wise answered, saying, Since there will not be enough for us and for you, go rather to the dealers and buy for yourselves. And while they were going to buy, the bridegroom came, and those who were ready went in with him to the marriage feast, and the door was shut. Afterward the other virgins came also, saying, Lord, lord, open to us. But he answered, Truly, I say to you, I do not know you. Watch therefore, for you know neither the day nor the hour.

\subsection{Marriage should be holy for future sake}
\label{sec:org7319849}
God's covenant was given to Noah and his wife and Noah's sons and their wives.

\textbf{Genesis 6:18} - But I will establish my covenant with you, and you shall come into the ark, you, your sons, your wife, and your sons' wives with you.

\textbf{Genesis 7:7} - And Noah and his sons and his wife and his sons' wives with him went into the ark to escape the waters of the flood.

Even the animals went into the ark two by two, \uline{male with their female}:

\textbf{Genesis 6:19} - And of every living thing of all flesh, you shall bring two of every sort into the ark to keep them alive with you. They shall be male and female.

Noah still had a wife, a believing wife, I assume.

\textbf{Matthew 24:38} - For as in those days before the flood they were eating and drinking, marrying and giving in marriage, until the day that Noah entered the ark,

\subsection{Covenant}
\label{sec:orgc893a2e}
\textbf{Malachi 2:14} - But you say, Why does he not?  Because the LORD was witness between you and the wife of your youth, to whom you have been faithless, though she is your companion and your wife by covenant.  (ESV)

Acts 15:19: Therefore my judgment is that we should not trouble those of the Gentiles who turn to God,
Acts 15:20: but should write to them to abstain from the things polluted by idols, and from sexual immorality, and from what has been strangled, and from blood.

\subsection{Marriage in the next age}
\label{sec:org09fc23d}
\subsubsection{Incorruptible love to make it into heaven, but not lust}
\label{sec:org60f44a2}
\textbf{Ephesians 6:24} - Grace be with all those who love our Lord Jesus Christ with incorruptible love.

\textbf{I Corinthians 13:8} - Love never ends. As for prophecies, they will pass away; as for tongues, they will cease; as for knowledge, it will pass away.

\subsubsection{There is no lust in heaven}
\label{sec:orgb75f410}

\textbf{II Peter 1:3-4} - seeing that His divine power has granted to us everything pertaining to life and godliness, through the true knowledge of Him who called us by His own glory and excellence. For by these He has granted to us His precious and magnificent promises, so that by them you may become \uline{partakers of the divine nature, having escaped the corruption that is in the world by lust}. (NASB)

\subsubsection{No-one \textbf{marrys} (verb) or is \textbf{given in marriage} (verb)}
\label{sec:org3d55cf1}
\textbf{Luke 20:33-36} - In the resurrection, therefore, whose wife will the woman be? For the seven had her as wife. And Jesus said to them, The sons of this age (G165 \textbf{aion}) marry (G1060 \textbf{gameo}) and are given in marriage (G1061 \textbf{gamisko}), but those who are considered worthy to attain to that age (G165 \textbf{aion}) and to the resurrection (G386 \textbf{anastasis}) from the dead neither marry nor are given in marriage, for they cannot die anymore, because they are equal to angels and are sons of God, being sons of the resurrection.

\subsubsection{In heaven, people are like angels - imperishable}
\label{sec:orgb3e9af3}
\textbf{Mark 12:25} -  For when they rise from the dead, they neither marry nor are given in marriage, but are like angels in heaven. (ESV)

\textbf{Revelation of John 21:4} - He will wipe away every tear from their eyes, and death shall be no more, neither shall there be mourning nor crying nor pain anymore, for the former things have passed away. (ESV)

We receive an imperishable reward:

\textbf{I Corinthians 9:25} - Everyone who competes in the games exercises self-control in all things. They then do it to receive a perishable wreath, but we an imperishable. (ESV)

\textbf{I Peter 1:4} - to obtain an inheritance which is imperishable and undefiled and will not fade away, reserved in heaven for you, (ESV)

Even our bodies will be imperishable:

\textbf{1 Corinthians 15:4} -  So is it with the resurrection of the dead.  What is sown is perishable; what is raised is imperishable. (ESV)

\textbf{I Corinthians 15:52} - in a moment, in the twinkling of an eye, at the last trumpet; for the trumpet will sound, and the dead will be raised imperishable, and we will be changed. (ESV)

\subsubsection{Jesus is incorruptible}
\label{sec:org2797a5f}
\textbf{Hebrews 1:3} - And He is the radiance of His glory and the exact representation of His nature (G5287 hupostasis), and upholds all things by the word of His power. When He had made purification of sins, He sat down at the right hand of the Majesty on high,

\textbf{Matthew 24:35} - Heaven and earth will pass away, but my words will not pass away.

\textbf{Luke 16:17} - But it is easier for heaven and earth to pass away than for one dot of the Law to become void.

\begin{verbatim}
1  :  5287  hupostasis  hoop-os'-tas-is
2  
3   from a compound of 5259 and 2476; a setting under (support), i.e.
4   (figuratively) concretely, essence, or abstractly, assurance
5   (objectively or subjectively):--confidence, confident, person,
6   substance.
7   see GREEK for 5259
8   see GREEK for 2476
\end{verbatim}

\subsubsection{We are married to Christ}
\label{sec:orgaaa66d1}
\textbf{Revelation of John 21:9} - Then came one of the seven angels who had the seven bowls full of the seven last plagues and spoke to me, saying, Come, I will show you the Bride, the wife of the Lamb.

\textbf{Ephesians 5:23-33} - For the husband is the head of the wife even as Christ is the head of the church, his body, and is himself its Savior. Now as the church submits to Christ, so also wives should submit in everything to their husbands. Husbands, love your wives, as Christ loved the church and gave himself up for her, that he might sanctify her, having cleansed her by the washing of water with the word, so that he might present the church to himself in splendor, without spot or wrinkle or any such thing, that she might be holy and without blemish. In the same way husbands should love their wives as their own bodies. He who loves his wife loves himself. For no one ever hated his own flesh, but nourishes and cherishes it, just as Christ does the church, because we are members of his body. Therefore a man shall leave his father and mother and hold fast to his wife, and the two shall become one flesh. This mystery is profound, and I am saying that it refers to Christ and the church. However, let each one of you love his wife as himself, and let the wife see that she respects her husband.

\textbf{1 Corinthians 15:42} -  So is it with the resurrection of the dead.  What is sown is perishable; what is raised is imperishable. (ESV)

\textbf{Galatians 3:26} - for in Christ Jesus you are all sons of God, through faith.

\textbf{Revelation 20:6} - Blessed and holy is the one who shares in the first resurrection! Over such the second death has no power, but they will be priests of God and of Christ, and they will reign with him for a thousand years. (ESV)

\subsubsection{We must present ourselves as virgins to Christ. We must be being sanctified}
\label{sec:org9b504e8}
\textbf{Matthew 25:1-13} - Then the kingdom of heaven will be like ten virgins who took their lamps and went to meet the bridegroom. Five of them were foolish, and five were wise. For when the foolish took their lamps, they took no oil with them, but the wise took flasks of oil with their lamps. As the bridegroom was delayed, they all became drowsy and slept. But at midnight there was a cry, Here is the bridegroom! Come out to meet him. Then all those virgins rose and trimmed their lamps. And the foolish said to the wise, Give us some of your oil, for our lamps are going out. But the wise answered, saying, Since there will not be enough for us and for you, go rather to the dealers and buy for yourselves. And while they were going to buy, the bridegroom came, and those who were ready went in with him to the marriage feast, and the door was shut. Afterward the other virgins came also, saying, Lord, lord, open to us. But he answered, Truly, I say to you, I do not know you. Watch therefore, for you know neither the day nor the hour.

\subsection{Marriage should not be forbidden}
\label{sec:org66a9c04}
\textbf{1 Timothy 4:1-8} - Now the Spirit expressly says that in later times some will depart from the faith by devoting themselves to deceitful spirits and teachings of demons, \textbf{through the insincerity of liars whose consciences are seared, who forbid marriage and require abstinence from foods that God created to be received with thanksgiving by those who believe and know the truth.} For everything created by God is good, and nothing is to be rejected if it is received with thanksgiving, for it is made holy by the word of God and prayer. If you put these things before the brothers, you will be a good servant of Christ Jesus, being trained in the words of the faith and of the good doctrine that you have followed. Have nothing to do with irreverent, silly myths. Rather train yourself for godliness; for while bodily training is of some value, godliness is of value in every way, as it holds promise for the present life and also for the life to come. (ESV)

Marriage itself is good.

\subsubsection{But gay 'marriage' should not be held in equal standing to God's design}
\label{sec:orgfe0f08c}

\textbf{Isaiah 6:20} - Woe to those who call evil good, and good evil; Who substitute darkness for light and light for darkness; Who substitute bitter for sweet and sweet for bitter!

\subsection{Bride of Christ}
\label{sec:org560069c}
\textbf{Revelation of John 21:9} - Then came one of the seven angels who had the seven bowls full of the seven last plagues and spoke to me, saying, Come, I will show you the Bride, the wife of the Lamb.

\textbf{Revelation of John 19:7-9} - Let us rejoice and exult and give him the glory, for the marriage of the Lamb has come, and his Bride has made herself ready; it was granted her to clothe herself with fine linen, bright and pure— for the fine linen is the righteous deeds of the saints. And the angel said to me, Write this: Blessed are those who are invited to the marriage supper of the Lamb. And he said to me, These are the true words of God. (ESV)

We must espouse ourselves to Christ:

\textbf{II Corinthians 11:2} - I feel a divine jealousy for you, for I \uline{betrothed you to one husband, to present you as a pure virgin to Christ}. (ESV)

The new Jerusalem is the Bride of Christ:

\textbf{Revelation of John 21:2} - And I saw the holy city, new Jerusalem, coming down out of heaven from God, prepared as a bride adorned for her husband. (ESV)

\textbf{John 3:29} - The one who has the bride is the bridegroom. The friend of the bridegroom, who stands and hears him, rejoices greatly at the bridegroom's voice. Therefore this joy of mine is now complete. (ESV)

John the Baptist says that the Christ is the bridegroom:

\textbf{John 3:28-31} - You yourselves bear me witness, that I said, I am not the Christ, but I have been sent before him. The one who has the bride is the bridegroom. The friend of the bridegroom, who stands and hears him, rejoices greatly at the bridegroom's voice. Therefore this joy of mine is now complete. He must increase, but I must decrease. He who comes from above is above all. He who is of the earth belongs to the earth and speaks in an earthly way. He who comes from heaven is above all.

Jesus reinforces that idea:

\textbf{Mark 2:18-20} - Now John's disciples and the Pharisees were fasting. And people came and said to him, Why do John's disciples and the disciples of the Pharisees fast, but your disciples do not fast? And Jesus said to them, Can the wedding guests fast while the bridegroom is with them? As long as they have the bridegroom with them, they cannot fast. The days will come when the bridegroom is taken away from them, and then they will fast in that day. (ESV)

\textbf{Revelation of John 21:9} - Then came one of the seven angels who had the seven bowls full of the seven last plagues and spoke to me, saying, Come, I will show you the Bride, the wife of the Lamb. (ESV)

\textbf{Isaiah 54:5} - For your Maker is your husband, the LORD of hosts is his name; and the Holy One of Israel is your Redeemer, the God of the whole earth he is called. (ESV)

\textbf{Revelation of John 21:9-11} - Then came one of the seven angels who had the seven bowls full of the seven last plagues and spoke to me, saying, Come, I will show you the Bride, the wife of the Lamb. And he carried me away in the Spirit to a great, high mountain, and showed me the holy city Jerusalem coming down out of heaven from God, having the glory of God, its radiance like a most rare jewel, like a jasper, clear as crystal. (ESV)

\textbf{Isaiah 62:3-5} - You shall be a crown of beauty in the hand of the Lord, and a royal diadem in the hand of your God. You shall no more be termed Forsaken, and your land shall no more be termed Desolate, but you shall be called My Delight Is in Her, and your land Married; for the Lord delights in you, and your land shall be married. For as a young man marries a young woman, so shall your sons marry you, and as the bridegroom rejoices over the bride, so shall your God rejoice over you.

\textbf{Revelation of John 22:17} - The Spirit and the Bride say, Come. And let the one who hears say, Come. And let the one who is thirsty come; let the one who desires take the water of life without price. (ESV)

\subsection{I do not endorse gay marriage - I consider it to be sin - grave sin, actually}
\label{sec:org7af5a86}
I personally do not endorse gay marriage. When I have in the past, I repent of that.

That is not to say it is not possible to endorse it yourself (and take the consequences of that) but a person is accountable to God for that act of annulling one of His commandments.

\textbf{Matthew 5:19} - Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven.

In the manner in which I judge, I know I will be judged.

\textbf{Matthew 7:1-2} - “Do not judge so that you will not be judged. For in the way you judge, you will be judged; and by your standard of measure, it will be measured to you.

So I believe that because I do not / no longer
endorse gay marriage for others, I do not
endorse it for myself, and I'll be held to
that standard.

\textbf{Leviticus 18:22} - You shall not lie with a male as with a woman; it is an abomination. (ESV)

However, endorsing gay marriage is not merely breaking commandment, but also it is contrary to the spiritual reality:

\textbf{Genesis 2:22-24} - And the rib that the Lord God had taken from the man he made into a woman and brought her to the man. Then the man said, This at last is bone of my bones and flesh of my flesh; she shall be called Woman, because she was taken out of Man. Therefore a man shall leave his father and his mother and hold fast to his wife, and they shall become one flesh. (ESV)

\subsection{God's law is still used. It's part of the gospel, and can certainly be used to judge the sinners, in clouding those who are unrepentant from sexual immorality}
\label{sec:orgaee62af}
\textbf{1 Timothy 1:8-11} - Now we know that the law is good, if one uses it lawfully, understanding this, that the law is not laid down for the just but for the lawless and disobedient, for the ungodly and sinners, for the unholy and profane, for those who strike their fathers and mothers, for murderers, the sexually immoral, men who practice \textbf{homosexuality}, enslavers, liars, perjurers, and whatever else is contrary to sound doctrine, in accordance with the glorious gospel of the blessed God with which I have been entrusted. (ESV)

\subsection{God's law is good. His precepts are good. I don't identify with any of this LGBT stuff}
\label{sec:orgb8871bd}
\textbf{Psalms 119:49-94} - Remember your word to your servant, in which you have made me hope. Zayin This is my comfort in my affliction, that your promise gives me life. The insolent utterly deride me, but I do not turn away from your law. When I think of your rules from of old, I take comfort, O LORD. Hot indignation seizes me because of the wicked, who forsake your law. Your statutes have been my songs in the house of my sojourning. I remember your name in the night, O LORD, and keep your law. This blessing has fallen to me, that I have kept your precepts. The LORD is my portion; I promise to keep your words. Heth I entreat your favor with all my heart; be gracious to me according to your promise. When I think on my ways, I turn my feet to your testimonies; I hasten and do not delay to keep your commandments. Though the cords of the wicked ensnare me, I do not forget your law. At midnight I rise to praise you, because of your righteous rules. I am a companion of all who fear you, of those who keep your precepts. The earth, O LORD, is full of your steadfast love; teach me your statutes! You have dealt well with your servant, O LORD, according to your word. Teth Teach me good judgment and knowledge, for I believe in your commandments. Before I was afflicted I went astray, but now I keep your word. You are good and do good; teach me your statutes. The insolent smear me with lies, but with my whole heart I keep your precepts; their heart is unfeeling like fat, but I delight in your law. It is good for me that I was afflicted, that I might learn your statutes. The law of your mouth is better to me than thousands of gold and silver pieces. Your hands have made and fashioned me; give me understanding that I may learn your commandments. Yodh Those who fear you shall see me and rejoice, because I have hoped in your word. I know, O LORD, that your rules are righteous, and that in faithfulness you have afflicted me. Let your steadfast love comfort me according to your promise to your servant. Let your mercy come to me, that I may live; for your law is my delight. Let the insolent be put to shame, because they have wronged me with falsehood; as for me, I will meditate on your precepts. Let those who fear you turn to me, that they may know your testimonies. May my heart be blameless in your statutes, that I may not be put to shame! My soul longs for your salvation; I hope in your word. Kaph My eyes long for your promise; I ask, When will you comfort me? For I have become like a wineskin in the smoke, yet I have not forgotten your statutes. How long must your servant endure? When will you judge those who persecute me? The insolent have dug pitfalls for me; they do not live according to your law. \textbf{All your commandments are sure; they persecute me with falsehood}; help me! They have almost made an end of me on earth, but \textbf{I have not forsaken your precepts}. In your steadfast love give me life, that I may keep the testimonies of your mouth. Forever, O LORD, your word is firmly fixed in the heavens. Lamedh Your faithfulness endures to all generations; you have established the earth, and it stands fast. By your appointment they stand this day, for all things are your servants. If your law had not been my delight, I would have perished in my affliction. I will never forget your precepts, for by them you have given me life. I am yours; save me, for I have sought your precepts. (ESV)

\uline{I have not forsaken your precepts} - AMEN!!

\subsection{Can gay 'marriage' exist anywhere in the Kingdom of God? It's certainly not generally endorsed, nor should it be normalised or made equal with marriage}
\label{sec:orgd2602e5}
I don't know if gay marriage can exist anywhere in the Kingdom of God.

I don't think it should be generally endorsed, especially by Christians.

\subsubsection{God still \underline{does not endorse} homosexuality}
\label{sec:org10c74cf}
\textbf{1 Timothy 1:8-11} - Now we know that the law is good, if one uses it lawfully, understanding this, that the law is not laid down for the just but for the lawless and disobedient, for the ungodly and sinners, for the unholy and profane, for those who strike their fathers and mothers, for murderers, the sexually immoral, men who practice \textbf{homosexuality}, enslavers, liars, perjurers, and whatever else is contrary to sound doctrine, in accordance with the glorious gospel of the blessed God with which I have been entrusted. (ESV)

\subsubsection{The most weighty matters of the law are justice, mercy, faithfulness, and service}
\label{sec:org03ef927}
Justice, mercy and faithfulness are \textbf{essential} for entering the Kingdom of God. Repentance and holiness are \uline{very important} for entering the Kingdom of God too. Greed and self-indulgence will stop a person from entering the Kingdom of God:

\textbf{Matthew 23:23-25} - Woe to you, scribes and Pharisees, hypocrites! For you tithe mint and dill and cumin, and have neglected the weightier matters of the law: \uline{justice and mercy and faithfulness. These you ought to have done, without neglecting the others}.  You blind guides, straining out a gnat and swallowing a camel!  Woe to you, scribes and Pharisees, hypocrites! For you clean the outside of the cup and the plate, but inside they are full of greed and self-indulgence.

When applying the law, justice and mercy and faithfulness are the weightier matters of the law.
However, the remainder of the law is not supposed to be neglected either.

\subsubsection{Even though the law came later, homosexuality has always been sinful}
\label{sec:orgd4858b5}
\textbf{Genesis 13:13} - Now the men of Sodom were wicked, great sinners against the Lord.

\textbf{Genesis 18:20} - Then the Lord said, Because the outcry against Sodom and Gomorrah is great and their sin is very grave,

\subsubsection{Faith in Jesus is required - Him paying the price for our sin}
\label{sec:org460367e}

I think endorsing LGBT, etc. leads the world progressively closer to the abyss.

I personally wouldn't do it or endorse it for eternal safety sake.

\textbf{Leviticus 18:22} - You shall not lie with a male as with a woman; it is an abomination. (ESV)

Yes, it is an issue in the law and in God's design, and Gay marriage is not endorsed or blessed by God.

\textbf{Matthew 5:14-20} - You are the light of the world. A city set on a hill cannot be hidden. Nor do people light a lamp and put it under a basket, but on a stand, and it gives light to all in the house. In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. Do not think that I have come to abolish the Law or the Prophets; I have not come to abolish them but to fulfill them. For truly, I say to you, until heaven and earth pass away, not an iota, not a dot, will pass from the Law until all is accomplished. Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. For I tell you, \uline{unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven}.

I currently believe this means that grace may possibly
exist for gay people who have faith in Jesus
but they are accountable to God for it, and
they wont \textbf{inherit} the kingdom of God and His saints.

To enter, a person's righteousness needs to exceed that of
the Pharisees and Scribes in order to enter the Kingdom of God and
the weightier matters of the law are \uline{justice, mercy and faithfulness}.

Also, I think eternal life is for those who:
\begin{itemize}
\item a) receive forgiveness from Jesus,
\item b) obey Jesus and become a bondservant of God.
\end{itemize}

\subsubsection{Sanctification (turning from sin, etc.) is essential for eternal life}
\label{sec:orgc3ec8cc}

\textbf{Romans 6:22} - But now that you have been set free from sin and have become slaves of God, the fruit you get leads to sanctification and its end, eternal life.

This is my current understanding. So most likely it is not tolerated in the kingdom of God.

I 100\% believe that anyone who has faith in Jesus Christ can be saved / spared from being condemned to hell, but that doesn't mean they inherit the Kingdom..
But faith requires obedience, and salvation requires turning from sin.

And it doesn't excuse them from repentance from sin.
But they're accountable for God to it.

Repentance is \textbf{essential} for eternal life.

\textbf{John 8:34-35} - Jesus answered them, Truly, truly, I say to you, everyone who commits sin is a slave to sin. The slave does not remain in the house forever; the son remains forever.

\subsubsection{Homosexuality is very sinful and so locking it in with a covenant is very self-destructive}
\label{sec:org121b5c0}
But justice, mercy and faithfulness are the weightier matters of the law.
What I mean to say is that without the sinners themselves showing justice,
mercy and faithfulness, gay 'marriage' would be totally unjustifiable.

Judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment.

God, please have mercy. I repent from all sexual immorality, and from endorsing it.

\subsubsection{Without following Jesus Christ's commandments, gay 'marriage' would never be justifiable}
\label{sec:org0695df6}
\textbf{Galatians 5:18} - But if you are led by the Spirit, you are not under the law.

But we have to speak and act as those who are to be judged under the law of liberty:

\textbf{James 2:10-13} - For whoever keeps the whole law but fails in one point has become accountable for all of it. For he who said, Do not commit adultery, also said, Do not murder. If you do not commit adultery but do murder, you have become a transgressor of the law. So speak and so act as those who are to be judged under the law of liberty. For judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment.

Without acknowledging the truth, and without acknowledging that God's law and design is good, gay 'marriage' would be totally unjustifiable.

\subsubsection{The slave to sin doesn't remain in God's house forever}
\label{sec:org5cb5371}
\textbf{John 8:34-35} - Jesus answered them, Truly, truly, I say to you, everyone who commits sin is a slave to sin. The slave does not remain in the house forever; the son remains forever.

Also, the Kingdom stretches from heaven to earth, so gay 'marriage' may happen on earth but such a thing could never exist in heaven.

But neither does marriage between man and woman even exist in heaven.

But those who practice sexual impurity which includes homosexuality probably wont \textbf{inherit} the kingdom,
nor enter into the New Jerusalem in Heaven - those are for the saints (those who keep God's commandments AND have faith in Jesus).

\textbf{II Corinthians 11:2} - I feel a divine jealousy for you, for I \uline{betrothed you to one husband, to present you as a pure virgin to Christ}. (ESV)

The new Jerusalem is the Bride of Christ:

\textbf{Revelation of John 21:2} - And I saw the holy city, new Jerusalem, coming down out of heaven from God, prepared as a bride adorned for her husband. (ESV)

But can they \textbf{enter} the kingdom on earth? I'm not sure.
God is the justifier.
So long as they continue in homosexuality, they wouldn't stay.

They have to be practicing righteousness, through following Jesus Christ - and obeying Jesus' commandments:

\textbf{I John 3:7} - Little children, let no one deceive you. Whoever practices righteousness is righteous, as he is righteous.

\textbf{Matthew 6:10} - Your kingdom come, your will be done, on earth as it is in heaven.

I don't think God ever endorses people to sin, but has grace for sinners.

\textbf{John 1:17} - For the law was given through Moses; grace and truth came through Jesus Christ.

I don't think it's possible to receive the grace without receiving the truth, because Jesus Christ is the grace and the truth.

\textbf{Luke 18:13} - But the tax collector, standing far off, would not even lift up his eyes to heaven, but beat his breast, saying, God, be merciful to me, a sinner! (ESV)

Prideful sin definitely doesn't make the cut.

\subsubsection{The everlasting covenant if one is in the everlasting covenant, should incite a person's shame for their past sin - not their pride}
\label{sec:org2d3fcd7}
\textbf{Ezekiel 16:58-63} - You bear the penalty of your lewdness and your abominations, declares the Lord.  For thus says the Lord God: I will deal with you as you have done, you who have despised the oath in breaking the covenant, yet I will remember my covenant with you in the days of your youth, and I will establish for you an everlasting covenant.  Then you will remember your ways and be ashamed when you take your sisters, both your elder and your younger, and I give them to you as daughters, but not on account of the covenant with you.  I will establish my covenant with you, and you shall know that I am the Lord, that you may remember and be confounded, and never open your mouth again because of your shame, when I atone for you for all that you have done, declares the Lord God.

\subsubsection{The abyss is a thing. And our security is faith in Christ}
\label{sec:org6429988}
\textbf{Romans 10:6-13} - But the righteousness based on faith says, Do not say in your heart, Who will ascend into heaven? (that is, to bring Christ down) or Who will descend into the abyss? (that is, to bring Christ up from the dead).  But what does it say? The word is near you, in your mouth and in your heart (that is, the word of faith that we proclaim); because, if you confess with your mouth that Jesus is Lord and believe in your heart that God raised him from the dead, you will be saved.  For \textbf{with the heart one believes (G4100 pisteuo) and is justified}, and with the mouth one confesses and is saved.  For the Scripture says, Everyone who believes in him will not be put to shame.  For there is no distinction between Jew and Greek; the same Lord is Lord of all, bestowing his riches on all who call on him.  For everyone who calls on the name of the Lord will be saved.

But just because Jesus can save us when we have the righteousness based on faith, that doesn't mean we should purposefully sin and go towards the abyss.

We want God's will to be done on earth, as it is done in heaven.

\textbf{Matthew 6:10} - Your kingdom come, your will be done, on earth as it is in heaven.

\subsubsection{Grace even for the evildoer}
\label{sec:org0f6eed4}
The Revelation of John is for Jesus' servants. I'm going to claim this.

\textbf{Revelation of John 1:1} - The revelation of Jesus Christ, which God gave him to show to his servants the things that must soon take place. He made it known by sending his angel to his servant John,

\textbf{Matthew 5:7} - Blessed are the merciful, for they shall receive mercy.

The merciful shall receive mercy.

\textbf{Revelation of John 22:14-15} - Blessed are those who wash their robes, so that they may have the right to the tree of life and that they may enter the city by the gates. Outside are the \textbf{dogs} and sorcerers and the sexually immoral and murderers and idolaters, and everyone who loves and practices falsehood. (ESV)

\textbf{Proverbs 26:11} - Like a dog that returns to his vomit is a fool who repeats \textbf{his folly}.

\textbf{II Peter 2:21-22} - For it would have been better for them never to have known the way of righteousness than after knowing it to turn back from the holy commandment delivered to them. What the true proverb says has happened to them: The \textbf{dog} returns to its own vomit, and the sow, after washing herself, returns to wallow in the mire.

Here's the grace. I choose to interpret this in this way, and I claim it because I claim to be a servant of Jesus:

\textbf{Mark 7:27-29} - And he said to her, Let the children be fed first, for it is not right to take the children's bread and throw it to the dogs. But she answered him, Yes, Lord; \textbf{yet even the dogs under the table eat the children's crumbs}. \uline{And he said to her, For this statement you may go your way; the demon has left your daughter}.

\textbf{Isaiah 56:11} - The \textbf{dogs} have a mighty appetite; they never have enough. But they are shepherds who have no understanding; \uline{they have all turned to their own way, each to his own gain, one and all}.

\textbf{Philippians 3:2-3} - Look out for the \uline{dogs, look out for the evildoers}, look out for those who mutilate the flesh. For we are the real circumcision, who worship by the Spirit of God and glory in Christ Jesus and put no confidence in the flesh—

\subsubsection{God's original design is male and female union and also the law reflects the spiritual reality}
\label{sec:org60b241d}

I saw a dark spot around my rib when I was born-again.
I think this indicates I am male, and there's a female kingdom partner out there for me!

\url{https://web.archive.org/web/20220402091720/https://mullikine.github.io/posts/astral-projection/}

Being born-again of the Spirit gave me insight, and I believed God was real.

\textbf{Proverbs 9:10} - The fear of the Lord is the beginning of wisdom, and the knowledge of the Holy One is insight.

\subsubsection{The truth is God made them male and female, but handed erroneous, rebellious people over to their lust in impurity}
\label{sec:org3c8d116}
\textbf{Genesis 1:27} - So God created man in his own image, in the image of God he created him; male and female he created them.

\textbf{Genesis 5:2} - Male and female he created them, and he blessed them and named them Man when they were created.

\textbf{Genesis 6:19} - And of every living thing of all flesh, you shall bring two of every sort into the ark to keep them alive with you. They shall be male and female.

\textbf{Joel 2:27-29} - You shall know that I am in the midst of Israel, and that I am the Lord your God and there is none else. And my people shall never again be put to shame. And it shall come to pass afterward, that I will pour out my Spirit on all flesh; your sons and your daughters shall prophesy, your old men shall dream dreams, and your young men shall see visions. Even on the male and female servants in those days I will pour out my Spirit. (ESV)

\textbf{Matthew 19:4} - He answered, Have you not read that he who created them from the beginning made them male and female, (ESV)

\textbf{Mark 10:6} - But from the beginning of creation, God made them male and female. (ESV)

\textbf{Romans 1:24-32} - Therefore God gave them up in the lusts of their hearts to impurity, to the dishonoring of their bodies among themselves, because they exchanged the truth about God for a lie and worshiped and served the creature rather than the Creator, who is blessed forever! Amen. For this reason God gave them up to dishonorable passions. For their women exchanged natural relations for those that are contrary to nature; and the men likewise gave up natural relations with women and were consumed with passion for one another, men committing shameless acts with men and receiving in themselves the due penalty for their error. And since they did not see fit to acknowledge God, God gave them up to a debased mind to do what ought not to be done. They were filled with all manner of unrighteousness, evil, covetousness, malice. They are full of envy, murder, strife, deceit, maliciousness. They are gossips, slanderers, haters of God, insolent, haughty, boastful, inventors of evil, disobedient to parents, foolish, faithless, heartless, ruthless. Though they know God's decree that those who practice such things deserve to die, they not only do them but give approval to those who practice them. (ESV)

\subsubsection{We have to walk the straight and narrow to reign with Christ}
\label{sec:org9fd44f9}
\textbf{II Timothy 2:11-13} - The saying is trustworthy, for: If we have died with him, we will also live with him; \uline{if we endure, we will also reign with him}; if we deny him, he also will deny us; if we are faithless, he remains faithful— for he cannot deny himself.

\section{Employment}
\label{sec:org54efbfe}
\subsection{Kingdom work \textbf{is} work}
\label{sec:org506c53a}
Jesus wants more kingdom labourers:

\textbf{Matthew 9:37-38} - Then he said to his disciples, The harvest is plentiful, but the laborers are few; therefore pray earnestly to the Lord of the harvest to send out laborers into his harvest. (ESV)

The Apostles prioritised themselves to focus on prayer and devotion to the ministry of the word over serving at tables, because it was more important for them to focus on the ministry of the word:

\textbf{Acts 6:2-4} - Then the twelve called the multitude of the disciples unto them, and said, It is not reason that we should leave the word of God, and serve tables. Wherefore, brethren, look ye out among you seven men of honest report, full of the Holy Ghost and wisdom, whom we may appoint over this business. But we will give ourselves continually to prayer, and to the ministry of the word.

Also Paul says he does indeed have the right to be a burden on others (because, I assume, they have given themselves to prayer and the ministry of the word), but rather he wants to be a good example for others to follow on how a Christian should work.

\textbf{2 Thessalonians 3:8-10} - nor did we eat anyone's bread without paying for it, but with toil and labor we worked night and day, that we might not be a burden to any of you. It was not because we do not have that right, but to give you in ourselves an example to imitate. For even when we were with you, we would give you this command: If anyone is not willing to work, let him not eat. (ESV)

\section{Hearing the gospel progresses to abiding in Christ}
\label{sec:org483efc0}
\textbf{I John 2:24} - Let what you heard from the beginning abide in you. If what you heard from the beginning abides in you, then you too will abide in the Son and in the Father.

\uline{If} what you heard from the beginning abides in you\ldots{}

\begin{itemize}
\item hearing the Gospel of Jesus Christ
\item Then there's letting the word abide in you
\begin{itemize}
\item Which leads to the following
\end{itemize}
\item Then there's abiding in Jesus - believing and confessing Jesus
\begin{itemize}
\item Which leads to the following
\end{itemize}
\item Then there's forever abiding in Jesus
\begin{itemize}
\item Not able to fall away
\end{itemize}
\end{itemize}

The word has to remain.

\textbf{Mark 4:3-20} - Listen! A sower went out to sow.  And as he sowed, some seed fell along the path, and the birds came and devoured it.  Other seed fell on rocky ground, where it did not have much soil, and immediately it sprang up, since it had no depth of soil.  And when the sun rose it was scorched, and since it had no root, it withered away.  Other seed fell among thorns, and the thorns grew up and choked it, and it yielded no grain.  And other seeds fell into good soil and produced grain, growing up and increasing and yielding thirtyfold and sixtyfold and a hundredfold.  And he said, He who has ears to hear, let him hear.  And when he was alone, those around him with the twelve asked him about the parables.  And he said to them, To you has been given the secret of the kingdom of God, but for those outside everything is in parables, so that they may indeed see but not perceive, and may indeed hear but not understand, lest they should turn and be forgiven.  And he said to them, Do you not understand this parable? How then will you understand all the parables?  The sower sows the word.  And these are the ones along the path, where the word is sown: when they hear, Satan immediately comes and takes away the word that is sown in them.  And these are the ones sown on rocky ground: the ones who, when they hear the word, immediately receive it with joy.  And they have no root in themselves, but endure for a while; then, when tribulation or persecution arises on account of the word, immediately they fall away.  And others are the ones sown among thorns. They are those who hear the word, but the cares of the world and the deceitfulness of riches and the desires for other things enter in and choke the word, and it proves unfruitful.  But those that were sown on the \textbf{good soil} are \textbf{the ones who hear the word and accept it and bear fruit}, thirtyfold and sixtyfold and a hundredfold.

Good soil:
\begin{itemize}
\item Hears the word
\item Accepts the word
\item Bears fruit
\end{itemize}

The word is spoken to us and we must receive it and nurture it and produce fruit:

\textbf{John 15:3-4} - Already you are clean because of the word that I have spoken to you. Abide in me, and I in you. As the branch cannot bear fruit by itself, unless it abides in the vine, neither can you, unless you abide in me.

To bear fruit involves sacrificing this life for the advancement of the kingdom:

\textbf{John 12:24-25} - Truly, truly, I say to you, unless a grain of wheat falls into the earth and dies, it remains alone; but if it dies, it bears much fruit. Whoever loves his life loses it, and whoever hates his life in this world will keep it for eternal life.

If your fruit abides then whatever you ask the Father in Jesus' name, He may give you:

\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that whatever you ask the Father in my name, he may give it to you.

God takes away fruitless branches:

\textbf{John 15:2} - Every branch of mine that does not bear fruit he takes away, and every branch that does bear fruit he prunes, that it may bear more fruit.

We must be fruitful branches, abiding in Jesus:

\textbf{John 15:5} - I am the vine; you are the branches. Whoever abides in me and I in him, he it is that bears much fruit, for apart from me you can do nothing.

\section{Abiding in Christ}
\label{sec:orgb3f3d11}
\textbf{John 3:36} - He who believes (G4100 pisteuo) in the Son (G5207 huios) has (G2192 echo) eternal (G166 aionios) life (G2222 zoe); but he who does not obey (G544 apeitheo) the Son (G5207 huios) will not see (G3708 horao) life (G2222 zoe), but the wrath (G3709 orge) of God (G2316 theos) abides (G3306 meno) on him.”

Abiding in Christ, one abides in God.

\textbf{1 John 4:15} - Whoever confesses that Jesus is the Son of God, God abides in him, and he in God. (ESV)

Thomas going from unbelief to belief.

\textbf{John 20:27-28} - Then he said to Thomas, Put your finger here, and see my hands; and put out your hand, and place it in my side. Do not disbelieve, but believe. Thomas answered him, My Lord and my God!

Jesus helped Thomas believe by giving him a commandment to do. It's implied that Thomas obeyed and arrived at belief.

\textbf{John 20:29-31} - Jesus said to him, Have you believed because you have seen me? Blessed are those who have not seen and yet have believed.  Now Jesus did many other signs in the presence of the disciples, which are not written in this book; but these are written so that you may believe that Jesus is the Christ, the Son of God, and that by believing you may have life in his name.

There's abiding in Christ, and then there is ABIDING FOREVER in Christ, and forever in God.

\textbf{I John 2:17} - And the world is passing away along with its desires, but \textbf{whoever does the will of God abides forever}.

\textbf{Ephesians 6:6} - not by the way of eye-service, as people-pleasers, but as servants of Christ, doing the will of God from the heart,

\textbf{I John 2:6} - the one who says (G3004 lego) he abides (G3306 meno) in Him ought (G3784 opheilo) himself (G846 autos) to walk (G4043 peripateo) in the same (G3779 houto) manner (G3779 houto) as He walked (G4043 peripateo).

I believe that to abide forever in Christ, one must produce good fruit.

\textbf{Matthew 3:8-10} - Bear fruit in keeping with repentance.  And do not presume to say to yourselves, We have Abraham as our father, for I tell you, God is able from these stones to raise up children for Abraham.  Even now the axe is laid to the root of the trees. Every tree therefore that does not bear good fruit is cut down and thrown into the fire.

I believe that producing good fruit is necessary for being saved:
\begin{itemize}
\item a heart that is turning away from sin
\item believing the Gospel and obeying Jesus
\end{itemize}

\subsection{When it says 'hate' here, it means 'unfollow'}
\label{sec:orgc438f22}
\textbf{Luke 14:26} - If anyone comes to me and does not hate his own father and mother and wife and children and brothers and sisters, yes, and even his own life, he cannot be my disciple.

\textbf{Luke 14:27} - Whoever does not bear his own cross and come after me cannot be my disciple.

\textbf{Luke 14:33} - So therefore, any one of you who does not renounce all that he has cannot be my disciple.

\subsection{The slave to sin doesn't abide forever. Repentance from sin is essential for eternal life}
\label{sec:orgcbb4df4}
\textbf{John 8:34-35} - Jesus answered them, Truly, truly, I say to you, everyone who commits sin is a slave to sin. The slave does not remain in the house forever; the son remains forever.

Like begets like:
\begin{itemize}
\item Like Father,
\item like Son (Jesus).
\item Like disciple of Jesus / adopted son
\end{itemize}

\textbf{Matthew 5:44-45} - But I say to you, love your enemies and pray for those who persecute you, so that you may be sons of your Father who is in heaven; for He causes His sun to rise on the evil and the good, and sends rain on the righteous and the unrighteous.

\textbf{Matthew 5:48} - Therefore you are to be perfect, as your heavenly Father is perfect.

\textbf{I Peter 1:16} - because it is written, “You shall be holy, for I am holy.”

\textbf{Luke 10:6} - And if a son of peace is there, your peace will rest upon him. But if not, it will return to you.

\subsection{Having the Spirit given to us and keeping Jesus' commandments}
\label{sec:orgd727ca3}
\textbf{I John 3:24} - Whoever keeps his commandments abides in him, and he in them. And by this we know that he abides in us, by the Spirit whom he has given us.

\subsection{Eternal life is forever abiding}
\label{sec:org97839d1}
A person must do the will of God for that.

The will of God is that we have faith in God and faith in Jesus.
The will of God is that we believe in Him whom He has sent - believing in Jesus.
The will of God is that we are bondservants of Christ from the heart.
The will of God is that we repent from sin.
The will of God is that we do good.

\textbf{II John 1:2} - because of the truth that abides in us and will be with us forever:

\textbf{II John 1:9} - Everyone who goes on ahead and does not abide in the teaching of Christ, does not have God. Whoever abides in the teaching has both the Father and the Son.

\textbf{Mark 3:35} - Whoever does the will of God, he is my brother and sister and mother.

\textbf{I Corinthians 5:11} - But now I am writing to you \uline{not to associate with anyone who bears the name of brother if he is guilty of sexual immorality or greed, or is an idolater, reviler, drunkard, or swindler—not even to eat with such a one}.

\textbf{Ephesians 6:6} - not by the way of eye-service, as people-pleasers, but as servants of Christ, doing the will of God from the heart,

\textbf{I Thessalonians 4:3} - For this is the will of God, your sanctification: that you abstain from sexual immorality;

\textbf{I Peter 2:15} - For this is the will of God, that by doing good you should put to silence the ignorance of foolish people.

\textbf{I John 2:17} - And the world is passing away along with its desires, but whoever does the will of God abides forever. (ESV)

\textbf{I John 2:14-17} - I have written to you, fathers, because you know Him who has been from the beginning. I have written to you, young men, because you are strong, and the word of God abides in you, and you have overcome the evil one.  Do not love the world nor the things in the world. If anyone loves the world, the love of the Father is not in him.  For all that is in the world, the lust of the flesh and the lust of the eyes and the boastful pride of life, is not from the Father, but is from the world.  The world is passing away, and also its lusts; but the one who does the will of God lives forever.

\textbf{I John 2:17} - The world (G2889 kosmos) is passing (G3855 parago) away (G3855 parago), and also its lusts (G1939 epithumia); but the one who does (G4160 poieo) the will (G2307 thelema) of God (G2316 theos) \textbf{lives (G3306 meno)} forever (G165 aion).

\begin{verbatim}
1  :  3306  meno  men'-o
2  
3   a primary verb; to stay (in a given place, state, relation or
4   expectancy):--abide, continue, dwell, endure, be present, remain,
5   stand, tarry (for), X thine own.
\end{verbatim}

\subsection{Whoever truly believes / has faith in Jesus has eternal life}
\label{sec:org590848b}
\textbf{John 3:33} - Whoever receives his testimony sets his seal to this, that God is true.

\textbf{John 4:13-14} - Jesus said to her, Everyone who drinks of this water will be thirsty again, but whoever drinks of the water that I will give him will never be thirsty forever. The water that I will give him will become in him \textbf{a spring of water welling up to eternal life.}

A spring which \textbf{wells up} to eternal life.

So a person believed and they embark on a relationship with God, leading to eternal life.
It wells-up to eternal life. So if they receive the living water then they receive eternal life.
When was eternal life received? When the person first truly believed, I guess.

Accomplishing the will of God the Father is \textbf{food}.

\textbf{John 4:34-38} - Jesus said to them, My food is to do the will of him who sent me and to accomplish his work. Do you not say, There are yet four months, then comes the harvest? Look, I tell you, lift up your eyes, and see that the fields are white for harvest. Already the one who reaps is receiving wages and gathering fruit for eternal life, so that sower and reaper may rejoice together. For here the saying holds true, One sows and another reaps. I sent you to reap that for which you did not labor. Others have labored, and you have entered into their labor.

Discern the will of God.

\textbf{Romans 12:2} Do not be conformed to this world, but be transformed by the renewal of your mind, that by testing you may discern what is the will of God, what is good and acceptable and perfect.

Yes, believing in Jesus is obeying the gospel - but there is so much more to the gospel! Doing the will of God.

\textbf{Romans 2:7-8} - to those who by patience in well-doing seek for glory and honor and immortality, he will give eternal life; but for those who are self-seeking and do not obey the truth, but obey unrighteousness, there will be wrath and fury.

\subsubsection{Every human being who does evil will receive tribulation and distress. God is fair.}
\label{sec:orgfde10ff}
\textbf{Romans 2:9-11} - There will be tribulation and distress for every human being who does evil, the Jew first and also the Greek, but glory and honor and peace for everyone who does good, the Jew first and also the Greek. For God shows no partiality.

\subsubsection{Human beings were totally at the mercy of God. We needed Jesus to come. We still need Jesus}
\label{sec:org0f1c162}
\textbf{Romans 3:10-13} - as it is written: None is righteous, no, not one; no one understands; no one seeks for God.  All have turned aside; together they have become worthless; no one does good, not even one.  Their throat is an open grave; they use their tongues to deceive. The venom of asps is under their lips.

\textbf{Psalms 53:1-3} -  The fool says in his heart, There is no God.  They are corrupt, doing abominable iniquity; there is none who does good.  To the choirmaster: according to Mahalath.  A Maskil of David.  God looks down from heaven on the children of man to see if there are any who understand, who seek after God.  They have all fallen away; together they have become corrupt; there is none who does good, not even one.  (ESV)

\subsubsection{Atonement and sanctification, and eternal life in Jesus - righteousness apart from the works of the law}
\label{sec:orgfbfc04c}
\textbf{Romans 3:20} - For by works of the law no human being will be justified in his sight, since through the law comes knowledge of sin.  But now the righteousness of God has been manifested apart from the law, although the Law and the Prophets bear witness to it— the righteousness of God through faith in Jesus Christ for all who believe. For there is no distinction: for all have sinned and fall short of the glory of God, and are justified by his grace as a gift, through the redemption that is in Christ Jesus, whom God put forward as a propitiation by his blood, to be received by faith. This was to show God's righteousness, because in his divine forbearance he had passed over former sins.  It was to show his righteousness at the present time, so that he might be just and the justifier of the one who has faith in Jesus.

If followed flawlessly then the law justifies.

Jesus both followed the law flawlessly and fulfilled the law prophetically, and was convicted by sinners. Jesus is our atonement.

\textbf{Hebrews 9:26} - for then he would have had to suffer repeatedly since the foundation of the world.  But as it is, he has appeared once for all at the end of the ages to put away sin by the sacrifice of himself.  (ESV)

\textbf{1 Peter 3:18} - For Christ also suffered once for sins, the righteous for the unrighteous, that he might bring us to God, being put to death in the flesh but made alive in the spirit,  (ESV)

\textbf{Leviticus 17:11} - For the life of the flesh is in the blood, and I have given it for you on the altar to make atonement for your souls, for it is the blood that makes atonement by the life.  (ESV)

\textbf{Hebrews 9:22} - Indeed, under the law almost everything is purified with blood, and without the shedding of blood there is no forgiveness of sins.  (ESV)

\textbf{John 1:29} - The next day he saw Jesus coming toward him, and said, Behold, the Lamb of God, who takes away the sin of the world!  (ESV)

\textbf{1 John 2:2} - He is the propitiation for our sins, and not for ours only but also for the sins of the whole world.  (ESV)

In Jesus, there is no sin.

\textbf{1 John 3:5} - You know that he appeared to take away sins, and in him there is no sin.  (ESV)

\textbf{Mark 10:45} -  For even the Son of Man came not to be served but to serve, and to give his life as a ransom for many.  (ESV)

\textbf{Isaiah 53:5} -  But he was wounded for our transgressions; he was crushed for our iniquities; upon him was the chastisement that brought us peace, and with his stripes we are healed.  (ESV)

Propitiation by Jesus' blood is to be received by faith.

\textbf{Romans 3:25} -  whom God put forward as a propitiation by his blood, to be received by faith.  This was to show God's righteousness, because in his divine forbearance he had passed over former sins.  (ESV)

\textbf{1 Corinthians 15:3} -  For I delivered to you as of first importance what I also received: that Christ died for our sins in accordance with the Scriptures,  (ESV)

God has enabled us to die to sin and live to righteousness.

\textbf{1 Peter 2:24} -  He himself bore our sins in his body on the tree, that we might die to sin and live to righteousness.  By his wounds you have been healed.  (ESV)

We are cleaned up by having faith in the truth. Having faith is a continuing process.

We must \textbf{both} believe the truth and be sanctified, \textbf{and} stop sinning:

\textbf{II Thessalonians 2:11-14} - Therefore God sends them a strong delusion, so that they may believe what is false, in order that all may be condemned who did not believe the truth but had pleasure in unrighteousness. But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through \textbf{sanctification by the Spirit} and \textbf{belief in the truth}. To this he called you through our gospel, so that you may obtain the glory of our Lord Jesus Christ.

\subsection{Abiding in Christ through His name}
\label{sec:org46cf821}
\begin{itemize}
\item Maintaining actual belief in Jesus is the basic requirement which prevents you from being cut off, because the life is in His name.
\begin{itemize}
\item Believing on His name
\begin{itemize}
\item Trusts in Jesus
\begin{itemize}
\item He is your Saviour in reality - entrusted yourself to Him
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

Believe that \uline{Jesus is the Christ, the Son of God}. Believe in, believe with. Trust in.

Having life in Jesus Christ's name by believing and trusting in Jesus Christ - Absolutely.
And with obedience to Jesus, He has promised eternal life.

\textbf{Matthew 16:16} - Simon Peter replied, You are the Christ, the Son of the living God.

\textbf{John 20:31} - but these are written so that you may believe that Jesus is the Christ, the Son of God, and that by believing you may have life in his name. (ESV)

\textbf{Exodus 23:21} - Pay attention to him, and listen to his voice. Don't provoke him, for he will not pardon your disobedience, for my name is in him.

God's name was \textbf{in} the angel:

\textbf{Exodus 23:20-22} - Behold, I send an angel before you to guard you on the way and to bring you to the place that I have prepared. Pay careful attention to him and obey his voice; do not rebel against him, for he will not pardon your transgression, for my name is in him. But if you \textbf{carefully obey his voice and do all that I say}, then I will be an enemy to your enemies and an adversary to your adversaries.

Believing is just the starting point. This is honestly just the starting point. Obedience is \textbf{expected}. Also, Jesus is forgiving, unlike the angel.

Continuing to trust in Jesus as the Messiah, your Saviour, and the Only-begotten Son of God through patient endurance is enough to get saved, I think, but it's not enough to be counted a 'disciple' of Jesus.

And it's 'saved' but 'being saved' at the same time.

One wants to progress from 'believing that' to having Jesus abide inside them.

I think that rejects His commandments but claiming to believe in Jesus Christ as the Son of God is an extremely precarious, and tentative position to be in,
and may indicate that the person doesn't \textbf{really} believe.

And if a person doesn't believe in reality, then that person probably isn't saved - so they are only lying to themself that they are saved.

\textbf{However}, if a person trusts him who justifies the ungodly, his faith is counted as righteousness.

\textbf{Romans 4:5} - And to the one who does not work but trusts him who justifies the ungodly, his faith is counted as righteousness,

This qualifies:

\textbf{Luke 18:13} - But the tax collector, standing far off, would not even lift up his eyes to heaven, but beat his breast, saying, God, be merciful to me, a sinner! (ESV)

\subsection{Jesus abiding in \textbf{you} / \textbf{me}}
\label{sec:org3d7c64c}
It quickly progresses to obeying Jesus, receiving the Spirit.

\textbf{I John 3:24} - Whoever keeps his commandments abides in him, \textbf{and he in them}. And by this we know that he abides in us, by the Spirit whom he has given us.

\subsection{Loving God and loving Jesus and loving others and abiding in His love}
\label{sec:org8bc5c51}
\textbf{I John 5:2} - By this we know that we love the children of God, when we love God and obey his commandments.

\textbf{I John 5:3} - For this is the love of God, that we keep his commandments. And his commandments are not burdensome.

\textbf{II John 1:6} - And this is love, that we walk according to his commandments; this is the commandment, just as you have heard from the beginning, so that you should walk in it.

\subsection{Saint - an imitator of Jesus - keeps the commandments of God AND has faith in Jesus}
\label{sec:orgbeaf269}
\textbf{John 15:10} - If you keep my commandments, you will abide in my love, just as I have kept my Father's commandments and abide in his love.

\textbf{Ephesians 1:1} - Paul, an apostle of Christ Jesus by the will of God, To the saints who are in Ephesus, and are faithful in Christ Jesus:

\textbf{Revelation of John 12:17} - Then the dragon became furious with the woman and went off to make war on the rest of her offspring, on those who keep the commandments of God and hold to the testimony of Jesus. And he stood on the sand of the sea.

\textbf{Revelation of John 14:12} - Here is a call for the endurance of the saints, those who keep the commandments of God and their faith in Jesus.

\textbf{Psalms 97:10} - O you who love the Lord, hate evil! He preserves the lives of his saints; he delivers them from the hand of the wicked.

\subsection{Followers of Jesus - the saints (people who keep God's commandments) judge the world}
\label{sec:orge1cb6d1}
\textbf{Matthew 19:16-30} - And behold, a man came up to him, saying, Teacher, what good deed must I do to have eternal life? And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me. When the young man heard this he went away sorrowful, for he had great possessions. And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. When the disciples heard this, they were greatly astonished, saying, Who then can be saved? But Jesus looked at them and said, With man this is impossible, but with God all things are possible. Then Peter said in reply, See, we have left everything and followed you. What then will we have? Jesus said to them, Truly, I say to you, in the new world, when the Son of Man will sit on his glorious throne, you who have followed me will also sit on twelve thrones, judging the twelve tribes of Israel. And everyone who has left houses or brothers or sisters or father or mother or children or lands, for my name's sake, will receive a hundredfold and will inherit eternal life. But many who are first will be last, and the last first.

\textbf{I Corinthians 6:2} - Or do you not know that the saints will judge the world? And if the world is to be judged by you, are you incompetent to try trivial cases?

\subsection{Saints inherit the Kingdom with Jesus}
\label{sec:org3136092}
\textbf{Daniel 7:18} - But the saints of the Most High shall receive the kingdom and possess the kingdom forever, forever and ever. (ESV)

\textbf{Revelation 2:26-28} - The one who conquers and who keeps my works until the end, to him I will give authority over the nations, and he will rule them with a rod of iron, as when earthen pots are broken in pieces, even as I myself have received authority from my Father. And I will give him the morning star. (ESV)

\subsection{Following Jesus}
\label{sec:orgb198c17}
\textbf{Luke 6:46-49} - Why do you call me Lord, Lord, and not \textbf{do what I tell you}? Everyone who comes to me and hears my words and \textbf{does them}, I will show you what he is like: he is like a man building a house, who dug deep and laid the foundation on the rock. And when a flood arose, the stream broke against that house and could not shake it, because it had been well built. But the one who hears and does not do them is like a man who built a house on the ground without a foundation. When the stream broke against it, immediately it fell, and the ruin of that house was great. (ESV)

OBEDIENCE!

\textbf{Matthew 6:24} - No one can serve two masters, for either he will hate the one and love the other, or he will be devoted to the one and despise the other. You cannot serve God and money. (ESV)

You cannot follow money. You have to drop money in order to follow Jesus!

OBEDIENCE!

\textbf{Hebrews 5:8-10} - Although he was a son, he learned obedience through what he suffered. And being made perfect, he became the source of \textbf{eternal salvation to all who obey him}, being designated by God a high priest after the order of Melchizedek.

\subsection{Make friends with charity while money hasn't yet failed}
\label{sec:orgbba760c}
Money is temporary. While it's in your hands, make friends with it, by giving in charity to those in need.

Money will fail - bitcoin will fail, ethereum will fail, and when it fails people will see you as a friend.

\textbf{Luke 16:1-8} - He also said to the disciples, There was a rich man who had a manager, and charges were brought to him that this man was wasting his possessions. And he called him and said to him, What is this that I hear about you? Turn in the account of your management, for you can no longer be manager. And the manager said to himself, What shall I do, since my master is taking the management away from me? I am not strong enough to dig, and I am ashamed to beg. I have decided what to do, so that when I am removed from management, people may receive me into their houses. So, summoning his master's debtors one by one, he said to the first, How much do you owe my master? He said, A hundred measures of oil. He said to him, Take your bill, and sit down quickly and write fifty. Then he said to another, And how much do you owe? He said, A hundred measures of wheat. He said to him, Take your bill, and write eighty. The master commended the dishonest manager for his shrewdness. For the sons of this world are more shrewd in dealing with their own generation than the sons of light. (ESV)

\textbf{Luke 16:8-9} - And I tell you, make friends for yourselves by means of unrighteous wealth, so that when it fails they may receive you into the eternal dwellings. (ESV)

\subsection{In this world God can see if we are to be trusted with true heavenly wealth by seeing how we used our money}
\label{sec:org0107363}
\textbf{Luke 16:11-12} - If then you have not been faithful in the unrighteous wealth, who will entrust to you the true riches? And if you have not been faithful in that which is another's, who will give you that which is your own?

\subsection{Be humble in this world and serve others of humble circumstances while in this world}
\label{sec:orge972b17}
\textbf{James 1:9-11} - But the brother of humble circumstances is to glory in his high position; and the rich man is to glory in his humiliation, because like flowering grass he will pass away. For the sun rises with a scorching wind and withers the grass; and its flower falls off and the beauty of its appearance is destroyed; so too the rich man in the midst of his pursuits will fade away. (NASB)

\textbf{Matthew 6:19-21} - Do not lay up for yourselves treasures on earth, where moth and rust destroy and where thieves break in and steal, but lay up for yourselves treasures in heaven, where neither moth nor rust destroys and where thieves do not break in and steal. For where your treasure is, there your heart will be also.

\textbf{John 12:25} - Whoever loves his life loses it, and whoever hates his life in this world will keep it for eternal life.

\textbf{John 12:26} - If anyone serves me, he must follow me; and where I am, there will my servant be also. If anyone serves me, the Father will honor him. (ESV)

\textbf{Matthew 25:35-40} - For I was hungry and you gave me food, I was thirsty and you gave me drink, I was a stranger and you welcomed me, I was naked and you clothed me, I was sick and you visited me, I was in prison and you came to me. Then the righteous will answer him, saying, Lord, when did we see you hungry and feed you, or thirsty and give you drink? And when did we see you a stranger and welcome you, or naked and clothe you? And when did we see you sick or in prison and visit you? And the King will answer them, Truly, I say to you, as you did it to one of the least of these my brothers, you did it to me.

\subsection{Jesus' friends are those who do what Jesus says}
\label{sec:org7b53d41}
\textbf{John 15:14-15} - You are my friends if you do what I command you. No longer do I call you servants, for the servant does not know what his master is doing; but I have called you friends, for all that I have heard from my Father I have made known to you.

\subsection{Entering the kingdom of heaven}
\label{sec:org90ad8c8}
It's possible while here on earth:

\textbf{Luke 9:27} - But I tell you truly, there are some standing here who will not taste death until they see the kingdom of God.

Following the commandments properly from the heart is a good thing to do.

\textbf{I Kings 11:38} - And if you will listen to all that I command you, and will walk in my ways, and do what is right in my eyes by keeping my statutes and my commandments, as David my servant did, I will be with you and will build you a sure house, as I built for David, \textbf{and I will give Israel to you}.

Jesus has to be your Lord in reality, i.e. doing Father God's will.

\textbf{Matthew 7:21} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven. (ESV)

\textbf{1 Thessalonians 4:3} - For this is the will of God, your sanctification: that you abstain from sexual immorality; (ESV)

\textbf{I Peter 2:15} - For this is the will of God, that by doing good you should put to silence the ignorance of foolish people.

\textbf{Obey} the word:

\textbf{I Peter 2:8} - and A stone of stumbling, and a rock of offense. They stumble because they disobey the word, as they were destined to do.

Jesus is the cornerstone. We must believe in Christ Jesus and obey His words, and let his words abide in us and continue in them.

\subsection{Knowing Jesus}
\label{sec:org0e1bc2c}
To know Jesus and Father God, then you \textbf{must} follow His commandments.

\textbf{I John 2:3} - And by this we know that we have come to know him, if we keep his commandments.

\textbf{I John 2:4} - Whoever says I know him but does not keep his commandments is a liar, and the truth is not in him,

Getting to know Jesus will come to result in you too abiding in the Son and in the Father.

\textbf{I John 2:24} - Let what you heard from the beginning abide in you. If what you heard from the beginning abides in you, then you too will abide in the Son and in the Father.

\textbf{I John 3:24} - Whoever keeps his commandments abides in him, and he in them. And by this we know that he abides in us, by the Spirit whom he has given us.

My intuition says that walking as Jesus walked and obeying His commandments and believing in the truth produces in us an empathy for Jesus.

\begin{description}
\item[{empathy}] understanding and entering into another's feelings
\end{description}

We can know in part what Jesus experienced by walking in the truth as he walked.

However, I believe keeping Jesus' word and obeying Jesus also leads to communion with Him and with Father God in the Spirit:

\begin{description}
\item[{communion}] sharing thoughts and feelings
\end{description}

\textbf{John 14:22-23} - Judas (not Iscariot) said to him, Lord, how is it that you will manifest yourself to us, and not to the world? Jesus answered him, If anyone loves me, he will keep my word, and my Father will love him, and we will come to him and make our home with him.

\subsubsection{Anyone who doesn't abide will be thrown away like a branch and withers. Eventually they will be into the fire (Hell, I assume)}
\label{sec:org50ea165}
\textbf{John 15:6} - If anyone does not abide in me he is thrown away like a branch and withers; and the branches are gathered, thrown into the fire, and burned.

\subsection{His name: Jesus Christ, the Son of God}
\label{sec:orgf9f6cc0}
\textbf{Acts 3:16} - And his name-by faith in his name-has made this man strong whom you see and know, and the faith that is through Jesus has given the man this perfect health in the presence of you all.??

\textbf{Hebrews 1:1-4} -  Long ago, at many times and in many ways, God spoke to our fathers by the prophets, but in these last days he has spoken to us by his Son, whom he appointed the heir of all things, through whom also he created the world.  He is the radiance of the glory of God and the exact imprint of his nature, and he upholds the universe by the word of his power.  After making purification for sins, he sat down at the right hand of the Majesty on high, having become as much superior to angels as the name he has inherited is more excellent than theirs. (ESV)

\textbf{Philippians 2:9-11} - Therefore God has highly exalted him and bestowed on him the name that is above every name, so that at the name of Jesus every knee should bow, in heaven and on earth and under the earth, and every tongue confess that Jesus Christ is Lord, to the glory of God the Father. (ESV)

\textbf{John 17:11-12} -  And I am no longer in the world, but they are in the world, and I am coming to you.  Holy Father, keep them in your name, which you have given me, that they may be one, even as we are one.  While I was with them, I kept them in your name, which you have given me.  I have guarded them, and not one of them has been lost except the son of destruction, that the Scripture might be fulfilled. (ESV)

\subsection{Securely abiding in Jesus, abiding in Jesus Christ's love}
\label{sec:orga621c1a}
\begin{itemize}
\item Loving Jesus and abiding in His love involves keeping His commandments
\begin{itemize}
\item Love one another as He loved us - the same way, selflessly, forgivingly, mercifully, compassionately
\item Love God faithfully
\begin{itemize}
\item An indicator is that the world hates you
\end{itemize}
\end{itemize}
\item Keeping all of Jesus' words, keeping His commandments
\begin{itemize}
\item Ask whatever you wish
\end{itemize}
\item Bear fruit
\begin{itemize}
\item Forgiving others, loving others (charity, etc.)
\item Bringing others to Christ
\item Prove to be a disciple of Jesus
\end{itemize}
\end{itemize}

\subsection{The fruit (work) of disciples of Jesus then abides}
\label{sec:org7092434}
\textbf{John 15:2} - Every branch of mine that does not bear fruit he takes away, and every branch that does bear fruit he prunes, that it may bear more fruit.

\textbf{John 15:5} - I am the vine; you are the branches. Whoever abides in me and I in him, he it is that bears much fruit, for apart from me you can do nothing.

\textbf{John 15:8} - By this my Father is glorified, that you bear much fruit and so prove to be my disciples.

\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that whatever you ask the Father in my name, he may give it to you.

\subsection{Secure rewards and a guarantee of eternal life for Jesus' disciples}
\label{sec:orga338666}

\textbf{Matthew 19:29} - And everyone who has left houses or brothers or sisters or father or mother or children or lands, for my name's sake, will receive a hundredfold and will inherit eternal life. (ESV)

\textbf{Luke 14:26-28} If anyone comes to me and does not hate his own father and mother and wife and children and brothers and sisters, yes, and even his own life, he cannot be my disciple. Whoever does not bear his own cross and come after me cannot be my disciple. For which of you, desiring to build a tower, does not first sit down and count the cost, whether he has enough to complete it?

\textbf{John 12:25} - Whoever loves his life loses it, and whoever hates his life in this world will keep it for eternal life. (ESV)

\textbf{Matthew 6:19-21} - Do not lay up for yourselves treasures on earth, where moth and rust destroy and where thieves break in and steal, but lay up for yourselves treasures in heaven, where neither moth nor rust destroys and where thieves do not break in and steal. For where your treasure is, there your heart will be also. (ESV)

\subsubsection{Eternal life is receiving an eternal name, I think}
\label{sec:org888c978}
\textbf{Isaiah 56:5} - I will give in my house and within my walls a monument and a name better than sons and daughters; I will give them an everlasting name that shall not be cut off. (ESV)

Receiving an eternal name.

Becoming a part of the Truth.
Full union with God.

\subsection{The work of God, believing in Jesus}
\label{sec:org236a904}
\textbf{John 6:29-40} - Jesus answered them, This is the work of God, that you believe in him whom he has sent. So they said to him, Then what sign do you do, that we may see and believe you? What work do you perform? Our fathers ate the manna in the wilderness; as it is written, He gave them bread from heaven to eat. Jesus then said to them, Truly, truly, I say to you, it was not Moses who gave you the bread from heaven, but my Father gives you the true bread from heaven. For the bread of God is he who comes down from heaven and gives life to the world. They said to him, Sir, give us this bread always. Jesus said to them, I am the bread of life; whoever comes to me shall not hunger, and whoever believes in me shall never thirst. But I said to you that you have seen me and yet do not believe. All that the Father gives me will come to me, and whoever comes to me I will never cast out. For I have come down from heaven, not to do my own will but the will of him who sent me. And this is the will of him who sent me, that I should lose nothing of all that he has given me, but raise it up on the last day. For this is the will of my Father, that everyone who looks on the Son and believes in him should have eternal life, and I will raise him up on the last day.

Jesus doesn't cast people out.

All that the Father gives me will come to me, and whoever comes to me I will
never cast out.

I think that salvation is a totally free gift and the baseline salvation is trusting in Jesus, because of His
finished work done on the cross. But the people that oppose obeying the full gospel of Jesus saying that works oppose grace and very deluded.

But salvation is a gift and God is sovereign to save.
That's why it's grace.
Saved by grace through faith.

I think a person needs \textbf{some} faith to be saved, and faith works.

\textbf{Ephesians 2:8} - For by grace you have been saved through faith. And this is not your own doing; it is the gift of God, (ESV)

\subsection{God the Father can graft people in and out of Christ}
\label{sec:org0f7af1e}
A person would have to reject Jesus to be grafted out, I think.

So most importantly, believe in Jesus, and that he has paid the price for your sin with His blood, and continue in relationship with Jesus.

\textbf{Hebrews 3:12} - Take care, brothers, lest there be in any of you an evil, unbelieving heart, leading you to fall away from the living God.

\textbf{Romans 11:23} - And even they, if they do not continue in their unbelief, will be grafted in, for God has the power to graft them in again.

The relationship is essential!
So take stopping sin seriously, and keep Jesus' words and His commandments, and also bearing fruit for Jesus.

\textbf{Revelation of John 3:2-3} - Wake up, and strengthen what remains and is about to die, for I have not found your works complete in the sight of my God. So remember what you have received and heard; and keep it, and repent. Therefore if you do not wake up, I will come like a thief, and you will not know at what hour I will come to you.

\textbf{John 15:1-14} - I am the true vine, and my Father is the vinedresser. Every branch of mine that does not bear fruit he takes away, and every branch that does bear fruit he prunes, that it may bear more fruit. Already you are clean because of the word that I have spoken to you. Abide in me, and I in you. As the branch cannot bear fruit by itself, unless it abides in the vine, neither can you, unless you abide in me. I am the vine; you are the branches. Whoever abides in me and I in him, he it is that bears much fruit, for apart from me you can do nothing. \textbf{If anyone does not abide in me he is thrown away like a branch and withers; and the branches are gathered, thrown into the fire, and burned}. If you abide in me, and my words abide in you, ask whatever you wish, and it will be done for you. By this my Father is glorified, that you bear much fruit and so prove to be my disciples. As the Father has loved me, so have I loved you. Abide in my love. If you keep my commandments, you will abide in my love, just as I have kept my Father's commandments and abide in his love. These things I have spoken to you, that my joy may be in you, and that your joy may be full. This is my commandment, that you love one another as I have loved you. Greater love has no one than this, that someone lays down his life for his friends. You are my friends if you do what I command you.

\textbf{Romans 11:15-32} - For if their rejection means the reconciliation of the world, what will their acceptance mean but life from the dead? If the dough offered as firstfruits is holy, so is the whole lump, and if the root is holy, so are the branches. But if some of the branches were broken off, and you, although a wild olive shoot, were grafted in among the others and now share in the nourishing root of the olive tree, do not be arrogant toward the branches. If you are, remember it is not you who support the root, but the root that supports you. Then you will say, Branches were broken off so that I might be grafted in. That is true. They were broken off because of their unbelief, but you stand fast through faith. So do not become proud, but stand in awe. For if God did not spare the natural branches, neither will he spare you. Note then the kindness and the severity of God: severity toward those who have fallen, but God's kindness to you, provided you continue in his kindness. Otherwise you too will be cut off. And even they, if they do not continue in their unbelief, will be grafted in, for God has the power to graft them in again. For if you were cut from what is by nature a wild olive tree, and grafted, contrary to nature, into a cultivated olive tree, how much more will these, the natural branches, be grafted back into their own olive tree. Lest you be wise in your own conceits, I want you to understand this mystery, brothers: a partial hardening has come upon Israel, until the fullness of the Gentiles has come in. And in this way all Israel will be saved, as it is written, The Deliverer will come from Zion, he will banish ungodliness from Jacob; and this will be my covenant with them when I take away their sins. As regards the gospel, they are enemies of God for your sake. But as regards election, they are beloved for the sake of their forefathers. For the gifts and the calling of God are irrevocable. Just as you were at one time disobedient to God but now have received mercy because of their disobedience, so they too have now been disobedient in order that by the mercy shown to you they also may now receive mercy. For God has consigned all to disobedience, that he may have mercy on all.

\textbf{Matthew 12:33-37} - Either make the tree good and its fruit good, or make the tree bad and its fruit bad, for the tree is known by its fruit. You brood of vipers! How can you speak good, when you are evil? For out of the abundance of the heart the mouth speaks. The good person out of his good treasure brings forth good, and the evil person out of his evil treasure brings forth evil. I tell you, on the day of judgment people will give account for every careless word they speak, for by your words you will be justified, and by your words you will be condemned. (ESV)

Rebellion = disobedience.

\textbf{1 Samuel 15:23} - For rebellion is as the sin of divination, and presumption is as iniquity and idolatry. Because you have rejected the word of the LORD, he has also rejected you from being king. (ESV)

\textbf{Ephesians 5:6} - Let no one deceive you with empty words, for because of these things the wrath of God comes upon the sons of disobedience. (ESV)

\subsection{The law of Christ}
\label{sec:orgd8b3d98}
We are still \emph{under} a 'law of faith', but we are not \textbf{under} the Mosaic law.

We are under the law of Christ which is a law of faith.

But the Mosaic law still exists.

\textbf{I Corinthians 9:21} - To those outside the law I became as one outside the law (not being outside the law of God but under the law of Christ) that I might win those outside the law.

\textbf{Galatians 6:2} - Bear one another's burdens, and so fulfill the law of Christ.

\textbf{I John 3:4-11} - Everyone who makes a practice of sinning also practices lawlessness; sin is lawlessness. You know that he appeared to take away sins, and in him there is no sin. No one who abides in him keeps on sinning; no one who keeps on sinning has either seen him or known him. Little children, let no one deceive you. Whoever practices righteousness is righteous, as he is righteous. Whoever makes a practice of sinning is of the devil, for the devil has been sinning from the beginning. The reason the Son of God appeared was to destroy the works of the devil. No one born of God makes a practice of sinning, for God's seed abides in him, and he cannot keep on sinning because he has been born of God. By this it is evident who are the children of God, and who are the children of the devil: whoever does not practice righteousness is not of God, nor is the one who does not love his brother. For this is the message that you have heard from the beginning, that we should love one another.

\subsection{Sharing Jesus' holiness / personal righteousness (fruit of righteousness) - coming \textbf{after} faith in Jesus}
\label{sec:orga27e67e}
\subsubsection{The yoke of the Lord Jesus}
\label{sec:org4791ce1}
Yes, there is an amount of following Jesus.

\emph{"resisted to the point of shedding your blood."}

\textbf{Hebrews 12:1-11} - Therefore, since we are surrounded by so great a cloud of witnesses, let us also lay aside every weight, and sin which clings so closely, and let us run with endurance the race that is set before us, looking to Jesus, the \textbf{founder} and \textbf{perfecter} of our \textbf{faith}, who for the joy that was set before him endured the cross, despising the shame, and is seated at the right hand of the throne of God. Consider him who endured from sinners such hostility against himself, so that you may not grow weary or fainthearted. In your struggle against sin you have \uline{not yet resisted to the point of shedding your blood}. And have you forgotten the exhortation that addresses you as sons? My son, do not regard lightly the discipline of the Lord, nor be weary when reproved by him. For the Lord disciplines the one he loves, and chastises every son whom he receives. It is for discipline that you have to endure. God is treating you as sons. For what son is there whom his father does not discipline? \textbf{If you are left without discipline, in which all have participated, then you are illegitimate children and not sons}. Besides this, we have had earthly fathers who disciplined us and we respected them. Shall we not much more be subject to the Father of spirits and live? For they disciplined us for a short time as it seemed best to them, but he disciplines us for our good, that we may \textbf{share his holiness}. For the moment all discipline seems painful rather than pleasant, but later it yields the peaceful \textbf{fruit of righteousness} to those who have been trained by it.

If a person is obedient and doing the will of God then God can use that person's human will and exertion. Jesus was faithful to God. Jesus was obedient to God.

I'm reluctant to use external sources outside of the Bible, but this is also described in the Didache.

The Didache's estimated range of dating is 50-120 A.D, according to \href{https://www.earlychristianwritings.com/text/didache-roberts.html}{earlychristianwritings.com}.

\textbf{Didache Chapter 6} - See that no one causes you to err from this way of the Teaching, since apart from God it teaches you. For if you are able to bear the entire yoke of the Lord, you will be perfect; but if you are not able to do this, do what you are able.

\textbf{Matthew 5:47-48} - And if you greet only your brothers, what more are you doing than others? Do not even the Gentiles do the same? You therefore must be perfect, as your heavenly Father is perfect.

Of course, I believe God doesn't send all His servants to be martyred, but probably uses what amount a person is willing to bear for the Lord Jesus.

\textbf{Matthew 19:21} - Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me.

\textbf{Matthew 11:29-30} - Take my yoke upon you, and learn from me, for I am gentle and lowly in heart, and you will find rest for your souls. For my yoke is easy, and my burden is light.

\subsection{Personal holiness}
\label{sec:orgcc29d25}
Everyone who names the name of the Lord must depart from iniquity:

\textbf{II Timothy 2:19-22} - But God's firm foundation stands, bearing this seal: The Lord knows those who are his, and, Let everyone who names the name of the Lord depart from iniquity. Now in a great house there are not only vessels of gold and silver but also of wood and clay, some for honorable use, some for dishonorable. Therefore, if anyone cleanses himself from what is dishonorable, he will be a vessel for honorable use, set apart as holy, useful to the master of the house, ready for every good work. So flee youthful passions and pursue righteousness, faith, love, and peace, along with those who call on the Lord from a pure heart.

Following Jesus means obeying Jesus:

\textbf{John 8:12} - Again Jesus spoke to them, saying, I am the light of the world. Whoever follows me will not walk in darkness, but will have the light of life.

\textbf{John 9:5} - As long as I am in the world, I am the light of the world.

Jesus instructed his his disciples to be holy:

\textbf{Matthew 5:14-20} - You are the light of the world. A city set on a hill cannot be hidden. Nor do people light a lamp and put it under a basket, but on a stand, and it gives light to all in the house. In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. Do not think that I have come to abolish the Law or the Prophets; I have not come to abolish them but to fulfill them. For truly, I say to you, until heaven and earth pass away, not an iota, not a dot, will pass from the Law until all is accomplished. Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. For I tell you, \uline{unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven}.

I believe following Jesus includes exercising personal righteousness/holiness.

I believe that God's grace extends to all who
put their faith in Jesus and have Jesus'
righteousness imputed onto them, the
righteousness of faith in Jesus Christ God's
Son who has paid through his blood the price
for our sin.

Imputed righteousness is important, but we need also personal holiness.
\begin{itemize}
\item \href{https://www.youtube.com/watch?v=S8rmiZRzqfg}{Holiness Demanded - Charles Spurgeon Sermon - YouTube}
\end{itemize}

We must live in holiness. This is practical holiness, the opposite of impurity.

\textbf{Hebrews 12:14} - Pursue peace with all men, and the sanctification without which no one will see the Lord.

\begin{itemize}
\item antinomianism is a heresy.
\end{itemize}

I believe one must know that God's law is
right and when presented with God's law, they
recognise that the law is right and recognise
their transgression, and continue towards
sanctification, putting off the old, sinful
self.

\textbf{Hebrews 12:14,15} -  Strive for peace with everyone, and for the holiness without which no one will see the Lord.  See to it that no one fails to obtain the grace of God; that no root of bitterness springs up and causes trouble, and by it many become defiled;  (ESV)

\textbf{I Thessalonians 3:13} - so that He may establish your hearts without blame in holiness before our God and Father at the coming of our Lord Jesus with all His saints.

I consider homosexuality to be erroneous and sinful, and God's original design to be correct.

\textbf{Matthew 19:4-12} - He answered, Have you not read that he who created them \textbf{from the beginning made them male and female}, and said, Therefore a man shall leave his father and his mother and hold fast to his wife, and they shall become one flesh?  So they are no longer two but one flesh. What therefore God has joined together, let not man separate.  They said to him, Why then did Moses command one to give a certificate of divorce and to send her away?  He said to them, Because of your hardness of heart Moses allowed you to divorce your wives, but \textbf{from the beginning it was not so}.  And I say to you: whoever divorces his wife, except for sexual immorality, and marries another, commits adultery.  The disciples said to him, If such is the case of a man with his wife, it is better not to marry.  But he said to them, Not everyone can receive this saying, but only those to whom it is given.  For there are eunuchs who have been so from birth, and there are eunuchs who have been made eunuchs by men, and there are eunuchs who have made themselves eunuchs for the sake of the kingdom of heaven. Let the one who is able to receive this receive it.

And no-one should endorse sinful things. Homosexuality is erroneous.
If they do, however, endorse it then I think that inhibits them from approaching God.

\subsection{Belief comes before or at the time of receiving the Holy Spirit (receiving the Holy Spirit comes at the time of or after believing)}
\label{sec:org89d3249}
I believe that the Holy Spirit goes to those who obey God. I believe belief in Jesus comes first.

\textbf{Acts 2:38} - And Peter said to them, Repent and be baptized every one of you in the name of Jesus Christ for the forgiveness of your sins, and you will receive the gift of the Holy Spirit. (ESV)

\textbf{Acts 5:32} - And we are witnesses to these things, and so is the Holy Spirit, whom God has given to those who obey him. (ESV)

\textbf{John 14:15-17} - If you love me, you will keep my commandments.  And I will ask the Father, and he will give you another Helper, to be with you forever, even the Spirit of truth, whom the world cannot receive, because it neither sees him nor knows him. You know him, for he dwells with you and will be in you. (ESV)

Belief in Jesus comes first but receiving the Holy Spirit and baptism may happen in any order after that.

I think this is generally the order of things.

\subsection{God is sovereign to reveal Himself, sovereign to save and sovereign to destroy}
\label{sec:org8657672}
\textbf{Romans 10:20} - Then Isaiah is so bold as to say, I have been found by those who did not seek me; I have shown myself to those who did not ask for me. (ESV)

\textbf{Matthew 10:28} - And do not fear those who kill the body but cannot kill the soul. Rather fear him who can destroy both soul and body in hell.

\subsection{Just saying a creed doesn't guarantee that a person is saved (I think)}
\label{sec:orgdeeac16}

God chooses who is saved, and how they are saved.
God justifies.

\textbf{I Timothy 6:11-16} - But as for you, O man of God, flee these things. Pursue righteousness, godliness, faith, love, steadfastness, gentleness.  Fight the good fight of the faith. Take hold of the eternal life to which you were called and about which you made the good confession in the presence of many witnesses.  I charge you in the presence of God, who gives life to all things, and of Christ Jesus, who in his testimony before Pontius Pilate made the good confession, to \uline{keep the commandment unstained and free from reproach until the appearing of our Lord Jesus Christ}, which he will display at the proper time—he who is the blessed and only Sovereign, the King of kings and Lord of lords, who alone has immortality, who dwells in unapproachable light, whom no one has ever seen or can see. To him be honor and eternal dominion. Amen.

Confessing and holding to a creed is working faith though.

\textbf{Hebrews 4:14} - Since then we have a great high priest who has passed through the heavens, Jesus, the Son of God, \textbf{let us hold fast our confession}.

\textbf{Hebrews 3:1} - Therefore, holy brothers, you who share in a heavenly calling, consider Jesus, the apostle and high priest of our confession,

\textbf{Hebrews 10:23} - Let us hold fast the confession of our hope without wavering, for he who promised is faithful.

\textbf{II Corinthians 9:13} - By their approval of this service, they will glorify God because of your submission flowing from your confession of the gospel of Christ, and the generosity of your contribution for them and for all others,

Jesus sees here that though they have little power, they kept His word and did not deny His name.

God justifies.

\textbf{Revelation of John 3:8} - I know your \textbf{works}. Behold, I have set before you an open door, which no one is able to shut. I know that you have but little power, and yet you have \textbf{kept my word and have not denied my name}. Behold, I will make those of the synagogue of Satan who say that they are Jews and are not, but lie-behold, I will make them come and bow down before your feet and they will learn that I have loved you. Because you have kept my word about \textbf{patient endurance}, I will keep you from the hour of trial that is coming on the whole world, to try those who dwell on the earth.

\subsection{It's the obedient who are justified, not the hearers}
\label{sec:orgba22cd2}

God keeps us from stumbling along the way:

\textbf{Jude 1:24-25} - Now to him who is able to keep you from stumbling and to present you blameless before the presence of his glory with great joy, to the only God, our Savior, through Jesus Christ our Lord, be glory, majesty, dominion, and authority, before all time and now and forever. Amen.

\textbf{I Peter 2:25} - For you were straying like sheep, but have now returned to the Shepherd and Overseer of your souls.

Fulfilling the requirement of the law is required of us by God. God judges the secrets of men by Christ Jesus.

\textbf{Romans 2:13-16} - For it is not the hearers of the law who are righteous before God, but the doers of the law who will be justified.  For when Gentiles, who do not have the law, by nature do what the law requires, they are a law to themselves, even though they do not have the law.  They show that the work of the law is written on their hearts, while their conscience also bears witness, and their conflicting thoughts accuse or even excuse them on that day when, according to my gospel, God judges the secrets of men by Christ Jesus.

\subsubsection{These people performed dead works, and never obeyed Jesus}
\label{sec:orgfe5a1ac}

\textbf{Matthew 7:21-27} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven.  On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name?  And then will I declare to them, I never knew you; depart from me, you workers of lawlessness.  Everyone then who hears these words of mine and does them will be like a wise man who built his house on the rock.  And the rain fell, and the floods came, and the winds blew and beat on that house, but it did not fall, because it had been founded on the rock.  And everyone who hears these words of mine and does not do them will be like a foolish man who built his house on the sand.  And the rain fell, and the floods came, and the winds blew and beat against that house, and it fell, and great was the fall of it. (ESV)

To get to know Jesus, follow His commandments - be obedient to Jesus.

\subsection{Outside of the Holy Spirit, noone can say Jesus is Lord}
\label{sec:org1bd0174}

\textbf{1 Corinthians 12:3} - Therefore I want you to understand that no one speaking in the Spirit of God ever says Jesus is accursed! and no one can say Jesus is Lord except in the Holy Spirit. (ESV)

\subsection{Works accompany the true believers}
\label{sec:org0ba2214}
\textbf{Mark 16:16-17} - Whoever believes and is baptized will be saved, but whoever does not believe will be condemned. And these signs will accompany those who believe: in my name they will cast out demons; they will speak in new tongues; (ESV)

\subsection{Those that reject the gospel are not the same as those who haven't heard the gospel}
\label{sec:org06b98ea}
\textbf{Mark 6:11} - And if any place will not receive you and they will not listen to you, when you leave, shake off the dust that is on your feet as a testimony against them.

\subsubsection{The following applies to believing Jesus, not to believing that a disciple of Jesus is Jesus}
\label{sec:org9bdd2d3}
\textbf{John 8:24} - I told you that you would die in your sins, for unless you believe that I am he you will die in your sins.  (ESV)

A disciple of Jesus isn't Jesus, but a disciple.

\subsubsection{There's more chances to accept Jesus after hearing the gospel and initially rejecting or being unsure}
\label{sec:org0cdbf1c}

\textbf{John 4:36-38} - Already the one who reaps is receiving wages and gathering fruit for eternal life, so that sower and reaper may rejoice together. For here the saying holds true, One sows and another reaps. I sent you to reap that for which you did not labor. Others have labored, and you have entered into their labor.

\textbf{John 4:34-38} - Jesus said to them, My food is to do the will of him who sent me and to accomplish his work. Do you not say, There are yet four months, then comes the harvest? Look, I tell you, lift up your eyes, and see that the fields are white for harvest. Already the one who reaps is receiving wages and gathering fruit for eternal life, so that sower and reaper may rejoice together. For here the saying holds true, One sows and another reaps. I sent you to reap that for which you did not labor. Others have labored, and you have entered into their labor.

\subsubsection{If someone receives the one who Jesus sends, they receive Jesus}
\label{sec:org4a76717}
\textbf{John 13:20} - Truly, truly, I say to you, whoever receives the one I send receives me, and whoever receives me receives the one who sent me.

\textbf{Matthew 10:40} - "He who receives you receives Me, and he who receives Me receives Him who sent Me.

\textbf{Mark 9:37} - "Whoever receives one child like this in My name receives Me; and whoever receives Me does not receive Me, but Him who sent Me."

\subsubsection{People always have the choice to believe the gospel}
\label{sec:orgdc62559}
\textbf{Romans 11:23} - And even they, if they do not continue in their unbelief, will be grafted in, for God has the power to graft them in again.

\textbf{Matthew 21:32} - For John came to you in the way of righteousness, and you did not believe him, but the tax collectors and the prostitutes believed him. And even when you saw it, you did not afterward change your minds and believe him. (ESV)

\textbf{Joel 2:12-13} - Yet even now, declares the LORD, return to me with all your heart, with fasting, with weeping, and with mourning; and rend your hearts and not your garments. Return to the LORD, your God, for he is gracious and merciful, slow to anger, and \uline{abounding in steadfast love; and he relents over disaster} . (ESV)

\subsubsection{I lean towards this interpretation}
\label{sec:org91e878b}
\begin{itemize}
\item People who hear the gospel and \uline{ultimately} reject it / reject Jesus / choose to not put their trust in Jesus are condemned.
\item There's more chances to accept Jesus after hearing the gospel and initially rejecting or being unsure
\item Rejecting Jesus in front of others is not good because it's a testimony against them
\item Acknowledging Jesus in front of others is very good
\end{itemize}

\textbf{John 3:19} - This is the judgment, that the Light has come into the world, and men loved the darkness rather than the Light, for their deeds were evil. (ESV)

\textbf{Luke 19:10} - For the Son of Man came to seek and to save the lost.

\subsubsection{Rejecting Jesus in front of others is not good}
\label{sec:org12d2d43}
\textbf{Luke 9:26} - For whoever is ashamed of me and of my words, of him will the Son of Man be ashamed when he comes in his glory and the glory of the Father and of the holy angels.

\textbf{I John 2:23} - No one who denies the Son has the Father. Whoever confesses the Son has the Father also.

\textbf{I John 4:15} - Whoever confesses that Jesus is the Son of God, God abides in him, and he in God.

\textbf{Matthew 10:32} - So everyone who acknowledges me before men, I also will acknowledge before my Father who is in heaven,

\textbf{Matthew 10:33} - but whoever denies me before men, I also will deny before my Father who is in heaven.

\textbf{Luke 12:8} - And I tell you, everyone who acknowledges me before men, the Son of Man also will acknowledge before the angels of God,

\subsubsection{It's \textbf{really} important to not reject Jesus through}
\label{sec:org0dbc61b}

\textbf{I Peter 3:18-21} - For Christ also suffered once for sins, the righteous for the unrighteous, that he might bring us to God, being put to \textbf{death in the flesh but made alive in the spirit}, in which he went and proclaimed to the spirits in prison, because \textbf{they formerly did not obey}, when God's patience waited in the days of Noah, while the ark was being prepared, in which a few, that is, eight persons, were brought safely through water. Baptism, which corresponds to this, now saves you, not as a removal of dirt from the body but as an appeal to God for a good conscience, through the resurrection of Jesus Christ,

If this verse suggests that Jesus went to the spirits in prison who had in the days of Noah disobeyed, then we should definitely obey the gospel while we're alive today.

\subsection{I believe that repentance is important in faith and faithfulness to God}
\label{sec:orgb41cb23}
\textbf{Acts 2:38} - And Peter said to them, Repent and be baptized every one of you in the name of Jesus Christ for the forgiveness of your sins, and you will receive the gift of the Holy Spirit. (ESV)

Basic repentance is 'metanoia' (a change of mind) - it's part of belief.
But this is what repentance looks like.

\textbf{Joel 2:12-13} - Yet even now, declares the LORD, return to me with all your heart, with fasting, with weeping, and with mourning; and rend your hearts and not your garments. Return to the LORD, your God, for he is gracious and merciful, slow to anger, and abounding in steadfast love; and he relents over disaster. (ESV)

And repentance has the fruit of in your heart truly deciding to tell the truth, not commit adultery, etc. - being accountable to God, knowing that He sees.

\textbf{Matthew 3:8} - Bear fruit in keeping with repentance. (ESV)

This is following the law by faith, I think; Truly loving God and one's neighbour.

There are a lot of 'do nots' in the law but the most important thing is the 2 'do' commandments.
The 'do nots' are to stop people from doing bad things, but the 2 Greatest commandments command us to love God and our neighbour.

\textbf{Matthew 22:37-40} - And he said to him, You shall love the Lord your God with all your heart and with all your soul and with all your mind. This is the great and first commandment. And a second is like it: You shall love your neighbor as yourself. On these two commandments depend all the Law and the Prophets.

\textbf{Colossians 3:4-9} - When Christ who is your life appears, then you also will appear with him in glory. Put to death therefore what is earthly in you: sexual immorality, impurity, passion, evil desire, and covetousness, which is idolatry. On account of these the wrath of God is coming. In these you too once walked, when you were living in them. But now you must put them all away: anger, wrath, malice, slander, and obscene talk from your mouth. Do not lie to one another, seeing that you have put off the old self with its practices

Lots of people say these days that trying to follow the law is self-righteousness and I don't really agree with that because to follow the law in faith is OK.
But to be 'under' the law is put oneself under a curse.

\subsection{Celebrating/endorsing sin / error is not right}
\label{sec:orgbde3111}

If a newly born-again Christian is spending all their time with sinners though and endorsing continually instead of being discipled, then they can
have their mind conformed to the sinners instead of being strengthened in the truth. This is why I think it's not especially great to, immediately after getting born-again,
be overly exposed to unbelievers and sinners.

Jesus ate with sinners but Jesus was the special guest. Think of Nicodemus inviting Jesus over.

\subsection{Faith has substance to it, and an amount to it, usually drawn out over time}
\label{sec:org899a4e1}
\textbf{Hebrews 11:1} - Now faith is the substance of things hoped for, the evidence of things not seen. (KJV)

For me, I was acting in faith ever since I was born-again, resulting in a huge chain of events and confirmations!

\subsection{Faith believes God and hopes in invisible things, and is convicted of them}
\label{sec:org8704ca6}

But at the end of the day, justification by faith in Jesus justifies the ungodly sinner - but it is faith that God justifies and not faithlessness. It's the type of belief that recognises one's sin, and results in love for Jesus, and it's obedient and submissive to God - it's repentant.

\textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God must believe that he exists and that he rewards those who seek him. (ESV)

Where we are unfaithful, though, God is faithful. God wants us to choose Him. He wants us to repent.

\subsection{Jesus' words never pass away. The law could only pass away after heaven and earth passes away}
\label{sec:orgeb1a77e}
\textbf{Psalms 119:160} - The sum of your word is truth, and every one of your righteous rules endures forever. (ESV)

\textbf{Matthew 11:25} - At that time Jesus declared, I thank you, Father, Lord of heaven and earth, that you have hidden these things from the wise and understanding and revealed them to little children;

\textbf{Matthew 24:35} - Heaven and earth will pass away, but my words will not pass away.

\textbf{Mark 13:31} - Heaven and earth will pass away, but my words will not pass away.

\textbf{Luke 10:21} - In that same hour he rejoiced in the Holy Spirit and said, I thank you, Father, Lord of heaven and earth, that you have hidden these things from the wise and understanding and revealed them to little children; yes, Father, for such was your gracious will.

\textbf{Luke 16:17} - But it is easier for heaven and earth to pass away than for one dot of the Law to become void.

\textbf{Matthew 5:14-20} - You are the light of the world. A city set on a hill cannot be hidden. Nor do people light a lamp and put it under a basket, but on a stand, and it gives light to all in the house. In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. Do not think that I have come to abolish the Law or the Prophets; I have not come to abolish them but to fulfill them. For truly, I say to you, until heaven and earth pass away, not an iota, not a dot, will pass from the Law until all is accomplished. Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. For I tell you, unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven. (ESV)

\textbf{Luke 21:33} - Heaven and earth will pass away, but my words will not pass away.

\subsection{Structure of the Kingdom}
\label{sec:orgf54a51b}
When applying the law, justice and mercy and faithfulness are the weightier matters of the law.
However, the remainder of the law is not supposed to be neglected either:

\textbf{Matthew 23:23-25} - Woe to you, scribes and Pharisees, hypocrites! For you tithe mint and dill and cumin, and have neglected the weightier matters of the law: justice and mercy and faithfulness. These you ought to have done, without neglecting the others.  You blind guides, straining out a gnat and swallowing a camel!  Woe to you, scribes and Pharisees, hypocrites! For you clean the outside of the cup and the plate, but inside they are full of greed and self-indulgence.

The law still exists. A thought I have : "Perhaps structure of God's kingdom might be determined by the law and Jesus' words."

\textbf{Psalms 119:160} - The sum of your word is truth, and every one of your righteous rules endures forever. (ESV)

Heaven is God's throne and its foundation is righteousness and justice.

\textbf{Psalms 97:2} - Clouds and thick darkness are all around him; righteousness and justice are the foundation of his throne.

\textbf{Psalms 89:14} - Righteousness and justice are the foundation of your throne; steadfast love and faithfulness go before you. (ESV)

\textbf{Acts 7:49} - 'Heaven is My throne, And earth is the footstool of My feet; What kind of house will you build for Me?' says the Lord, 'Or what place is there for My repose?

The universe is upheld by the word of Jesus' power.

\textbf{Hebrews 1:3} - He is the radiance of the glory of God and the exact imprint of his nature, and he upholds the universe by the word of his power. After making purification for sins, he sat down at the right hand of the Majesty on high, (ESV)

\textbf{Revelation of John 20:4} - Then I saw thrones, and seated on them were those to whom the authority to judge was committed. Also I saw the souls of those who had been beheaded for the testimony of Jesus and for the word of God, and who had not worshiped the beast or its image and had not received its mark on their foreheads or their hands. They came to life and reigned with Christ for a thousand years.

\subsubsection{Great or small in the kingdom of God}
\label{sec:orgc683e99}
\subsubsection{The least will be greatest}
\label{sec:orgcb6a918}
\textbf{Luke 9:48} - and said to them, Whoever receives this child in my name receives me, and whoever receives me receives him who sent me. For he who is least among you all is the one who is great. (ESV)

\subsubsection{Your servant will be greater}
\label{sec:org0f47b8b}

\textbf{Mark 9:35} - And he sat down and called the twelve. And he said to them, If anyone would be first, he must be last of all and servant of all. (ESV)

\textbf{Mark 10:43} - But it shall not be so among you. But whoever would be great among you must be your servant, (ESV)

\subsubsection{The humble and obedient will be called great}
\label{sec:org38f013e}
\textbf{Matthew 5:6} - Blessed are those who hunger and thirst for righteousness, for they shall be satisfied.

Those who annul and teach others to break the law will be called least in the kingdom.
\begin{itemize}
\item It's prideful to say that God is wrong, Jesus behaved badly and that the Law is wrong
\begin{itemize}
\item It refuses to acknowledge sin
\end{itemize}
\end{itemize}
Those who keep God's commandments and AND the righteousness of faith / the testimony of Jesus will be called great in the kingdom.
\begin{itemize}
\item This is humility to keep God's commandments by faith (and not works)
\end{itemize}

There is a self-righteous way of trying to keep the law, and there is a humble way.
\begin{itemize}
\item The self-righteous way
\begin{itemize}
\item Pursues the law as if by works
\item Observes the law in detail but doesn't follow even the basics from the heart and in truth, or in faith.
\item Doesn't maintain being honest and faithful to God.
\item Doesn't maintain loving one's neighbour in truth and reality.
\item Lacks mercy.
\item Often criticizes others but with hypocrisy, not seeing they break the law while they accuse.
\item Often makes the mistake of condemning the innocent.
\item Often makes the mistake of being without mercy, or love.
\end{itemize}
\item The humble way, with faith
\begin{itemize}
\item Is accountable to God - it's not lying to God.
\item No deceit.
\item It's acknowledging that God is right, and His law is right.
\item It's loving God, and loving one's neighbour.
\item It's \textbf{compatible} with being led by the Spirit, not opposed
\end{itemize}
\end{itemize}

\textbf{Matthew 7:3-5} - Why do you see the speck that is in your brother's eye, but do not notice the log that is in your own eye? Or how can you say to your brother, Let me take the speck out of your eye, when there is the log in your own eye? You hypocrite, first take the log out of your own eye, and then you will see clearly to take the speck out of your brother's eye. (ESV)

\textbf{Galatians 5:18} - But if you are led by the Spirit, you are not under the law. Now the works of the flesh are evident: sexual immorality, impurity, sensuality, idolatry, sorcery, enmity, strife, jealousy, fits of anger, rivalries, dissensions, divisions, envy, drunkenness, orgies, and things like these. I warn you, as I warned you before, that those who do such things will not inherit the kingdom of God.

\subsubsection{God's kingdom is from Heaven to Earth}
\label{sec:orgdc88ca0}
\textbf{Genesis 14:19} - And he blessed him and said, Blessed be Abram by God Most High, Possessor of heaven and earth;

\textbf{Isaiah 66:1} - Thus says the Lord, "Heaven is My throne and the earth is My footstool. Where then is a house you could build for Me? And where is a place that I may rest???

\textbf{Jeremiah 23:24} - "Can a man hide himself in hiding places So I do not see him?" declares the Lord. "Do I not fill the heavens and the earth?" declares the Lord.??

\textbf{Acts 7:49} - 'Heaven is My throne, And earth is the footstool of My feet; What kind of house will you build for Me?' says the Lord, 'Or what place is there for My repose???

\textbf{Matthew 11:25} - At that time Jesus said, "I praise You, Father, Lord of heaven and earth, that You have hidden these things from the wise and intelligent and have revealed them to infants.

\textbf{Luke 10:21} - At that very time He rejoiced greatly in the Holy Spirit, and said, "I praise You, O Father, Lord of heaven and earth, that You have hidden these things from the wise and intelligent and have revealed them to infants. Yes, Father, for this way was well-pleasing in Your sight.

\textbf{Revelation of John 14:7} - And he said with a loud voice, Fear God and give him glory, because the hour of his judgment has come, and worship him who made heaven and earth, the sea and the springs of water.

\textbf{Acts 17:24} - The God who made the world and all things in it, since He is Lord of heaven and earth, does not dwell in temples made with hands;

\subsubsection{Jesus inherits the entire Kingdom}
\label{sec:orge584cb1}
\textbf{Hebrews 1:2} - in these last days has spoken to us in His Son, whom He appointed heir of all things, through whom also He made the world.

\textbf{I Corinthians 15:25} - For He must reign until He has put all His enemies under His feet.

\textbf{I Corinthians 15:27} - For He has put all things in subjection under His feet. But when He says, "All things are put in subjection," it is evident that He is excepted who put all things in subjection to Him.

\textbf{Ephesians 1:22} - And He put all things in subjection under His feet, and gave Him as head over all things to the church,

\textbf{Hebrews 2:8} - You have put all things in subjection under his feet." For in subjecting all things to him, He left nothing that is not subject to him. But now we do not yet see all things subjected to him.

\textbf{Hebrews 10:13} - waiting from that time onward until His enemies be made a footstool for His feet.

\subsubsection{Jesus' sheep/followers/saints inherit the Kingdom with Jesus. Jesus' sheep follow Jesus}
\label{sec:org737d6d3}
\textbf{Matthew 24:45-47} - Who then is the faithful and wise servant, whom his master has set over his household, to give them their food at the proper time? Blessed is that servant whom his master will find so doing when he comes. Truly, I say to you, he will set him over all his possessions. (ESV)

\textbf{Luke 12:32} - Fear not, little flock, for it is your Father's good pleasure to give you the kingdom.

\textbf{John 10:27} - My sheep hear my voice, and I know them, and they follow me.

\textbf{Luke 9:23} - And he said to all, If anyone would come after me, let him deny himself and take up his cross daily and follow me.

\textbf{Luke 18:22} - When Jesus heard this, he said to him, One thing you still lack. Sell all that you have and distribute to the poor, and you will have treasure in heaven; and come, follow me.

\textbf{John 12:26} - If anyone serves me, he must follow me; and where I am, there will my servant be also. If anyone serves me, the Father will honor him.

\textbf{John 21:22} - Jesus said to him, If it is my will that he remain until I come, what is that to you? You follow me!

\textbf{1 Corinthians 6:9-20} - Do you not know that the unrighteous will not inherit the kingdom of God? Do not be deceived: neither the sexually immoral, nor idolaters, nor adulterers, nor men who practice homosexuality, nor thieves, nor the greedy, nor drunkards, nor revilers, nor swindlers will inherit the kingdom of God. And such were some of you. But you were washed, you were sanctified, you were justified in the name of the Lord Jesus Christ and by the Spirit of our God. All things are lawful for me, but not all things are helpful. All things are lawful for me, but I will not be enslaved by anything. Food is meant for the stomach and the stomach for food-and God will destroy both one and the other. The body is not meant for sexual immorality, but for the Lord, and the Lord for the body. And God raised the Lord and will also raise us up by his power. Do you not know that your bodies are members of Christ? Shall I then take the members of Christ and make them members of a prostitute? Never! Or do you not know that he who is joined to a prostitute becomes one body with her? For, as it is written, The two will become one flesh. But he who is joined to the Lord becomes one spirit with him. Flee from sexual immorality. Every other sin a person commits is outside the body, but the sexually immoral person sins against his own body. Or do you not know that your body is a temple of the Holy Spirit within you, whom you have from God? You are not your own, for you were bought with a price. So glorify God in your body. (ESV)

\textbf{Zechariah 8:23} - Thus says the Lord of hosts: In those days ten men from the nations of every tongue shall take hold of the robe of a Jew, saying, Let us go with you, for we have heard that God is with you.

\textbf{Revelation of John 2:26} - The one who conquers and who keeps my works until the end, to him I will give authority over the nations,

\subsubsection{Followers of Jesus become fishers of men}
\label{sec:org6e6795d}

\textbf{Mark 1:17} - And Jesus said to them, Follow me, and I will make you become fishers of men.

\subsubsection{One must be born-again to enter in and inherit the Kingdom of God}
\label{sec:orgf945927}
\textbf{John 3:3} - Jesus answered him, Truly, truly, I say to you, unless one is born again he cannot see the kingdom of God.

\textbf{John 3:5} - Jesus answered, Truly, truly, I say to you, unless one is born of water and the Spirit, he cannot enter the kingdom of God.

\textbf{I Corinthians 15:50d} - I tell you this, brothers: flesh and blood cannot inherit the kingdom of God, nor does the perishable inherit the imperishable.

\subsection{There is no sexual immorality in Heaven, no violence, no sinners.}
\label{sec:org4734054}
Heaven is not Earth. It's a place without sinning.

But the Kingdom of God exists from Heaven to Earth.

\textbf{II Peter 3:13-14} - But according to his promise we are waiting for new heavens and a new earth in which righteousness dwells. Therefore, beloved, since you are waiting for these, be diligent to be found by him without spot or blemish, and at peace.

\textbf{Revelation 21:22-27} - And I saw no temple in the city, for its temple is the Lord God the Almighty and the Lamb. And the city has no need of sun or moon to shine on it, for the glory of God gives it light, and its lamp is the Lamb. By its light will the nations walk, and the kings of the earth will bring their glory into it, and its gates will never be shut by day-and there will be no night there. They will bring into it the glory and the honor of the nations. But nothing unclean will ever enter it, nor anyone who does what is detestable or false, but only those who are written in the Lamb's book of life. (ESV)

\textbf{Isaiah 11:6} - The wolf shall dwell with the lamb, and the leopard shall lie down with the young goat, and the calf and the lion and the fattened calf together; and a little child shall lead them. (ESV)

\textbf{Matthew 22:30} - For in the resurrection they neither marry nor are given in marriage, but are like angels in heaven.

\subsection{Adhering to the law like a Pharisee - pursuing the law by works}
\label{sec:org56e0c7c}
But adhering to the law like a Pharisee is like strapping yourself to a razor blade, but that doesn't mean the law is wrong.

\textbf{Romans 3:20} - For by works of the law no human being will be justified in his sight, since through the law comes knowledge of sin.

\subsection{Follow the law mercifully and without self-righteousness, accountable to God, being a servant to others}
\label{sec:org7537694}
So as to not become a hypocrite or condemn the innocent.
Accountable to God - a relationship with God.
Without self-righteousness.

\textbf{Acts 23:3} - Then Paul said to him, God is going to strike you, you whitewashed wall! Are you sitting to judge me according to the law, and yet contrary to the law you order me to be struck?

\textbf{Matthew 12:3-8} - He said to them, Have you not read what David did when he was hungry, and those who were with him: how he entered the house of God and ate the bread of the Presence, which it was not lawful for him to eat nor for those who were with him, but only for the priests? Or have you not read in the Law how on the Sabbath the priests in the temple profane the Sabbath and are guiltless? I tell you, something greater than the temple is here. And if you had known what this means, I desire mercy, and not sacrifice, you would not have condemned the guiltless. For the Son of Man is lord of the Sabbath.

The greatest among you will be your servant.
Keeping the commandments by faith results in a person a who is a servant, serving others.

\textbf{Luke 22:26} - But it is not this way with you, but the one who is the greatest among you must become like the youngest, and the leader like the servant.

\textbf{Matthew 5:19} - Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven.

Not the best example, but, for example, when someone says you owe them money, and you can see they are blind, it's paying them because you're the one submitting to God.
It's humbling yourself even to others and following God's commandments in truth and reality, with a real faith relationship with God.
It's serving others as Jesus has served us.
It's keeping accountable to God and maintaining faithfulness to God, not keeping others accountable to you.

This isn't self-righteousness, but is a self-sacrificial obedience to continue working as a bond-servant of Christ, being the light of the world.

\textbf{Philippians 2:14-16} - Do all things without grumbling or questioning, that you may be blameless and innocent, children of God without blemish in the midst of a crooked and twisted generation, among whom you shine as lights in the world, holding fast to the word of life, so that in the day of Christ I may be proud that I did not run in vain or labor in vain.

\subsection{All the law is still used}
\label{sec:orgce0ee13}
We're not \uline{under} / condemned by the Mosaic law but we still don't encourage the breaking of the Mosaic law.

The law is good and it still exists, and God still uses the law. All of it. We are supposed to stand for truth and live righteously as the light of the world.

We all fall short of the glory of God and require the God's righteousness imputed to us through faith in Jesus, but having the righteousness of God through faith in Jesus is not license to sin.

Jesus Christ is the end of the law to all who believe, but grace isn't an excuse to sin.

God's commandments (especially the 10 Commandments; loving God and your neighbour) are still binding on us - written on our heart when we get born-again.

\subsubsection{Even the smallest of laws still come into effect in certain circumstances}
\label{sec:orgbbc4678}

\textbf{Leviticus 19:27} - You shall not round off the hair on your temples or mar the edges of your beard. (ESV)

For example, if Jesus sends you as an ambassador to some pagans and they asked you to shave your head in this specific way, or eat food sacrificed to idols.

\textbf{James 4:17} - So whoever knows the right thing to do and fails to do it, for him it is sin. (ESV)

\textbf{Romans 14:23} - But whoever has doubts is condemned if he eats, because the eating is not from faith. For whatever does not proceed from faith is sin. (ESV)

Therefore, a person should do what is out of love and faith for the LORD, based on their knowledge of the law,
their faithfulness to God and their conviction.

\subsection{Justification by faith - Jews + Gentiles, and in-between}
\label{sec:org01e8a82}
\href{https://youtu.be/34pBf5pZq\_I?t=536}{The Law Refutes Justification by Law: Galatians 3:6a??9, Part 1 - YouTube}

To be raised up as a child of Abraham, bear fruit in keeping with repentance:

\textbf{Luke 3:8} - \uline{Bear fruits in keeping with repentance.} And do not begin to say to yourselves, We have Abraham as our father. For I tell you, \uline{God is able from these stones to raise up children for Abraham.}

To be justified, a person must \uline{walk in the footsteps of the faith that our father Abraham had before he was circumcised}:

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

\textbf{John 8:39} - They answered him, Abraham is our father. Jesus said to them, If you were Abraham's children, you \uline{would be doing what Abraham did},

God can raise up children from anyone who has repentance and may grant being a child of Abraham to anyone who walks in the footsteps of the faith that Abraham had before he was circumcised.

\textbf{Luke 3:3-8} - And he went into all the region around the Jordan, proclaiming a baptism of repentance for the forgiveness of sins. As it is written in the book of the words of Isaiah the prophet, The voice of one crying in the wilderness: Prepare the way of the Lord, make his paths straight. Every valley shall be filled, and every mountain and hill shall be made low, and the crooked shall become straight, and the rough places shall become level ways, and all flesh shall see the salvation of God. He said therefore to the crowds that came out to be baptized by him, You brood of vipers! Who warned you to flee from the wrath to come? \uline{Bear fruits in keeping with repentance}. And do not begin to say to yourselves, We have Abraham as our father. For I tell you, \uline{God is able from these stones to raise up children for Abraham.}

John the Baptist even taught people to love one another:

\textbf{Luke 3:11-15} - And he answered them, Whoever has two tunics is to share with him who has none, and whoever has food is to do likewise. Tax collectors also came to be baptized and said to him, Teacher, what shall we do? And he said to them, Collect no more than you are authorized to do. Soldiers also asked him, And we, what shall we do? And he said to them, Do not extort money from anyone by threats or by false accusation, and be content with your wages. As the people were in expectation, and all were questioning in their hearts concerning John, whether he might be the Christ,

And I assume that repentance and loving one's neighbour are good precursors to being baptised by Jesus with the Holy Spirit and fire:

\textbf{Luke 3:16} - John answered them all, saying, I baptize you with water, but he who is mightier than I is coming, the strap of whose sandals I am not worthy to untie. He will baptize you with the Holy Spirit and with fire.

Justification by faith is the correct teaching but the promise is for the gentiles AND the adherent of the law but they all must have faith, and pursuing the law as if by works is the problem, but pursuing the law by faith is ok.

I believe in-between is OK, so long as it is by faith.

\textbf{Romans 7:22} - For I delight in the law of God, in my inner being, (ESV)

It's possible for Gentiles to keep Jewish commandments if they want (I think it's honorable) - but we are justified by faith in Jesus, not by being under the law:

\textbf{Romans 2:25-29} - For circumcision indeed is of value if you obey the law, but if you break the law, your circumcision becomes uncircumcision. So, if a man who is uncircumcised keeps the precepts of the law, will not his uncircumcision be regarded as circumcision? Then he who is physically uncircumcised but keeps the law will condemn you who have the written code and circumcision but break the law. For no one is a Jew who is merely one outwardly, nor is circumcision outward and physical. But a Jew is one inwardly, and circumcision is a matter of the heart, by the Spirit, not by the letter. His praise is not from man but from God.

It's possible to keep commandments by faith:

\textbf{Romans 9:30-32} - What shall we say, then? That Gentiles who did not pursue righteousness have attained it, that is, a righteousness that is by faith; but that Israel who pursued a law that would lead to righteousness did not succeed in reaching that law. Why? Because they did not pursue it by faith, but as if it were based on works. They have stumbled over the stumbling stone, (ESV)

\textbf{Romans 4:15-16} - For the law brings wrath, but where there is no law there is no transgression. That is why it depends on faith, in order that the promise may rest on grace and be guaranteed to all his offspring-not only to the adherent of the law but also to the one who shares the faith of Abraham, who is the father of us all, (ESV)

\textbf{Matthew 5:17-25} - Do not think that I have come to abolish the Law or the Prophets; I have not come to abolish them but to fulfill them. For truly, I say to you, until heaven and earth pass away, not an iota, not a dot, will pass from the Law until all is accomplished. Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. For I tell you, unless your righteousness exceeds that of the scribes and Pharisees, you will never enter the kingdom of heaven. You have heard that it was said to those of old, You shall not murder; and whoever murders will be liable to judgment. But I say to you that everyone who is angry with his brother will be liable to judgment; whoever insults his brother will be liable to the council; and whoever says, You fool! will be liable to the hell of fire. So if you are offering your gift at the altar and there remember that your brother has something against you, leave your gift there before the altar and go. First be reconciled to your brother, and then come and offer your gift. Come to terms quickly with your accuser while you are going with him to court, lest your accuser hand you over to the judge, and the judge to the guard, and you be put in prison. (ESV)

\subsection{Theoretically belief usually comes before or at the time receiving the Holy Spirit}
\label{sec:org3cbf0fb}
But for me I believe before I was born-again and before I was baptised in the Holy Spirit.

\textbf{Acts 19:1-7} - And it happened that while Apollos was at Corinth, Paul passed through the inland country and came to Ephesus. There he found some disciples. And he said to them, Did you receive the Holy Spirit when you believed? And they said, No, we have not even heard that there is a Holy Spirit. And he said, Into what then were you baptized? They said, Into John's baptism. And Paul said, John baptized with the baptism of repentance, telling the people to believe in the one who was to come after him, that is, Jesus. On hearing this, they were baptized in the name of the Lord Jesus. And when Paul had laid his hands on them, the Holy Spirit came on them, and they began speaking in tongues and prophesying. There were about twelve men in all. (ESV)

\section{Receive through the hearing of the word and faith}
\label{sec:org21e0488}
\textbf{Galatians 3:2} - Let me ask you only this: Did you receive the Spirit by works of the law or by hearing with faith? (ESV)

Not just by hearing but by hearing with faith.

\subsection{Faith requires obedience}
\label{sec:org628bfa7}
\textbf{Acts 5:32} - And we are witnesses to these things, and so is \textbf{the Holy Spirit, whom God has given to those who obey him}. (ESV)

\textbf{Galatians 3:14} - so that in Christ Jesus the blessing of Abraham might come to the Gentiles, so that we might \textbf{receive the promised Spirit through faith}. (ESV)

\subsection{The promised Spirit is received through faith}
\label{sec:orgc3cfbf5}
\textbf{Galatians 3:14} - so that in Christ Jesus the blessing of Abraham might come to the Gentiles, so that we might receive the promised Spirit through faith. (ESV)

\textbf{Matthew 19:16-26} - And behold, a man came up to him, saying, Teacher, what good deed must I do to have eternal life? And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me. When the young man heard this he went away sorrowful, for he had great possessions. And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. When the disciples heard this, they were greatly astonished, saying, Who then can be saved? But Jesus looked at them and said, With man this is impossible, but with God all things are possible.

I was born-again on 2 April 2022. On 1 April 2022 (one day before) I was wearing a pendant which on one side I had written 1023 which is decimal for the binary 1111111111 - which are ten ones. I was trying hard to follow the ten commandments from the heart, like Jesus teaches. I was doing this to seek Jesus. Then I was born-again. What a mystery.

Since then I've been trying to follow Jesus' commandments to get to know Him out of love for God, and because He has commanded His disciples to be fruitful for Him, and to abide in Him.

I had my belief in Jesus Christ and I had taken small steps of faith in remaining loyal to Jesus.

\textbf{Ezekiel 11:19-20} - And I will give them one heart, and a new spirit I will put within them. I will remove the heart of stone from their flesh and give them a heart of flesh, that they may walk in my statutes and keep my rules and obey them. And they shall be my people, and I will be their God. (ESV)

The following links obeying the commandments it to Jesus:

\textbf{I Kings 11:38} - And if you will listen to all that I command you, and will walk in my ways, and do what is right in my eyes by keeping my statutes and my commandments, as David my servant did, I will be with you and will build you a sure house, as I built for David, and I will give Israel to you.

\textbf{II Timothy 2:8} - Remember Jesus Christ, risen from the dead, the offspring of David, as preached in my gospel,

\subsubsection{Everlasting covenant}
\label{sec:org12ed5be}
\textbf{Genesis 17:19} - God said, No, but Sarah your wife shall bear you a son, and you shall call his name Isaac. I will establish my covenant with him as an everlasting covenant for his offspring after him.􀧁

An indicator of the ones who are saved is that they have the fear of God in their hearts.

\textbf{Jeremiah 32:40} - I will make with them an everlasting covenant, that I will not turn away from doing good to them. And I will put the fear of me in their hearts, that they may not turn from me. (ESV)

An indicator of the ones who are saved is that they have remorse for their past sin.

\textbf{Ezekiel 16:58-63} - You bear the penalty of your lewdness and your abominations, declares the Lord.  For thus says the Lord God: I will deal with you as you have done, you who have despised the oath in breaking the covenant, yet I will remember my covenant with you in the days of your youth, and I will establish for you an \textbf{everlasting covenant}.  Then you will \uline{remember your ways and be ashamed} when you take your sisters, both your elder and your younger, and I give them to you as daughters, but not on account of the covenant with you.  I will establish my covenant with you, and \uline{you shall know that I am the Lord}, that you may remember and be confounded, and never open your mouth again because of your shame, when I atone for you for all that you have done, declares the Lord God.

\textbf{Hebrews 8:10-13} - For this is the covenant that I will make with the house of Israel after those days, declares the Lord: I will put my laws into their minds, and write them on their hearts, and I will be their God, and they shall be my people. And they shall not teach, each one his neighbor and each one his brother, saying, Know the Lord, for they shall all know me, from the least of them to the greatest. For I will be merciful toward their iniquities, and I will remember their sins no more. In speaking of a new covenant, he makes the first one obsolete. And what is becoming obsolete and growing old is ready to vanish away.

God gives the Spirit to help keep the commandments. When she says the gospel is loving your neighbour, she is actually speaking part of the gospel. In the way that the man on the cross next to Jesus also spoke part of the full gospel message. They deserve the punishment but Jesus has done no wrong.

\textbf{Hosea 2:19-20} - And I will betroth you to me forever. I will betroth you to me in righteousness and in justice, in steadfast love and in mercy. I will betroth you to me in faithfulness. And you shall know the LORD. (ESV)

\subsubsection{2 years before being born again of the Spirit - prayer - proving belief came before being born-again}
\label{sec:orgc46f848}
\url{https://web.archive.org/web/20220402091720/https://mullikine.github.io/posts/prayer/}

Not that I have to prove it though!

\subsubsection{Over easter}
\label{sec:org8c496d1}
The old covenant is growing old and ready to vanish, but the New Covenant still involves the commandments but they are written on our heart.
We follow them in faith.

\subsubsection{Being born-again}
\label{sec:orgbb54740}
\url{https://web.archive.org/web/20220402091720/https://mullikine.github.io/posts/astral-projection/}

As interesting as what happened to me is, regarding a light body, I believe more important is objectively walking in the light of the truth.

\textbf{John 1:9-11} - The true light, which enlightens everyone, was coming into the world. He was in the world, and the world was made through him, yet the world did not know him. He came to his own, and his own people did not receive him. (ESV)

\textbf{John 12:36} - While you have the light, \uline{believe in the light, that you may become sons of light}. When Jesus had said these things, he departed and hid himself from them.

\subsubsection{Meeting with the Holy Spirit}
\label{sec:org9d47860}
\url{https://web.archive.org/web/20220402091720/https://mullikine.github.io/posts/astral-projection-pt-2/}

\textbf{I Timothy 6:20} - O Timothy, guard what has been entrusted to you, avoiding worldly and empty chatter and the opposing arguments of what is falsely called “knowledge”--

\textbf{II Timothy 1:14} - Guard, through the Holy Spirit who dwells in us, the treasure which has been entrusted to you.

\subsubsection{I wrote about following the law by faith, also law written on my heart.}
\label{sec:orgc2da3c4}

\url{https://web.archive.org/web/20220703044748/https://mullikine.github.io/posts/the-tapestry-of-truth/}

\subsubsection{Baptised in the Holy Spirit}
\label{sec:org4df2de4}
\url{https://web.archive.org/web/20220806085237/https://mullikine.github.io/posts/astral-projection-pt-3/}

Betrothed to God:

\textbf{Hosea 2:19-20} - And I will betroth you to me forever. I will betroth you to me in righteousness and in justice, in steadfast love and in mercy. I will betroth you to me in faithfulness. And you shall know the LORD. (ESV)

AMEN!!

\textbf{Hosea 2:21-23} - And in that day I will answer, declares the Lord, I will answer the heavens, and they shall answer the earth, and the earth shall answer the grain, the wine, and the oil, and they shall answer Jezreel, and I will sow her for myself in the land. And I will have mercy on No Mercy, and I will say to Not My People, You are my people; and he shall say, You are my God.

AMEN!!

\textbf{II Corinthians 11:2} - I feel a divine jealousy for you, for I \uline{betrothed you to one husband, to present you as a pure virgin to Christ}. (ESV)

\subsection{Later in the year}
\label{sec:orgcd03f54}
\url{https://web.archive.org/web/20220402091720/https://mullikine.github.io/posts/dream-the-way-the-truth-the-life/}

\subsection{New covenant}
\label{sec:org29bd1d6}
\textbf{Hebrews 8:10-13} - For this is the covenant that I will make with the house of Israel after those days, declares the Lord: I will put my laws into their minds, and write them on their hearts, and I will be their God, and they shall be my people. And they shall not teach, each one his neighbor and each one his brother, saying, Know the Lord, for they shall all know me, from the least of them to the greatest. For I will be merciful toward their iniquities, and I will remember their sins no more. In speaking of a new covenant, he makes the first one obsolete. And what is becoming obsolete and growing old is ready to vanish away.

Covenants require faithfulness between both parties, but we are able to move on from dead works and focus more on faith towards God, and serving God now.

\textbf{Hebrews 6:1} - Therefore leaving the elementary teaching about the Christ, let us press on to maturity, not laying again a foundation of repentance from dead works and of faith toward God, (ESV)

\textbf{Hebrews 9:14} - how much more will the blood of Christ, who through the eternal Spirit offered Himself without blemish to God, cleanse your conscience from dead works to serve the living God? (ESV)

\textbf{Hebrews 9:11-15} - But when Christ appeared as a high priest of the good things that have come, then through the greater and more perfect tent (not made with hands, that is, not of this creation) he entered once for all into the holy places, not by means of the blood of goats and calves but by means of his own blood, thus securing an eternal redemption. For if the sprinkling of defiled persons with the blood of goats and bulls and with the ashes of a heifer sanctifies for the purification of the flesh, how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God. Therefore he is the mediator of a new covenant, so that those who are called may receive the promised eternal inheritance, since a death has occurred that redeems them from the transgressions committed under the first covenant. (ESV)

\textbf{Hebrews 9:18-20} - Therefore not even the first covenant was inaugurated without blood. For when every commandment of the law had been declared by Moses to all the people, he took the blood of calves and goats, with water and scarlet wool and hyssop, and sprinkled both the book itself and all the people, saying, This is the blood of the covenant that God commanded for you. (ESV)

\textbf{Mark 14:22-25} - And as they were eating, he took bread, and after blessing it broke it and gave it to them, and said, Take; this is my body. And he took a cup, and when he had given thanks he gave it to them, and they all drank of it. And he said to them, This is my blood of the covenant, which is poured out for many. Truly, I say to you, I will not drink again of the fruit of the vine until that day when I drink it new in the kingdom of God. (ESV)

\textbf{Luke 22:15-20} - And he said to them, I have earnestly desired to eat this Passover with you before I suffer. For I tell you I will not eat it until it is fulfilled in the kingdom of God. And he took a cup, and when he had given thanks he said, Take this, and divide it among yourselves. For I tell you that from now on I will not drink of the fruit of the vine until the kingdom of God comes. And he took bread, and when he had given thanks, he broke it and gave it to them, saying, This is my body, which is given for you. Do this in remembrance of me. And likewise the cup after they had eaten, saying, This cup that is poured out for you is the new covenant in my blood. (ESV)

\textbf{John 6:46-51} - Not that anyone has seen the Father, except the One who is from God; He has seen the Father. Truly, truly, I say to you, he who believes has eternal life. I am the bread of life. Your fathers ate the manna in the wilderness, and they died. This is the bread which comes down out of heaven, so that one may eat of it and not die. I am the living bread that came down out of heaven; if anyone eats of this bread, he will live forever; and the bread also which I will give for the life of the world is My flesh.” (ESV)

\textbf{John 6:52} - Then the Jews began to argue with one another, saying, “How can this man give us His flesh to eat?”

\textbf{John 6:53-56} - So Jesus said to them, “Truly, truly, I say to you, unless you eat the flesh of the Son of Man and drink His blood, you have no life in yourselves. He who eats My flesh and drinks My blood has eternal life, and I will raise him up on the last day. For My flesh is true food, and My blood is true drink. He who eats My flesh and drinks My blood abides in Me, and I in him. (ESV)

\textbf{John 6:57-58} - As the living Father sent Me, and I live because of the Father, so he who eats Me, he also will live because of Me. This is the bread which came down out of heaven; not as the fathers ate and died; he who eats this bread will live forever.”

\textbf{John 6:59-60} - These things He said in the synagogue as He taught in Capernaum. Therefore many of His disciples, when they heard this said, “This is a difficult statement; who can listen to it?”

\textbf{John 6:61-62} - But Jesus, conscious that His disciples grumbled at this, said to them, “Does this cause you to stumble? What then if you see the Son of Man ascending to where He was before?

\textbf{John 6:63-65} - It is the Spirit who gives life; the flesh profits nothing; the words that I have spoken to you are spirit and are life. But there are some of you who do not believe.” For Jesus knew from the beginning who they were who did not believe, and who it was that would betray Him. And He was saying, “For this reason I have said to you, that no one can come to Me unless it has been granted him from the Father.”

\subsection{Born of God}
\label{sec:orgaf3707f}
When a person is born-again of the Spirit, they receive the Spirit which helps them to stop sinning and it's really important to do so.

\textbf{1 Peter 1:23} - since you have been born again, not of perishable seed but of imperishable, through the living and abiding word of God; (ESV)

\textbf{1 John 5:18} - We know that everyone who has been born of God does not keep on sinning, but he who was born of God protects him, and the evil one does not touch him. (ESV)

\textbf{Ezekiel 11:19-20} - And I will give them one heart, and a new spirit I will put within them. I will remove the heart of stone from their flesh and give them a heart of flesh, that they may walk in my statutes and keep my rules and obey them. And they shall be my people, and I will be their God. (ESV)

\textbf{Jeremiah 32:40} - I will make with them an everlasting covenant, that I will not turn away from doing good to them. And I will put the fear of me in their hearts, that they may not turn from me. (ESV)

\textbf{I John 3:9} - No one born of God makes a practice of sinning, for God's seed abides in him, and he cannot keep on sinning because he has been born of God.

But I would much like my dream life to be like the following:

\textbf{John 5:19} - So Jesus said to them, Truly, truly, I say to you, the Son can do nothing of his own accord, but only what he sees the Father doing. For whatever the Father does, that the Son does likewise.

Whoever loves in the way Jesus loved us and the way Jesus commanded us has been born of God and knows God.

\textbf{I John 4:7} - Beloved, let us love one another, for love is from God, and whoever loves has been born of God and knows God.

Anyone who \textbf{truly believes}.

We must receive Jesus' words, walk in them and come to \textbf{know in truth} (we must truly know) that Jesus came from God.

\textbf{John 17:8} - For I have given them the words that you gave me, and they have received them and have \textbf{come to know in truth that I came from you}; and they have believed that you sent me.

Therefore, we should obey Jesus and arrive at the truth. Obedience is a part of faith. Like Abraham obeying God, or like Israel crossing through the Red Sea, it's obedience which leads to sure belief.
And the obedience doesn't end.

\textbf{John 8:31-32} - So Jesus was saying to those Jews who had believed Him, “If you \textbf{continue in My word}, then you are truly disciples of Mine; and \textbf{you will know the truth}, and the truth will make you free.” (NASB)

\textbf{I John 5:1} - Everyone who believes that Jesus is the Christ has been born of God, and everyone who loves the Father loves whoever has been born of him.

\textbf{I John 5:4} - For everyone who has been born of God overcomes the world. And this is the victory that has overcome the world-our faith.

\textbf{I John 5:18} - We know that everyone who has been born of God does not keep on sinning, but he who was born of God protects him, and the evil one does not touch him.

I feel like stopping sin is very important after being born again.

\textbf{John 5:14} - Afterward Jesus found him in the temple and said to him, See, you are well! Sin no more, that nothing worse may happen to you.

\subsection{Justification by faith for the both adherents of the law and the gentiles}
\label{sec:org45b64db}
Justification by faith is the correct teaching but the promise is for the gentiles AND the adherent of the law but they all must have faith, and pursuing the law as if by works is the problem, but pursuing the law by faith is ok.

\textbf{Romans 7:22} - For I delight in the law of God, in my inner being, (ESV)

\textbf{Romans 9:30-32} - What shall we say, then? That Gentiles who did not pursue righteousness have attained it, that is, a righteousness that is by faith; but that Israel who pursued a law that would lead to righteousness did not succeed in reaching that law. Why? Because they did not pursue it by faith, but as if it were based on works. They have stumbled over the stumbling stone, (ESV)

\textbf{Romans 4:15-16} - For the law brings wrath, but where there is no law there is no transgression. That is why it depends on faith, in order that the promise may rest on grace and be guaranteed to all his offspring-not only to the adherent of the law but also to the one who shares the faith of Abraham, who is the father of us all, (ESV)

\subsection{Paul used the law to judge back, but without hypocrisy}
\label{sec:org2f10229}
\textbf{Matthew 23:27} - Woe to you, scribes and Pharisees, hypocrites! For you are like whitewashed tombs, which outwardly appear beautiful, but within are full of dead people's bones and all uncleanness.

\textbf{Acts 23:3} - Then Paul said to him, God is going to strike you, you whitewashed wall! Are you sitting to judge me according to the law, and yet contrary to the law you order me to be struck?

\subsection{Justified by God through faith and works}
\label{sec:org3b139a3}
Predestined, called, justified, glorified - sounds like election.
\subsubsection{God is the one who justifies}
\label{sec:orga786a4e}

\textbf{Romans 8:33} - Who shall bring any charge against God's elect? It is God who justifies.

\textbf{Romans 8:30} - And those whom he predestined he also called, and those whom he called he also justified, and those whom he justified he also glorified. (ESV)

But repentance is a work of the heart which is an act of faith.
I believe repentance is inseparable from faith because intrinsic to faith is belief and intrinsic to belief is metanoia (changing one's mind).

At it's most basic form repentance means a person believes in Jesus as the Son of God and the Messiah who, being innocent, paid the price for their sin through His broken body and shed blood on the cross - a perfect and eternal offering; that He died there but God resurrected Him, and He is Lord of Heaven and Earth.

But I believe we are forgiven to forgive others. That must be part of the act of faith and the change of heart, I think.

\textbf{Matthew 6:15} - but if you do not forgive others their trespasses, neither will your Father forgive your trespasses. (ESV)

\subsubsection{Justified by faith alone. But faith is substantiated by works}
\label{sec:org637d10f}
\textbf{James 2:10} - For whoever keeps the whole law but fails in one point has become accountable for all of it. For he who said, Do not commit adultery, also said, Do not murder. If you do not commit adultery but do murder, you have become a transgressor of the law. So speak and so act as those who are to be judged under the law of liberty. For judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment. What good is it, my brothers, if someone says he has faith but does not have works? Can that faith save him? If a brother or sister is poorly clothed and lacking in daily food, and one of you says to them, Go in peace, be warmed and filled, without giving them the things needed for the body, what good is that? So also faith by itself, if it does not have works, is dead. But someone will say, You have faith and I have works. Show me your faith apart from your works, and I will show you my faith by my works. You believe that God is one; you do well. Even the demons believe-and shudder! Do you want to be shown, you foolish person, that faith apart from works is useless? Was not Abraham our father justified by works when he offered up his son Isaac on the altar? You see that faith was active along with his works, and faith was completed by his works; and the Scripture was fulfilled that says, Abraham believed God, and it was counted to him as righteousness-and he was called a friend of God. You see that a person is justified by works and not by faith alone.

I tend to agree with James on this.
Eliminating works from faith is not good.

Works:
\begin{itemize}
\item obedience
\item faithfulness
\begin{itemize}
\item keeping God's commandments
\end{itemize}
\item trust
\item fear of God
\item response of love
\begin{itemize}
\item thankfulness
\item praise
\item forgiving others
\end{itemize}
\item humility
\begin{itemize}
\item keeping God's commandments
\end{itemize}
\item patient endurance (time)
\end{itemize}

If a person believes that Jesus Christ is the Son of the Living God then they abide in Christ.
But do they \textbf{really} believe? Because if they don't \textbf{really} believe it deep down then but are lying to themself they may not abide in Christ at all.
How can a person believe without having a relationship with God? A relationship involves more than belief.

If a person does not have obedience, trust and
repentance from sin, but their faith has belief, then they only
abide in Jesus extremely precariously, and also that person's 'faith' probably wont receive much at all from God.

\begin{verbatim}
 1  Faith-in-God = Hope-from/in-God * Work/Love
 2  
 3  Hope-from/in-God = Belief(believing God) * Truth(God's word is truth)
 4  
 5  Work/Love = Obedience * Faithfulness * Fear-of-God * Response-of-love-to-Jesus * Patient-Endurance(time)
 6  
 7  Obedience = Submitting to the Righteousness of God * Turning from sin, loving, showing mercy, etc.
 8  
 9  Fear-of-God = e.g. The poor in spirit recognise their need of God's mercy and tremble at His Word: "beat his breast, saying, God, be merciful to me, a sinner!"
10  
11  Response-of-love-to-Jesus = e.g. praise, thankfulness, obeying His commandments
12  
13  Love is proportional-to the baggage which has been forgiven
14  Love ∝ forgiven-baggage
15  
16  Obedience ∝ Love
17  
18  F = H * L
19  
20  Faith-in-God when tested by God is found to be true Faith in God.
21  Faith-in-God must submit to the Righteousness of God through faith in Jesus Christ,
22  Jesus Christ having paid the price of sin, enabling a relationship with God.
\end{verbatim}

These things are factors of faith.

\textbf{Galatians 5:6} - For in Christ Jesus neither circumcision nor uncircumcision counts for anything, but \textbf{only faith working through love}. (ESV)

God is the judge.

A person must/should \textbf{do} what Jesus said.

\textbf{Luke 6:47-49} - Everyone who comes to me and hears my words and does them, I will show you what he is like: he is like a man building a house, who dug deep and laid the foundation on the rock. And when a flood arose, the stream broke against that house and could not shake it, because it had been well built.  But the one who hears and does not do them is like a man who built a house on the ground without a foundation. When the stream broke against it, immediately it fell, and the ruin of that house was great.

\textbf{Matthew 7:24-27} - Everyone then who hears these words of mine and does them will be like a wise man who built his house on the rock. And the rain fell, and the floods came, and the winds blew and beat on that house, but it did not fall, because it had been founded on the rock. And everyone who hears these words of mine and does not do them will be like a foolish man who built his house on the sand. And the rain fell, and the floods came, and the winds blew and beat against that house, and it fell, and great was the fall of it. (ESV)

\begin{verbatim}
1  :  4102  pistis  pis'-tis
2  
3   from 3982; persuasion, i.e. credence; moral conviction (of religious
4   truth, or the truthfulness of God or a religious teacher), especially
5   reliance upon Christ for salvation; abstractly, constancy in such
6   profession; by extension, the system of religious (Gospel) truth
7   itself:--assurance, belief, believe, faith, fidelity.
8   see GREEK for 3982
\end{verbatim}

\textbf{Galatians 2:15} - "We are Jews (G2453 Ioudaios) by nature (G5449 phusis) and not sinners (G268 hamartolos) from among (G1537 ek) the Gentiles (G1484 ethnos);

Justified \emph{\textbf{through (G1223 dia) faith (G4102 pistis) in Christ.}}

\textbf{Galatians 2:16} - nevertheless (G1161 de) knowing (G3609 oikeios) that a man (G444 anthropos) is not justified (G1344 dikaioo) by the works (G2041 ergon) of the Law (G3551 nomos) but through (G1223 dia) faith (G4102 pistis) in Christ (G5547 Christos) Jesus (G2424 Iesous), even (G2532 kai) we have believed (G4100 pisteuo) in Christ (G5547 Christos) Jesus (G2424 Iesous), so (G2443 hina) that we may be justified (G1344 dikaioo) by faith (G4102 pistis) in Christ (G5547 Christos) and not by the works (G2041 ergon) of the Law (G3551 nomos); since (G3754 hoti) by the works (G2041 ergon) of the Law (G3551 nomos) no (G3756 ou) (G3956 pas) flesh (G4561 sarx) will be justified (G1344 dikaioo).

Justified through (G1223 dia) faith (G4102 \textbf{pistis}) in Christ (G5547 Christos) Jesus (G2424 Iesous).
Pistis is a strong word for faith that doesn't merely encapsulate belief, but it includes trust.

The greeks can turn the noun faith into the verb believing faith (G4100 pisteuo).
It's not the noun 'believe' as the root of the verb faith

\emph{\textbf{we have believed (G4100 pisteuo) in Christ}} means we have \emph{\textbf{'faithed'}} in Christ.

The 'believing faith' verb pisteuo has a root of faith (pistis).

Faith is a relationship with God.
Before Abraham believed God, he obeyed God.
Faith requires belief but it's more than belief.

\textbf{I Timothy 4:1}: But the Spirit (G4151 pneuma) explicitly says that in later times some will fall away from the faith (G4102 pistis), paying attention to deceitful spirits (G4151 pneuma) and doctrines of demons (G1140 daimonion), (NASB)

Faith is ongoing. Ongoing faith is patience endurance. Jesus says patience endurance is a work.

\textbf{Revelation of John 2:19} - I know your works, your love and faith and service and patient endurance, and that your latter works exceed the first.

\subsubsection{Paul here mentions trust even for the one who trusts in Him who justifies the ungodly}
\label{sec:orge0ad923}
\textbf{Romans 4:2} - For if Abraham was justified by works, he has something to boast about, but not before God.

Paul doesn't deny that Abraham could have been
justified by works, but he claims that Abraham
doesn't have anything to boast about before
God.

\textbf{Romans 4:5} - And to the one who does not work but trusts him who justifies the ungodly, his faith is counted as righteousness,

So Paul says that for someone who does not
have any works but trusts Him who justifies
the ungodly, the person's trusting faith is
counted as righteousness.

AMEN!! God is good for justifying people who are poor of spirit, and have fear of God.

\subsection{Conditional Promises In The New Testament}
\label{sec:org587802b}
\textbf{Matthew 5:3} - Blessed are the poor in spirit, for theirs is the kingdom of heaven.

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Those who are poor in spirit & Some will be inherit the kingdom of Heaven\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 5:4} - Blessed are those who mourn, for they shall be comforted. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Those that mourn & Some will be comforted\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 5:5} - Blessed are the meek, for they shall inherit the earth. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If you are gentle, humble and/or meek & You will inherit the Earth.\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 5:10} - Blessed are those who are persecuted for righteousness' sake, for theirs is the kingdom of heaven. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If you have been persecuted for the sake of righteousness. & The Kingdom of Heaven will be yours.\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 5:11-12} - Blessed are you when others revile you and persecute you and utter all kinds of evil against you falsely on my account. Rejoice and be glad, for your reward is great in heaven, for so they persecuted the prophets who were before you. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If people revile and persecute you for Jesus' sake and your faith in Him. & The Son of Man (Jesus) will reward people in Heaven and the reward will be great.\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 7:7} - Ask, and it will be given to you; seek, and you will find; knock, and it will be opened to you. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If you ask & It will be given you\\[0pt]
If you seek & You will find\\[0pt]
If you knock & It will be opened to you\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 16:27} - For the Son of Man is going to come with his angels in the glory of his Father, and then he will repay each person according to what he has done. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
You will be rewarded according to your own deeds in this life. & The Son of Man (Jesus) is going to come in His glory and will reward people.\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 24:14} - And this gospel of the kingdom will be proclaimed throughout the whole world as a testimony to all nations, and then the end will come. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
When the Gospel has been preached to all nations in the whole world. & The end (eschaton) will come.\\[0pt]
\end{tabular}
\end{center}

\textbf{Matthew 24:45-47} - Who then is the faithful and wise servant, whom his master has set over his household, to give them their food at the proper time? Blessed is that servant whom his master will find so doing when he comes. Truly, I say to you, he will set him over all his possessions. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If that person is faithful and wise in charge of the "little things". & God will make a person ruler over all that is His (His possessions).\\[0pt]
\end{tabular}
\end{center}

\textbf{Mark 9:41} - For truly, I say to you, whoever gives you a cup of water to drink because you belong to Christ will by no means lose his reward. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Giving a cup of water (being charitable) in Christ's name for the exact reason that we belong to Christ. & A person will not lose their reward.\\[0pt]
\end{tabular}
\end{center}

\textbf{John 3:16} - For God so loved the world, that he gave his only Son, that whoever believes in him should not perish but have eternal life. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
To whosoever will believe that God sent His only begotten son to die in our place as a sin offering. & You will have eternal life\\[0pt]
\end{tabular}
\end{center}

Stress: Trust in God.

\textbf{Romans 8:31} - What then shall we say to these things? If God is for us, who can be against us? (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
When God is for you. & No one can be against you.\\[0pt]
\end{tabular}
\end{center}

\textbf{Philippians 3:21} - who will transform our lowly body to be like his glorious body, by the power that enables him even to subject all things to himself. (ESV)

\textbf{Philippians 4:1} - Therefore, my brothers, whom I love and long for, my joy and crown, stand firm thus in the Lord, my beloved. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
We must stand firm in the Lord (4:1) & Jesus will transform our current perishing bodies in exchange for a body that does not perish like His glorious body (Resurrection body) (3:21).\\[0pt]
\end{tabular}
\end{center}

\textbf{Philippians 4:13} - I can do all things through him who strengthens me. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If Christ strengthens us. & We can do all things.\\[0pt]
\end{tabular}
\end{center}

\textbf{Colossians 3:1-4} - If then you have been raised with Christ, seek the things that are above, where Christ is, seated at the right hand of God. Set your minds on things that are above, not on things that are on earth. For you have died, and your life is hidden with Christ in God. When Christ who is your life appears, then you also will appear with him in glory. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If we too are risen or raised up in Christ, and seeking the things above. & When Christ appears at the second coming, we will appear with Him in glory.\\[0pt]
\end{tabular}
\end{center}

\textbf{1 Thessalonians 4:14-17} - For since we believe that Jesus died and rose again, even so, through Jesus, God will bring with him those who have fallen asleep. For this we declare to you by a word from the Lord, that we who are alive, who are left until the coming of the Lord, will not precede those who have fallen asleep. For the Lord himself will descend from heaven with a cry of command, with the voice of an archangel, and with the sound of the trumpet of God. And the dead in Christ will rise first. Then we who are alive, who are left, will be caught up together with them in the clouds to meet the Lord in the air, and so we will always be with the Lord. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
We need to believe that Jesus died and rose again. & The dead in Christ will rise first, then we who are still alive will be called up together with them in the clouds to meet the Lord in the air. We will then be with the Lord forever after that.\\[0pt]
\end{tabular}
\end{center}

\textbf{1 Timothy 4:1-8} - Now the Spirit expressly says that in later times some will depart from the faith by devoting themselves to deceitful spirits and teachings of demons, through the insincerity of liars whose consciences are seared, who forbid marriage and require abstinence from foods that God created to be received with thanksgiving by those who believe and know the truth. For everything created by God is good, and nothing is to be rejected if it is received with thanksgiving, for it is made holy by the word of God and prayer. If you put these things before the brothers, you will be a good servant of Christ Jesus, being trained in the words of the faith and of the good doctrine that you have followed. Have nothing to do with irreverent, silly myths. Rather train yourself for godliness; for while bodily training is of some value, godliness is of value in every way, as it holds promise for the present life and also for the life to come. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Those awarded will have loved His appearing and faithfully preach the Gospel and the Word of God in season and out of season. & There is a crown of righteousness laid up for us by God which I will be awarded with on my day of glory.\\[0pt]
\end{tabular}
\end{center}

\textbf{Hebrews 12:28} - Therefore let us be grateful for receiving a kingdom that cannot be shaken, and thus let us offer to God acceptable worship, with reverence and awe, (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If we serve Him with reverence and fear. & We will serve God acceptably.\\[0pt]
\end{tabular}
\end{center}

\textbf{James 1:5-6} - If any of you lacks wisdom, let him ask God, who gives generously to all without reproach, and it will be given him. But let him ask in faith, with no doubting, for the one who doubts is like a wave of the sea that is driven and tossed by the wind. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Wisdom will be given. & If you ask of God in faith.\\[0pt]
\end{tabular}
\end{center}

\textbf{James 1:12} - Blessed is the man who remains steadfast under trial, for when he has stood the test he will receive the crown of life, which God has promised to those who love him. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If we endure trials by temptation and love the Lord. & We will receive the crown of life\\[0pt]
\end{tabular}
\end{center}

\textbf{1 Peter 5:1-4} - So I exhort the elders among you, as a fellow elder and a witness of the sufferings of Christ, as well as a partaker in the glory that is going to be revealed: shepherd the flock of God that is among you, exercising oversight, not under compulsion, but willingly, as God would have you; not for shameful gain, but eagerly; not domineering over those in your charge, but being examples to the flock. And when the chief Shepherd appears, you will receive the unfading crown of glory. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If they feed the flock God has given them, by taking the oversight of the flock willingly and not for money (blood money). Thereby setting an example for said flock. & Elders will receive a crown of glory that will not fade.\\[0pt]
\end{tabular}
\end{center}

\textbf{1 John 3:2} - Beloved, we are God's children now, and what we will be has not yet appeared; but we know that when he appears we shall be like him, because we shall see him as he is. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If we are children of God & When Jesus appears we will be like Him\\[0pt]
\end{tabular}
\end{center}

\textbf{1 John 3:9} - No one born of God makes a practice of sinning, for God's seed abides in him, and he cannot keep on sinning because he has been born of God. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If/because we have been born of God & A Christian cannot habitually sin without feeling horrible and wishing to repentant of it.\\[0pt]
\end{tabular}
\end{center}

\textbf{2 John 1:7-8} - For many deceivers have gone out into the world, those who do not confess the coming of Jesus Christ in the flesh. Such a one is the deceiver and the antichrist. Watch yourselves, so that you may not lose what we have worked for, but may win a full reward. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If we acknowledge that Jesus has indeed come in the flesh (incarnate). & We will receive our full reward from God.\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 2:7} - He who has an ear, let him hear what the Spirit says to the churches. To the one who conquers I will grant to eat of the tree of life, which is in the paradise of God. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If we persevere over evil and endure for Christ's namesake and overcome (persecution and trials) & We will be allowed to eat from the Tree of Life which is in the paradise of God\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 2:10} - Do not fear what you are about to suffer. Behold, the devil is about to throw some of you into prison, that you may be tested, and for ten days you will have tribulation. Be faithful unto death, and I will give you the crown of life. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Do not fear and are faithful to the point of death. & Jesus Himself will give you a crown of life.\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 2:11} - He who has an ear, let him hear what the Spirit says to the churches. The one who conquers will not be hurt by the second death. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If they overcome persecution and trials & People will not be hurt by the second death which is damnation in the Lake of Fire\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 2:17} - He who has an ear, let him hear what the Spirit says to the churches. To the one who conquers I will give some of the hidden manna, and I will give him a white stone, with a new name written on the stone that no one knows except the one who receives it. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
If people overcome persecution and trials & Jesus will allow people to eat of the hidden Manna and will give a white stone with a new name written on it that only the one that receives it will know.\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 2:23} - and I will strike her children dead. And all the churches will know that I am he who searches mind and heart, and I will give to each of you as your works deserve. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
According to their works. & Jesus will give to every one.\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 2:26-28} - The one who conquers and who keeps my works until the end, to him I will give authority over the nations, and he will rule them with a rod of iron, as when earthen pots are broken in pieces, even as I myself have received authority from my Father. And I will give him the morning star. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
To those that overcome and keep Jesus' works until the bitter end & Jesus will give power over the nations and will give the morning star\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 3:21} - The one who conquers, I will grant him to sit with me on my throne, as I also conquered and sat down with my Father on his throne. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
To those that overcome persecution and trials. & Jesus will allow people to sit with Him on His throne\\[0pt]
\end{tabular}
\end{center}

\textbf{Revelation 20:4} - Then I saw thrones, and seated on them were those to whom the authority to judge was committed. Also I saw the souls of those who had been beheaded for the testimony of Jesus and for the word of God, and who had not worshiped the beast or its image and had not received its mark on their foreheads or their hands. They came to life and reigned with Christ for a thousand years. (ESV)

\begin{center}
\begin{tabular}{ll}
Condition & Promise\\[0pt]
\hline
Those that did not worship the beast, nor his image, nor received his mark (666) & Some will live and reign with Christ for 1000 years.\\[0pt]
\end{tabular}
\end{center}

\subsection{Body without spirit is dead. But I think the spirit without the body is still alive}
\label{sec:orgeb4ba0c}
\textbf{James 2:26} - For as the body apart from the spirit is dead, so also faith apart from works is dead.

\textbf{Matthew 22:32} - I am the God of Abraham, and the God of Isaac, and the God of Jacob? He is not God of the dead, but of the living.

\textbf{Mark 12:27} - He is not God of the dead, but of the living. You are quite wrong.

\textbf{Luke 20:38} - Now he is not God of the dead, but of the living, for all live to him.

Yet we await an imperishable body.

\subsection{Forgiveness and ongoing sin}
\label{sec:org1905a5b}
\textbf{I Corinthians 9:25-27} - Every athlete exercises self-control in all things. They do it to receive a perishable wreath, but we an imperishable. So I do not run aimlessly; I do not box as one beating the air. But I discipline my body and keep it under control, \textbf{lest after preaching to others I myself should be disqualified}.

\subsubsection{New covenant}
\label{sec:org20e6d5d}
\textbf{Jeremiah 31:31-34} - Behold, the days are coming, declares the LORD, when I will make a new covenant with the house of Israel and the house of Judah, not like the covenant that I made with their fathers on the day when I took them by the hand to bring them out of the land of Egypt, my covenant that they broke, though I was their husband, declares the LORD. But this is the covenant that I will make with the house of Israel after those days, declares the LORD: I will put my law within them, and I will write it on their hearts. And I will be their God, and they shall be my people. And no longer shall each one teach his neighbor and each his brother, saying, Know the LORD, for they shall all know me, from the least of them to the greatest, declares the LORD. For I will forgive their iniquity, and I will remember their sin no more. (ESV)

I'm confident that God gives a person a new life in Christ Jesus, where God has totally forgiven their past sin,
but expects them to turn a new leaf and turn away from sin.

\textbf{1 Peter 1:18-20} - knowing that you were ransomed from the futile ways inherited from your forefathers, not with perishable things such as silver or gold, but with the precious blood of Christ, like that of a lamb without blemish or spot. He was foreknown before the foundation of the world but was made manifest in the last times for your sake, (ESV)

We \textbf{must} have faith in Jesus for the righteousness of God that comes by faith.

\textbf{Romans 10:4} - For Christ is the end of the law for righteousness to everyone who believes.

Jesus is our High Priest
\begin{itemize}
\item \textbf{Romans 8:1} - There is therefore now no condemnation for those who are in Christ Jesus.
\item \textbf{Romans 8:3-4} - For God has done what the law, weakened by the flesh, could not do. By sending his own Son in the likeness of sinful flesh and for sin, he condemned sin in the flesh, \textbf{in order that the righteous requirement of the law might be fulfilled in us}, who walk not according to the flesh but according to the Spirit.
\end{itemize}

Jesus condemned sin in the flesh. Now we walk according to the spirit so that the righteous requirement of the law might be fulfilled in us.
It's still really important to put a stop to sin!

\subsubsection{We must stop sinning after receiving the 'big forgiveness' for past sin}
\label{sec:orgc493286}
\textbf{Matthew 12:33} - Either make the tree good and its fruit good, or make the tree bad and its fruit bad, for the tree is known by its fruit.

\textbf{Hebrews 10:26-31} - For if we go on sinning deliberately after receiving the knowledge of the truth, there no longer remains a sacrifice for sins, but a fearful expectation of judgment, and a fury of fire that will consume the adversaries. Anyone who has set aside the law of Moses dies without mercy on the evidence of two or three witnesses. How much worse punishment, do you think, will be deserved by the one who has spurned the Son of God, and has profaned the blood of the covenant by which he was sanctified, and has outraged the Spirit of grace? For we know him who said, Vengeance is mine; I will repay. And again, The Lord will judge his people. It is a fearful thing to fall into the hands of the living God. (ESV)

The big forgiveness, and that we must stop sinning to be provided an entrance into the eternal kingdom of our Lord and Saviour Jesus Christ:

\textbf{II Peter 1:1-11} - Simeon Peter, a servant and apostle of Jesus Christ, To those who have obtained a faith of equal standing with ours by the righteousness of our God and Savior Jesus Christ: May grace and peace be multiplied to you in the knowledge of God and of Jesus our Lord.  His divine power has granted to us all things that pertain to life and godliness, through the knowledge of him who called us to his own glory and excellence, by which he has granted to us his precious and very great promises, so that through them you may become partakers of the divine nature, having escaped from the corruption that is in the world because of sinful desire.  For this very reason, make every effort to supplement your faith with virtue, and virtue with knowledge, and knowledge with self-control, and self-control with steadfastness, and steadfastness with godliness, and godliness with brotherly affection, and brotherly affection with love.  For if these qualities are yours and are increasing, they keep you from being ineffective or unfruitful in the knowledge of our Lord Jesus Christ.  For whoever lacks these qualities is so nearsighted that he is blind, having forgotten that he was cleansed from his former sins.  Therefore, brothers, be all the more diligent to make your calling and election sure, for if you practice these qualities you will never fall.  For in this way \uline{there will be richly provided for you an entrance into the eternal kingdom of our Lord and Savior Jesus Christ}.

We \textbf{must} stop sinning after the big forgiveness:

\textbf{II Peter 2:20-22} - For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first. For it would have been better for them never to have known the way of righteousness than after knowing it to turn back from the holy commandment delivered to them. What the true proverb says has happened to them: The dog returns to its own vomit, and the sow, after washing herself, returns to wallow in the mire.

\subsubsection{We totally \textbf{should} stop sinning, since we await a place without sinning}
\label{sec:org3082371}

\textbf{II Peter 3:13-14} - But according to his promise we are waiting for new heavens and a new earth in which righteousness dwells. Therefore, beloved, since you are waiting for these, be diligent to be found by him without spot or blemish, and at peace.

\begin{itemize}
\item \textbf{Mark 10:19} - You know the commandments: Do not murder, Do not commit adultery, Do not steal, Do not bear false witness, Do not defraud, Honor your father and mother. (ESV)
\item \textbf{1 John 3:4-9} - Everyone who makes a practice of sinning also practices lawlessness; sin is lawlessness.  You know that he appeared to take away sins, and in him there is no sin.  No one who abides in him keeps on sinning; no one who keeps on sinning has either seen him or known him.  Little children, let no one deceive you.  Whoever practices righteousness is righteous, as he is righteous.  Whoever makes a practice of sinning is of the devil, for the devil has been sinning from the beginning.  The reason the Son of God appeared was to destroy the works of the devil.  No one born of God makes a practice of sinning, for God's seed abides in him, and he cannot keep on sinning because he has been born of God.  (ESV)
\end{itemize}

If Israel had pursued the Mosaic law by faith they would have reached the righteousness of God.

\begin{itemize}
\item \textbf{Romans 9:30-32} - What shall we say, then? That Gentiles who did not pursue righteousness have attained it, that is, a righteousness that is by faith; but that Israel who pursued a law that would lead to righteousness did not succeed in reaching that law.  Why? \textbf{Because they did not pursue it by faith}, but as if it were based on works. They have stumbled over the stumbling stone,
\end{itemize}

This is prophetic - the attitude we are called to is the same today as it was back then:

\textbf{Deuteronomy 10:12-15} - And now, Israel, what does the Lord your God require of you, but to fear the Lord your God, to walk in all his ways, to love him, to serve the Lord your God with all your heart and with all your soul, and to keep the commandments and statutes of the Lord, which I am commanding you today for your good? Behold, to the Lord your God belong heaven and the heaven of heavens, the earth with all that is in it. Yet the Lord set his heart in love on your fathers and chose their offspring after them, you above all peoples, as you are this day.

Circumcise your heart and do not be stubborn:

\textbf{Deuteronomy 10:16-17} - Circumcise therefore the foreskin of your heart, and be no longer stubborn. For the Lord your God is God of gods and Lord of lords, the great, the mighty, and the awesome God, who is not partial and takes no bribe.

\subsubsection{The 'all time' means we can still approach Jesus for forgiveness for future sins}
\label{sec:orga6abf38}
\textbf{Hebrews 10:12} - But when Christ had offered for all time a single sacrifice for sins, he sat down at the right hand of God,

\textbf{Hebrews 10:14} - For by a single offering he has perfected for all time those who are being sanctified.

\textbf{Hebrews 4:16} - Let us then with confidence draw near to the throne of grace, that we may receive mercy and find grace to help in time of need.

\subsubsection{If we sin}
\label{sec:org2ffb7b9}
\textbf{1 John 1:9} -  If we confess our sins, he is faithful and just to forgive us our sins and to cleanse us from all unrighteousness.  (ESV)

\textbf{1 Peter 4:8} -  Above all, keep loving one another earnestly, since love covers a multitude of sins.  (ESV)

\section{Personally judging sin}
\label{sec:orgca99185}
\subsection{We should always discern what is right on our own initiative}
\label{sec:orge81696c}
\textbf{Luke 12:57} - "And why do you not even on your own initiative judge what is right?"

\subsection{We should be examining, judging, cleaning ourselves up, taking a look in the mirror first}
\label{sec:org3856486}
Judge yourself first (by God's standards) before judging others.

Clean yourself up first before the Lord judges you (in this world) - the Lord judges a believer while this world to discipline them and clean them up before final judgement.
I know this is talking specifically about taking communion, but I believe it applies also at the macroscopic level.

\textbf{I Corinthians 11:28-32} - But a man must examine himself, and in so doing he is to eat of the bread and drink of the cup.  For he who eats and drinks, eats and drinks judgment to himself if he does not judge the body rightly.  For this reason many among you are weak and sick, and a number sleep.  But if we judged ourselves rightly, we would not be judged.  But when we are judged, we are disciplined by the Lord so that we will not be condemned along with the world.

God looks at the heart:

\textbf{II Corinthians 5:10-12} - For we must all appear before the judgment seat of Christ, so that each one may receive what is due for what he has done in the body, whether good or evil. Therefore, knowing the fear of the Lord, we persuade others. But what we are is known to God, and I hope it is known also to your conscience. We are not commending ourselves to you again but giving you cause to boast about us, so that you may be able to answer those who boast about outward appearance and not about \uline{what is in the heart}.

Make yourself ready \uline{imminently}:

\textbf{Matthew 24:42-44} - Therefore, stay awake, for you do not know on what day your Lord is coming. But know this, that if the master of the house had known in what part of the night the thief was coming, he would have stayed awake and would not have let his house be broken into. Therefore you also must be ready, for the Son of Man is coming at an hour you do not expect. (ESV)

\textbf{Matthew 7:3} - Why do you see the speck that is in your brother's eye, but do not notice the log that is in your own eye?  Or how can you say to your brother, Let me take the speck out of your eye, when there is the log in your own eye?  You hypocrite, first take the log out of your own eye, and then you will see clearly to take the speck out of your brother's eye.

\textbf{II Corinthians 7:1} - Therefore, having these promises, beloved, let us cleanse ourselves (G1438 heautou) from all (G3956 pas) defilement of flesh (G4561 sarx) and spirit (G4151 pneuma), perfecting holiness in the fear of God (G2316 theos).

\textbf{Revelation of John 22:14} - Blessed are those who wash their robes, so that they may have the right to the tree of life and that they may enter the city by the gates. (ESV)

I hold myself accountable to the standard which I subscribe to.

\textbf{I Corinthians 9:27} - But I discipline my body and keep it under control, lest after preaching to others I myself should be disqualified.

I try to keep the 10 commandments by faith.
I observe the Mosaic law, and try to keep parts of it by faith, particularly
on the topic of sexual morality, body markings, etc.

\subsection{It is necessary sometimes to judge others, but do it properly}
\label{sec:org11c5a56}
\textbf{John 7:24} - Do not judge by appearances, but judge with right judgment.

\textbf{Matthew 7:1} - Judge not, that you be not judged.  For with the judgment you pronounce you will be judged, and with the measure you use it will be measured to you.

I don't hold others accountable to the same standard that I hold myself to.

For Gentile believers I'm with the Apostles on the following:

\textbf{Acts 15:28-29} - For it has seemed good to the Holy Spirit and to us to lay on you no greater burden than these requirements: that you abstain from what has been sacrificed to idols, and from blood, and from what has been strangled, and from sexual immorality. If you keep yourselves from these, you will do well. Farewell.

But I also would add that one should not bear false-witness or worship idols.

\subsubsection{Here we go}
\label{sec:org8c6edc6}
\textbf{I Corinthians 10:14-20} - Therefore, my beloved, flee from idolatry.  I speak as to sensible people; judge for yourselves what I say.  The cup of blessing that we bless, is it not a participation in the blood of Christ? The bread that we break, is it not a participation in the body of Christ?  Because there is one bread, we who are many are one body, for we all partake of the one bread.  Consider the people of Israel: are not those who eat the sacrifices participants in the altar?  What do I imply then? That food offered to idols is anything, or that an idol is anything?  No, I imply that what pagans sacrifice they offer to demons and not to God. I do not want you to be participants with demons.

\subsection{I repent from being liberal and ever endorsing LGBT or idolatry}
\label{sec:org97b9fa0}
At first, to not judge that others wear
clothes of the opposite sex seemed mostly
harmless to me, but I feel like endorsing
sinful, erroneous things, or annulling laws
is not helpful in liberating people from sin.

\subsubsection{Endorsing sinful things endorses people to become enslaved by sin / stuck in falsehood}
\label{sec:org1fd11d1}
Also, I feel as though endorsing it is in a
way similar to endorsing that people commit
adultery, in that it gets people stuck in sin,
even without the awareness they are in sin,
and makes it harder for people to find God.

I feel like getting a person unstuck from sin
is a bit like freeing an animal in that they
are often not aware that they need freeing.

\url{https://www.youtube.com/watch?v=hbB2K7YP4zE\&ab\_channel=DustinZornig}

\subsubsection{Endorsing sinful behavior welcomes demons}
\label{sec:orgc07b592}
Also, I believe that endorsing sinful behavior
or annulling God's law allows people who do
such things to come into one's life and
situation - a bit like putting holes in a
boat, or lowering the drawbridge to a castle.

It's spiritual, so I think it may actually
welcome demons into a person's life to endorse
sinful things.

\textbf{Deuteronomy 7:26} - And you shall not bring an abominable thing into your house and become devoted to destruction like it. You shall utterly detest and abhor it, for \uline{it is devoted to destruction}.  (ESV)

\subsubsection{Personal holiness}
\label{sec:orgf4ae071}
\textbf{I Corinthians 9:27} - But I discipline my body and keep it under control, lest after preaching to others I myself should be disqualified.

Well, I repent of endorsing sinful things,
which are explicitly mentioned in old
testament law, such as transvestisim.

I no longer think that in order to be compassionate I must say "I do not judge."
But if someone were to ask me if I think it is sinful, I would say, "I believe it is sinful."

I pursue personal holiness for myself, and I
think deliberate lawbreaking is wrong,
but I stress I am not \textbf{under} the Mosaic law.

I'm under the law of faith in Christ and I believe
LGBT and transvestism are sinful.

\textbf{Deuteronomy 22:5} - A woman shall not wear a man's garment, nor shall a man put on a woman's cloak, for whoever does these things is an abomination to the LORD your God. (ESV)

\section{The law of liberty}
\label{sec:org65e58b9}
\textbf{James 1:25} - But one who looks intently at the perfect law, the law of liberty, and abides by it, not having become a forgetful hearer but an effectual doer, this man will be blessed in what he does.

\textbf{James 2:11-13} - For he who said, Do not commit adultery, also said, Do not murder. If you do not commit adultery but do murder, you have become a transgressor of the law.  So speak and so act as those who are to be judged under the law of liberty.  For judgment is without mercy to one who has shown no mercy. Mercy triumphs over judgment.

\subsection{Submitting to God is submitting to Christ}
\label{sec:org3cad4a8}
\textbf{Psalms 81:11} - But my people did not listen to my voice; Israel would not submit to me.

\textbf{James 4:7} - Submit yourselves therefore to God. Resist the devil, and he will flee from you.

\textbf{Ephesians 5:23} - For the husband is the head of the wife even as Christ is the head of the church, his body, and is himself its Savior.

\textbf{I Corinthians 11:3} - But I want you to understand that the head of every man is Christ, the head of a wife is her husband, and the head of Christ is God. (ESV)

\subsection{The freedom Christ gives us involves obeying Christ}
\label{sec:orgbee9e94}

Obeying Jesus, even Jesus' commandments, is actually freedom. To disobey Jesus is to submit to slavery.

\textbf{Galatians 5:1} - For freedom Christ has set us free; stand firm therefore, and do not submit again to a yoke of slavery.

\textbf{Ephesians 5:24} - Now as the church submits to Christ, so also wives should submit in everything to their husbands.

\textbf{Romans 8:21} - that the creation itself will be set free from its bondage to decay and obtain the freedom of the glory of the children of God.

\textbf{II Corinthians 3:17} - Now the Lord is the Spirit, and where the Spirit of the Lord is, there is freedom.

\textbf{John 6:63} - It is the Spirit who gives life; the flesh is of no avail. The words that I have spoken to you are spirit and life.

Don't think that obeying Jesus is submitting to slavery.

We are bondservants of Christ and it is freedom.

\textbf{Romans 1:1} - Paul, a servant of Christ Jesus, called to be an apostle, set apart for the gospel of God,

\subsection{We are no longer 'under' the Mosaic Law but we have freedom as we are led by the Spirit}
\label{sec:org96b01a5}

\textbf{Galatians 2:3-5} - But not even Titus, who was with me, though he was a Greek, was compelled to be circumcised. But it was because of the false brethren secretly brought in, who had sneaked in to spy out our liberty which we have in Christ Jesus, in order to bring us into bondage. But we did not yield in subjection to them for even an hour, so that the truth of the gospel would remain with you.

\textbf{If} you are led by the Spirit, you are not under the Law.
If you are disobedient to God then you are under the Law.

\textbf{Galatians 5:18} - But if you are led by the Spirit, you are not under the Law.

\textbf{I Peter 2:16} - Live as people who are free, not using your freedom as a cover-up for evil, but living as servants of God.

\textbf{Galatians 5:1} - For freedom Christ has set us free; stand firm therefore, and do not submit again to a yoke of slavery.

\textbf{Galatians 5:13} - For you were called to freedom, brothers. Only do not use your freedom as an opportunity for the flesh, but through love serve one another.

\textbf{II Peter 2:19} - They promise them freedom, but they themselves are slaves of corruption. For whatever overcomes a person, to that he is enslaved.

\subsection{Submitting to God's righteousness involves obeying Jesus because Jesus is God's righteousness}
\label{sec:org856664e}

\textbf{Romans 10:3} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness.

\section{Both God the Father and God the Son raise the dead}
\label{sec:org1434696}
Both the Father and the Son give life to whom they will.

\textbf{John 5:21} - For as the Father raises the dead and gives them life, so also the Son gives life to whom he will. (ESV)

\textbf{John 10:28} - I give them eternal life, and they will never perish, and no one will snatch them out of my hand.

God gives life.

\textbf{Deuteronomy 32:39} - See now that I, even I, am he, and there is no god beside me; I kill and I make alive; I wound and I heal; and there is none that can deliver out of my hand. (ESV)

\textbf{John 10:29} - My Father, who has given them to me, is greater than all, and no one is able to snatch them out of the Father's hand.

God the Father and God the Son are one.

\textbf{John 10:30} - I and the Father are one.

God the Father raised this child from the dead:

\textbf{I Kings 17:21-22} - Then he stretched himself upon the child three times and cried to the Lord, O Lord my God, let this child's life come into him again. And the Lord listened to the voice of Elijah. And the life of the child came into him again, and he revived.

God the Father raised this child from the dead too:

\textbf{2 Kings 4:32-35} -  When Elisha came into the house, he saw the child lying dead on his bed.  So he went in and shut the door behind the two of them and prayed to the LORD.  Then he went up and lay on the child, putting his mouth on his mouth, his eyes on his eyes, and his hands on his hands.  And as he stretched himself upon him, the flesh of the child became warm.  Then he got up again and walked once back and forth in the house, and went up and stretched himself upon him. The child sneezed seven times, and the child opened his eyes.  (ESV)

God the Father raised Jesus from the dead:

\textbf{Romans 8:11} - If the Spirit of him who raised Jesus from the dead dwells in you, he who raised Christ Jesus from the dead will also give life to your mortal bodies through his Spirit who dwells in you. (ESV)

God gave authority to Jesus to raise the dead:

\textbf{John 17:2} - since you have given him authority over all flesh, to give eternal life to all whom you have given him. (ESV)

Jesus raises people from the dead:

\textbf{John 11:25} - Jesus said to her, I am the resurrection and the life. Whoever believes in me, though he die, yet shall he live, (ESV)

\textbf{Luke 7:13-15} - And when the Lord saw her, he had compassion on her and said to her, Do not weep. Then he came up and touched the bier, and the bearers stood still. And he said, Young man, I say to you, arise. And the dead man sat up and began to speak, and Jesus gave him to his mother.

People recognised Jesus as a great prophet like Elijah or Elisha

\textbf{Luke 7:16} - Fear seized them all, and they glorified God, saying, A great prophet has arisen among us! and God has visited his people!

Jesus was doing the works of Father God:

\textbf{John 10:37-38} - If I am not doing the works of my Father, then do not believe me; but if I do them, even though you do not believe me, believe the works, that you may know and understand that the Father is in me and I am in the Father.

Who can question it?

\textbf{Acts 26:8} -  Why is it thought incredible by any of you that God raises the dead?  (ESV)

\subsection{Leaving the tomb / spiritual prison which was a result of disobedience}
\label{sec:orgdb6ea46}
This is really interesting.

\textbf{Romans 6:8-9} - Now if we have died with Christ, we believe that we will also live with him. We know that Christ being raised from the dead will never die again; death no longer has dominion over him.

\textbf{John 5:25} - Truly, truly, I say to you, an hour is coming and now is, when the dead will hear the voice of the Son of God, and those who hear will live. (ESV)

Jesus as a life-giving spirit proclaimed to the spirits in prison.

Baptism is an appeal to God for a good conscience - It's an \textbf{appeal} to God but not strictly required to be saved.
It is an appeal to God for a good conscience, through the resurrection of Jesus Christ.
I definitely believe that "believer's baptism" is the right way to perform baptism.
Baptism does save.

\textbf{I Peter 3:18-21} - For Christ also suffered once for sins, the righteous for the unrighteous, that he might bring us to God, being put to \textbf{death in the flesh but made alive in the spirit}, in which he went and proclaimed to the spirits in prison, because \textbf{they formerly did not obey}, when God's patience waited in the days of Noah, while the ark was being prepared, in which a few, that is, eight persons, were brought safely through water. Baptism, which corresponds to this, now saves you, not as a removal of dirt from the body but as an appeal to God for a good conscience, through the resurrection of Jesus Christ,

This sounds interesting:

\textbf{John 5:28-29} - Do not marvel at this, for an hour is coming when all who are in the tombs will hear his voice and come out, those who have done good to the resurrection of life, and those who have done evil to the resurrection of judgment.

It's totally worth following Jesus, doing good and proclaiming the gospel after getting born-again - following Jesus, even faithfully stopping sin, is the correct response,
for if being born-again is dying with Christ, and being given life by the life giving Spirit of Jesus,
we are partaking in the death and resurrection of Jesus, where Jesus had actually suffered for sins, the righteous for the unrighteous, so we too should continue living in a way that is turning away from sin.

\textbf{Galatians 6:7-8} - Do not be deceived: God is not mocked, for whatever one sows, that will he also reap. For the one who sows to his own flesh will from the flesh reap corruption, but the one who sows to the Spirit will from the Spirit reap eternal life. (ESV)

Spiritually died with Christ:

\textbf{Colossians 2:20} - If with Christ you died to the elemental spirits of the world, why, as if you were still alive in the world, do you submit to regulations—

Spiritually raised with Christ:

\textbf{Colossians 3:1} - If then you have been raised with Christ, seek the things that are above, where Christ is, seated at the right hand of God.

OK, so spiritually resurrected and raised. Now we wait for the resurrection of the body.

Things make a bit more sense now:

\textbf{Matthew 19:16-26} - And behold, a man came up to him, saying, Teacher, what good deed must I do to have eternal life? And he said to him, Why do you ask me about what is good? There is only one who is good. If you would enter life, keep the commandments. He said to him, Which ones? And Jesus said, You shall not murder, You shall not commit adultery, You shall not steal, You shall not bear false witness, Honor your father and mother, and, You shall love your neighbor as yourself. The young man said to him, All these I have kept. What do I still lack? Jesus said to him, If you would be perfect, go, sell what you possess and give to the poor, and you will have treasure in heaven; and come, follow me. When the young man heard this he went away sorrowful, for he had great possessions. And Jesus said to his disciples, Truly, I say to you, only with difficulty will a rich person enter the kingdom of heaven. Again I tell you, it is easier for a camel to go through the eye of a needle than for a rich person to enter the kingdom of God. When the disciples heard this, they were greatly astonished, saying, Who then can be saved? But Jesus looked at them and said, With man this is impossible, but with God all things are possible.

Jesus is the Saviour of the world.

\textbf{I John 4:14} - And we have seen and testify that the Father has sent his Son to be the Savior of the world.

\textbf{Isaiah 43:10-11} - You are my witnesses, declares the Lord, and my servant whom I have chosen, that you may know and believe me and understand that I am he. Before me no god was formed, nor shall there be any after me. I, I am the Lord, and besides me there is no savior.

God saves through Jesus. 

\textbf{Jude 1:25} - to the only God, our Savior, through Jesus Christ our Lord, be glory, majesty, dominion, and authority, before all time and now and forever. Amen.

\textbf{Titus 1:1-3} - Paul, a servant of God and an apostle of Jesus Christ, for the sake of the faith of God's elect and their knowledge of the truth, which accords with godliness, in hope of eternal life, which God, who never lies, promised before the ages began and at the proper time manifested in his word through the preaching with which I have been entrusted by the command of God our Savior;

\textbf{John 5:43} - I have come in my Father's name, and you do not receive me. If another comes in his own name, you will receive him.

\textbf{John 10:25} - Jesus answered them, I told you, and you do not believe. The works that I do in my Father's name bear witness about me,

\textbf{Titus 3:4-7} - But when the goodness and loving kindness of God our Savior appeared, he saved us, not because of works done by us in righteousness, but according to his own mercy, by the washing of regeneration and renewal of the Holy Spirit, whom he poured out on us richly through Jesus Christ our Savior, so that being justified by his grace we might become heirs according to the hope of eternal life.

\textbf{I Peter 3:19} - in which also He went and made proclamation to the spirits now in prison,

\textbf{Romans 8:10} - If Christ is in you, though the body is dead because of sin, yet the spirit is alive because of righteousness.

That was a total gift. Thanks Jesus!

So in this life we can know that we will partake in the resurrection at the second coming.

\section{The resurrection at the second coming}
\label{sec:org3cd7872}
\textbf{Hebrews 9:27-28} - And just as it is appointed for man to die once, and after that comes judgment, so Christ, having been offered once to bear the sins of many, will appear a second time, not to deal with sin but to save those who are eagerly waiting for him.

\subsection{So don't be in Adam, but be in Christ, because all in Christ will be made alive, but all in Adam will be destroyed}
\label{sec:orgef5e473}
\begin{enumerate}
\item Christ the firstfruits, then
\item \uline{at his coming} those who belong to Christ.
\end{enumerate}

\textbf{I Corinthians 15:20-26} - But in fact Christ has been raised from the dead, the firstfruits of those who have fallen asleep.  For as by a man came death, by a man has come also the resurrection of the dead.  For as in Adam all die, so also \textbf{in Christ shall all be made alive}.  But each in his own order: Christ the firstfruits, then \textbf{at his coming} those who belong to Christ.  Then comes the end, when he delivers the kingdom to God the Father after destroying every rule and every authority and power.  For he must reign until he has put all his enemies under his feet.  The last enemy to be destroyed is death.

\subsection{What it looks like}
\label{sec:org5d6339d}
Our heavenly inheritance is imperishable!

\textbf{1 Peter 1:4} -  to an inheritance that is imperishable, undefiled, and unfading, kept in heaven for you,  (ESV)

\subsubsection{The resurrection of the just}
\label{sec:org1850dff}
\begin{itemize}
\item \textbf{Luke 14:12-14} - He said also to the man who had invited him, When you give a dinner or a banquet, do not invite your friends or your brothers or your relatives or rich neighbors, lest they also invite you in return and you be repaid. But when you give a feast, invite the poor, the crippled, the lame, the blind, and you will be blessed, because they cannot repay you. You will be repaid at the resurrection of the just. (ESV)
\end{itemize}

\subsubsection{The natural first, then the spiritual}
\label{sec:orgc60aad8}
We may die a natural death in this life but be raised at the second coming with an incorruptible body.

\textbf{I Corinthians 15:42-48} - So is it with the resurrection of the dead. What is sown is perishable; what is raised is imperishable.  It is sown in dishonor; it is raised in glory. It is sown in weakness; it is raised in power.  It is sown a natural body; it is raised a spiritual body. If there is a natural body, there is also a spiritual body.  Thus it is written, The first man Adam became a living being; the last Adam became a life-giving spirit.  But it is not the spiritual that is first but the natural, and then the spiritual.  The first man was from the earth, a man of dust; the second man is from heaven.  As was the man of dust, so also are those who are of the dust, and as is the man of heaven, so also are those who are of heaven.

\textbf{Philippians 3:21} -  who will transform our lowly body to be like his glorious body, by the power that enables him even to subject all things to himself.  (ESV)

\textbf{1 Corinthians 15:49} -  Just as we have borne the image of the man of dust, we shall also bear the image of the man of heaven.  (ESV)

\subsubsection{This - we are made like the man of heaven}
\label{sec:org9be5bf6}
\textbf{I Corinthians 15:49} - Just as we have borne the image of the man of dust, we shall also bear the image of the man of heaven.

AMEN!!

And then it's possible to inherit the imperishable:

\textbf{I Corinthians 15:50} - I tell you this, brothers: flesh and blood cannot inherit the kingdom of God, nor does the perishable inherit the imperishable.

\textbf{I Corinthians 15:51-54} - Behold! I tell you a mystery. We shall not all sleep, but we shall all be changed, in a moment, in the twinkling of an eye, at the last trumpet. For the trumpet will sound, and the dead will be raised imperishable, and we shall be changed.

\subsubsection{The mortal puts on immortality (at the resurrection)}
\label{sec:org5875079}
\textbf{I Corinthians 15:53} - For this perishable body must put on the imperishable, and this mortal body must put on immortality. When the perishable puts on the imperishable, and the mortal puts on immortality, then shall come to pass the saying that is written: Death is swallowed up in victory.

\textbf{Isaiah 25:8} - He will swallow up death forever; and the Lord God will wipe away tears from all faces, and the reproach of his people he will take away from all the earth, for the Lord has spoken.

\subsubsection{Victory over sin and death through Jesus}
\label{sec:orgc4d75b9}
Because truth is truth, it is imperishable.

\textbf{I Peter 1:22-25} - Having purified your souls by your obedience to the truth for a sincere brotherly love, love one another earnestly from a pure heart, since you have been born again, not of perishable seed but of imperishable, through the living and abiding word of God; for All flesh is like grass and all its glory like the flower of grass. The grass withers, and the flower falls, but the word of the Lord remains forever. And this word is the good news that was preached to you. (ESV)

\textbf{II John 1:1-2} - The elder to the elect lady and her children, whom I love in truth, and not only I, but also all who know the truth, because of the truth that abides in us and will be with us forever:

\textbf{Titus 1:1-3} - Paul, a servant of God and an apostle of Jesus Christ, for the sake of the faith of God's elect and their knowledge of the truth, which accords with godliness, in hope of eternal life, which God, who never lies, promised before the ages began and at the proper time manifested in his word through the preaching with which I have been entrusted by the command of God our Savior;

A strong indicator that we are \uline{of the truth} is that against every condemnation, we know God is greater than our heart and knows everything

\textbf{I John 3:18-20} - Little children, let us not love in word or talk but in deed and in truth. By this we shall know that we are of the truth and reassure our heart before him; for whenever our heart condemns us, God is greater than our heart, and he knows everything.

More strong indicators that we are \uline{of the truth} are that:
\begin{itemize}
\item if our heart does not condemn us, we  have confidence before God:
\item whatever we ask of God, we receive from Him
\begin{itemize}
\item because we keep His commandments and do what pleases Him
\begin{itemize}
\item we know we are believing in the name of His Son Jesus Christ, and
\item we know we are loving one another,
\item just has He has commanded us.
\end{itemize}
\end{itemize}
\end{itemize}

\textbf{I John 3:21-23} - Beloved, if our heart does not condemn us, we have confidence before God;
and whatever we ask we receive from him, because we keep his commandments and do what pleases him. And this is his commandment, that we believe in the name of his Son Jesus Christ and love one another, just as he has commanded us.

Who is of God listens to us:

\textbf{I John 4:6} - We are from God. Whoever knows God listens to us; whoever is not from God does not listen to us. By this we know the Spirit of truth and the spirit of error.

We know that God abides in us by the Spirit whom He has given us:

\textbf{I John 3:24} - Whoever keeps his commandments abides in him, and he in them. And by this we know that he abides in us, by the Spirit whom he has given us.

We will be raised imperishable, just as the truth is imperishable:

\textbf{I Corinthians 15:51-58} - Behold! I tell you a mystery. We shall not all sleep, but we shall all be changed, in a moment, in the twinkling of an eye, at the last trumpet. For the trumpet will sound, and the dead will be raised imperishable, and we shall be changed. For this perishable body must put on the imperishable, and this mortal body must put on immortality. When the perishable puts on the imperishable, and the mortal puts on immortality, then shall come to pass the saying that is written: Death is swallowed up in victory. O death, where is your victory? O death, where is your sting? The sting of death is sin, and the power of sin is the law. But thanks be to God, who gives us the victory through our Lord Jesus Christ. Therefore, my beloved brothers, be steadfast, immovable, always abounding in the work of the Lord, knowing that in the Lord your labor is not in vain. (ESV)

\subsubsection{No lust/corruption in heaven. The divine nature does not have lust/corruption}
\label{sec:org4370fff}
\textbf{II Peter 1:3-4} - seeing that His divine power has granted to us everything pertaining to life and godliness, through the true knowledge of Him who called us by His own glory and excellence. For by these He has granted to us His precious and magnificent promises, so that by them you may become \uline{partakers of the divine nature, having escaped the corruption that is in the world by lust}. (NASB)

\textbf{I John 2:15-17} - Do not love the world nor the things in the world. If anyone loves the world, the love of the Father is not in him. For all that is in the world, the lust of the flesh and the lust of the eyes and the boastful pride of life, is not from the Father, but is from the world. The world is passing away, and also its lusts; but the one who does the will of God lives forever.

\textbf{I Thessalonians 4:5} - not in the passion of lust like the Gentiles who do not know God;

Addictions, the lusts of the world, the pride of life, etc.

\textbf{II Peter 2:19-21} - They promise them freedom, but they themselves are slaves of corruption. For whatever overcomes a person, to that he is enslaved. For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first. For it would have been better for them never to have known \textbf{the way of righteousness} than after knowing it to turn back from the holy commandment delivered to them.

\textbf{John 8:34} - Jesus answered them, “Truly, truly, I say to you, everyone who commits sin is the slave of sin.

We must be holy.

\textbf{Ephesians 1:4} - even as he chose us in him before the foundation of the world, that we should be holy and blameless before him. In love

\textbf{I Peter 1:15-16} - but as he who called you is holy, you also be holy in all your conduct, since it is written, You shall be holy, for I am holy.

\textbf{Revelation of John 22:11} - Let the evildoer still do evil, and the filthy still be filthy, and the righteous still do right, and the holy still be holy.

\textbf{Ephesians 5:27} - so that he might present the church to himself in splendor, without spot or wrinkle or any such thing, that she might be holy and without blemish.

These angels were corrupted:

\textbf{Genesis 6:2} - that the sons of God saw that the daughters of men were beautiful; and they took wives for themselves, whomever they chose.

\subsubsection{Incorruptible inheritance}
\label{sec:org6aba684}
God is incorruptible:

\textbf{Romans 1:23} - and exchanged the glory of the incorruptible God for an image in the form of corruptible man and of birds and four-footed animals and crawling creatures.

We will receive an incorruptible body as Jesus' resurrection body does not corrupt:

\textbf{Acts 13:36-37} - For David, after he had served the purpose of God in his own generation, fell asleep and was laid with his fathers and saw corruption, but he whom God raised up did not see corruption.

Incorruptible love is something we can have in this life:

\textbf{Ephesians 6:24} - Grace be with all those who love our Lord Jesus Christ with incorruptible love.

\textbf{I Corinthians 13:8} - Love never ends. As for prophecies, they will pass away; as for tongues, they will cease; as for knowledge, it will pass away.

An imperishable reward:

\textbf{I Corinthians 9:25} - Everyone who competes in the games exercises self-control in all things. They then do it to receive a perishable wreath, but we an imperishable.

\textbf{I Peter 1:4} - to obtain an inheritance which is imperishable and undefiled and will not fade away, reserved in heaven for you,

The Holy Spirit dwelling within us guarantees our imperishable inheritance:

\textbf{II Timothy 1:14} - By the Holy Spirit who dwells within us, guard the good deposit entrusted to you.

\textbf{I Peter 1:23} - for you have been born again not of seed which is perishable but imperishable, that is, through the living and enduring word of God.

\textbf{Ephesians 1:13,14} -  In him you also, when you heard the word of truth, the gospel of your salvation, and believed in him, were sealed with the promised Holy Spirit, who is the guarantee of our inheritance until we acquire possession of it, to the praise of his glory.  (ESV)

Even our bodies will be raised imperishable:

\textbf{I Corinthians 15:52} - in a moment, in the twinkling of an eye, at the last trumpet; for the trumpet will sound, and the dead will be raised imperishable, and we will be changed.

\section{Commandments of God}
\label{sec:org406d3a5}
Commandments of Father God in the New Testament:
\begin{itemize}
\item Listen to Jesus and believe Jesus is God's Son
\begin{itemize}
\item \textbf{Mark 9:7} - And a cloud overshadowed them, and a voice came out of the cloud, This is my beloved Son; listen to him. (ESV)
\item \textbf{Luke 9:35} - And a voice came out of the cloud, saying, This is my Son, my Chosen One; listen to him! (ESV)
\item \textbf{Acts 3:22} - Moses said, The Lord God will raise up for you a prophet like me from your brothers. You shall listen to him in whatever he tells you. (ESV)
\begin{itemize}
\item \textbf{Deuteronomy 18:15-19} - The LORD your God will raise up for you a prophet like me from among you, from your brothers—it is to him you shall listen— just as you desired of the LORD your God at Horeb on the day of the assembly, when you said, Let me not hear again the voice of the LORD my God or see this great fire any more, lest I die. And the LORD said to me, They are right in what they have spoken. I will raise up for them a prophet like you from among their brothers. And I will put my words in his mouth, and he shall speak to them all that I command him. And whoever will not listen to my words that he shall speak in my name, I myself will require it of him. (ESV)
\end{itemize}
\end{itemize}
\item Walk in the truth, love one another and do not deny that Jesus Christ has come in the flesh
\begin{itemize}
\item \textbf{II John 1:4-9} - I rejoiced greatly to find some of your children walking in the truth, just as we were commanded by the Father. And now I ask you, dear lady—not as though I were writing you a new commandment, but the one we have had from the beginning—that we love one another. And this is love, that we walk according to his commandments; this is the commandment, just as you have heard from the beginning, so that you should walk in it. For many deceivers have gone out into the world, those who do not confess the coming of Jesus Christ in the flesh. Such a one is the deceiver and the antichrist. Watch yourselves, so that you may not lose what we have worked for, but may win a full reward. Everyone who goes on ahead and does not abide in the teaching of Christ, does not have God. Whoever abides in the teaching has both the Father and the Son. (ESV)
\end{itemize}
\end{itemize}

Commandments of Jesus:
\begin{itemize}
\item Have faith in God
\begin{itemize}
\item \textbf{Mark 11:22} - And Jesus answered them, Have (G2192 echo) faith (G4102 \textbf{pistis}) in God (G2316 theos).
\begin{itemize}
\item \textbf{pisis} is the faith noun.
\end{itemize}
\end{itemize}
\item Have faith in God and have faith in Jesus
\begin{itemize}
\item \textbf{John 14:1} - “Do not let your heart be troubled; believe (G4100 \textbf{pisteuo}) in God, believe (G4100 \textbf{pisteuo}) also in Me.
\begin{itemize}
\item \textbf{pisteuo} is the faith verb.
\end{itemize}
\end{itemize}
\item Repent, for the kingdom of heaven is near
\begin{itemize}
\item \textbf{Matthew 3:2} - Repent, for the kingdom of heaven is at hand. (ESV)
\end{itemize}
\item Follow the 10 commandments from the heart in truth as far as to not idolize or covet your material possessions, leave behind your old life and follow Him (Jesus). 
\begin{itemize}
\item \textbf{Luke 18:18-22} - And a ruler asked him, Good Teacher, what must I do to inherit eternal life? And Jesus said to him, Why do you call me good? No one is good except God alone. You know the commandments: Do not commit adultery, Do not murder, Do not steal, Do not bear false witness, Honor your father and mother. And he said, All these I have kept from my youth. When Jesus heard this, he said to him, One thing you still lack. Sell all that you have and distribute to the poor, and you will have treasure in heaven; and come, follow me. (ESV)
\item Have faith in God to help you achieve this
\begin{itemize}
\item \textbf{Luke 18:26-27} - Those who heard it said, Then who can be saved? But he said, What is impossible with men is possible with God. (ESV)
\end{itemize}
\end{itemize}
\item Come and follow Jesus and allow Him to make you into a fisher of men
\begin{itemize}
\item \textbf{Matthew 4:19} - And he said to them, Follow me, and I will make you fishers of men. (ESV)
\end{itemize}
\item Rejoice when you're persecuted in My name
\begin{itemize}
\item \textbf{Matthew 5:11-12} - Blessed are you when others revile you and persecute you and utter all kinds of evil against you falsely on my account. Rejoice and be glad, for your reward is great in heaven, for so they persecuted the prophets who were before you. (ESV)
\end{itemize}
\item Let your light shine before all people
\begin{itemize}
\item \textbf{Matthew 5:16} - In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. (ESV)
\end{itemize}
\item Be reconciled to one another
\begin{itemize}
\item \textbf{Matthew 5:23-24} - So if you are offering your gift at the altar and there remember that your brother has something against you, leave your gift there before the altar and go. First be reconciled to your brother, and then come and offer your gift. (ESV)
\end{itemize}
\item Take sin very seriously
\begin{itemize}
\item \textbf{Matthew 5:29-30} - If your right eye causes you to sin, tear it out and throw it away. For it is better that you lose one of your members than that your whole body be thrown into hell. And if your right hand causes you to sin, cut it off and throw it away. For it is better that you lose one of your members than that your whole body go into hell. (ESV)
\end{itemize}
\item Follow the commandments from the heart, and in truth, accountable to God
\begin{itemize}
\item \textbf{Matthew 5:32} - But I say to you that everyone who divorces his wife, except on the ground of sexual immorality, makes her commit adultery. And whoever marries a divorced woman commits adultery. (ESV)
\end{itemize}
\item Turn the other cheek
\begin{itemize}
\item \textbf{Matthew 5:39} - But I say to you, Do not resist the one who is evil. But if anyone slaps you on the right cheek, turn to him the other also. (ESV)
\end{itemize}
\item Go above and beyond. Forgive 
\begin{itemize}
\item \textbf{Matthew 5:40-42} - And if anyone would sue you and take your tunic, let him have your cloak as well. And if anyone forces you to go one mile, go with him two miles. Give to the one who begs from you, and do not refuse the one who would borrow from you. (ESV)
\end{itemize}
\item Love your enemies as well as your friends. Be like Your Heavenly Father. Be perfect
\begin{itemize}
\item \textbf{Matthew 5:43-48} - You have heard that it was said, You shall love your neighbor and hate your enemy. But I say to you, Love your enemies and pray for those who persecute you, so that you may be sons of your Father who is in heaven. For he makes his sun rise on the evil and on the good, and sends rain on the just and on the unjust. For if you love those who love you, what reward do you have? Do not even the tax collectors do the same? And if you greet only your brothers, what more are you doing than others? Do not even the Gentiles do the same? You therefore must be perfect, as your heavenly Father is perfect. (ESV)
\end{itemize}
\item Be perfect as your heavenly Father is perfect
\begin{itemize}
\item \textbf{Matthew 5:48} - You therefore must be perfect, as your heavenly Father is perfect. (ESV)
\end{itemize}
\item Be accountable to God. Do not seek reward from others but from God. Focus on spiritual disciplines for the right reasons. 
\begin{itemize}
\item \textbf{Matthew 6:1-18} - Beware of practicing your righteousness before other people in order to be seen by them, for then you will have no reward from your Father who is in heaven. Thus, when you give to the needy, sound no trumpet before you, as the hypocrites do in the synagogues and in the streets, that they may be praised by others. Truly, I say to you, they have received their reward. But when you give to the needy, do not let your left hand know what your right hand is doing, so that your giving may be in secret. And your Father who sees in secret will reward you. And when you pray, you must not be like the hypocrites. For they love to stand and pray in the synagogues and at the street corners, that they may be seen by others. Truly, I say to you, they have received their reward. But when you pray, go into your room and shut the door and pray to your Father who is in secret. And your Father who sees in secret will reward you. And when you pray, do not heap up empty phrases as the Gentiles do, for they think that they will be heard for their many words. Do not be like them, for your Father knows what you need before you ask him. Pray then like this: Our Father in heaven, hallowed be your name. Your kingdom come, your will be done, on earth as it is in heaven. Give us this day our daily bread, and forgive us our debts, as we also have forgiven our debtors. And lead us not into temptation, but deliver us from evil. For if you forgive others their trespasses, your heavenly Father will also forgive you, but if you do not forgive others their trespasses, neither will your Father forgive your trespasses. And when you fast, do not look gloomy like the hypocrites, for they disfigure their faces that their fasting may be seen by others. Truly, I say to you, they have received their reward. But when you fast, anoint your head and wash your face, that your fasting may not be seen by others but by your Father who is in secret. And your Father who sees in secret will reward you. (ESV)
\item Have a relationship with God
\begin{itemize}
\item \textbf{Hebrews 11:6} - And without faith it is impossible to please him, for whoever would draw near to God must believe that he exists and that he rewards those who seek him. (ESV)
\end{itemize}
\end{itemize}
\item Seek heavenly reward, not earthly reward. Have a heart seeking reward from God and not from man. Have your heart in heaven, not in eart
\begin{itemize}
\item \textbf{Matthew 6:19-21} - Do not lay up for yourselves treasures on earth, where moth and rust destroy and where thieves break in and steal, but lay up for yourselves treasures in heaven, where neither moth nor rust destroys and where thieves do not break in and steal. For where your treasure is, there your heart will be also. (ESV)
\end{itemize}
\item Seek God's kingdom and His righteousness first of all
\begin{itemize}
\item \textbf{Matthew 6:33} - But seek first the kingdom of God and his righteousness, and all these things will be added to you. (ESV)
\item Obey the law by faith (repent from sin)
\item Submit to the righteousness of God through faith in Jesus Christ (repent from disbelief)
\end{itemize}
\item Do not worry about tomorrow
\begin{itemize}
\item \textbf{Matthew 6:34} - Therefore do not be anxious about tomorrow, for tomorrow will be anxious for itself. Sufficient for the day is its own trouble. (ESV)
\end{itemize}
\item Use right judgment. We should be examining, judging, cleaning ourselves up, taking a look in the mirror first (by God's standards) before judging others
\begin{itemize}
\item \textbf{Matthew 7:1-5} - Judge not, that you be not judged. For with the judgment you pronounce you will be judged, and with the measure you use it will be measured to you. Why do you see the speck that is in your brother's eye, but do not notice the log that is in your own eye? Or how can you say to your brother, Let me take the speck out of your eye, when there is the log in your own eye? You hypocrite, first take the log out of your own eye, and then you will see clearly to take the speck out of your brother's eye. (ESV)
\end{itemize}
\item Practice discretion
\begin{itemize}
\item \textbf{Matthew 7:6} - Do not give dogs what is holy, and do not throw your pearls before pigs, lest they trample them underfoot and turn to attack you. (ESV)
\end{itemize}
\item Ask, seek, and knock
\begin{itemize}
\item \textbf{Matthew 7:7-8} - Ask, and it will be given to you; seek, and you will find; knock, and it will be opened to you. For everyone who asks receives, and the one who seeks finds, and to the one who knocks it will be opened. (ESV)
\item Ask God for your needs, which includes asking God for the Holy Spirit
\begin{itemize}
\item \textbf{Luke 11:1-11} - Now Jesus was praying in a certain place, and when he finished, one of his disciples said to him, Lord, teach us to pray, as John taught his disciples. And he said to them, When you pray, say: Father, hallowed be your name. Your kingdom come. Give us each day our daily bread, and forgive us our sins, for we ourselves forgive everyone who is indebted to us. And lead us not into temptation. And he said to them, Which of you who has a friend will go to him at midnight and say to him, Friend, lend me three loaves, for a friend of mine has arrived on a journey, and I have nothing to set before him; and he will answer from within, Do not bother me; the door is now shut, and my children are with me in bed. I cannot get up and give you anything? I tell you, though he will not get up and give him anything because he is his friend, yet because of his impudence he will rise and give him whatever he needs. And I tell you, ask, and it will be given to you; \textbf{seek, and you will find}; knock, and it will be opened to you. For \textbf{everyone who asks receives}, and \textbf{the one who seeks finds}, and to \textbf{the one who knocks it will be opened}. What father among you, if his son asks for a fish, will instead of a fish give him a serpent; (ESV)
\end{itemize}
\end{itemize}
\item Treat others as you would like to be treated
\begin{itemize}
\item \textbf{Matthew 7:12} - So whatever you wish that others would do to you, do also to them, for this is the Law and the Prophets. (ESV)
\end{itemize}
\item Choose the narrow path to life
\begin{itemize}
\item \textbf{Matthew 7:13-14} - Enter by the narrow gate. For the gate is wide and the way is easy that leads to destruction, and those who enter by it are many. For the gate is narrow and the way is hard that leads to life, and those who find it are few. (ESV)
\end{itemize}
\item Look out for false prophets
\begin{itemize}
\item \textbf{Matthew 7:15-20} - Beware of false prophets, who come to you in sheep's clothing but inwardly are ravenous wolves. You will recognize them by their fruits. Are grapes gathered from thornbushes, or figs from thistles? So, every healthy tree bears good fruit, but the diseased tree bears bad fruit. A healthy tree cannot bear bad fruit, nor can a diseased tree bear good fruit. Every tree that does not bear good fruit is cut down and thrown into the fire. Thus you will recognize them by their fruits. (ESV)
\end{itemize}
\item Pray for kingdom laborers. Pray that God sends out kingdom laborers
\begin{itemize}
\item \textbf{Matthew 9:37-38} - Then he said to his disciples, The harvest is plentiful, but the laborers are few; therefore pray earnestly to the Lord of the harvest to send out laborers into his harvest. (ESV)
\end{itemize}
\item Be on your guard. Jesus sends us out to be like scapegoats. Be wise and remain blameless
\begin{itemize}
\item \textbf{Matthew 10:16-17} - Behold, I am sending you out as sheep in the midst of wolves, so be wise as serpents and innocent as doves. Beware of men, for they will deliver you over to courts and flog you in their synagogues, (ESV)
\end{itemize}
\item Do not fear persecutors. Fear God. But put your trust in God because He takes care of those who fear Him. Speak the truth
\begin{itemize}
\item \textbf{Matthew 10:26-31} - So have no fear of them, for nothing is covered that will not be revealed, or hidden that will not be known. What I tell you in the dark, say in the light, and what you hear whispered, proclaim on the housetops. And do not fear those who kill the body but cannot kill the soul. Rather fear him who can destroy both soul and body in hell. Are not two sparrows sold for a penny? And not one of them will fall to the ground apart from your Father. But even the hairs of your head are all numbered. Fear not, therefore; you are of more value than many sparrows. (ESV)
\end{itemize}
\item Take Jesus' yoke upon yourself
\begin{itemize}
\item \textbf{Matthew 11:28-30} - Come to me, all who labor and are heavy laden, and I will give you rest. Take my yoke upon you, and learn from me, for I am gentle and lowly in heart, and you will find rest for your souls. For my yoke is easy, and my burden is light. (ESV)
\end{itemize}
\item Do not despise the little ones
\begin{itemize}
\item \textbf{Matthew 18:10} - See that you do not despise one of these little ones. For I tell you that in heaven their angels always see the face of my Father who is in heaven. (ESV)
\end{itemize}
\item How to deal with offenders
\begin{itemize}
\item \textbf{Matthew 18:15-17} - If your brother sins against you, go and tell him his fault, between you and him alone. If he listens to you, you have gained your brother. But if he does not listen, take one or two others along with you, that every charge may be established by the evidence of two or three witnesses. If he refuses to listen to them, tell it to the church. And if he refuses to listen even to the church, let him be to you as a Gentile and a tax collector. (ESV)
\end{itemize}
\item Forgive extremely generously / almost without limits
\begin{itemize}
\item \textbf{Matthew 18:21-22} - Then Peter came up and said to him, Lord, how often will my brother sin against me, and I forgive him? As many as seven times? Jesus said to him, I do not say to you seven times, but seventy times seven. (ESV)
\end{itemize}
\item Lead through service
\begin{itemize}
\item \textbf{Matthew 20:25-28} - But Jesus called them to him and said, You know that the rulers of the Gentiles lord it over them, and their great ones exercise authority over them. It shall not be so among you. But whoever would be great among you must be your servant, and whoever would be first among you must be your slave, even as the Son of Man came not to be served but to serve, and to give his life as a ransom for many. (ESV)
\end{itemize}
\item Love God with all your heart, mind, and soul
\begin{itemize}
\item \textbf{Matthew 22:37-38} - And he said to him, You shall love the Lord your God with all your heart and with all your soul and with all your mind. This is the great and first commandment. (ESV)
\end{itemize}
\item Love your neighbor as yourself - fulfill the requirement of the law
\begin{itemize}
\item \textbf{Matthew 22:39} - And a second is like it: You shall love your neighbor as yourself. (ESV)
\end{itemize}
\item Stay alert and keep watch
\begin{itemize}
\item \textbf{Matthew 24:42-44} - Therefore, stay awake, for you do not know on what day your Lord is coming. But know this, that if the master of the house had known in what part of the night the thief was coming, he would have stayed awake and would not have let his house be broken into. Therefore you also must be ready, for the Son of Man is coming at an hour you do not expect. (ESV)
\end{itemize}
\item Make disciples of all the nations, teaching them to obey Jesus
\begin{itemize}
\item \textbf{Matthew 28:18-20} - And Jesus came and said to them, All authority in heaven and on earth has been given to me. Go therefore and make disciples of all nations, baptizing them in the name of the Father and of the Son and of the Holy Spirit, teaching them to observe all that I have commanded you. And behold, I am with you always, to the end of the age. (ESV)
\end{itemize}
\item Deny yourself daily, and follow Jesus
\begin{itemize}
\item \textbf{Luke 9:23-24} - And he said to all, If anyone would come after me, let him deny himself and take up his cross daily and follow me. For whoever would save his life will lose it, but whoever loses his life for my sake will save it. (ESV)
\end{itemize}
\item Do not covet your possessions
\begin{itemize}
\item \textbf{Luke 12:15} - And he said to them, Take care, and be on your guard against all covetousness, for one's life does not consist in the abundance of his possessions. (ESV)
\end{itemize}
\item Give to those who can't reciprocate
\begin{itemize}
\item \textbf{Luke 14:12-14} - He said also to the man who had invited him, When you give a dinner or a banquet, do not invite your friends or your brothers or your relatives or rich neighbors, lest they also invite you in return and you be repaid. But when you give a feast, invite the poor, the crippled, the lame, the blind, and you will be blessed, because they cannot repay you. You will be repaid at the resurrection of the just. (ESV)
\end{itemize}
\item You must be born again
\begin{itemize}
\item \textbf{John 3:7} - Do not marvel that I said to you, You must be born again. (ESV)
\end{itemize}
\item If you love Jesus, keep His commandments. The one who keeps Jesus' commandments is the one who loves Jesus
\begin{itemize}
\item \textbf{John 14:15} - If you love me, you will keep my commandments.
\item \textbf{John 14:21} - Whoever has my commandments and keeps them, he it is who loves me. And he who loves me will be loved by my Father, and I will love him and manifest myself to him.
\end{itemize}
\item Those who have testimony of Jesus should preach testify that he is the one appointed by God to be judge of the living and the dead
\begin{itemize}
\item \textbf{Acts 10:41-44} - not to all the people but to us who had been chosen by God as witnesses, who ate and drank with him after he rose from the dead. And he commanded us to preach to the people and to testify that he is the one appointed by God to be judge of the living and the dead. To him all the prophets bear witness that everyone who believes in him receives forgiveness of sins through his name. While Peter was still saying these things, the Holy Spirit fell on all who heard the word. (ESV)
\item \textbf{Acts 13:47} - For so the Lord has commanded us, saying, I have made you a light for the Gentiles, that you may bring salvation to the ends of the earth.
\end{itemize}
\item Those who proclaim the gospel should get their living by the gospel
\begin{itemize}
\item \textbf{I Corinthians 9:14} - In the same way, the Lord commanded that those who proclaim the gospel should get their living by the gospel.
\end{itemize}
\end{itemize}

Precepts of Paul:
\begin{itemize}
\item Pursue godliness with contentment but not without contentment. Pursue personal righteousness
\begin{itemize}
\item \textbf{I Timothy 6:3-11} - If anyone teaches a different doctrine and does not agree with the sound words of our Lord Jesus Christ and the teaching that accords with godliness, he is puffed up with conceit and understands nothing. He has an unhealthy craving for controversy and for quarrels about words, which produce envy, dissension, slander, evil suspicions, and constant friction among people who are depraved in mind and deprived of the truth, imagining that godliness is a means of gain.  Now there is great gain in godliness with contentment, for we brought nothing into the world, and we cannot take anything out of the world.  But if we have food and clothing, with these we will be content.  But those who desire to be rich fall into temptation, into a snare, into many senseless and harmful desires that plunge people into ruin and destruction.  For the love of money is a root of all kinds of evils. It is through this craving that some have wandered away from the faith and pierced themselves with many pangs.  But as for you, O man of God, flee these things. Pursue righteousness, godliness, faith, love, steadfastness, gentleness. (ESV)
\begin{itemize}
\item righteousness,
\item godliness,
\item faith,
\item love,
\item steadfastness,
\item gentleness.
\end{itemize}
\end{itemize}
\end{itemize}

\section{Free will and justification. The Scripture says \textbf{Abraham} believed God}
\label{sec:orgc36454b}
The onus is on us to believe:

\textbf{Genesis 15:4-6} - And behold, the word of the Lord came to him: This man shall not be your heir; your very own son shall be your heir. And he brought him outside and said, Look toward heaven, and number the stars, if you are able to number them. Then he said to him, So shall your offspring be. And \textbf{he believed the Lord, and he counted it to him as righteousness}.

\textbf{Romans 4:3} - For what does the Scripture say? Abraham believed God, and it was counted to him as righteousness.

\textbf{Galatians 3:6} - just as Abraham believed God, and it was counted to him as righteousness?

\textbf{James 2:23} - and the Scripture was fulfilled that says, Abraham believed God, and it was counted to him as righteousness—and he was called a friend of God.

\subsection{Also, in advance of being given the promise, Abraham was faithful to God}
\label{sec:org184be6e}
\textbf{Genesis 13:14-18} - The Lord said to Abram, after Lot had separated from him, Lift up your eyes and look from the place where you are, northward and southward and eastward and westward, for all the land that you see I will give to you and to your offspring forever. I will make your offspring as the dust of the earth, so that if one can count the dust of the earth, your offspring also can be counted. \uline{Arise, walk through the length and the breadth of the land, for I will give it to you}. So Abram moved his tent and came and settled by the oaks of Mamre, which are at Hebron, and there he built an altar to the Lord.

\textbf{Genesis 14:23} - that I would not take a thread or a sandal strap or anything that is yours, lest you should say, I have made Abram rich.

\subsection{Also, in advance of being given the promise, Abraham was doing the will of God}
\label{sec:org421a2f0}
That is when God \uline{rewarded} Abraham with a promise:

\textbf{Genesis 15:1-6} - After these things the word of the Lord came to Abram in a vision: Fear not, Abram, I am your shield; your reward shall be very great. But Abram said, O Lord God, what will you give me, for I continue childless, and the heir of my house is Eliezer of Damascus? And Abram said, Behold, you have given me no offspring, and a member of my household will be my heir. And behold, the word of the Lord came to him: This man shall not be your heir; your very own son shall be your heir. And he brought him outside and said, Look toward heaven, and number the stars, if you are able to number them. Then he said to him, So shall your offspring be. And he believed the Lord, and he counted it to him as righteousness.

Rewards are for people who \uline{choose} to do the right thing.
It doesn't say, God rewarded God. God said that Abraham's reward shall be very great. God rewarded Abraham.

\section{godliness}
\label{sec:orgdcdba0a}
The word godliness, I think means, to \uline{act in a way fitting of having true knowledge of our God, and of our Lord and Saviour Jesus Christ}, and preparing oneself for eternity.

\textbf{Titus 1:1} - Paul, a bond-servant (G1401 doulos) of God (G2316 theos) and an apostle of Jesus (G2424 Iesous) Christ (G5547 Christos), for the faith (G4102 pistis) of those chosen of God (G2316 theos) and the knowledge (G1922 epignosis) of the truth (G225 aletheia) which is according to godliness (G2150 eusebeia),

Perfect godliness revealing God through Jesus Christ:

\textbf{I Timothy 3:16} - Great indeed, we confess, is the mystery of godliness: He was manifested in the flesh, vindicated by the Spirit, seen by angels, proclaimed among the nations, believed on in the world, taken up in glory. (ESV)

\begin{center}
\begin{tabular}{ll}
Relevant verses & Characteristics of godliness\\[0pt]
\hline
Titus 1:2 & Behaviour in accordance with true knowledge about God\\[0pt]
Isaiah 32:6, Romans 1:18 & Disinclined towards wickedness; inclined to practice righteousness\\[0pt]
Isaiah 32:6, Romans 1:18 & Speaks the truth about the Lord\\[0pt]
Isaiah 32:6 & Takes care of their neighbour\\[0pt]
Romans 1:21 & Honours God as God\\[0pt]
Romans 1:21 & Gives thanks to God\\[0pt]
Romans 1:18-22, Proverbs 1:7 & Has the fear of God\\[0pt]
I Timothy 3:8 & Knows God can see your heart\\[0pt]
I Timothy 2:1-4 & Cares that any person, even the worldly, may be saved and come to the knowledge of the truth\\[0pt]
I Timothy 2:9, I Timothy 3:8 & Not worldliness, knowing that humility pleases God\\[0pt]
I Timothy 6:10-11 & Not worldliness, knowing that true riches are in heaven\\[0pt]
I Timothy 2:10 & Performs good works (works which are pleasing to God)\\[0pt]
I Timothy 3:11 & Dignified, sober-minded\\[0pt]
I Timothy 3:11 & Faithful in all things\\[0pt]
I Timothy 4:7-8 & Profitable for all things (physical and spiritual), present life and eternity\\[0pt]
I Timothy 6:4, II Timothy 2:16 & Has eyes set on God. Doesn't fall into vain, time-wasting arguments\\[0pt]
II Timothy 3:5 & Keeps themself accountable to God. Has a real relationship with God.\\[0pt]
Titus 2:11-14 & Cooperates with Jesus purifying them, and employing them in good works, for eternal life\\[0pt]
Titus 1:2, Titus 2:11-14 & Hopes for eternal life\\[0pt]
II Peter 3:10-12 & Prepares for eternity\\[0pt]
II Peter 1:3 & Responds well to Jesus' supply to us of what we need to live godly lives.\\[0pt]
II Peter 1:5-7 & Supplements steadfastness (helps us to be more steadfast)\\[0pt]
II Peter 1:5-7 & Is supplemented by brotherly affection (in accordance with true knowledge about God)\\[0pt]
\end{tabular}
\end{center}

\subsection{Verses}
\label{sec:org3460191}
\textbf{Isaiah 32:6} - For a fool speaks nonsense, And his heart inclines toward wickedness: To practice ungodliness and to speak error against the Lord (H3068 Yhovah), To keep the hungry person unsatisfied And to withhold drink from the thirsty.

\textbf{Romans 1:18} - For the wrath of God (G2316 theos) is revealed from heaven (G3772 ouranos) against all (G3956 pas) ungodliness and unrighteousness of men who suppress the truth (G225 aletheia) in unrighteousness,

\textbf{Romans 11:26} - and so all (G3956 pas) Israel will be saved (G4982 sozo); just as it is written, “The Deliverer will come from Zion, He will remove ungodliness from Jacob.”

\textbf{I Timothy 2:1-4} - First of all, then, I urge that supplications, prayers, intercessions, and thanksgivings be made for all people, for kings and all who are in high positions, that we may lead a peaceful and quiet life, godly and dignified in every way. This is good, and it is pleasing in the sight of God our Savior, who desires all people to be saved and to come to the knowledge of the truth.

\textbf{I Timothy 2:10} - but rather by means of good works (G2041 ergon), as is proper for women making a claim to godliness.

\textbf{I Timothy 3:16} - By common confession, great is the mystery (G3466 musterion) of godliness (G2150 eusebeia): He who (G3739 hos) was revealed in the flesh (G4561 sarx), Was vindicated in the Spirit (G4151 pneuma), Seen by angels, Proclaimed among the nations, Believed on in the world (G2889 kosmos), Taken up in glory (G1391 doxa).

\textbf{I Timothy 4:7-8} - But have nothing to do with worldly fables fit only for old women. On the other hand, discipline yourself for the purpose of godliness (G2150 eusebeia); for bodily discipline is only of little profit, but godliness (G2150 eusebeia) is profitable for all (G3956 pas) things (G3956 pas), since it holds promise for the present life (G2222 zoe) and also for the life to come.

\textbf{I Timothy 6:3-6} - If anyone teaches a different doctrine and does not agree with the sound words of our Lord Jesus Christ and the teaching that accords with godliness, he is puffed up with conceit and understands nothing. He has an unhealthy craving for controversy and for quarrels about words, which produce envy, dissension, slander, evil suspicions, and constant friction among people who are depraved in mind and deprived of the truth, imagining that godliness is a means of gain. But godliness (G2150 eusebeia) actually is a means of great gain when accompanied by contentment.

\textbf{I Timothy 6:10-11} - For the love of money is a root of all kinds of evils. It is through this craving that some have wandered away from the faith and pierced themselves with many pangs. But as for you, O man of God, flee these things. Pursue righteousness, godliness, faith, love, steadfastness, gentleness.

\textbf{II Timothy 2:16} - But avoid worldly and empty chatter, for it will lead to further ungodliness,

\textbf{II Timothy 3:5} - holding to a form of godliness (G2150 eusebeia), although they have denied its power (G1411 dunamis); Avoid such men as these.

\textbf{Titus 1:1} - Paul, a bond-servant (G1401 doulos) of God (G2316 theos) and an apostle of Jesus (G2424 Iesous) Christ (G5547 Christos), for the faith (G4102 pistis) of those chosen of God (G2316 theos) and the knowledge (G1922 epignosis) of the truth (G225 aletheia) which is according to godliness (G2150 eusebeia),

\textbf{Titus 2:11-14} - For the grace of God has appeared, bringing salvation for all people, training us to renounce ungodliness and worldly passions, and to live self-controlled, upright, and godly lives in the present age, waiting for our blessed hope, the appearing of the glory of our great God and Savior Jesus Christ, who gave himself for us to redeem us from all lawlessness and to purify for himself a people for his own possession who are zealous for good works.

Jesus has granted us what we need to live a godly life:

\textbf{II Peter 1:3} - seeing that His divine power (G1411 dunamis) has granted to us everything (G3956 pas) pertaining to life (G2222 zoe) and godliness (G2150 eusebeia), through the true (G1922 epignosis) knowledge (G1922 epignosis) of Him who called us by His own glory (G1391 doxa) and excellence.

\textbf{II Peter 1:5-7} - For this very reason, make every effort to supplement your faith with virtue, and virtue with knowledge, and knowledge with self-control, and self-control with steadfastness, and steadfastness with godliness, and godliness with brotherly affection, and brotherly affection with love.

\textbf{II Peter 3:10-12} - But the day of the Lord will come like a thief, and then the heavens will pass away with a roar, and the heavenly bodies will be burned up and dissolved, and the earth and the works that are done on it will be exposed. Since all these things are thus to be dissolved, what sort of people ought you to be in lives of holiness and godliness, waiting for and hastening the coming of the day of God, because of which the heavens will be set on fire and dissolved, and the heavenly bodies will melt as they burn!

\section{'Election' / predestination, theology etc. is a massive distraction, I think}
\label{sec:org3449c28}
I believe that here on earth, God wants us to choose Jesus. But from God's perspective, who knows how it works.

God can raise up children from anyone who has repentance and may grant being a child of Abraham to anyone who walks in the footsteps of the faith that Abraham had before he was circumcised.

\textbf{Luke 3:8} - \uline{Bear fruits in keeping with repentance.} And do not begin to say to yourselves, We have Abraham as our father. For I tell you, \uline{God is able from these stones to raise up children for Abraham.}

\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.

We do have the ability to make choices:

\textbf{Isaiah 66:3} - He who slaughters an ox is like one who kills a man; he who sacrifices a lamb, like one who breaks a dog's neck; he who presents a grain offering, like one who offers pig's blood; he who makes a memorial offering of frankincense, like one who blesses an idol. These have chosen their own ways, and their soul delights in their abominations; (ESV)

A gift can be accepted or rejected - and this is a choice we \uline{can} make:

\textbf{Romans 5:17} - If, because of one man's trespass, death reigned through that one man, much more will those who receive the abundance of grace and the free gift of righteousness reign in life through the one man Jesus Christ. (ESV)

We should not lean on our own understanding:

\textbf{Isaiah 55:9} - For as the heavens are higher than the earth, so are my ways higher than your ways and my thoughts than your thoughts.

What we should do now is acknowledge the LORD, keep our eyes on Jesus, and live godly lives:

\textbf{Proverbs 3:5-6} - Trust in the LORD with all your heart, and do not lean on your own understanding. In all your ways acknowledge him, and he will make straight your paths. (ESV)

Focusing on predestination, election etc. without obeying what Jesus said to do, is not really obeying the will of God and \textbf{may} put a person in this category:

\textbf{2 Thessalonians 2:11-13} - Therefore God sends them a strong delusion, so that they may believe what is false, in order that all may be condemned who did not believe the truth but had pleasure in unrighteousness.  But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through sanctification by the Spirit and belief in the truth.  (ESV)

Although God chooses who He has mercy on, we should still have a godly and humble response to God's mercy:

\textbf{Romans 9:10-16} - And not only so, but also when Rebecca had conceived children by one man, our forefather Isaac, though they were not yet born and had done nothing either good or bad—in order that God's purpose of election might continue, not because of works but because of his call— she was told, The older will serve the younger. As it is written, Jacob I loved, but Esau I hated. What shall we say then? Is there injustice on God's part? By no means! For he says to Moses, I will have mercy on whom I have mercy, and I will have compassion on whom I have compassion. So then it depends not on human will or exertion, but on God, who has mercy.

We should be confident that God will continue to take care of us:

\textbf{Romans 8:29-39}- For those whom he foreknew he also predestined to be conformed to the image of his Son, in order that he might be the firstborn among many brothers. And those whom he predestined he also called, and those whom he called he also justified, and those whom he justified he also glorified. What then shall we say to these things? If God is for us, who can be against us? He who did not spare his own Son but gave him up for us all, how will he not also with him graciously give us all things? Who shall bring any charge against God's elect? It is God who justifies. Who is to condemn? Christ Jesus is the one who died—more than that, who was raised—who is at the right hand of God, who indeed is interceding for us. Who shall separate us from the love of Christ? Shall tribulation, or distress, or persecution, or famine, or nakedness, or danger, or sword? As it is written, For your sake we are being killed all the day long; we are regarded as sheep to be slaughtered. No, in all these things we are more than conquerors through him who loved us. For I am sure that neither death nor life, nor angels nor rulers, nor things present nor things to come, nor powers, nor height nor depth, nor anything else in all creation, will be able to separate us from the love of God in Christ Jesus our Lord.

God has good plans for us and we should submit to His wisdom, and obey Him:

\textbf{Isaiah 64:8} - But now, O Lord, you are our Father; we are the clay, and you are our potter; we are all the work of your hand.

\textbf{Romans 8:28} - And we know that \uline{for those who love God} \uline{all things work together for good}, \uline{for those who are called according to his purpose}.

Who chooses who? I believe Jesus chose me and I also choose Jesus every day but \uline{Jesus chose me first}:

\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that whatever you ask the Father in my name, he may give it to you. (ESV)

\textbf{Romans 8:29} - For those whom he foreknew he also predestined to be conformed to the image of his Son, in order that he might be the firstborn among many brothers.

God is the Creator, our Maker.

\begin{itemize}
\item For those who love God
\begin{itemize}
\item obedient to God
\end{itemize}
\item For those who are called according to His purpose
\item All things work together for good
\end{itemize}

God's ultimately the one in control of us but from our perspective we must submit to His righteousness and His will and be obedient.

To \uline{make election sure}, and \textbf{to not fail}, one must practice personal righteousness and put a stop to sin.

\textbf{II Peter 1:10-11} - Therefore, brothers, be all the more diligent to make your calling and election sure, for if you practice these qualities you will never fall. For in this way there will be richly provided for you an entrance into the eternal kingdom of our Lord and Savior Jesus Christ.

\textbf{Acts 13:14-16} - but they went on from Perga and came to Antioch in Pisidia.  And on the Sabbath day they went into the synagogue and sat down.  After the reading from the Law and the Prophets, the rulers of the synagogue sent a message to them, saying, Brothers, if you have any word of exhortation for the people, say it.  So Paul stood up, and motioning with his hand said: Men of Israel and \textbf{you who fear God}, listen.  (ESV)

\begin{itemize}
\item The elect fear God
\begin{itemize}
\item They had soft hearts
\begin{itemize}
\item able to believe and obey
\end{itemize}
\end{itemize}
\item The non-elect \textbf{judge themselves} unworthy of eternal life
\begin{itemize}
\item They had hard hearts
\begin{itemize}
\item unable to believe and obey
\end{itemize}
\end{itemize}
\end{itemize}

One thing is for sure. The elect do not have hard hearts.
So I'd say if a person's heart is not totally hard, then soften it.

A heart not easy to be moved with virtuous affections:
\begin{itemize}
\item \textbf{Deuteronomy 15:7} - If among you, one of your brothers should become poor, in any of your towns within your land that the Lord your God is giving you, you shall not harden your heart or shut your hand against your poor brother, (ESV)
\item \textbf{Mark 3:4-5} - And He said to them, “Is it lawful to do good or to do harm on the Sabbath, to save a life or to kill?” But they kept silent. After looking around at them with anger, grieved at their hardness of heart, He said to the man, “Stretch out your hand.” And he stretched it out, and his hand was restored. (ESV)
\item \href{https://www.youtube.com/watch?v=JaMVzW9yiBc}{Do I Have a Hard Heart? - YouTube}
\item \textbf{Mark 8:17} - And Jesus, aware of this, said to them, Why are you discussing the fact that you have no bread? Do you not yet perceive or understand? Are your hearts hardened? (ESV)
\item \textbf{II Chronicles 36:12-13} - He did what was evil in the sight of the Lord his God. He did not humble himself before Jeremiah the prophet, who spoke from the mouth of the Lord. He also rebelled against King Nebuchadnezzar, who had made him swear by God. He stiffened his neck and hardened his heart against turning to the Lord, the God of Israel. (ESV)
\item \textbf{Romans 2:4} - Or do you presume on the riches of his kindness and forbearance and patience, not knowing that God's kindness is meant to lead you to repentance? (ESV)
\item \textbf{Zechariah 7:12} - They made their hearts diamond-hard lest they should hear the law and the words that the Lord of hosts had sent by his Spirit through the former prophets. Therefore great anger came from the Lord of hosts. (ESV)
\end{itemize}

If we have a hard heart, we should ask for a new one:
\begin{itemize}
\item \textbf{Ezekiel 36:26} - And I will give you a new heart, and a new spirit I will put within you. And I will remove the heart of stone from your flesh and give you a heart of flesh.
\end{itemize}

Don't let your heart go hard - find a community of encouraging believers:
\begin{itemize}
\item \textbf{Hebrews 3:13} - But exhort one another every day, as long as it is called today, that none of you may be hardened by the deceitfulness of sin.
\end{itemize}

\textbf{Acts 13:46-48} - And Paul and Barnabas spoke out boldly, saying, It was necessary that the word of God be spoken first to you.  Since you thrust it aside and \textbf{judge yourselves unworthy} of eternal life, behold, we are turning to the Gentiles.  For so the Lord has commanded us, saying, I have made you a light for the Gentiles, that you may bring salvation to the ends of the earth.  And when the Gentiles heard this, they began rejoicing and glorifying the word of the Lord, and as many as were appointed to eternal life believed. (ESV)

I do believe, however, that \textbf{cooperation} is generally required on the part of the believer:
\begin{itemize}
\item Before regeneration, and
\item After regeneration
\end{itemize}

Before regeneration, I was trying hard to repent of my sin by trying to obey the 10 commandments from the heart.
And I would say I was also making progress.
After regeneration, I had to learn to walk in Jesus' commandments, and to submit to His righteousness.

John the Baptist taught repentance and love for one's neighbour before receiving the baptisim of the Holy Spirit:

\textbf{Luke 3:3-8} - And he went into all the region around the Jordan, proclaiming a baptism of repentance for the forgiveness of sins. As it is written in the book of the words of Isaiah the prophet, The voice of one crying in the wilderness: Prepare the way of the Lord, make his paths straight. Every valley shall be filled, and every mountain and hill shall be made low, and the crooked shall become straight, and the rough places shall become level ways, and all flesh shall see the salvation of God. He said therefore to the crowds that came out to be baptized by him, You brood of vipers! Who warned you to flee from the wrath to come? \uline{Bear fruits in keeping with repentance}. And do not begin to say to yourselves, We have Abraham as our father. For I tell you, \uline{God is able from these stones to raise up children for Abraham.}

Regeneration is the sovereign work of the Holy Spirit, though. AMEN!! Nevertheless, I believe in allowing Jesus Christ to be my Lord.

\textbf{John 3:5-8} - Jesus answered, Truly, truly, I say to you, unless one is born of water and the Spirit, he cannot enter the kingdom of God. That which is born of the flesh is flesh, and that which is born of the Spirit is spirit. Do not marvel that I said to you, You must be born again. The wind blows where it wishes, and you hear its sound, but you do not know where it comes from or where it goes. So it is with everyone who is born of the Spirit.

\textbf{John 6:45-47} - It is written in the Prophets, And they will all be taught by God. \uline{Everyone who has heard and learned from the Father comes to me} — not that anyone has seen the Father except he who is from God; he has seen the Father. Truly, truly, I say to you, whoever believes (G4100 \textbf{pisteuo}) has eternal life.

Also, I believe that this is what God actually wants from us - to seek Him and worship Him of our own volition.

\textbf{Romans 11:7-10} - What then? Israel failed to obtain what it was seeking. The \textbf{elect} obtained it, but \textbf{the rest were hardened}, as it is written, God gave them a spirit of stupor, eyes that would not see and ears that would not hear, down to this very day.  And David says, Let their table become a snare and a trap, a stumbling block and a retribution for them; let their eyes be darkened so that they cannot see, and bend their backs forever.

The Gentiles should not harden their own hearts. Neither should the Jews.

\textbf{Psalms 95:8} - do not harden your hearts, as at Meribah, as on the day at Massah in the wilderness,

\textbf{Hebrews 3:8} - do not harden your hearts as in the rebellion, on the day of testing in the wilderness,

\textbf{Hebrews 3:15} - As it is said, Today, if you hear his voice, do not harden your hearts as in the rebellion.

\textbf{Hebrews 4:7} - again he appoints a certain day, Today, saying through David so long afterward, in the words already quoted, \textbf{Today, if you hear his voice, do not harden your hearts}.

God puts the fear of Him into the elect's heart.

\textbf{Jeremiah 32:40} - I will make with them an everlasting covenant, that I will not turn away from doing good to them. And I will put the fear of me in their hearts, that they may not turn from me. (ESV)

I still think there is co-operation by the believer before and after spiritual regeneration.

Having heard the truth, the Spirit sanctifies us through our obedience to the Spirit, and are we are conformed to holiness, not to impurity:

\textbf{I Peter 1:14-16} - As obedient children, do not be conformed to the passions of your former ignorance, but as he who called you is holy, you also be holy in all your conduct, since it is written, You shall be holy, for I am holy.

We purify ourselves as we have faith in Jesus:

\textbf{I John 3:3} - And everyone who thus hopes in him purifies himself as he is pure.

Having purified ourselves by obedience to the truth:

This here says we must obey for the sake of purification of our souls even after being born-again:

\textbf{I Peter 1:22-23} - Having purified your souls by your obedience to the truth for a sincere brotherly love, love one another earnestly from a pure heart, since you have been born again, not of perishable seed but of imperishable, through the living and abiding word of God;

And Jesus instructs us to have an obedient heart if we want to know that Jesus' teaching is from God:

\textbf{John 7:17} - If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.  (ESV)

\subsection{God loved us first}
\label{sec:org56abd0d}
\textbf{I John 4:8-11} - Anyone who does not love does not know God, because God is love. In this the love of God was made manifest among us, that God sent his only Son into the world, so that we might live through him. In this is love, not that we have loved God but that he loved us and sent his Son to be the propitiation for our sins. Beloved, if God so loved us, we also ought to love one another.

\subsubsection{God's love is greater}
\label{sec:org87bb7e7}
\textbf{Romans 8:35} - Who shall separate us from the love of Christ? Shall tribulation, or distress, or persecution, or famine, or nakedness, or danger, or sword?

\textbf{Romans 8:39} - nor height nor depth, nor anything else in all creation, will be able to separate us from the love of God in Christ Jesus our Lord.

\subsection{God was faithful to us first}
\label{sec:org0b2ae47}
\subsubsection{God's faithfulness is greater}
\label{sec:org0b73a4f}
\textbf{Romans 3:3-4} - What if some were unfaithful? Does their faithlessness nullify the faithfulness of God? By no means! Let God be true though every one were a liar, as it is written, That you may be justified in your words, and prevail when you are judged.

\textbf{II Timothy 2:13} - if we are faithless, he remains faithful— for he cannot deny himself.

\subsection{The Way is available for everyone, but not everyone ends up walking it}
\label{sec:org2edbfcd}
Jesus made the Way - He \textbf{is} the Way:

\textbf{Romans 5:18-19} - Therefore, as one trespass led to condemnation for all men, so one act of righteousness \uline{leads to} \textbf{justification and life} for \textbf{all men}. For as by the one man's disobedience the many were made sinners, so by the one man's obedience \textbf{the many} will be made righteous.

\begin{itemize}
\item for all men
\item the many
\end{itemize}

\subsection{Seeking God}
\label{sec:orgc2b4eb7}
\begin{itemize}
\item Blessed are those who like being around Jesus and trust Him:
\begin{itemize}
\item \textbf{Luke 7:23} - And blessed is the one who is not offended by me.
\end{itemize}

\item Blessed are those who have believed before having come to see and know for certain:
\begin{itemize}
\item \textbf{John 20:29} - Jesus said to him, Have you believed because you have seen me? Blessed are those who have not seen and yet have believed.􇩙
\end{itemize}

\item Blessed are those who ask and seek for a blessing:
\begin{itemize}
\item \textbf{Matthew 7:7-8} - Ask, and it will be given to you; seek, and you will find; knock, and it will be opened to you. For everyone who asks receives, and the one who seeks finds, and to the one who knocks it will be opened.
\end{itemize}
\end{itemize}

\subsection{Run the race}
\label{sec:org7d1988d}
\begin{itemize}
\item \textbf{Hebrews 12:1} - Therefore, since we are surrounded by so great a cloud of witnesses, let us also lay aside every weight, and sin which clings so closely, and let us run with endurance the race that is set before us,
\end{itemize}
= \textbf{I Corinthians 9:24} - Do you not know that in a race all the runners compete, but only one receives the prize? So run that you may obtain it.
\begin{itemize}
\item \textbf{Luke 13:24} - Strive to enter through the narrow door. For many, I tell you, will seek to enter and will not be able.
\item \textbf{Galatians 5:7} - You were running well. Who hindered you from obeying the truth? (ESV)
\item \textbf{Philippians 3:13-14} - Brothers, I do not consider that I have made it my own. But one thing I do: forgetting what lies behind and straining forward to what lies ahead, I press on toward the goal for the prize of the upward call of God in Christ Jesus. (ESV)
\item \textbf{II Timothy 4:6-9} - For I am already being poured out as a drink offering, and the time of my departure has come. I have fought the good fight, I have finished the race, I have kept the faith. Henceforth there is laid up for me the crown of righteousness, which the Lord, the righteous judge, will award to me on that Day, and not only to me but also to all who have loved his appearing. Do your best to come to me soon.
\end{itemize}

\subsection{God has planned in advance our salvation}
\label{sec:org536cc45}
\subsubsection{Grace alone - \texttt{sola gratia} (by grace alone) AMEN!!}
\label{sec:orgd2f2233}
\textbf{Ephesians 1:3} - Blessed be the God and Father of our Lord Jesus Christ, who has blessed us in Christ with every spiritual blessing in the heavenly places, (ESV)

\textbf{Ephesians 1:4-5} - just as He chose (G1586 eklegomai) us in Him before (G4253 pro) the foundation of the world (G2889 kosmos), that we would be holy and blameless before Him. In love He predestined (G4309 \textbf{proorizo}) us to adoption as sons through Jesus Christ to Himself, according to the kind intention (G2107 eudokia) of His will, (NASB)

\begin{verbatim}
1  :  1586  eklegomai  ek-leg'-om-ahee
2  
3   middle voice from 1537 and 3004 (in its primary sense); to
4   select:--make choice, choose (out), chosen.
5   see GREEK for 1537
6   see GREEK for 3004
\end{verbatim}

\begin{verbatim}
1  :  4309  proorizo  pro-or-id'-zo
2  
3   from 4253 and 3724; to limit in advance, i.e. (figuratively)
4   predetermine:--determine before, ordain, predestinate.
5   see GREEK for 4253
6   see GREEK for 3724
\end{verbatim}

In the fullness of time, all things in heaven and earth are united to God:

\textbf{Ephesians 1:10} - as a plan for the fullness of time, to unite all things in him, things in heaven and things on earth.

Given that we have an inheritance, it's evident that God must have predestined us:

\textbf{Ephesians 1:11-14} - In him we have obtained an inheritance, having been predestined according to the purpose of him who works all things according to the counsel of his will, so that we who were the first to hope in Christ might be to the praise of his glory. In him you also, when you heard the word of truth, the gospel of your salvation, and believed in him, were sealed with the promised Holy Spirit, who is the guarantee of our inheritance until we acquire possession of it, to the praise of his glory.

\subsection{We are fellow workers with God. It's by God's power that our work flourishes}
\label{sec:org4d20d41}
\textbf{Ephesians 3:16} - that according to the riches of his glory he may grant you to be \textbf{strengthened with power through his Spirit} in your inner being,

\subsubsection{Without God we can do nothing}
\label{sec:org6763b34}
\textbf{I Corinthians 3:6-9} - I planted, Apollos watered, but God gave the growth. So neither he who plants nor he who waters is anything, but only God who gives the growth. He who plants and he who waters are one, and each will receive his wages according to his labor. For we are God's fellow workers. You are God's field, God's building.

\textbf{John 1:3} -  All things were made through him, and without him was not any thing made that was made.  (ESV)

We work in God's field:

\textbf{John 4:34-38} - Jesus said to them, My food is to do the will of him who sent me and to accomplish his work. Do you not say, There are yet four months, then comes the harvest? Look, I tell you, lift up your eyes, and see that the fields are white for harvest. Already the one who reaps is receiving wages and gathering fruit for eternal life, so that sower and reaper may rejoice together. For here the saying holds true, One sows and another reaps. I sent you to reap that for which you did not labor. Others have labored, and you have entered into their labor.

\subsubsection{God's power through Jesus, through the man's faith in Jesus' name made the man walk}
\label{sec:org77f9515}
\textbf{Acts 3:12} - And when Peter saw it, he answered unto the people, Ye men of Israel, why marvel ye at this? or why look ye so earnestly on us, as though by our own power or holiness we had made this man to walk? (KJV)

The man had faith - faith enters into the truth / receives from God:

\textbf{Acts 3:5-8} - And he began to give them his attention, \uline{expecting to receive something from them}. But Peter said, “I do not possess silver and gold, but what I do have I give to you: In the name of Jesus Christ the Nazarene-- walk!” And seizing him by the right hand, he raised him up; and immediately his feet and his ankles were strengthened. With a leap he stood upright and began to walk; and he entered the temple with them, walking and leaping and praising God.

Jesus made the man walk through Jesus' power and Jesus' holiness:

\textbf{Acts 3:11-12} - While he was clinging to Peter and John, all the people ran together to them at the so-called portico of Solomon, full of amazement. But when Peter saw this, he replied to the people, “Men of Israel, why are you amazed at this, or \uline{why do you gaze at us, as if by our own power or piety we had made him walk}?

The faith which He had in Jesus' name is what healed him:

\textbf{Acts 3:16} - And on the basis of faith in His name, it is \uline{the name of Jesus which has strengthened this man whom you see and know}; and \uline{the faith which comes through Him has given him this perfect health} in the presence of you all.

There are other instances of this - it's faith in Jesus which makes a person well and receives forgiveness and salvation from Jesus:

\textbf{Mark 5:34} -  And he said to her, Daughter, your faith has made you well; go in peace, and be healed of your disease.  (ESV)

\textbf{Luke 7:47-50} - Therefore I tell you, her sins, which are many, are forgiven-for she loved much. But he who is forgiven little, loves little. And he said to her, Your sins are forgiven. Then those who were at table with him began to say among themselves, Who is this, who even forgives sins? And he said to the woman, Your faith has saved you; go in peace. (ESV)

\section{Sanctification}
\label{sec:orgf47842d}
\textbf{2 Thessalonians 2:13-15} -  But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through sanctification by the Spirit and belief in the truth.  To this he called you through our gospel, so that you may obtain the glory of our Lord Jesus Christ.  So then, brothers, stand firm and hold to the traditions that you were taught by us, either by our spoken word or by our letter.  (ESV)

\textbf{II Thessalonians 2:13} - But we should always give thanks (G2168 eucharisteo) to God for you, brethren beloved by the Lord, because God has chosen you from the beginning (G746 arche) for salvation through sanctification by the Spirit and faith (G4102 \textbf{pistis}) in the truth (G225 aletheia). (NASB)

\textbf{Faith} in the truth - strong faith word!

\textbf{II Thessalonians 2:11-15} - Therefore God sends them a strong delusion, so that they may believe what is false, in order that all may be condemned who did not believe the truth but had pleasure in unrighteousness. But we ought always to give thanks to God for you, brothers beloved by the Lord, because God chose you as the firstfruits to be saved, through \textbf{sanctification by the Spirit} and \textbf{belief in the truth}. To this he called you through our gospel, so that you may obtain the glory of our Lord Jesus Christ. So then, brothers, stand firm and hold to the traditions that you were taught by us, either by our spoken word or by our letter.  (ESV)

\textbf{Hebrews 10:10} - And by that will we have been sanctified through the offering of the body of Jesus Christ once for all. (ESV)

\textbf{1 Thessalonians 4:3} -  For this is the will of God, your sanctification: that you \uline{abstain} from sexual immorality;  (ESV)

\uline{Abstain} means stop.

\subsection{God is the source of our life in Christ Jesus. Jesus is \underline{the source of} our wisdom and righteousness and sanctification and redemption}
\label{sec:org0fceece}
\textbf{1 Corinthians 1:30-31} -  He is the source of your life in Christ Jesus, whom God made our wisdom and our righteousness and sanctification and redemption.  Therefore, as it is written, Let the one who boasts, boast in the Lord.  (ESV)

\subsubsection{We only boast in Christ Jesus, since He is our wisdom, righteousness, sanctification and redemption}
\label{sec:org9853abb}
He is our wisdom, righteousness, sanctification and redemption.
We are wise for salvation through faith in Christ Jesus.

\textbf{2 Timothy 3:15} -  and how from childhood you have been acquainted with the sacred writings, which are able to make you wise for salvation through faith in Christ Jesus.  (ESV)

We must put our trust in Jesus and believe Him and obey Him.

\textbf{I Corinthians 1:28-29} - God chose what is low and despised in the world, even things that are not, to bring to nothing things that are, so that no human being might boast in the presence of God.

\textbf{Psalms 5:5} -  The boastful shall not stand before your eyes; you hate all evildoers.  (ESV)

\textbf{Galatians 6:14} -  But far be it from me to boast except in the cross of our Lord Jesus Christ, by which the world has been crucified to me, and I to the world.  (ESV)

\subsubsection{Filled with the fruit of righteousness that comes through Jesus Christ, to the glory and praise of God}
\label{sec:orgc1f5474}
Jesus is the source of our personal righteousness, and He \textbf{is} our righteousness.

\textbf{Philippians 1:9-11} - And it is my prayer that your love may abound more and more, with knowledge and all discernment, so that you may approve what is excellent, and so be pure and blameless for the day of Christ, filled with the fruit of righteousness that comes through Jesus Christ, to the glory and praise of God.

\subsection{We must \textbf{both} believe the truth and be sanctified, \textbf{and} stop sinning to be saved}
\label{sec:org0421959}
\textbf{II Thessalonians 2:13} - But we should always give thanks (G2168 eucharisteo) to God for you, brethren beloved by the Lord, because God has chosen you from the beginning (G746 arche) for salvation through sanctification by the Spirit \textbf{and} faith (G4102 \textbf{pistis}) in the truth (G225 aletheia). (NASB)

Cleaned up (stop sinning) by having faith in the truth.

\textbf{Faith} in the truth - strong faith word! Belief and ongoing faithfulness, trust, reliance.

\begin{verbatim}
1  :  4102  pistis  pis'-tis
2  
3   from 3982; persuasion, i.e. credence; moral conviction (of religious
4   truth, or the truthfulness of God or a religious teacher), especially
5   reliance upon Christ for salvation; abstractly, constancy in such
6   profession; by extension, the system of religious (Gospel) truth
7   itself:--assurance, belief, believe, faith, fidelity.
8   see GREEK for 3982
\end{verbatim}

\subsubsection{Bad desire - leads to death. We do not want to be enslaved to corruption}
\label{sec:org0ad98af}
\begin{itemize}
\item Lust is super bad, even after born-again.
\end{itemize}

\textbf{I John 2:15-17} - Do not love the world nor the things in the world. If anyone loves the world, the love of the Father is not in him. For all that is in the world, the lust of the flesh and the lust of the eyes and the boastful pride of life, is not from the Father, but is from the world. The world is passing away, and also its lusts; but the one who does the will of God lives forever.

\textbf{II Peter 2:19-21} - They promise them freedom, but they themselves are slaves of corruption. For whatever overcomes a person, to that he is enslaved. For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first. For it would have been better for them never to have known \textbf{the way of righteousness} than after knowing it to turn back from the holy commandment delivered to them.

\subsubsection{Good desire - Love God and one's neighbour}
\label{sec:orgba711a1}
\textbf{Deuteronomy 11:13} - And if you will indeed obey my commandments that I command you today, to love the Lord your God, and to serve him with all your heart and with all your soul,

\textbf{Deuteronomy 30:6} - And the Lord your God will circumcise your heart and the heart of your offspring, so that you will love the Lord your God with all your heart and with all your soul, that you may live.

\textbf{Joshua 22:5} - Only be very careful to observe the commandment and the law that Moses the servant of the Lord commanded you, to love the Lord your God, and to walk in all his ways and to keep his commandments and to cling to him and to serve him with all your heart and with all your soul.

\textbf{Luke 10:27} - And he answered, You shall love the Lord your God with all your heart and with all your soul and with all your strength and with all your mind, and your neighbor as yourself.

\textbf{Leviticus 19:18} - You shall not take vengeance or bear a grudge against the sons of your own people, but you shall love your neighbor as yourself: I am the Lord.

\section{Father God}
\label{sec:orge5b2f30}
\textbf{II Chronicles 15:3-4} - For a long time Israel was without the true God, and without a teaching priest and without law, but when in their distress they turned to the Lord, the God of Israel, and sought him, he was found by them.

\textbf{Jeremiah 10:10} - But the Lord is the true God; he is the living God and the everlasting King. At his wrath the earth quakes, and the nations cannot endure his indignation.

\textbf{Ephesians 3:9-11} - and to bring to light for everyone what is the plan of the mystery hidden for ages in God who created all things, so that through the church the manifold wisdom of God might now be made known to the rulers and authorities in the heavenly places. This was according to the eternal purpose that he has realized in Christ Jesus our Lord,

\textbf{Romans 1:18-25} - For the wrath of God is revealed from heaven against all ungodliness and unrighteousness of men, who by their unrighteousness suppress the truth. For what can be known about God is plain to them, because God has shown it to them. For his invisible attributes, namely, his eternal power and divine nature, have been clearly perceived, ever since the creation of the world, in the things that have been made. So they are without excuse. For although they knew God, they did not honor him as God or give thanks to him, but they became futile in their thinking, and their foolish hearts were darkened. Claiming to be wise, they became fools, and exchanged the glory of the immortal God for images resembling mortal man and birds and animals and reptiles. Therefore God gave them up in the lusts of their hearts to impurity, to the dishonoring of their bodies among themselves, because they exchanged the truth about God for a lie and worshiped and served the creature rather than the Creator, who is blessed forever! Amen.

\section{Sun's light failing as the curtain was torn and Jesus died}
\label{sec:org842a933}
\textbf{Mark 15:37-39} - And Jesus uttered a loud cry and breathed his last. And the curtain of the temple was torn in two, from top to bottom. And when the centurion, who stood facing him, saw that in this way he breathed his last, he said, Truly this man was the Son of God! (ESV)

\textbf{Matthew 27:51} - And behold, the curtain of the temple was torn in two, from top to bottom. And the earth shook, and the rocks were split. (ESV)

\textbf{Mark 15:38} - And the curtain of the temple was torn in two, from top to bottom. (ESV)

\textbf{Luke 23:43-46} - And he said to him, Truly, I say to you, today you will be with me in Paradise. It was now about the sixth hour, and there was darkness over the whole land until the ninth hour, while the sun's light failed. And the curtain of the temple was torn in two. Then Jesus, calling out with a loud voice, said, Father, into your hands I commit my spirit! And having said this he breathed his last. (ESV)

\textbf{Hebrews 6:19-20} - We have this as a sure and steadfast anchor of the soul, a hope that enters into the inner place behind the curtain, where Jesus has gone as a forerunner on our behalf, having become a high priest forever after the order of Melchizedek. (ESV)

\textbf{Hebrews 9:11-15} - But when Christ appeared as a high priest of the good things that have come, then through the greater and more perfect tent (not made with hands, that is, not of this creation) he entered once for all into the holy places, not by means of the blood of goats and calves but by means of his own blood, thus securing an eternal redemption. For if the sprinkling of defiled persons with the blood of goats and bulls and with the ashes of a heifer sanctifies for the purification of the flesh, how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God. Therefore he is the mediator of a new covenant, so that those who are called may receive the promised eternal inheritance, since a death has occurred that redeems them from the transgressions committed under the first covenant. (ESV)

\textbf{Hebrews 10:12-14} - But when Christ had offered for all time a single sacrifice for sins, he sat down at the right hand of God, waiting from that time until his enemies should be made a footstool for his feet. For by a single offering he has perfected for all time those who are being sanctified. (ESV)

\textbf{Hebrews 10:19-20} - Therefore, brothers, since we have confidence to enter the holy places by the blood of Jesus, by the new and living way that he opened for us through the curtain, that is, through his flesh, (ESV)

\section{Jesus rose from the dead and ascended}
\label{sec:org7e428d0}
\textbf{Luke 24:1-7} - But on the first day of the week, at early dawn, they came to the tomb bringing the spices which they had prepared. And they found the stone rolled away from the tomb, but when they entered, they did not find the body of the Lord Jesus. While they were perplexed about this, behold, two men suddenly stood near them in dazzling clothing; and as the women were terrified and bowed their faces to the ground, the men said to them, “Why do you seek the living One among the dead? He is not here, but He has risen. Remember how He spoke to you while He was still in Galilee, saying that the Son of Man must be delivered into the hands of sinful men, and be crucified, and the third day rise again.” (ESV)

\textbf{Luke 24:25-26} - And he said to them, O foolish ones, and slow of heart to believe all that the prophets have spoken! Was it not necessary that the Christ should suffer these things and enter into his glory? (ESV)

\textbf{Luke 24:38-49} - And he said to them, Why are you troubled, and why do doubts arise in your hearts? See my hands and my feet, that it is I myself. Touch me, and see. For a spirit does not have flesh and bones as you see that I have. And when he had said this, he showed them his hands and his feet. And while they still disbelieved for joy and were marveling, he said to them, Have you anything here to eat? They gave him a piece of broiled fish, and he took it and ate before them. Then he said to them, These are my words that I spoke to you while I was still with you, that everything written about me in the Law of Moses and the Prophets and the Psalms must be fulfilled. Then he opened their minds to understand the Scriptures, and said to them, Thus it is written, that the Christ should suffer and on the third day rise from the dead, and that repentance and forgiveness of sins should be proclaimed in his name to all nations, beginning from Jerusalem. You are witnesses of these things. And behold, I am sending the promise of my Father upon you. But stay in the city until you are clothed with power from on high. (ESV)

\subsection{Ascension}
\label{sec:org5a46d78}
\textbf{Luke 24:50-53} - And He led them out as far as Bethany, and He lifted up His hands and blessed them. While He was blessing them, He parted from them and was carried up into heaven. And they, after worshiping Him, returned to Jerusalem with great joy, and were continually in the temple praising God. (ESV)

\textbf{Acts 1:1-12} - The first account I composed, Theophilus, about all that Jesus began to do and teach, until the day when He was taken up to heaven, after He had by the Holy Spirit given orders to the apostles whom He had chosen. To these He also presented Himself alive after His suffering, by many convincing proofs, appearing to them over a period of forty days and speaking of the things concerning the kingdom of God. Gathering them together, He commanded them not to leave Jerusalem, but to wait for what the Father had promised, “Which,” He said, “you heard of from Me; for John baptized with water, but you will be baptized with the Holy Spirit not many days from now.” So when they had come together, they were asking Him, saying, “Lord, is it at this time You are restoring the kingdom to Israel?” He said to them, “It is not for you to know times or epochs which the Father has fixed by His own authority; but you will receive power when the Holy Spirit has come upon you; and you shall be My witnesses both in Jerusalem, and in all Judea and Samaria, and even to the remotest part of the earth.” And after He had said these things, He was lifted up while they were looking on, and a cloud received Him out of their sight. And as they were gazing intently into the sky while He was going, behold, two men in white clothing stood beside them. They also said, “Men of Galilee, why do you stand looking into the sky? This Jesus, who has been taken up from you into heaven, will come in just the same way as you have watched Him go into heaven.” Then they returned to Jerusalem from the mount called Olivet, which is near Jerusalem, a Sabbath day’s journey away. (ESV)

\section{Solae}
\label{sec:org1edbd0c}
I believe in all of theses:
\begin{itemize}
\item \texttt{sola fida} (by faith alone) AMEN!!.
\begin{itemize}
\item The justifying faith may include 'acts of faith', which is just visible faith.
\item Works done outside of faith \textbf{do not} qualify for justification.
\end{itemize}
\item \texttt{sola gratia} (by grace alone) AMEN!!
\item \texttt{sola scriptura} (by Scripture alone) AMEN!!
\item \texttt{Solus Christus} AMEN!!
\item \texttt{Soli Deo gloria} (glory to God alone) AMEN!! But the glory God gives us glorifies God.
\begin{itemize}
\item When it comes to forgiving offenses of others, my understanding is that it is about forgiving others' offenses against 'you', thereby ultimately still going through Christ for forgiveness, since
\item \textbf{John 20:22-23} - And when he had said this, he breathed on them and said to them, Receive the Holy Spirit. (ESV)
\item \textbf{Proverbs 19:11} - Good sense makes one slow to anger, and it is his glory to overlook an offense. (ESV)
\item \textbf{Matthew 6:12} - and forgive us our debts, as we also have forgiven our debtors.
\item \textbf{Matthew 18:35} - So also my heavenly Father will do to every one of you, if you do not forgive your brother from your heart.
\item \textbf{Mark 11:25} - And whenever you stand praying, forgive, if you have anything against anyone, so that your Father also who is in heaven may forgive you your trespasses.
\item \textbf{Ephesians 4:32} - Be kind to one another, tender-hearted, forgiving each other, just as God in Christ also has forgiven you.
\item \textbf{Matthew 10:8} -  Heal the sick, raise the dead, cleanse lepers, cast out demons.  You received without paying; give without pay. (ESV)
\end{itemize}
\end{itemize}

\section{Then, glorification}
\label{sec:org847818e}
Jesus sent us. We seek to glorify Jesus. We seek to glorify our Master.
We seek to glorify God. We seek to be found in Jesus. We seek the glorification that comes from being found in our Master, Jesus Christ.

\textbf{John 7:18} - The one who speaks on his own authority seeks his own glory, but the one who seeks the glory of him who sent him is true, and in him there is no falsehood.

The glory comes from God:

\textbf{John 5:44} - How can you believe, when you receive glory from one another and do not seek the glory that comes from the only God?

\textbf{Psalms 73:24} - You guide me with your counsel, and afterward you will receive me to glory.

God glorifies Jesus:

\textbf{John 5:41} - I do not receive glory from people.

\textbf{John 8:54} - Jesus answered, If I glorify myself, my glory is nothing. It is my Father who glorifies me, of whom you say, He is our God.

God glorifies Himself through glorifying Jesus through working through Jesus. The power comes from God:

\textbf{John 11:4} - But when Jesus heard it he said, This illness does not lead to death. It is for the glory of God, so that the Son of God may be glorified through it.

\textbf{John 13:32} - If God is glorified in him, God will also glorify him in himself, and glorify him at once.

Jesus glorifies us by working through us to do God's work which also glorifies Jesus and glorifies God:

\textbf{John 14:13} - Whatever you ask in my name, this I will do, that the Father may be glorified in the Son.

\textbf{John 15:8} - By this my Father is glorified, that you bear much fruit and so prove to be my disciples.

The Spirit whom those who have faith in Jesus receive works through us:

\textbf{John 7:39} - Now this he said about the Spirit, whom those who believed in him were to receive, for as yet the Spirit had not been given, because Jesus was not yet glorified.

Jesus glorified God by accomplishing the work that God gave Him - Jesus obeyed God.

\textbf{John 17:4} - I glorified you on earth, having accomplished the work that you gave me to do.

Likewise, we must obey God, and obey God by obeying Jesus, and being sanctified in the Truth. By having faith in Jesus and trusting in the Truth, and obeying, we are cleaned, transformed and made to glorify God:

\textbf{John 17:8-26} - For I have given them the words that you gave me, and they have received them and have come to know in truth that I came from you; and they have believed that you sent me.  I am praying for them. I am not praying for the world but for those whom you have given me, for they are yours.  All mine are yours, and yours are mine, and I am glorified in them.  And I am no longer in the world, but they are in the world, and I am coming to you. Holy Father, keep them in your name, which you have given me, that they may be one, even as we are one.  While I was with them, I kept them in your name, which you have given me. I have guarded them, and not one of them has been lost except the son of destruction, that the Scripture might be fulfilled.  But now I am coming to you, and these things I speak in the world, that they may have my joy fulfilled in themselves.  I have given them your word, and the world has hated them because they are not of the world, just as I am not of the world.  I do not ask that you take them out of the world, but that you keep them from the evil one.  They are not of the world, just as I am not of the world.  Sanctify them in the truth; your word is truth.  As you sent me into the world, so I have sent them into the world.  And for their sake I consecrate myself, that they also may be sanctified in truth.  I do not ask for these only, but also for those who will believe in me through their word, that they may all be one, just as you, Father, are in me, and I in you, that they also may be in us, so that the world may believe that you have sent me.  The glory that you have given me I have given to them, that they may be one even as we are one, I in them and you in me, that they may become perfectly one, so that the world may know that you sent me and loved them even as you loved me.  Father, I desire that they also, whom you have given me, may be with me where I am, to see my glory that you have given me because you loved me before the foundation of the world.  O righteous Father, even though the world does not know you, I know you, and these know that you have sent me.  I made known to them your name, and I will continue to make it known, that the love with which you have loved me may be in them, and I in them.

\textbf{II Thessalonians 1:10} - when he comes on that day to be glorified in his saints, and to be marveled at among all who have believed, because our testimony to you was believed.

\subsubsection{Glorification is Christ-likeness}
\label{sec:org8b5f540}
Glorification is the good works including forgiving others, relieving others' burdens, etc. suffering for the sake of righteousness and obedience to God.

Imitating Jesus, forgiving others, walking righteously, and doing good works (bearing one-another's burdens) glorifies Jesus and glorifies God.

This should never replace Jesus, but glorifies Jesus because it's being a disciple of Jesus.

\textbf{Hebrews 2:10} - For it was fitting for Him, for whom (G3739 hos) are all (G3956 pas) things (G3956 pas), and through whom (G3739 hos) are all (G3956 pas) things (G3956 pas), in \textbf{bringing many sons to glory} (G1391 doxa), to perfect (G5048 teleioo) the author of their salvation (G4991 soteria) through sufferings.

If someone's lord is money and not Jesus and then they try to do good works such as setting up businesses, I feel like this glorifies money, not Jesus.

Here, Zacchaeus, renounces money and makes Jesus his Lord. This must happen first.

\textbf{Luke 19:8} - And Zacchaeus stood and said to the Lord, Behold, Lord, the half of my goods I give to the poor. And if I have defrauded anyone of anything, I restore it fourfold. (ESV)

Abram did this too. It's a necessary act of faith.

\textbf{Genesis 14:20-24} - and blessed be God Most High, who has delivered your enemies into your hand! And Abram gave him a tenth of everything. And the king of Sodom said to Abram, Give me the persons, but take the goods for yourself. But Abram said to the king of Sodom, I have lifted my hand to the Lord, God Most High, Possessor of heaven and earth, that I would not take a thread or a sandal strap or anything that is yours, lest you should say, I have made Abram rich. I will take nothing but what the young men have eaten, and the share of the men who went with me. Let Aner, Eshcol, and Mamre take their share.

\textbf{Genesis 15:1} - After these things the word of the Lord came to Abram in a vision: Fear not, Abram, I am your shield; your reward shall be very great.

\subsubsection{True obedience leads to glory/holiness/Christ-likeness}
\label{sec:org8fcc955}
For example, to truly obey God and love / do no harm to one's neighbour involves relieving other's burdens as they ask more from you.

\textbf{Philippians 2:8} - And being found in human form, he humbled himself by becoming obedient to the point of death, even death on a cross.

Jesus endured the weight of His cross to lighten our burden.

\textbf{Hebrews 12:3} - Consider him who endured from sinners such hostility against himself, so that you may not grow weary or fainthearted.

We are called to do the same, lightening the burdens of others.
We are forgiven and given grace, then we can choose to forgive others and lighten their burdens - grace propagates.

\textbf{Hebrews 12:4-6} - In your struggle against sin you have not yet resisted to the point of shedding your blood. And have you forgotten the exhortation that addresses you as sons? My son, do not regard lightly the discipline of the Lord, nor be weary when reproved by him. For the Lord disciplines the one he loves, and chastises every son whom he receives.

\textbf{Hebrews 12:10} - For they disciplined us for a short time as it seemed best to them, but he disciplines us for our good, that we may share his holiness.

\subsubsection{Forgive others' offenses towards you is glory}
\label{sec:org5283ad1}
\textbf{Proverbs 19:11} - Good sense makes one slow to anger, and it is his glory to overlook an offense. (ESV)

\textbf{Ephesians 4:32} - Be kind to one another, tenderhearted, forgiving one another, as God in Christ forgave you. (ESV)

You are required to:
\begin{itemize}
\item forgive others for your sake
\item forgive others for their sake
\item forgive others as a response of love to Jesus for your sins being forgiven
\item to be able to forgive others is a gift to you and part of glorification
\end{itemize}

This is simultaneously required and is part of glorification/holiness.

I think there's something very important about forgiving others especially for things which happen after being born-again of the Spirit and receiving the Holy Spirit.

\textbf{Colossians 3:13} - bearing with one another and, if one has a complaint against another, forgiving each other; as the Lord has forgiven you, so you also must forgive.

\textbf{John 20:21-23} - Jesus said to them again, Peace be with you. As the Father has sent me, even so I am sending you. And when he had said this, he breathed on them and said to them, Receive the Holy Spirit. If you forgive the sins of anyone, they are forgiven; if you withhold forgiveness from anyone, it is withheld.

Especially immediately after receiving the Holy Spirit, Jesus forgives those who you forgive - this is partaking in the process of forgiveness.

Jesus is the one who forgives sin, but we actually participate in propagating that forgiveness.

\emph{\textbf{Forgiving others entirely is also required}}

Jesus can forgive others even if you do not, but Father God cannot forgive you unless you forgive.

\textbf{Matthew 6:12} - and forgive us our debts, as we also have forgiven our debtors.

\textbf{Matthew 6:14-15} - For if you forgive others their trespasses, your heavenly Father will also forgive you,

\textbf{Matthew 18:35} - So also my heavenly Father will do to every one of you, if you do not forgive your brother from your heart.

\subsubsection{Be extremely generous - give without limits to relieve the burdens of others}
\label{sec:org2419f05}
\textbf{Matthew 10:8} - Heal the sick, raise the dead, cleanse lepers, cast out demons. You received without paying; give without pay. (ESV)

\textbf{1 Peter 4:8} - Above all, keep loving one another earnestly, since love covers a multitude of sins. (ESV)

\textbf{Luke 6:35-36} - But love your enemies, and do good, and lend, expecting nothing in return, and your reward will be great, and you will be sons of the Most High, for he is kind to the ungrateful and the evil. Be merciful, even as your Father is merciful. (ESV)

\textbf{Mark 12:41-44} - And he sat down opposite the treasury and watched the people putting money into the offering box. Many rich people put in large sums. And a poor widow came and put in two small copper coins, which make a penny. And he called his disciples to him and said to them, Truly, I say to you, this poor widow has put in more than all those who are contributing to the offering box. For they all contributed out of their abundance, but s he out of her poverty has put in everything she had, all she had to live on. (ESV)

Dominating others in your flock is like witchcraft, and will forfeit glorification.

\textbf{1 Peter 5:1-4} - So I exhort the elders among you, as a fellow elder and a witness of the sufferings of Christ, as well as a partaker in the \textbf{glory} that is going to be revealed: shepherd the flock of God that is among you, exercising oversight, not under compulsion, but willingly, as God would have you; not for shameful gain, but eagerly; \textbf{not domineering} over those in your charge, but being examples to the flock. And when the chief Shepherd appears, you will receive the unfading crown of glory. (ESV)

One is supposed to suffer with Christ for glory and be an example to the flock.

\subsubsection{Do the good works which have been gifted to you}
\label{sec:org70d40be}
\textbf{Ephesians 2:10} - For we are his workmanship, created in Christ Jesus for good works, which God prepared beforehand, that we should walk in them. (ESV)

\textbf{Matthew 5:16} - In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. (ESV)

\subsubsection{Walk in righteousness}
\label{sec:org8a57fa7}

\textbf{Daniel 12:3} - And those who are wise shall shine like the brightness of the sky above; and those who turn many to righteousness, like the stars forever and ever. (ESV)

\subsubsection{The deeds of glory - Christlikeness}
\label{sec:orge02bd84}
All the times a person has acted in Christlike obedience:
\begin{itemize}
\item forgiving others in knowledge they have been forgiven themselves
\item giving mercy to others in knowledge they have themselves received mercy
\item encouraging one-another
\item serve others
\item suffering as a Christian
\item etc.
\end{itemize}

God glorifies Jesus (His Son) so Jesus may glorify Him (God).
Jesus glorifies us (His disciples) so we may glorify Him (Jesus) and glorify God by glorifying Jesus.

This is obedience.

\textbf{John 17:1} - When Jesus had spoken these words, he lifted up his eyes to heaven, and said, Father, the hour has come; glorify your Son that the Son may glorify you,

\textbf{John 17:4} - I glorified you on earth, having accomplished the work that you gave me to do.

God glorifies Jesus.
Jesus obeyed God and accomplished the work God gave Him.
Jesus showed God's truthfulness through His obedience. Jesus showed God to be true and glorified God:
\begin{itemize}
\item \textbf{Romans 15:8-9} - For I tell you that Christ became a servant to the circumcised to show God's truthfulness, in order to confirm the promises given to the patriarchs, and \textbf{in order that the Gentiles might glorify God for his mercy}. As it is written, Therefore I will praise you among the Gentiles, and sing to your name.
\end{itemize}

Jesus glorifies us:
We must obey Jesus and accomplish the work God gives us.

\textbf{John 8:54} - Jesus answered, If I glorify myself, my glory is nothing. It is my Father who glorifies me, of whom you say, He is our God.

Jesus is glorified in us - our glory is His glory because we obey Him and show Jesus's truthfulness as Jesus has shown God's truthfulness:

\textbf{John 17:22-23} - The glory that you have given me I have given to them, that they may be one even as we are one, I in them and you in me, that they may become perfectly one, so that the world may know that you sent me and loved them even as you loved me.

Jesus is glorified in us.

\textbf{John 17:10} - All mine are yours, and yours are mine, and I am glorified in them. (ESV)

Jesus accomplished His work.
we must accomplish our work.

\textbf{John 17:4} - I glorified you on earth, having accomplished the work that you gave me to do.

Christlikeness:
\begin{itemize}
\item \textbf{I Peter 2:12} - Keep your conduct among the Gentiles honorable, so that when they speak against you as evildoers, they may see your good deeds and glorify God on the day of visitation.

\item \textbf{Romans 12:1} - I appeal to you therefore, brothers, by the mercies of God, to present your bodies as a living sacrifice, holy and acceptable to God, which is your spiritual worship.

\item \textbf{Revelation of John 19:8} - it was granted her to clothe herself with fine linen, bright and pure— for the fine linen is the righteous deeds of the saints.

\item Suffering for Christian obedience, as Christ suffered for His obedience
\begin{itemize}
\item \textbf{John 21:18-19} - Truly, truly, I say to you, when you were young, you used to dress yourself and walk wherever you wanted, but when you are old, you will stretch out your hands, and another will dress you and carry you where you do not want to go. (This he said to show by what kind of death he was to glorify God. ) And after saying this he said to him, Follow me.
\item \textbf{I Peter 4:16} - Yet if anyone suffers as a Christian, let him not be ashamed, but let him glorify God in that name.
\end{itemize}

\item Please your neighbour for their good
\begin{itemize}
\item \textbf{Romans 15:2-3} - Let each of us please his neighbor for his good, to build him up. For Christ did not please himself, but as it is written, The reproaches of those who reproached you fell on me.
\end{itemize}

\item Welcome one another as Christ has welcomed you. Live in harmony with one-another, encouraging and serving one another [as Christ did]
\begin{itemize}
\item \textbf{Romans 15:5-7} May the God of endurance and encouragement grant you to live in such harmony with one another, in accord with Christ Jesus, that together you may with one voice glorify the God and Father of our Lord Jesus Christ. Therefore welcome one another as Christ has welcomed you, for the glory of God.
\end{itemize}
\item Be merciful and serving to others, show God's truthfulness. glorify God by your conduct
\begin{itemize}
\item \textbf{Romans 15:8-9} - For I tell you that Christ became a servant to the circumcised to show God's truthfulness, in order to confirm the promises given to the patriarchs, and \textbf{in order that the Gentiles might glorify God for his mercy}. As it is written, Therefore I will praise you among the Gentiles, and sing to your name.
\begin{itemize}
\item Others then praise God
\end{itemize}
\end{itemize}
\item Supply the needs of the saints
\begin{itemize}
\item \textbf{II Corinthians 9:12} - For the ministry of this service is not only supplying the needs of the saints, but is also overflowing in many thanksgivings to God.
\end{itemize}
\item Be thankful to God
\begin{itemize}
\item \textbf{II Corinthians 9:13} - By their approval of this service, they will glorify God because of your submission flowing from your confession of the gospel of Christ, and the generosity of your contribution for them and for all others,
\end{itemize}
\end{itemize}

\subsubsection{Seeing Jesus, appearing in glory}
\label{sec:orgba9db22}
\textbf{1 John 3:2} -  Beloved, we are God's children now, and what we will be has not yet appeared; but we know that when he appears we shall be like him, because we shall see him as he is.  (ESV)

\textbf{1 Corinthians 1:4-8} - I give thanks to my God always for you because of the grace of God that was given you in Christ Jesus, that in every way you were enriched in him in all speech and all knowledge— even as the testimony about Christ was confirmed among you— so that you are not lacking in any spiritual gift, as you wait for the revealing of our Lord Jesus Christ, who will sustain you to the end, guiltless in the day of our Lord Jesus Christ. (ESV)

\textbf{Colossians 3:4} - When Christ who is your life appears, then you also will appear with him in glory. (ESV)

\textbf{Philippians 1:6} - And I am sure of this, that he who began a good work in you will bring it to completion at the day of Jesus Christ. (ESV)

\textbf{Philippians 1:10} - so that you may approve what is excellent, and so be pure and blameless for the day of Christ, (ESV)

\textbf{Philippians 2:16} - holding fast to the word of life, so that in the day of Christ I may be proud that I did not run in vain or labor in vain. (ESV)

\textbf{John 6:39} -  And this is the will of him who sent me, that I should lose nothing of all that he has given me, but raise it up on the last day.  (ESV)

\subsubsection{The putting off of the body}
\label{sec:org8e575f8}
\textbf{II Peter 1:13-21} - I think it right, as long as I am in this body, to stir you up by way of reminder, since I know that the putting off of my body will be soon, as our Lord Jesus Christ made clear to me.  And I will make every effort so that after my departure you may be able at any time to recall these things.  For we did not follow cleverly devised myths when we made known to you the power and coming of our Lord Jesus Christ, but we were eyewitnesses of his majesty.  For when he received honor and glory from God the Father, and the voice was borne to him by the Majestic Glory, This is my beloved Son, with whom I am well pleased, we ourselves heard this very voice borne from heaven, for we were with him on the holy mountain.  And we have something more sure, the prophetic word, to which you will do well to pay attention as to a lamp shining in a dark place, until the day dawns and the morning star rises in your hearts, knowing this first of all, that no prophecy of Scripture comes from someone's own interpretation.  For no prophecy was ever produced by the will of man, but men spoke from God as they were carried along by the Holy Spirit.

\subsubsection{I think to relax commandments is throw away glorification}
\label{sec:org1d63082}
\textbf{Matthew 5:19} - Therefore whoever relaxes one of the least of these commandments and teaches others to do the same will be called least in the kingdom of heaven, but whoever does them and teaches them will be called great in the kingdom of heaven. (ESV)

However, I'm not placing myself under the Mosaic law.
My job is to do God's will, and I believe I have to maintain faithfulness to God with regards to His will for my life,
being led by the Holy Spirit, not making Mosaic law compliance my objective, but making God's will my objective.
So, for example, that means making disciples of Jesus.
Also, that means deepening my relationship with Jesus.

\textbf{Matthew 24:35} - Heaven and earth will pass away, but my words will not pass away.

\section{Praising and thanking God in Heaven:}
\label{sec:org9812d12}
We should start now.

\textbf{Revelation 7:9-12} -   After this I looked, and behold, a great multitude that no one could number, from every nation, from all tribes and peoples and languages, standing before the throne and before the Lamb, clothed in white robes, with palm branches in their hands, and crying out with a loud voice, Salvation belongs to our God who sits on the throne, and to the Lamb! And all the angels were standing around the throne and around the elders and the four living creatures, and they fell on their faces before the throne and worshiped God, saying, Amen! Blessing and glory and wisdom and thanksgiving and honor and power and might be to our God forever and ever! Amen.  (ESV)

\section{I don't want to think too hard about theology, but it is important - writing this was worthwhile in arriving at a sound understanding}
\label{sec:org514bfac}
By God's grace I've been set free from sin, and brought into a relationship with God, and have hope for the future now.

\textbf{Ephesians 2:12-13} -  remember that you were at that time separated from Christ, alienated from the commonwealth of Israel and strangers to the covenants of promise, having no hope and without God in the world.  But now in Christ Jesus you who once were far off have been brought near by the blood of Christ.  (ESV)

\textbf{Deuteronomy 29:29} -  The secret things belong to the LORD our God, but the things that are revealed belong to us and to our children forever, that we may do all the words of this law.  (ESV)

\textbf{Proverbs 3:5-6} - Trust in the LORD with all your heart, and do not lean on your own understanding. In all your ways acknowledge him, and he will make straight your paths. (ESV)

\textbf{Jeremiah 29:11} -  For I know the plans I have for you, declares the LORD, plans for wholeness and not for evil, to give you a future and a hope.  (ESV)

\textbf{Ephesians 2:10} - For we are his workmanship, created in Christ Jesus for good works, which God prepared beforehand, that we should walk in them. (ESV)

\textbf{Matthew 5:16} - In the same way, let your light shine before others, so that they may see your good works and give glory to your Father who is in heaven. (ESV)

\section{Jesus Christ is Lord! :)}
\label{sec:org5edf494}
\textbf{I Timothy 1:17} - To the King of ages, immortal, invisible, the only God, be honor and glory forever and ever. Amen.

\section{AMEN!!}
\label{sec:org4c2ec0a}
\href{https://www.youtube.com/watch?v=TEa3UWFgwnk}{Therea??s Only One Acceptable Motive To Serve God - YouTube}

The motivation for everything must be to glorify God.

\subsection{Do the will of the Father - obey Jesus - AMEN!!}
\label{sec:org9afd249}

\href{https://www.youtube.com/watch?v=v60efH7\_POE\&t=616s}{The most terrifying passage in the Bible | Matthew 7:21-23 - YouTube}

\textbf{Luke 8:21} - But He answered and said to them, “My mother and My brothers are these who hear the word of God \uline{and do it}.” (ESV)

It's obedience which leads to righteousness, even the righteousness of faith.

\textbf{Romans 6:16} - Do you not know that if you present yourselves to anyone as obedient slaves, you are slaves of the one whom you obey, either of sin, which leads to death, or of \textbf{obedience, which leads to righteousness}? (ESV)

\textbf{Romans 4:12-13} - and to make him the father of the circumcised who are not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised. For the promise to Abraham and his offspring that he would be heir of the world did not come through the law but through the righteousness of faith.

\subsubsection{A heart of obedience is the start of faith}
\label{sec:orgbae7924}

\textbf{John 7:17} -  If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.  (ESV)

\subsection{For one's work to stand the test of fire}
\label{sec:orgaa9779b}
\begin{itemize}
\item For God's Glory
\item Obedience to the Word of God
\item Working in the power of the Holy Spirit
\end{itemize}

\begin{center}
\begin{tabular}{l}
God's telephone number\\[0pt]
\hline
\textbf{Jeremiah 33:3} - Call to me and I will answer you, and will tell you great and hidden things that you have not known. (ESV)\\[0pt]
\\[0pt]
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{l}
The password\\[0pt]
\hline
\textbf{Psalms 100:4} -  Enter his gates with thanksgiving, and his courts with praise! Give thanks to him; bless his name!  (ESV)\\[0pt]
\end{tabular}
\end{center}

\subsection{Prayer of thanks}
\label{sec:orge3f7ba5}
\begin{verbatim}
 1  Dear Heavenly Father, Almighty Jehovah God!
 2  Your will be done.
 3  We praise Your name! We praise You God! And, Lord Jesus Christ, we praise You also.
 4  And Holy Spirit, we praise You also!
 5  Thank You God for Your mercy! 
 6  Thank You Father God for making a way for us to be reconciled with You through Your Son Jesus Christ!
 7  Thank You Jesus for dying on the cross to pay the price for our sins.
 8  Thank You Father God for raising Jesus from the dead!
 9  I believe that You've raised Jesus from dead.
10  Please help us to continue carrying out Your great commission.
11  And I'm going to do my best to prepare myself to be holy and blameless for the day of Christ Jesus and to honor You with my life.
12  All glory to You, God.
13  In Jesus Christ's name I pray,
14  AMEN!!
\end{verbatim}

\begin{itemize}
\item \textbf{Romans 3:25} -  whom God put forward as a propitiation by his blood, to be received by faith.  This was to show God's righteousness, because in his divine forbearance he had passed over former sins.  (ESV)

\item \textbf{Colossians 2:14} - by canceling the record of debt that stood against us with its legal demands. This he set aside, nailing it to the cross.

\item \textbf{Philippians 1:9-11} - And it is my prayer that your love may abound more and more, with knowledge and all discernment, so that you may approve what is excellent, and so be pure and blameless for the day of Christ, filled with the fruit of righteousness that comes through Jesus Christ, to the glory and praise of God.
\end{itemize}
\end{document}