% Created 2024-03-08 Fri 17:48
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}
\author{Shane Mulligan}
\date{\textit{<2024-06-02 Sun>}}
\title{Gospel of Jesus Christ}
\hypersetup{
 pdfauthor={Shane Mulligan},
 pdftitle={Gospel of Jesus Christ},
 pdfkeywords={faith christianity},
 pdfsubject={},
 pdfcreator={Emacs 29.1.50 (Org mode 9.6.8)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{\underline{Belief} and \underline{Obedience} are both essential for permanent abiding in Christ}
\label{sec:orgc92279d}
If someone obeys Jesus they should arrive at belief in Jesus and who He is and what He has accomplished; they should accept Him:

\begin{quote}
\textbf{John 8:42} - Jesus said to them, If God were your Father, you would love me, for I came from God and I am here. I came not of my own accord, but he sent me.
\end{quote}

If a person believes on Jesus and what He has accomplished they should arrive at obedience. Technically, if someone believes on Him they have begun to obey Him:

\begin{quote}
\textbf{John 15:10-14} - If you keep my commandments, you will abide in my love, just as I have kept my Father's commandments and abide in his love. These things I have spoken to you, that my joy may be in you, and that your joy may be full. This is my commandment, that you love one another as I have loved you. Greater love has no one than this, that someone lays down his life for his friends. You are my friends if you do what I command you.
\end{quote}

I think faith in Jesus grows as both of these qualities increase.

\begin{itemize}
\item Those who believe in part yet do not obey the gospel, I think fall into condemnation.
\item Those who obey in part yet do not believe the gospel, I think also fall into condemnation
\end{itemize}

Love (obedience) and belief:

\begin{quote}
\textbf{John 16:27-28} - for the Father himself loves you, because you have loved me and have believed that I came from God. I came from the Father and have come into the world, and now I am leaving the world and going to the Father.
\end{quote}

\begin{quote}
\textbf{John 15:16} - You did not choose me, but I chose you and appointed you that you should go and bear fruit and that your fruit should abide, so that whatever you ask the Father in my name, he may give it to you.
\end{quote}

\subsection{Forever abiding is believing and being a disciple}
\label{sec:org34cc782}
\begin{quote}
\textbf{John 15:4-8} - Abide in me, and I in you. As the branch cannot bear fruit by itself, unless it abides in the vine, neither can you, unless you abide in me. I am the vine; you are the branches. Whoever abides in me and I in him, he it is that bears much fruit, for apart from me you can do nothing. If anyone does not abide in me he is thrown away like a branch and withers; and the branches are gathered, thrown into the fire, and burned. If you abide in me, and my words abide in you, ask whatever you wish, and it will be done for you. By this my Father is glorified, that you bear much fruit and so prove to be my disciples.
\end{quote}

\begin{quote}
\textbf{John 12:20-26} - Now among those who went up to worship at the feast were some Greeks. So these came to Philip, who was from Bethsaida in Galilee, and asked him, Sir, we wish to see Jesus. Philip went and told Andrew; Andrew and Philip went and told Jesus. And Jesus answered them, The hour has come for the Son of Man to be glorified. Truly, truly, I say to you, unless a grain of wheat falls into the earth and dies, it remains alone; but if it dies, it bears much fruit. Whoever loves his life loses it, and whoever hates his life in this world will keep it for eternal life. If anyone serves me, he must follow me; and where I am, there will my servant be also. If anyone serves me, the Father will honor him. (ESV)
\end{quote}

AMEN!!

\section{Gospel}
\label{sec:org63a606a}
\begin{quote}
\textbf{John 3:16-21} - For God so loved the world, that he gave his only Son, that whoever (G3956 pas) believes (G4100 pisteuo) in him should not perish but have eternal life. For God did not send his Son into the world to condemn the world, but in order that the world might be saved through him. Whoever believes in him is not condemned, but whoever does not believe is condemned already, because he has not believed in the name of the only Son of God. And this is the judgment: the light has come into the world, and people loved the darkness rather than the light because their deeds were evil. For everyone who does wicked things hates the light and does not come to the light, lest his deeds should be exposed. But \uline{whoever does what is true comes to the light}, so that \uline{it may be clearly seen that his deeds have been carried out in God}. (ESV)
\end{quote}

The gospel involves a believing and obedient heart.

Whoever \uline{does what is true comes to the light.}

\uline{Whoever has faith in and puts their trust in in Jesus Christ is not condemned and should not perish.}

We must honour Jesus Christ:

\begin{quote}
\textbf{John 5:21-24} - For as the Father raises the dead and gives them life, so also the Son gives life to whom he will. The Father judges no one, but has given all judgment to the Son, that all may honor the Son, just as they honor the Father. \uline{Whoever does not honor the Son does not honor the Father who sent him}. Truly, truly, I say to you, whoever \uline{hears my word and believes (G4100 \textbf{pisteuo}) him who sent me has eternal life}. He does not come into judgment, but has passed from death to life.
\end{quote}

I believe \texttt{John 5:24} is a true statement and that it should not be read outside of the words Jesus said directly before it (\texttt{Whoever does not honor the Son does not honor the Father who sent him}).

We do not nullify the rest of what Jesus has commanded of and asked of us. If Jesus is your judge, then I think it's wise to take on board the rest of what Jesus has said:

\begin{quote}
\textbf{Philippians 1:15-22} - Some indeed preach Christ from envy and rivalry, but others from good will. The latter do it out of love, knowing that I am put here for the defense of the gospel. The former proclaim Christ out of rivalry, not sincerely but thinking to afflict me in my imprisonment. What then? Only that in every way, whether in pretense or in truth, Christ is proclaimed, and in that I rejoice. Yes, and I will rejoice, for I know that through your prayers and the help of the Spirit of Jesus Christ this will turn out for my deliverance, as \uline{it is my eager expectation and hope that I will not be at all ashamed, but that with full courage now as always Christ will be honored in my body, whether by life or by death}. For to me to live is Christ, and to die is gain. \uline{If I am to live in the flesh, that means fruitful labor for me.} Yet which I shall choose I cannot tell.
\end{quote}

We're not justified through the works of the law but through faith, and faith involves obedience to Jesus Christ:

\begin{quote}
\textbf{Galatians 2:15-16} - “We are Jews by nature and not sinners from among the Gentiles; nevertheless knowing that a man is not justified by the works of the Law but through faith in Christ Jesus, even we have believed in Christ Jesus, so that we may be \textbf{justified by faith in Christ} and not by the works of the Law; since by the works of the Law no flesh will be justified.
\end{quote}

It's by faith in Christ that we are justified, and faith involves obedience (at least of the heart).

\begin{quote}
\textbf{John 3:36} - Whoever believes (G4100 pisteuo) in the Son has eternal life; whoever does not \textbf{obey} the Son shall not see life, but the wrath of God remains on him. (ESV)
\end{quote}

It's faith in the heart which we need; obedience to Jesus Christ and belief in Jesus Christ in the heart, and belief and obedience to God who has \uline{raised from the dead Jesus our Lord, who was delivered up for our trespasses and raised for our justification}.

\begin{quote}
\textbf{John 7:17} -  If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.  (ESV)
\end{quote}

The Father is not the Son (Jesus Christ) but Jesus has been perfectly obedient, so Jesus speaks what Father God speaks, and when someone seeks Jesus Christ, they see Father God, because Father God has been revealed in Jesus Christ:

\uline{the Father who sent me has himself given me a commandment—what to say and what to speak.}

\textbf{John 12:44-48} - And Jesus cried out and said, Whoever believes in me, believes not in me but in him who sent me. And whoever sees me sees him who sent me. I have come into the world as light, so that whoever believes in me may not remain in darkness. If anyone hears my words and does not keep them, I do not judge him; for I did not come to judge the world but to save the world. The one who rejects me and does not receive my words has a judge; the word that I have spoken will judge him on the last day.

Jesus' words bring eternal life. The commandment which Father God gave Jesus is eternal life and the commandment is what Jesus Christ has spoken:

\textbf{John 12:49-50}- For I have not spoken on my own authority, but \uline{the Father who sent me has himself given me a commandment—what to say and what to speak.} And I know that \uline{his commandment is eternal life. What I say, therefore, I say as the Father has told me.}

We need to obey Jesus Christ and walk as God has commanded and spoken through Jesus:

\textbf{John 14:6-11} - Jesus said to him, I am the way, and the truth, and the life. No one comes to the Father except through me. If you had known me, you would have known my Father also. From now on you do know him and have seen him. Philip said to him, Lord, show us the Father, and it is enough for us. Jesus said to him, Have I been with you so long, and you still do not know me, Philip? Whoever has seen me has seen the Father. How can you say, Show us the Father? Do you not believe that I am in the Father and the Father is in me? The words that I say to you I do not speak on my own authority, but the Father who dwells in me does his works. Believe me that I am in the Father and the Father is in me, or else believe on account of the works themselves.

We must believe Jesus, and have faith in Jesus Christ, obeying Jesus:

\begin{quote}
\textbf{John 3:16} - For God so loved the world, that he gave his only Son, that whoever believes (G4100 pisteuo) in him should not perish but have eternal life. (ESV)
\end{quote}

\begin{verbatim}
1  :  4100  pisteuo  pist-yoo'-o
2  
3   from 4102; to have faith (in, upon, or with respect to, a person or
4   thing), i.e. credit; by implication, to entrust (especially one's
5   spiritual well-being to Christ):--believe(-r), commit (to trust), put
6   in trust with.
7   see GREEK for 4102
\end{verbatim}

\begin{verbatim}
1  :  166  aionios  ahee-o'-nee-os
2  
3   from 165; perpetual (also used of past time, or past and future as
4   well):--eternal, for ever, everlasting, world (began).
5   see GREEK for 165
\end{verbatim}

\begin{verbatim}
1  :  2222  zoe  dzo-ay'
2  
3   from 2198; life (literally or figuratively):--life(-time). Compare
4   5590.
5   see GREEK for 2198
6   see GREEK for 5590
\end{verbatim}

\begin{quote}
\textbf{1 John 3:23} - And this is his commandment, that we believe in the name of his Son Jesus Christ and love one another, just as he has commanded us. (ESV)
\end{quote}

\begin{quote}
\textbf{Matthew 22:37-39} - And he said to him, You shall love the Lord your God with all your heart and with all your soul and with all your mind. This is the great and first commandment. And a second is like it: You shall love your neighbor as yourself. (ESV)
\end{quote}

Jesus Christ is the Son of the Living God. Believing on His name is God's will for us, and loving one another is God's will for us as He has commanded. There is more that Jesus has commanded us, too.

The promise to Gentiles:

\begin{quote}
\textbf{Galatians 3:8} - And the Scripture, foreseeing that God would justify the Gentiles by faith, preached the gospel beforehand to Abraham, saying, In you shall all the nations be blessed. (ESV)
\end{quote}

\begin{quote}
\textbf{Genesis 12:3} - I will bless those who bless you, and him who dishonors you I will curse, and in you all the families of the earth shall be blessed. (ESV)
\end{quote}

Because Abraham \uline{obeyed God's voice}:

\begin{quote}
\textbf{Genesis 22:18} - and in your offspring shall all the nations of the earth be blessed, because you have obeyed my voice. (ESV)
\end{quote}

Repentance and coming to the light are absolutely part of the gospel!

\begin{quote}
\textbf{1 Corinthians 15:1-4} -  Now I would remind you, brothers, of the gospel I preached to you, which you received, in which you stand, and by which you are being saved, if you hold fast to the word I preached to you-unless you believed in vain.  For I delivered to you as of first importance what I also received: that Christ died for our sins in accordance with the Scriptures, that he was buried, that he was raised on the third day in accordance with the Scriptures,  (ESV)
\end{quote}

\begin{quote}
\textbf{Acts 2:47} - Praising God, and having favour with all the people. And the Lord added to the church daily such as should be saved. (ESV)
\end{quote}

\subsection{I believe that I should try as hard as I can to enter via the narrow gate}
\label{sec:org0501709}
\subsubsection{Narrow is the gate and hard is the lway that leads to life}
\label{sec:org27d0a76}
\begin{quote}
\textbf{Matthew 7:13} - Enter by the narrow gate. For the gate is wide and the way is easy that leads to destruction, and those who enter by it are many.
\end{quote}

\begin{quote}
\textbf{Matthew 7:14} - For the gate is narrow and the way is hard that leads to life, and those who find it are few.
\end{quote}

\begin{quote}
\textbf{Luke 13:24} - Strive to enter through the narrow door. For many, I tell you, will seek to enter and will not be able.
\end{quote}

\subsubsection{Obedience}
\label{sec:orgb35b06a}
\begin{quote}
\textbf{Ezekiel 33:31} - And they come to you as people come, and they sit before you as my people, and \uline{they hear what you say but they will not do it}; for with lustful talk in their mouths they act; their heart is set on their gain. (ESV)
\end{quote}

\subsubsection{The way is easy that leads to destruction}
\label{sec:orgfb4118e}
\begin{quote}
\textbf{Matthew 7:13} - Enter by the narrow gate. For the gate is wide and the way is easy that leads to destruction, and those who enter by it are many.
\end{quote}

\subsubsection{Narrow gate}
\label{sec:org91e8439}
\begin{quote}
\textbf{II Peter 1:10} - Therefore, brothers, be all the more diligent to make your calling and election sure, for if you practice these qualities you will never fall. (ESV)
\end{quote}

\begin{quote}
\textbf{Hebrews 4:11} - Let us therefore strive to enter that rest, so that no one may fall by the same sort of disobedience. (ESV)
\end{quote}

\begin{quote}
\textbf{I Corinthians 9:24-27} - Do you not know that in a race all the runners compete, but only one receives the prize? So run that you may obtain it. Every athlete exercises self-control in all things. They do it to receive a perishable wreath, but we an imperishable. So I do not run aimlessly; I do not box as one beating the air. But I discipline my body and keep it under control, lest after preaching to others I myself should be disqualified. (ESV)
\end{quote}

\begin{quote}
\textbf{Philippians 2:12-13} - Therefore, my beloved, as you have always obeyed, so now, not only as in my presence but much more in my absence, work out your own salvation with fear and trembling, for it is God who works in you, both to will and to work for his good pleasure. (ESV)
\end{quote}

\subsubsection{Submit to God's righteousness}
\label{sec:org7d2b9d7}
\begin{quote}
\textbf{Romans 10:3} - For, being ignorant of the righteousness that comes from God, and seeking to establish their own, they did not submit to God's righteousness. (ESV)
\end{quote}

\subsubsection{We must do the will of God, which is the food and drink which Jesus gives us}
\label{sec:org99caf4e}
\begin{quote}
\textbf{John 6:27} - Do not labor for the food that perishes, but for the food that endures to eternal life, which the Son of Man will give to you. For on him God the Father has set his seal. (ESV)
\end{quote}

\begin{quote}
\textbf{John 7:34-39} - You will seek me and you will not find me. Where I am you cannot come. (ESV) The Jews said to one another, Where does this man intend to go that we will not find him? Does he intend to go to the Dispersion among the Greeks and teach the Greeks?  What does he mean by saying, You will seek me and you will not find me, and, Where I am you cannot come?  On the last day of the feast, the great day, Jesus stood up and cried out, If anyone thirsts, let him come to me and drink.  Whoever believes in me, as the Scripture has said, Out of his heart will flow rivers of living water.  Now this he said about the Spirit, whom those who believed in him were to receive, for as yet the Spirit had not been given, because Jesus was not yet glorified.
\end{quote}

\subsection{A life of faith (living in accordance with the truth, and in relationship with God) is required - faith continues}
\label{sec:org34179a8}
What I mean by relationship is:
\begin{itemize}
\item being obedient to God,
\begin{itemize}
\item abiding in Jesus
\end{itemize}
\item being accountable to God,
\item waiting on God,
\item trusting on God,
\item being led by the Spirit of God,
\item etc.
\end{itemize}

\subsubsection{We must abide by his teaching}
\label{sec:org4317990}

\begin{quote}
\textbf{II John 1:9} - Everyone who goes on ahead and does not abide in the teaching of Christ, does not have God. Whoever abides in the teaching has both the Father and the Son.
\end{quote}

It is a gift to be obedient to Jesus:

\begin{quote}
\textbf{Romans 6:23} - For the wages of sin is death, but the free gift of God is eternal life \uline{in} Christ Jesus our Lord. (ESV)
\end{quote}

\subsubsection{We must live sowing to the Spirit}
\label{sec:orgbcdbf13}

\begin{quote}
\textbf{Galatians 6:7-8} - Do not be deceived: God is not mocked, for whatever one sows, that will he also reap. For the one who sows to his own flesh will from the flesh reap corruption, but the one who sows to the Spirit will from the Spirit reap eternal life. (ESV)
\end{quote}

\subsubsection{We must be servants of Christ}
\label{sec:orgb99bd9b}

\begin{quote}
\textbf{Ephesians 6:6} - not by the way of eye-service, as people-pleasers, but as servants of Christ, doing the will of God from the heart,
\end{quote}

\subsubsection{We must remain faithful to Jesus Christ}
\label{sec:org56e73a0}

\begin{quote}
\textbf{Jude 1:4} - For certain persons have crept in unnoticed, those who were long beforehand marked out for this condemnation, ungodly persons who turn the grace of our God into licentiousness and deny our only Master and Lord, Jesus Christ. (NASB)
\end{quote}

\begin{quote}
\textbf{Colossians 2:18-19} - Let no one disqualify you, insisting on asceticism and worship of angels, going on in detail about visions, puffed up without reason by his sensuous mind, and not holding fast to the Head, from whom the whole body, nourished and knit together through its joints and ligaments, grows with a growth that is from God.
\end{quote}

\subsubsection{We should clean ourselves with the aid of the Word and the Holy Spirit}
\label{sec:orgd89e0b8}
We should clean ourselves up:

\begin{quote}
\textbf{II Timothy 2:21} - Therefore, if anyone cleanses himself from what is dishonorable, he will be a vessel for honorable use, set apart as holy, useful to the master of the house, ready for every good work.
\end{quote}

Through faith, the Holy Spirit cleanses us:

\begin{quote}
\textbf{Acts 15:8-9} - And God, who knows the heart, bore witness to them, by giving them the Holy Spirit just as he did to us, and he made no distinction between us and them, having cleansed their hearts by faith.
\end{quote}

By obedience to the word of God:

\begin{quote}
\textbf{Ephesians 5:25-27} - Husbands, love your wives, as Christ loved the church and gave himself up for her, that he might sanctify her, having cleansed her by the washing of water with the word, so that he might present the church to himself in splendor, without spot or wrinkle or any such thing, that she might be holy and without blemish.
\end{quote}

By the Holy Spirit washing and renewing us:

\begin{quote}
\textbf{Titus 3:4-6}- But when the goodness and loving kindness of God our Savior appeared, he saved us, not because of works done by us in righteousness, but according to his own mercy, by the washing of regeneration and renewal of the Holy Spirit, whom he poured out on us richly through Jesus Christ our Savior,
\end{quote}

It's the will of God:

\begin{quote}
\textbf{I Thessalonians 4:3} - For this is the will of God, your sanctification: that you abstain from sexual immorality;
\end{quote}

\subsubsection{We \textbf{must} clean ourselves up with God's help}
\label{sec:org522f04b}

\begin{quote}
\textbf{Daniel 12:9-10} - He said, Go your way, Daniel, for the words are shut up and sealed until the time of the end.  Many shall purify themselves and make themselves white and be refined, but the wicked shall act wickedly. And none of the wicked shall understand, but those who are wise shall understand.
\end{quote}

\begin{quote}
\textbf{Revelation of John 21:27} - But nothing unclean will ever enter it, nor anyone who does what is detestable or false, but only those who are written in the Lamb's book of life.
\end{quote}

\begin{quote}
\textbf{Revelation of John 22:14} - Blessed are those who wash their robes, so that they may have the right to the tree of life and that they may enter the city by the gates. (ESV)
\end{quote}

\subsubsection{We must stop sinning}
\label{sec:org8c70fb7}

\begin{quote}
\textbf{II Peter 2:2-4} - And many will follow their sensuality, and because of them \uline{the way of truth} will be blasphemed. And in their greed they will exploit you with false words. Their condemnation from long ago is not idle, and their destruction is not asleep. For if God did not spare angels when they sinned, but cast them into hell and committed them to chains of gloomy darkness to be kept until the judgment;
\end{quote}

\begin{quote}
\textbf{II Peter 2:19-20} - They promise them freedom, but they themselves are slaves of corruption. For \uline{whatever overcomes a person, to that he is enslaved}. For if, after they have escaped the defilements of the world through the knowledge of our Lord and Savior Jesus Christ, they are again entangled in them and overcome, the last state has become worse for them than the first.
\end{quote}

Therefore, the way of truth involves following Jesus and putting a stop to sin.

I agree with Billy Graham:
\begin{itemize}
\item \url{https://www.youtube.com/watch?v=jCrhHjQgVhA}
\end{itemize}

\begin{quote}
\textbf{Revelation of John 21:8} - But as for the cowardly, the faithless, the detestable, as for murderers, the sexually immoral, sorcerers, idolaters, and all liars, their portion will be in the lake that burns with fire and sulfur, which is the second death." (ESV)
\end{quote}

\subsubsection{We should put the ignorant to silence through doing good}
\label{sec:orge3ad8d4}

\begin{quote}
\textbf{I Peter 2:15} - For this is the will of God, that by doing good you should put to silence the ignorance of foolish people.
\end{quote}

Jesus says you must obey God to be part of His family:

\begin{quote}
\textbf{Luke 8:21} - But He answered and said to them, “My mother and My brothers are these who hear the word of God and do it.”
\end{quote}

Jesus implies you must obey Him (Jesus) to be part of His family:

\begin{quote}
\textbf{John 7:16} - So Jesus answered them, My teaching is not mine, but his who sent me.
\end{quote}

\subsection{The obedient children are the ones who are not conformed to the passions of our former ignorance}
\label{sec:orge78d77e}
\begin{quote}
\textbf{I Peter 1:14-16} - As obedient children, do not be conformed to the passions of your former ignorance, but as he who called you is holy, you also be holy in all your conduct, since it is written, You shall be holy, for I am holy.
\end{quote}

\subsection{The sons of disobedience are the ones who are conformed to sexual immorality, impurity, or covetousness, etc.}
\label{sec:orgb43dded}
\begin{quote}
\textbf{Ephesians 5:5-7} - For you may be sure of this, that everyone who is sexually immoral or impure, or who is covetous (that is, an idolater), has no inheritance in the kingdom of Christ and God. Let no one deceive you with empty words, for because of these things the wrath of God comes upon the sons of disobedience. Therefore do not associate with them;
\end{quote}

\subsection{Get to know Jesus by following His commandments}
\label{sec:org523546d}
\begin{quote}
\textbf{Matthew 7:21-27} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven.  On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name?  And then will I declare to them, I never knew you; depart from me, you workers of lawlessness.  Everyone then who hears these words of mine and does them will be like a wise man who built his house on the rock.  And the rain fell, and the floods came, and the winds blew and beat on that house, but it did not fall, because it had been founded on the rock.  And everyone who hears these words of mine and does not do them will be like a foolish man who built his house on the sand.  And the rain fell, and the floods came, and the winds blew and beat against that house, and it fell, and great was the fall of it. (ESV)
\end{quote}

\begin{quote}
\textbf{Luke 6:46-49} - Why do you call me Lord, Lord, and not do what I tell you? Everyone who comes to me and hears my words and does them, I will show you what he is like: he is like a man building a house, who dug deep and laid the foundation on the rock. And when a flood arose, the stream broke against that house and could not shake it, because it had been well built. But the one who hears and does not do them is like a man who built a house on the ground without a foundation. When the stream broke against it, immediately it fell, and the ruin of that house was great. (ESV)
\end{quote}

\begin{quote}
\textbf{I John 2:4} - Whoever says I know him but does not keep his commandments is a liar, and the truth is not in him,
\end{quote}

\begin{quote}
\textbf{Matthew 7:21-27} - Not everyone who says to me, Lord, Lord, will enter the kingdom of heaven, but the one who does the will of my Father who is in heaven.  On that day many will say to me, Lord, Lord, did we not prophesy in your name, and cast out demons in your name, and do many mighty works in your name?  And then will I declare to them, I never knew you; depart from me, you workers of lawlessness.  Everyone then who hears these words of mine and does them will be like a wise man who built his house on the rock.  And the rain fell, and the floods came, and the winds blew and beat on that house, but it did not fall, because it had been founded on the rock.  And everyone who hears these words of mine and does not do them will be like a foolish man who built his house on the sand.  And the rain fell, and the floods came, and the winds blew and beat against that house, and it fell, and great was the fall of it. (ESV)
\end{quote}

You must obey Jesus:

\begin{quote}
\textbf{John 3:36} - Whoever believes (G4100 \textbf{pisteuo}) in the Son has eternal life; whoever does not \textbf{obey} the Son shall not see life, but the wrath of God remains on him. (ESV)
\end{quote}

We must obey God. We have faith in God who was delivered up for our trespasses and raised for our justification, and having faith in God is having faith in His Son which is believing in and obeying Jesus Christ:

\begin{quote}
\textbf{Romans 4:23-25} - But the words it was counted to him were not written for his sake alone, but for ours also. It will be counted to us who believe (G4100 \textbf{pisteuo}) in him who raised from the dead Jesus our Lord, who was delivered up for our trespasses and raised for our justification. (ESV)
\end{quote}

\subsection{Atonement}
\label{sec:org5746bd2}
Jesus' sacrifice is the only atonement for our sin we need. It's comprehensive.
It must be received through faith in Jesus Christ.

\begin{quote}
\begin{itemize}
\item \textbf{Romans 3:25} -  whom God put forward as a propitiation by his blood, to be received by faith.  This was to show God's righteousness, because in his divine forbearance he had passed over former sins.  (ESV)
\end{itemize}
\end{quote}

\begin{quote}
\begin{itemize}
\item \textbf{Colossians 2:14} - by canceling the record of debt that stood against us with its legal demands. This he set aside, nailing it to the cross.
\end{itemize}
\end{quote}

\begin{quote}
\begin{itemize}
\item \textbf{Philippians 1:9-11} - And it is my prayer that your love may abound more and more, with knowledge and all discernment, so that you may approve what is excellent, and so be pure and blameless for the day of Christ, filled with the fruit of righteousness that comes through Jesus Christ, to the glory and praise of God.
\end{itemize}
\end{quote}

We receive reconciliation through Jesus Christ who is our Lord.

\begin{quote}
\textbf{Romans 5:11} - More than that, we also rejoice in God through our Lord Jesus Christ, through whom we have now received reconciliation. (ESV)
\end{quote}

\begin{quote}
\textbf{Romans 5:19} - For as by the one man's disobedience the many were made sinners, so by the one man's obedience the many will be made righteous. (ESV)
\end{quote}

\subsection{Whoever makes an appeal to God, calls upon His name will be saved}
\label{sec:orgeae35f5}
\begin{verbatim}
1  :  1941  epikaleomai  ep-ee-kal-eh'-om-ahee
2  
3   middle voice from 1909 and 2564; to entitle; by implication, to invoke
4   (for aid, worship, testimony, decision, etc.):--appeal (unto), call
5   (on, upon), surname.
6   see GREEK for 1909
7   see GREEK for 2564
\end{verbatim}

Confessing that Jesus is Lord is becoming obedient to Him:

\begin{quote}
\textbf{Romans 10:8-9} - But what does it say? “The word is near you, in your mouth and in your heart”-- that is, the word (G4487 rhema) of faith (G4102 pistis) which we are preaching, that if you confess (G3670 homologeo) with your mouth Jesus as Lord, and \uline{believe (G4100 \textbf{pisteuo}) in your heart} (G2588 kardia) that God raised Him from the dead, you will be saved; (NASB)
\end{quote}

It's faith in the heart that a person needs.

\begin{quote}
\textbf{John 7:17} -  If anyone's will is to do God's will, he will know whether the teaching is from God or whether I am speaking on my own authority.  (ESV)
\end{quote}

Therefore, to arrive at the knowledge of the truth, you've got to have an obedient heart.

How can they call on Him whom they have not had faith in?

How will they have faith in Him whom they have not heard?

How will they hear without a preacher?

\begin{quote}
\textbf{Romans 10:14-15}- But how are they to call on him in whom they have not believed? And how are they to believe in him of whom they have never heard? And how are they to hear without someone preaching? And how are they to preach unless they are sent? As it is written, How beautiful are the feet of those who preach the good news!
\end{quote}

Confess:

\begin{verbatim}
1  :  3670  homologeo  hom-ol-og-eh'-o
2  
3   from a compound of the base of 3674 and 3056; to assent, i.e.
4   covenant, acknowledge:--con- (pro-)fess, confession is made, give
5   thanks, promise.
6   see GREEK for 3674
7   see GREEK for 3056
\end{verbatim}

\subsubsection{Baptism is an appeal}
\label{sec:orga8b5828}
Baptism is an appeal to God for a good conscience - It's an \textbf{appeal} to God but not strictly required to be saved.
It is an appeal to God for a good conscience, through the resurrection of Jesus Christ.
I definitely believe that "believer's baptism" is the right way to perform baptism.
Baptism does save.

\begin{quote}
\textbf{I Peter 3:18-21} - For Christ also suffered once for sins, the righteous for the unrighteous, that he might bring us to God, being put to \textbf{death in the flesh but made alive in the spirit}, in which he went and proclaimed to the spirits in prison, because \textbf{they formerly did not obey}, when God's patience waited in the days of Noah, while the ark was being prepared, in which a few, that is, eight persons, were brought safely through water. Baptism, which corresponds to this, now saves you, not as a removal of dirt from the body but as an appeal to God for a good conscience, through the resurrection of Jesus Christ,
\end{quote}

\subsection{God adopts children, fellow heirs with Christ}
\label{sec:orgb022024}
The sons of God on earth who are being adopted by God:
\begin{itemize}
\item are led by the Spirit
\begin{itemize}
\item obeying Jesus Christ
\end{itemize}
\item are sons of Abraham, with the faith of Abraham
\begin{itemize}
\item demonstrating the faith that Abraham had
\end{itemize}
\item have had faith in Jesus Christ's name
\item suffer with Christ in order to be glorified with Him
\item await their adoption as sons when our bodies are redeemed
\item have the creation eagerly longing for their revealing
\item have heard God and had faith
\end{itemize}

\begin{quote}
\textbf{Romans 8:14-23} - For \uline{all who are led by the Spirit of God are sons of God.} For you did not receive the spirit of slavery to fall back into fear, but you have received the Spirit of adoption as sons, by whom we cry, Abba! Father! The Spirit himself bears witness with our spirit that we are children of God, and if children, then heirs—heirs of God and fellow heirs with Christ, \uline{provided we suffer with him in order that we may also be glorified with him.} For I consider that the sufferings of this present time are not worth comparing with the glory that is to be revealed to us. For the creation waits with eager longing for the revealing of the sons of God. For the creation was subjected to futility, not willingly, but because of him who subjected it, in hope that the creation itself will be set free from its bondage to decay and obtain the freedom of the glory of the children of God. For we know that the whole creation has been groaning together in the pains of childbirth until now. And not only the creation, but we ourselves, who have the firstfruits of the Spirit, groan inwardly as \uline{we wait eagerly for adoption as sons, the redemption of our bodies.} (ESV)
\end{quote}

To those who had faith in His name:

\begin{quote}
\textbf{Acts 3:16} - And his name—by faith in his name—has made this man strong whom you see and know, and the faith that is through Jesus has given the man this perfect health in the presence of you all.
\end{quote}

John the Baptist came as a witness to the Light that is Jesus Christ, so that through John the Baptist's testimony, all might come to faith:

\begin{quote}
\textbf{John 1:6-7} - There came a man sent from God, whose name was John. He came as a witness (G3141 marturia), to testify (G3140 martureo) about the Light, so that all might believe (G4100 pisteuo) through him. (NASB)
\end{quote}

Jesus Christ is \uline{received} through \uline{faith}:

\begin{quote}
\textbf{John 1:12} - But \uline{to all who did receive (G2983 lambano) him, who believed (G4100 pisteuo) in his name,} he gave the right to become children of God, (ESV)
\end{quote}

\begin{verbatim}
 1  :  2983  lambano  lam-ban'-o
 2  
 3   a prolonged form of a primary verb, which is use only as an alternate
 4   in certain tenses; to take (in very many applications, literally and
 5   figuratively (properly objective or active, to get hold of; whereas
 6   1209 is rather subjective or passive, to have offered to one; while
 7   138 is more violent, to seize or remove)):--accept, + be amazed,
 8   assay, attain, bring, X when I call, catch, come on (X unto), +
 9   forget, have, hold, obtain, receive (X after), take (away, up).
10   see GREEK for 1209
11   see GREEK for 138
\end{verbatim}

Receiving is a mixture of believing, obeying, trusting, believing to receive - as Abraham's faith was. The faith to receive Jesus, getting to know Him I think is a span of time (it could be instantaneous to a lengthy period of time), I presume, as a person continues to trust Him:

\begin{quote}
\textbf{Romans 4:9-12} - Is this blessing then only for the circumcised, or also for the uncircumcised? We say that faith was counted to Abraham as righteousness. How then was it counted to him? Was it before or after he had been circumcised? It was not after, but before he was circumcised. He received the sign of circumcision as a seal of the righteousness that he had by faith while he was still uncircumcised. The purpose was to make him the father of all who believe without being circumcised, so that righteousness would be counted to them as well, and to make him the father of the circumcised who are \uline{not merely circumcised but who also walk in the footsteps of the faith that our father Abraham had before he was circumcised}.
\end{quote}

\begin{quote}
\textbf{Galatians 3:7} - Know then that it is those of faith who are the sons of Abraham.
\end{quote}

\begin{quote}
\textbf{Galatians 3:9} - So then, those who are of faith are blessed along with Abraham, the man of faith. (ESV)
\end{quote}

\begin{quote}
\textbf{Romans 8:19} - For the creation waits with eager longing for the revealing of the sons of God. (ESV)
\end{quote}

\begin{quote}
\textbf{Galatians 3:3-6} - Are you so foolish? Having begun by the Spirit, are you now being perfected by the flesh? \uline{Did you suffer so many things} in vain—if indeed it was in vain? Does he who supplies the Spirit to you and works miracles among you do so by works of the law, or by \uline{hearing with faith—} just as Abraham believed God, and it was counted to him as righteousness?
\end{quote}
\end{document}